### 2014-03-07 docs/related-work.tex
Skeleton of related work.

\documentclass{article}

\begin{document}

\section{Related work}

\cite{foci12-winter}

\bibliographystyle{plain}
\bibliography{related-work}

\end{document}

### 2014-03-07 docs/related-work.tex
Some related work and outline.

@@
 \documentclass{article}
+\usepackage{url}
 
@@
 
+% VPN arms race
+% We seek to build a system that remains difficult to block even after it has many users.
+
 \section{Related work}
 
+Broadly speaking, there are two main challenges to proxy-based circumvention.
+The first is obfuscation: making circumvention traffic difficult to distinguish
+from traffic the censor wishes to allow.
+The second is proxy address unblockability: making it difficult for
+the censor simply to block proxies by address.
+Past works have considered one or both of these problems.
+
+There are different approaches to obfuscation.
+One technique is to look unlike anything forbidden by the censor; that is, fail to match a blacklist.
+Another is to resemble a protocol that is explicitly allowed; that is, match a whitelist.
+Falling into the first category are ``look-like-nothing'' transports
+whose payloads are indistinguishable from a uniformly random byte stream.
+A examples of such a transport is obfsproxy~\cite{obfsproxy},
+long the go-to obfuscated transport used by Tor.
+ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the content of its payloads,
+but takes additional steps to obscure its signature of packet lengths and timing,
+and is designed to resist active scanning for proxies
+(the proxy server says nothing until the client proves knowledge of a shared secret).
+
+Another path to obfsucation is the steganographic approach:
+look like something the censor doesn't block.
+stegotorus
+freewave
+codetalker tunnel (skypemorph)
+fte
+dust
+
+Difficulties of look-like-something transports:
+the parrot is dead
+cover your acks
+
+Tor has long faced the problem of its entry relays being blocked.
+The list of relays is public, so it easy to block all of them by IP address.
+Tor bridges~\cite{tor-blocking} are relays that are not universally known,
+intended to serve as entry points for censored users.
+A system called BridgeDB seeks to provide a few bridges to anyone who asks,
+while at the same time making it difficult to learn the entire list of secret bridges.
+The plain Tor protocol remains relatively easy to detect,
+so BridgeDB is also capable of distributing obfsproxy and ScrambleSuit bridges.
+
+telex
+censorspoofer
+no direction home
+
+Flash proxy~\cite{flashproxy-pets12} attempts to address the problem of proxy diversity
+by conscripting web users as temporary proxies.
+Proxies last only as long as a web user stays on a page, so the pool of proxies is
+constantly changing and difficult to block.
+Their approach to proxy unblockability is in a sense opposite to this work's:
+where flash proxy uses many, cheap, unreliable proxies,
+we use just one high-value proxy, to block which would cause expensive collateral damage.
+There exists a prototype transport that combines flash proxy with obfsproxy~\cite{obfs-flash},
+however it is limited because it is not possible to obfuscate flash proxy's outermost WebSocket layer.
+
+A technique known as OSS~\cite{oss}, for ``online scanning systems,''
+closely resembles ours in important ways.
+It uses a third-party web service as a conduit to carry traffic,
+encoded either in a URL or in an HTTP body.
+Because web services cannot in general be assumed to reproduce a web server's
+response exactly
+(a translation service, for example, returns a response after translating it to another language),
+OSS does not use response bodies to carry data,
+instead requiring the relay to initiate a reflected request back to the client.
+OSS also does not claim that any one service is difficult to block, rather that there are many web services that can be used.
+The main ways in which this work differs is that we effectively control the OSS:
+we can count on response bodies being preserved and so use them to send downstream data;
+and we put the OSS on infrastructure that is expensive to block.
+
+How the GFW is blocking Tor.
 \cite{foci12-winter}
+
+GoAgent
+
+% CORDON? Say how meek would be classified in it?
 

### 2014-03-07 docs/related-work.tex
Fill some paragraphs and slightly changed the structure.

@@
 
-% VPN arms race
-% We seek to build a system that remains difficult to block even after it has many users.
+% VPN arms race We seek to build a system that remains difficult to block even
+% after it has many users.
 
@@
 
+In response to Internet censorship, many research papers and pragmatic systems
+such Freegate, Psiphon, and Lantern have explored the design space of censorship
+circumvention. All these schemes are based on a simple idea: deploy a set of
+proxies outside the censor's domain, and let the user connect to one of them
+which can pass data on to the true destination for the user.
+
 Broadly speaking, there are two main challenges to proxy-based circumvention.
 The first is obfuscation: making circumvention traffic difficult to distinguish
-from traffic the censor wishes to allow.
-The second is proxy address unblockability: making it difficult for
-the censor simply to block proxies by address.
-Past works have considered one or both of these problems.
+from traffic the censor wishes to allow. The second is proxy address
+unblockability: making it difficult for the censor simply to block proxies by
+address. Past works have considered one or both of these problems.
 
-There are different approaches to obfuscation.
-One technique is to look unlike anything forbidden by the censor; that is, fail to match a blacklist.
-Another is to resemble a protocol that is explicitly allowed; that is, match a whitelist.
-Falling into the first category are ``look-like-nothing'' transports
-whose payloads are indistinguishable from a uniformly random byte stream.
-A examples of such a transport is obfsproxy~\cite{obfsproxy},
-long the go-to obfuscated transport used by Tor.
-ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the content of its payloads,
-but takes additional steps to obscure its signature of packet lengths and timing,
-and is designed to resist active scanning for proxies
-(the proxy server says nothing until the client proves knowledge of a shared secret).
+To protect the relays from being detected and blocked, a school of research
+tries to use covert channels for the communication with relays. FreeWave~\cite{freewave}
+encodes data into audio streams and use the Skype P2P network to communicate
+with the proxy located outside the censored domain, which is essentially another
+Skype client that decodes the stream. The proxy then forward the traffic to the
+true destination. A technique known as OSS~\cite{oss}, for ``online scanning
+systems,'' closely resembles ours in important ways. It uses a third-party web
+service as a conduit to carry traffic, encoded either in a URL or in an HTTP
+body. Because web services cannot in general be assumed to reproduce a web
+server's response exactly (a translation service, for example, returns a
+response after translating it to another language), OSS does not use response
+bodies to carry data, instead requiring the relay to initiate a reflected
+request back to the client. OSS also does not claim that any one service is
+difficult to block, rather that there are many web services that can be used.
+The main ways in which this work differs is that we effectively control the OSS:
+we can count on response bodies being preserved and so use them to send
+downstream data; and we put the OSS on infrastructure that is expensive to
+block.
 
-Another path to obfsucation is the steganographic approach:
-look like something the censor doesn't block.
-stegotorus
-freewave
-codetalker tunnel (skypemorph)
-fte
-dust
+Traffic using covert channels may exhibit distinguishable characteristics. As
+noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
+distinguishable from what is regarded as harmless traffic. Therefore, another
+school of research focuses on obfuscation techniques for hiding protocol
+patterns. One technique is to look unlike anything forbidden by the censor; that
+is, fail to match a blacklist. Another is to resemble a protocol that is
+explicitly allowed; that is, match a whitelist. Falling into the first category
+are ``look-like-nothing'' transports whose payloads are indistinguishable from a
+uniformly random byte stream. A examples of such a transport is
+obfsproxy~\cite{obfsproxy}, long the go-to obfuscated transport used by Tor.
+ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the content of its
+payloads, but takes additional steps to obscure its signature of packet lengths
+and timing, and is designed to resist active scanning for proxies (the proxy
+server says nothing until the client proves knowledge of a shared secret).
+Another path to obfsucation is the steganographic approach: look like something
+the censor doesn't block. StegoTorus~\cite{stegotorus} and SkypeMorph~\cite{skypemorph} camouflage Tor
+traffic and attempt to mimic HTTP or Skype traffic.
 
-Difficulties of look-like-something transports:
-the parrot is dead
-cover your acks
+Houmansadr et al.~\cite{parrot} evaluate these steganography-based (parrot)
+systems and conclude that unobservability by imitation is a ``fundamentally
+flawed approach'', since these kind of systems must successfully mimic another
+protocol. To fully mimic a complex and sometimes proprietary protocol like Skype
+is difficult in that the system must mimic the protocol,  reaction to errors and
+network conditions, typical traffic, and implementation-specific artifacts
+correctly, otherwise a weak censor can recognize such traffic at a low cost.
+Therefore we avoid the parrot approach and use HTTPS as the channel. Geddes  et
+al.~\cite{acks} demonstrate that even non-parrot systems may be vulnerable to
+attacks that disrupt that covert communication while having no effect or less
+effect on legitimate traffic. Their examination is specific to VoIP protocols,
+where packet losses and duplication are acceptable. The censor then can
+deliberately drop or inject ACKs to disrupt the covert channel without causing
+much collateral damage.
 
-Tor has long faced the problem of its entry relays being blocked.
-The list of relays is public, so it easy to block all of them by IP address.
-Tor bridges~\cite{tor-blocking} are relays that are not universally known,
-intended to serve as entry points for censored users.
-A system called BridgeDB seeks to provide a few bridges to anyone who asks,
-while at the same time making it difficult to learn the entire list of secret bridges.
-The plain Tor protocol remains relatively easy to detect,
-so BridgeDB is also capable of distributing obfsproxy and ScrambleSuit bridges.
+Tor has long faced the problem of its entry relays being blocked. The list of
+relays is public, so it easy to block all of them by IP address. Tor
+bridges~\cite{tor-blocking} are relays that are not universally known, intended
+to serve as entry points for censored users. A system called BridgeDB seeks to
+provide a few bridges to anyone who asks, while at the same time making it
+difficult to learn the entire list of secret bridges. The plain Tor protocol
+remains relatively easy to detect, so BridgeDB is also capable of distributing
+obfsproxy and ScrambleSuit bridges.
 
-telex
-censorspoofer
-no direction home
+telex censorspoofer no direction home
 
-Flash proxy~\cite{flashproxy-pets12} attempts to address the problem of proxy diversity
-by conscripting web users as temporary proxies.
-Proxies last only as long as a web user stays on a page, so the pool of proxies is
-constantly changing and difficult to block.
-Their approach to proxy unblockability is in a sense opposite to this work's:
-where flash proxy uses many, cheap, unreliable proxies,
-we use just one high-value proxy, to block which would cause expensive collateral damage.
-There exists a prototype transport that combines flash proxy with obfsproxy~\cite{obfs-flash},
-however it is limited because it is not possible to obfuscate flash proxy's outermost WebSocket layer.
+Flash proxy~\cite{flashproxy-pets12} attempts to address the problem of proxy
+diversity by conscripting web users as temporary proxies. Proxies last only as
+long as a web user stays on a page, so the pool of proxies is constantly
+changing and difficult to block. Their approach to proxy unblockability is in a
+sense opposite to this work's: where flash proxy uses many, cheap, unreliable
+proxies, we use just one high-value proxy, to block which would cause expensive
+collateral damage. There exists a prototype transport that combines flash proxy
+with obfsproxy~\cite{obfs-flash}, however it is limited because it is not
+possible to obfuscate flash proxy's outermost WebSocket layer.
 
-A technique known as OSS~\cite{oss}, for ``online scanning systems,''
-closely resembles ours in important ways.
-It uses a third-party web service as a conduit to carry traffic,
-encoded either in a URL or in an HTTP body.
-Because web services cannot in general be assumed to reproduce a web server's
-response exactly
-(a translation service, for example, returns a response after translating it to another language),
-OSS does not use response bodies to carry data,
-instead requiring the relay to initiate a reflected request back to the client.
-OSS also does not claim that any one service is difficult to block, rather that there are many web services that can be used.
-The main ways in which this work differs is that we effectively control the OSS:
-we can count on response bodies being preserved and so use them to send downstream data;
-and we put the OSS on infrastructure that is expensive to block.
-
-How the GFW is blocking Tor.
-\cite{foci12-winter}
+How the GFW is blocking Tor. \cite{foci12-winter}
 
@@
 
-\bibliographystyle{plain}
-\bibliography{related-work}
+\bibliographystyle{plain} bibliography{related-work}
 

### 2014-03-07 docs/related-work.tex
Update bibliography.

@@
 proxies outside the censor's domain, and let the user connect to one of them
-which can pass data on to the true destination for the user.
+which can pass data on to the true destination for the user.\\
 
@@
 unblockability: making it difficult for the censor simply to block proxies by
-address. Past works have considered one or both of these problems.
+address. Past works have considered one or both of these problems.\\
 
@@
 downstream data; and we put the OSS on infrastructure that is expensive to
-block.
+block.\\
 
@@
 the censor doesn't block. StegoTorus~\cite{stegotorus} and SkypeMorph~\cite{skypemorph} camouflage Tor
-traffic and attempt to mimic HTTP or Skype traffic.
+traffic and attempt to mimic HTTP or Skype traffic.\\
 
@@
 deliberately drop or inject ACKs to disrupt the covert channel without causing
-much collateral damage.
+much collateral damage.\\
 
@@
 remains relatively easy to detect, so BridgeDB is also capable of distributing
-obfsproxy and ScrambleSuit bridges.
+obfsproxy and ScrambleSuit bridges.\\
 
-telex censorspoofer no direction home
+telex censorspoofer no direction home\\
 
@@
 with obfsproxy~\cite{obfs-flash}, however it is limited because it is not
-possible to obfuscate flash proxy's outermost WebSocket layer.
+possible to obfuscate flash proxy's outermost WebSocket layer.\\
 
-How the GFW is blocking Tor. \cite{foci12-winter}
+How the GFW is blocking Tor. \cite{foci12-winter}\\
 
-GoAgent
+GoAgent\\
 
@@
 
-\bibliographystyle{plain} bibliography{related-work}
+\bibliographystyle{plain} 
+\bibliography{related-work}
 

### 2014-03-07 docs/related-work.tex
Cites for decoy routing.
Online scanning service, not system.

@@
 true destination. A technique known as OSS~\cite{oss}, for ``online scanning
-systems,'' closely resembles ours in important ways. It uses a third-party web
+service,'' closely resembles ours in important ways. It uses a third-party web
 service as a conduit to carry traffic, encoded either in a URL or in an HTTP
@@
 
-telex censorspoofer no direction home\\
+telex~\cite{telex} censorspoofer~\cite{censorspoofer} no direction home~\cite{nodirectionhome}
+\\
 

### 2014-03-07 docs/related-work.tex
SkypeMorph is called Code Talker Tunnel now.
GoAgent paragraph.

@@
 Another path to obfsucation is the steganographic approach: look like something
-the censor doesn't block. StegoTorus~\cite{stegotorus} and SkypeMorph~\cite{skypemorph} camouflage Tor
+the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker Tunnel (formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor
 traffic and attempt to mimic HTTP or Skype traffic.\\
@@
 
-GoAgent\\
+GoAgent~\cite{goagent} is a direct inspiration for our work in its use of App Engine
+and Host header--based domain fronting.
+GoAgent requires users to upload a personal copy of the server code to App Engine,
+and App Engine itself makes HTTP requests, not some proxy farther out.
+According to a May 2013 survey~\cite{collateral-freedom},
+GoAgent was then the circumvention tool most used in China,
+with 35\% of survey respondants having used it in the previous month.
+This figure is higher than that of paid~(29\%) and free VPNs~(18\%),
+and far above that of other special-purpose tools like Tor~(2.9\%)
+and Psiphon~(2.5\%).
+\\
 

### 2014-03-07 docs/related-work.tex
Add Telex and No direction home.

@@
 
-telex~\cite{telex} censorspoofer~\cite{censorspoofer} no direction home~\cite{nodirectionhome}
-\\
+censorspoofer~\cite{censorspoofer} \\
 
-Flash proxy~\cite{flashproxy-pets12} attempts to address the problem of proxy
-diversity by conscripting web users as temporary proxies. Proxies last only as
-long as a web user stays on a page, so the pool of proxies is constantly
-changing and difficult to block. Their approach to proxy unblockability is in a
-sense opposite to this work's: where flash proxy uses many, cheap, unreliable
-proxies, we use just one high-value proxy, to block which would cause expensive
+There are a few approaches proposed to address the problem of proxy diversity.
+Flash proxy~\cite{flashproxy-pets12} attempts to address the problem  by
+conscripting web users as temporary proxies. Proxies last only as long as a web
+user stays on a page, so the pool of proxies is constantly changing and
+difficult to block. Their approach to proxy unblockability is in a sense
+opposite to this work's: where flash proxy uses many, cheap, unreliable proxies,
+we use just one high-value proxy, to block which would cause expensive
 collateral damage. There exists a prototype transport that combines flash proxy
 with obfsproxy~\cite{obfs-flash}, however it is limited because it is not
-possible to obfuscate flash proxy's outermost WebSocket layer.\\
+possible to obfuscate flash proxy's outermost WebSocket layer. Decoy routing is
+a recently proposed approach for proxy diversity. Telex~\cite{telex} is an
+instance of circumvention systems that leverages decoy routing. Telex relies on
+friendly ISPs that deploy Telex stations on paths between censors' networks and
+popular, uncensored Internet destinations. Telex stations would divert the
+seemingly  innocuous flows to a forbidden site if a special ``tag'' is
+presented. Telex will prevail only if a large number of ISPs are cooperative and
+willing to deploy such stations. A recent study~\cite{nodirectionhome} on ASes
+topology suggests that defeating decoy routing is likely to be expensive for the
+censors, if the decoy routers are strategically deployed. Despite that decoy
+routing is a sound technical approach, it is still questionable if ISPs are
+willing to act against state-level censors. However, the takeaway is that the
+censors are unwilling to completely block day-to-day Internet access, which we
+can take advantage of. \\
 

### 2014-03-07 docs/related-work.tex
Add CensorSpoofer

@@
-\documentclass{article} 
-\usepackage{url}
+\documentclass{article}  usepackage{url}
 
@@
 To protect the relays from being detected and blocked, a school of research
-tries to use covert channels for the communication with relays. FreeWave~\cite{freewave}
-encodes data into audio streams and use the Skype P2P network to communicate
-with the proxy located outside the censored domain, which is essentially another
-Skype client that decodes the stream. The proxy then forward the traffic to the
-true destination. A technique known as OSS~\cite{oss}, for ``online scanning
-service,'' closely resembles ours in important ways. It uses a third-party web
-service as a conduit to carry traffic, encoded either in a URL or in an HTTP
-body. Because web services cannot in general be assumed to reproduce a web
-server's response exactly (a translation service, for example, returns a
-response after translating it to another language), OSS does not use response
-bodies to carry data, instead requiring the relay to initiate a reflected
-request back to the client. OSS also does not claim that any one service is
-difficult to block, rather that there are many web services that can be used.
-The main ways in which this work differs is that we effectively control the OSS:
-we can count on response bodies being preserved and so use them to send
+tries to use covert channels for the communication with relays.
+FreeWave~\cite{freewave} encodes data into audio streams and use the Skype P2P
+network to communicate with the proxy located outside the censored domain, which
+is essentially another Skype client that decodes the stream. The proxy then
+forward the traffic to the true destination. CensorSpoofer~\cite{censorspoofer}
+decouples the upstream and downstream channel. It assumes the existence of a
+low-bandwidth indirect channel that is immune from censorship. It uses this
+channel for send requests (URLs) to the proxy while sending dummy requests to a
+dummy host. The proxy then fetches the web content and spoofs the dummy host's
+IP address to deliver the content back. A technique known as OSS~\cite{oss}, for
+``online scanning service,'' closely resembles ours in important ways. It uses a
+third-party web service as a conduit to carry traffic, encoded either in a URL
+or in an HTTP body. Because web services cannot in general be assumed to
+reproduce a web server's response exactly (a translation service, for example,
+returns a response after translating it to another language), OSS does not use
+response bodies to carry data, instead requiring the relay to initiate a
+reflected request back to the client. OSS also does not claim that any one
+service is difficult to block, rather that there are many web services that can
+be used. The main ways in which this work differs is that we effectively control
+the OSS: we can count on response bodies being preserved and so use them to send
 downstream data; and we put the OSS on infrastructure that is expensive to
@@
 Another path to obfsucation is the steganographic approach: look like something
-the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker Tunnel (formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor
-traffic and attempt to mimic HTTP or Skype traffic.\\
+the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker Tunnel
+(formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor traffic and
+attempt to mimic HTTP or Skype traffic. CensorSpoofer also mimics SIP-based VoIP
+to hide the upstream channel.\\
 
@@
 obfsproxy and ScrambleSuit bridges.\\
-
-censorspoofer~\cite{censorspoofer} \\
 
@@
 
-GoAgent~\cite{goagent} is a direct inspiration for our work in its use of App Engine
-and Host header--based domain fronting.
-GoAgent requires users to upload a personal copy of the server code to App Engine,
-and App Engine itself makes HTTP requests, not some proxy farther out.
-According to a May 2013 survey~\cite{collateral-freedom},
-GoAgent was then the circumvention tool most used in China,
-with 35\% of survey respondants having used it in the previous month.
-This figure is higher than that of paid~(29\%) and free VPNs~(18\%),
-and far above that of other special-purpose tools like Tor~(2.9\%)
-and Psiphon~(2.5\%).
+GoAgent~\cite{goagent} is a direct inspiration for our work in its use of App
+Engine and Host header--based domain fronting. GoAgent requires users to upload
+a personal copy of the server code to App Engine, and App Engine itself makes
+HTTP requests, not some proxy farther out. According to a May 2013 survey~\cite
+{collateral-freedom}, GoAgent was then the circumvention tool most used in
+China, with 35\% of survey respondants having used it in the previous month.
+This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
+above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
 \\
@@
 
-\bibliographystyle{plain} 
-\bibliography{related-work}
+\bibliographystyle{plain}  bibliography{related-work}
 

### 2014-03-07 docs/related-work.tex
Add how GFW blocks Tor.

@@
 noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
-distinguishable from what is regarded as harmless traffic. Therefore, another
-school of research focuses on obfuscation techniques for hiding protocol
-patterns. One technique is to look unlike anything forbidden by the censor; that
-is, fail to match a blacklist. Another is to resemble a protocol that is
-explicitly allowed; that is, match a whitelist. Falling into the first category
-are ``look-like-nothing'' transports whose payloads are indistinguishable from a
-uniformly random byte stream. A examples of such a transport is
-obfsproxy~\cite{obfsproxy}, long the go-to obfuscated transport used by Tor.
-ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the content of its
-payloads, but takes additional steps to obscure its signature of packet lengths
-and timing, and is designed to resist active scanning for proxies (the proxy
-server says nothing until the client proves knowledge of a shared secret).
-Another path to obfsucation is the steganographic approach: look like something
-the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker Tunnel
-(formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor traffic and
+distinguishable from what is regarded as harmless traffic. In addition, their
+experiments show that the Great Firewall of China actively scans for Tor bridges
+and block them. Therefore, another school of research focuses on obfuscation
+techniques for hiding protocol patterns. One technique is to look unlike
+anything forbidden by the censor; that is, fail to match a blacklist. Another is
+to resemble a protocol that is explicitly allowed; that is, match a whitelist.
+Falling into the first category are ``look-like-nothing'' transports whose
+payloads are indistinguishable from a uniformly random byte stream. A examples
+of such a transport is obfsproxy~\cite{obfsproxy}, long the go-to obfuscated
+transport used by Tor. ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the
+content of its payloads, but takes additional steps to obscure its signature of
+packet lengths and timing, and is designed to resist active scanning for proxies
+(the proxy server says nothing until the client proves knowledge of a shared
+secret). Another path to obfsucation is the steganographic approach: look like
+something the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker
+Tunnel (formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor traffic and
 attempt to mimic HTTP or Skype traffic. CensorSpoofer also mimics SIP-based VoIP
@@
 
-How the GFW is blocking Tor. \cite{foci12-winter}\\
-
 GoAgent~\cite{goagent} is a direct inspiration for our work in its use of App
@@
 {collateral-freedom},  GoAgent was then the circumvention tool most used in
-China, with 35\% of survey respondants having used it in the previous month.
+China, with 35\% of survey respondents having used it in the previous month.
 This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far

### 2014-03-07 docs/related-work.tex
Fix file format
Winter paper.

@@
-\documentclass{article}  usepackage{url}
+\documentclass{article}  
+\usepackage{url}
 
@@
 censors are unwilling to completely block day-to-day Internet access, which we
-can take advantage of. \\
+can take advantage of.\\
 
@@
 
+Winter and Lindskog~\cite{foci12-winter} investigated how China's Great Firewall blocks Tor.
+They confirmed an earlier discovery of Wilde~\cite{wilde} that the firewall identifies Tor relays using more than passive monitoring:
+it actively probes destination addresses to see if they speak the Tor protocol, and if so,
+blocks them for the future.
+(At the time, the firewall identified connections for future probing by looking for a distinctive
+list of ciphersuites sent by a Tor client in its TLS client hello.) %\cite{bug4744}
+The discovery of active probing was the motivation for probing resistance in ScrambleSuit.
+\\
+
 % CORDON? Say how meek would be classified in it?
 
-\bibliographystyle{plain}  bibliography{related-work}
+\bibliographystyle{plain}  
+\bibliography{related-work}
 

### 2014-03-07 docs/related-work.tex
Typo.
Remove redundant description of active probing.

@@
 low-bandwidth indirect channel that is immune from censorship. It uses this
-channel for send requests (URLs) to the proxy while sending dummy requests to a
+channel for sending requests (URLs) to the proxy while sending dummy requests to a
 dummy host. The proxy then fetches the web content and spoofs the dummy host's
@@
 noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
-distinguishable from what is regarded as harmless traffic. In addition, their
-experiments show that the Great Firewall of China actively scans for Tor bridges
-and block them. Therefore, another school of research focuses on obfuscation
+distinguishable from what is regarded as harmless traffic. Therefore, another school of research focuses on obfuscation
 techniques for hiding protocol patterns. One technique is to look unlike

### 2014-03-07 docs/related-work.tex
Nonbreaking space in "et al.".

@@
 Traffic using covert channels may exhibit distinguishable characteristics. As
-noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
+noted by Winter et~al.~\cite{foci12-winter}, Tor traffic is currently
 distinguishable from what is regarded as harmless traffic. Therefore, another school of research focuses on obfuscation
@@
 (the proxy server says nothing until the client proves knowledge of a shared
-secret). Another path to obfsucation is the steganographic approach: look like
+secret). Another path to obfuscation is the steganographic approach: look like
 something the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker
@@
 
-Houmansadr et al.~\cite{parrot} evaluate these steganography-based (parrot)
+Houmansadr et~al.~\cite{parrot} evaluate these steganography-based (parrot)
 systems and conclude that unobservability by imitation is a ``fundamentally
@@
 correctly, otherwise a weak censor can recognize such traffic at a low cost.
-Therefore we avoid the parrot approach and use HTTPS as the channel. Geddes et
-al.~\cite{acks} demonstrate that even non-parrot systems may be vulnerable to
+Therefore we avoid the parrot approach and use HTTPS as the channel. Geddes et~al.~\cite{acks}
+demonstrate that even non-parrot systems may be vulnerable to
 attacks that disrupt that covert communication while having no effect or less

### 2014-03-08 docs/related-work.tex
Use \parskip instead of explicit \\ breaks.

@@
 \usepackage{url}
+
+\setlength{\parskip}{\baselineskip}
 
@@
 proxies outside the censor's domain, and let the user connect to one of them
-which can pass data on to the true destination for the user.\\
+which can pass data on to the true destination for the user.
 
@@
 unblockability: making it difficult for the censor simply to block proxies by
-address. Past works have considered one or both of these problems.\\
+address. Past works have considered one or both of these problems.
 
@@
 downstream data; and we put the OSS on infrastructure that is expensive to
-block.\\
+block.
 
@@
 attempt to mimic HTTP or Skype traffic. CensorSpoofer also mimics SIP-based VoIP
-to hide the upstream channel.\\
+to hide the upstream channel.
 
@@
 deliberately drop or inject ACKs to disrupt the covert channel without causing
-much collateral damage.\\
+much collateral damage.
 
@@
 remains relatively easy to detect, so BridgeDB is also capable of distributing
-obfsproxy and ScrambleSuit bridges.\\
+obfsproxy and ScrambleSuit bridges.
 
@@
 censors are unwilling to completely block day-to-day Internet access, which we
-can take advantage of.\\
+can take advantage of.
 
@@
 above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
-\\
 
@@
 The discovery of active probing was the motivation for probing resistance in ScrambleSuit.
-\\
 

### 2014-03-08 docs/related-work.tex
Note on similarity with Telex.

@@
 
+Of the decoy routing systems, Telex is the most similar to ours.
+Both use a piece of network infrastructure as a decoy to redirect certain flows
+(for Telex it is an ISP router; for us it is the Google frontend server),
+and both tag flows in a way that is visible only to the decoy
+(for Telex a tag is a hash embedded in the TLS client randomness; for us it is the HTTP Host header).
+
 GoAgent~\cite{goagent} is a direct inspiration for our work in its use of App

### 2014-03-08 docs/related-work.tex
Reunite a split escape sequence.

@@
 a personal copy of the server code to App Engine, and App Engine itself makes
-HTTP requests, not some proxy farther out. According to a May 2013 survey~\cite
-{collateral-freedom},  GoAgent was then the circumvention tool most used in
+HTTP requests, not some proxy farther out. According to a May 2013 survey~\cite{collateral-freedom},
+GoAgent was then the circumvention tool most used in
 China, with 35\% of survey respondents having used it in the previous month.

### 2014-03-08 docs/related-work.tex
Proofreading and rearranging.

@@
 
-To protect the relays from being detected and blocked, a school of research
-tries to use covert channels for the communication with relays.
-FreeWave~\cite{freewave} encodes data into audio streams and use the Skype P2P
-network to communicate with the proxy located outside the censored domain, which
-is essentially another Skype client that decodes the stream. The proxy then
-forward the traffic to the true destination. CensorSpoofer~\cite{censorspoofer}
-decouples the upstream and downstream channel. It assumes the existence of a
-low-bandwidth indirect channel that is immune from censorship. It uses this
-channel for sending requests (URLs) to the proxy while sending dummy requests to a
-dummy host. The proxy then fetches the web content and spoofs the dummy host's
-IP address to deliver the content back. A technique known as OSS~\cite{oss}, for
-``online scanning service,'' closely resembles ours in important ways. It uses a
-third-party web service as a conduit to carry traffic, encoded either in a URL
-or in an HTTP body. Because web services cannot in general be assumed to
-reproduce a web server's response exactly (a translation service, for example,
-returns a response after translating it to another language), OSS does not use
-response bodies to carry data, instead requiring the relay to initiate a
-reflected request back to the client. OSS also does not claim that any one
-service is difficult to block, rather that there are many web services that can
-be used. The main ways in which this work differs is that we effectively control
-the OSS: we can count on response bodies being preserved and so use them to send
-downstream data; and we put the OSS on infrastructure that is expensive to
-block.
-
-Traffic using covert channels may exhibit distinguishable characteristics. As
-noted by Winter et~al.~\cite{foci12-winter}, Tor traffic is currently
-distinguishable from what is regarded as harmless traffic. Therefore, another school of research focuses on obfuscation
-techniques for hiding protocol patterns. One technique is to look unlike
-anything forbidden by the censor; that is, fail to match a blacklist. Another is
+The problem of traffic obfuscation has been approached in many different ways.
+They may be classified into two general techniques.
+The first is to look unlike
+anything forbidden by the censor; that is, fail to match a blacklist. The second is
 to resemble a protocol that is explicitly allowed; that is, match a whitelist.
@@
 (the proxy server says nothing until the client proves knowledge of a shared
-secret). Another path to obfuscation is the steganographic approach: look like
-something the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker
-Tunnel (formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor traffic and
-attempt to mimic HTTP or Skype traffic. CensorSpoofer also mimics SIP-based VoIP
-to hide the upstream channel.
+secret).
 
-Houmansadr et~al.~\cite{parrot} evaluate these steganography-based (parrot)
-systems and conclude that unobservability by imitation is a ``fundamentally
-flawed approach'', since these kind of systems must successfully mimic another
-protocol. To fully mimic a complex and sometimes proprietary protocol like Skype
-is difficult in that the system must mimic the protocol,  reaction to errors and
-network conditions, typical traffic, and implementation-specific artifacts
-correctly, otherwise a weak censor can recognize such traffic at a low cost.
+Another path to obfuscation is the steganographic approach: look like
+something the censor doesn't block. StegoTorus~\cite{stegotorus}
+encodes traffic so as to look like a cover protocol, such as unencrypted HTTP,
+using special-purpose encoders.
+Code Talker
+Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
+FreeWave~\cite{freewave} encodes a digital stream into an acoustic signal
+and sends it over VoIP to a proxy which decodes and forwards it.
+
+% fte
+
+Houmansadr et~al.~\cite{parrot} evaluate ``parrot'' systems that imitate a particular implementation of a protocol
+and conclude that unobservability by imitation is a ``fundamentally
+flawed approach.''
+To fully mimic a complex and sometimes proprietary protocol like Skype
+is difficult in that the system must mimic not only the protocol operating normally, but also its reaction to errors,
+typical traffic patterns, and quirks of its implementation,
+otherwise a weak censor can recognize such traffic at a low cost.
 Therefore we avoid the parrot approach and use HTTPS as the channel. Geddes et~al.~\cite{acks}
@@
 
+There are a few approaches proposed to address the problem of proxy address unblockability.
 Tor has long faced the problem of its entry relays being blocked. The list of
@@
 
-There are a few approaches proposed to address the problem of proxy diversity.
-Flash proxy~\cite{flashproxy-pets12} attempts to address the problem  by
+Flash proxy~\cite{flashproxy} attempts to address the problem  by
 conscripting web users as temporary proxies. Proxies last only as long as a web
@@
 with obfsproxy~\cite{obfs-flash}, however it is limited because it is not
-possible to obfuscate flash proxy's outermost WebSocket layer. Decoy routing is
-a recently proposed approach for proxy diversity. Telex~\cite{telex} is an
-instance of circumvention systems that leverages decoy routing. Telex relies on
-friendly ISPs that deploy Telex stations on paths between censors' networks and
-popular, uncensored Internet destinations. Telex stations would divert the
-seemingly  innocuous flows to a forbidden site if a special ``tag'' is
-presented. Telex will prevail only if a large number of ISPs are cooperative and
-willing to deploy such stations. A recent study~\cite{nodirectionhome} on ASes
+possible to obfuscate flash proxy's outermost WebSocket layer.
+
+A technique known as OSS~\cite{oss}, for
+``online scanning service,'' resembles ours in certain ways. OSS bounces data
+through third-party web services that are capable of making HTTP requests.
+Even though such services are capable of fetching a web page, they do not in general
+preserve the contents of the page when it is returned to the requestor.
+(A translation service, for example,
+returns a response after translating it to another language.)
+For this reason, OSS does not rely on sending downstream data in HTTP response bodies,
+but rather requires the server to make a symmetric reflected HTTP request back to the client.
+The main ways in which this work differs is that we are effectively using an OSS that we fully control:
+we can count on response bodies being preserved (and so use them to carry
+downstream data);
+and we make the OSS hard to block by hosting it on an important network resource.
+
+Decoy routing is
+a recently proposed approach to making proxies hard to block. Telex~\cite{telex}
+relies on friendly ISPs that deploy special software on routers between censors' networks and
+popular, uncensored Internet destinations.
+Circumvention software is marked with a special ``tag'' that is distinguishable from random only
+by Telex routers (not by the censor).
+On receiving such a tagged communication, the Telex router shunts it away from its apparent destination.
+CensorSpoofer~\cite{censorspoofer}
+decouples the upstream and downstream channels. A CensorSpoofer proxy protects its address by
+spoofing the source IP address of all packets it sends to the client.
+In addition to spoofing, the CensorSpoofer authors propose a SIP-based steganographic channel for downstream data.
+Upstream data are carried over a low-bandwidth covert channel such as email.
+A recent study~\cite{nodirectionhome} on AS
 topology suggests that defeating decoy routing is likely to be expensive for the
@@
 can take advantage of.
-
 Of the decoy routing systems, Telex is the most similar to ours.
@@
 (for Telex a tag is a hash embedded in the TLS client randomness; for us it is the HTTP Host header).
+
+% Routing around decoys
+% Cirripede
+
+Winter and Lindskog~\cite{foci12-winter} investigated how China's Great Firewall blocks Tor.
+They confirmed an earlier discovery of Wilde~\cite{wilde} that the firewall identifies Tor relays using more than passive monitoring:
+it actively probes destination addresses to see if they speak the Tor protocol, and if so,
+blocks them for the future.
+(At the time, the firewall identified connections for future probing by looking for a distinctive
+list of ciphersuites sent by a Tor client in its TLS client hello.) %\cite{bug4744}
+The discovery of active probing was the motivation for probing resistance in ScrambleSuit.
 
@@
 
-Winter and Lindskog~\cite{foci12-winter} investigated how China's Great Firewall blocks Tor.
-They confirmed an earlier discovery of Wilde~\cite{wilde} that the firewall identifies Tor relays using more than passive monitoring:
-it actively probes destination addresses to see if they speak the Tor protocol, and if so,
-blocks them for the future.
-(At the time, the firewall identified connections for future probing by looking for a distinctive
-list of ciphersuites sent by a Tor client in its TLS client hello.) %\cite{bug4744}
-The discovery of active probing was the motivation for probing resistance in ScrambleSuit.
-
 % CORDON? Say how meek would be classified in it?

### 2014-03-08 docs/related-work.tex
Something about FTE.
I think this paragraph is too similar to the introduction of CensorSpoofer.

@@
 
-In response to Internet censorship, many research papers and pragmatic systems
-such Freegate, Psiphon, and Lantern have explored the design space of censorship
-circumvention. All these schemes are based on a simple idea: deploy a set of
-proxies outside the censor's domain, and let the user connect to one of them
-which can pass data on to the true destination for the user.
+% In response to Internet censorship, many research papers and pragmatic systems
+% such Freegate, Psiphon, and Lantern have explored the design space of censorship
+% circumvention. All these schemes are based on a simple idea: deploy a set of
+% proxies outside the censor's domain, and let the user connect to one of them
+% which can pass data on to the true destination for the user.
 
@@
 and sends it over VoIP to a proxy which decodes and forwards it.
-
-% fte
+Format-transforming encryption~\cite{fte} encodes data into strings matching a given regular expression,
+enabling it to match a firewall's whitelist or avoid matching its blacklist.
 

### 2014-03-08 docs/related-work.tex
Proofreading.

@@
 
-The problem of traffic obfuscation has been approached in many different ways.
-They may be classified into two general techniques.
-The first is to look unlike
+Traffic obfuscation has been approached in many different ways,
+which may be classified into two general techniques.
+The first technique is to look unlike
 anything forbidden by the censor; that is, fail to match a blacklist. The second is
-to resemble a protocol that is explicitly allowed; that is, match a whitelist.
+to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
 Falling into the first category are ``look-like-nothing'' transports whose
-payloads are indistinguishable from a uniformly random byte stream. A examples
-of such a transport is obfsproxy~\cite{obfsproxy}, long the go-to obfuscated
+payloads are indistinguishable from a uniformly random byte stream.
+The classic example of a look-like-nothing
+protocol is obfsproxy~\cite{obfsproxy}, long the go-to obfuscated
 transport used by Tor. ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the
-content of its payloads, but takes additional steps to obscure its signature of
-packet lengths and timing, and is designed to resist active scanning for proxies
-(the proxy server says nothing until the client proves knowledge of a shared
+content of its payloads, but it takes additional steps to obscure its traffic signature
+(packet lengths and timing), and is designed to resist active scanning for proxies
+(the proxy server remains silent until the client proves knowledge of a shared
 secret).
 
-Another path to obfuscation is the steganographic approach: look like
+The other category of obfuscation contains transports that take the the steganographic approach: look like
 something the censor doesn't block. StegoTorus~\cite{stegotorus}
@@
 FreeWave~\cite{freewave} encodes a digital stream into an acoustic signal
-and sends it over VoIP to a proxy which decodes and forwards it.
-Format-transforming encryption~\cite{fte} encodes data into strings matching a given regular expression,
-enabling it to match a firewall's whitelist or avoid matching its blacklist.
+and sends it over VoIP to a proxy which decodes and forwards it to the destination.
+Format-transforming encryption~\cite{fte} encodes data into strings that a given regular expression,
+in order to match a firewall's whitelist or avoid matching its blacklist.
 
@@
 To fully mimic a complex and sometimes proprietary protocol like Skype
-is difficult in that the system must mimic not only the protocol operating normally, but also its reaction to errors,
-typical traffic patterns, and quirks of its implementation,
-otherwise a weak censor can recognize such traffic at a low cost.
-Therefore we avoid the parrot approach and use HTTPS as the channel. Geddes et~al.~\cite{acks}
+is difficult in that the system must imitate not only the protocol's normal operation, but also its reaction to errors,
+its typical traffic patterns, and quirks of common implementations.
+Geddes et~al.~\cite{acks}
 demonstrate that even non-parrot systems may be vulnerable to
-attacks that disrupt that covert communication while having no effect or less
-effect on legitimate traffic. Their examination is specific to VoIP protocols,
-where packet losses and duplication are acceptable. The censor then can
-deliberately drop or inject ACKs to disrupt the covert channel without causing
+attacks that disrupt covert communication while having little effect
+on legitimate traffic. Their examination is specific to VoIP protocols,
+where packet losses and duplication are acceptable. The censor may
+deliberately drop or inject ACKs in order to disrupt the covert channel, without causing
 much collateral damage.
 
-There are a few approaches proposed to address the problem of proxy address unblockability.
+The other grand challenge of proxy-based circumvention is proxy address unblockability,
+for which there have been a few approaches proposed.
 Tor has long faced the problem of its entry relays being blocked. The list of
@@
 bridges~\cite{tor-blocking} are relays that are not universally known, intended
-to serve as entry points for censored users. A system called BridgeDB seeks to
-provide a few bridges to anyone who asks, while at the same time making it
-difficult to learn the entire list of secret bridges. The plain Tor protocol
-remains relatively easy to detect, so BridgeDB is also capable of distributing
-obfsproxy and ScrambleSuit bridges.
+to serve as entry points for censored users. A bridge database (BridgeDB) seeks to
+provide a few secret bridges to anyone who asks, while at the same time making it
+difficult to learn the entire list. BridgeDB is capable of distributing
+the addresses of obfsproxy and ScrambleSuit bridges, and the combination
+of selective bridge distribution and traffic obfuscation has had some success as comprehensive circumvention.
+It remains the case that there are simply not enough bridges to keep them all secret for long against a resourceful adversary.
 
@@
 user stays on a page, so the pool of proxies is constantly changing and
-difficult to block. Their approach to proxy unblockability is in a sense
-opposite to this work's: where flash proxy uses many, cheap, unreliable proxies,
-we use just one high-value proxy, to block which would cause expensive
-collateral damage. There exists a prototype transport that combines flash proxy
+difficult to block.
+Flash proxy's approach to proxy unblockability is in a sense
+the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
+we use just one high-value proxy, which shares its fate with network
+infrastructure that is expensive to block.
+There exists a prototype transport that attempts to get both
+obfuscation and address unblockability by combining flash proxy
 with obfsproxy~\cite{obfs-flash}, however it is limited because it is not
@@
 
-A technique known as OSS~\cite{oss}, for
-``online scanning service,'' resembles ours in certain ways. OSS bounces data
+% Lantern
+% Psiphon
+
+A technique known as OSS~\cite{oss} (for
+``online scanning service'') resembles ours in certain ways. OSS bounces data
 through third-party web services that are capable of making HTTP requests.
-Even though such services are capable of fetching a web page, they do not in general
+Even though such services can fetch a web page, they do not in general
 preserve the contents of the page when it is returned to the requestor.
 (A translation service, for example,
-returns a response after translating it to another language.)
-For this reason, OSS does not rely on sending downstream data in HTTP response bodies,
+returns the page after translating it to another language.)
+For this reason, OSS does not rely on being able to send downstream data in HTTP response bodies,
 but rather requires the server to make a symmetric reflected HTTP request back to the client.
 The main ways in which this work differs is that we are effectively using an OSS that we fully control:
-we can count on response bodies being preserved (and so use them to carry
-downstream data);
+we can ensure that reflected HTTP traffic is unmodified;
 and we make the OSS hard to block by hosting it on an important network resource.
@@
 Decoy routing is
-a recently proposed approach to making proxies hard to block. Telex~\cite{telex}
-relies on friendly ISPs that deploy special software on routers between censors' networks and
+a recently proposed anti-blocking approach. Telex~\cite{telex}
+asks friendly ISPs to deploy special software on routers between censored users and
 popular, uncensored Internet destinations.
-Circumvention software is marked with a special ``tag'' that is distinguishable from random only
+Circumvention traffic is marked with a special ``tag'' that is distinguishable from random only
 by Telex routers (not by the censor).
-On receiving such a tagged communication, the Telex router shunts it away from its apparent destination.
+On receiving such a tagged communication, the Telex router shunts it away from its apparent destination
+and toward the censored destination requested by the client.
 CensorSpoofer~\cite{censorspoofer}
-decouples the upstream and downstream channels. A CensorSpoofer proxy protects its address by
-spoofing the source IP address of all packets it sends to the client.
-In addition to spoofing, the CensorSpoofer authors propose a SIP-based steganographic channel for downstream data.
+decouples the upstream and downstream channels.
 Upstream data are carried over a low-bandwidth covert channel such as email.
+The CensorSpoofer proxy protects its address by
+spoofing the source IP address of all downstream data sent back to the client.
+In addition to spoofing, the CensorSpoofer authors propose a obfuscating the downstream with a SIP-based steganographic channel.
 A recent study~\cite{nodirectionhome} on AS
@@
 censors, if the decoy routers are strategically deployed. Despite that decoy
-routing is a sound technical approach, it is still questionable if ISPs are
+routing is a sound technical approach, it is still questionable whether ISPs are
 willing to act against state-level censors. However, the takeaway is that the
@@
 can take advantage of.
-Of the decoy routing systems, Telex is the most similar to ours.
-Both use a piece of network infrastructure as a decoy to redirect certain flows
+Of the decoy routing systems, Telex is the most similar to our work.
+Both systems use a piece of network infrastructure as a decoy to redirect certain flows
 (for Telex it is an ISP router; for us it is the Google frontend server),
-and both tag flows in a way that is visible only to the decoy
+and both tag flows in a way that is visible only to the decoy router
 (for Telex a tag is a hash embedded in the TLS client randomness; for us it is the HTTP Host header).
@@
 (At the time, the firewall identified connections for future probing by looking for a distinctive
-list of ciphersuites sent by a Tor client in its TLS client hello.) %\cite{bug4744}
-The discovery of active probing was the motivation for probing resistance in ScrambleSuit.
+list of ciphersuites sent by a Tor client in its TLS client hello---a failure of obfuscation.) %\cite{bug4744}
+The discovery of Chinese active probing was the motivation for probing resistance in ScrambleSuit
+and in our work.
 
-GoAgent~\cite{goagent} is a direct inspiration for our work in its use of App
+GoAgent~\cite{goagent} is a direct inspiration for our system in its use of App
 Engine and Host header--based domain fronting. GoAgent requires users to upload
-a personal copy of the server code to App Engine, and App Engine itself makes
-HTTP requests, not some proxy farther out. According to a May 2013 survey~\cite{collateral-freedom},
+a personal copy of the server code to App Engine, and works only with HTTP and HTTPS,
+not other TCP-based protocols.
+According to a May 2013 survey~\cite{collateral-freedom},
 GoAgent was then the circumvention tool most used in
@@
 above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
+Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.
 

### 2014-03-09 docs/paper.tex
Add paper.tex as a copy of related-work.tex.

--- 2014-03-08 docs/related-work.tex
@@
 
-The other category of obfuscation contains transports that take the the steganographic approach: look like
+The other category of obfuscation contains transports that take the steganographic approach: look like
 something the censor doesn't block. StegoTorus~\cite{stegotorus}
-encodes traffic so as to look like a cover protocol, such as unencrypted HTTP,
+encodes traffic to look like a cover protocol, such as unencrypted HTTP,
 using special-purpose encoders.
@@
 and sends it over VoIP to a proxy which decodes and forwards it to the destination.
-Format-transforming encryption~\cite{fte} encodes data into strings that a given regular expression,
-in order to match a firewall's whitelist or avoid matching its blacklist.
+Format-transforming encryption~\cite{fte} encodes data into strings that match a given regular expression,
+in order to match a firewall's whitelist or avoid matching a blacklist.
 
@@
 on legitimate traffic. Their examination is specific to VoIP protocols,
-where packet losses and duplication are acceptable. The censor may
+where packet loss and duplication are acceptable. The censor may
 deliberately drop or inject ACKs in order to disrupt the covert channel, without causing
@@
 bridges~\cite{tor-blocking} are relays that are not universally known, intended
-to serve as entry points for censored users. A bridge database (BridgeDB) seeks to
+to serve as entry points for censored users. A database of bridges (BridgeDB) seeks to
 provide a few secret bridges to anyone who asks, while at the same time making it
@@
 the addresses of obfsproxy and ScrambleSuit bridges, and the combination
-of selective bridge distribution and traffic obfuscation has had some success as comprehensive circumvention.
+of selective bridge distribution and traffic obfuscation has had some success as a comprehensive circumvention solution.
 It remains the case that there are simply not enough bridges to keep them all secret for long against a resourceful adversary.
@@
 difficult to block.
-Flash proxy's approach to proxy unblockability is in a sense
+Flash proxy's approach to unblockability is in a sense
 the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
@@
 popular, uncensored Internet destinations.
-Circumvention traffic is marked with a special ``tag'' that is distinguishable from random only
+Circumvention traffic is marked with a special ``tag'' that is distinguishable from a random string only
 by Telex routers (not by the censor).
@@
 spoofing the source IP address of all downstream data sent back to the client.
-In addition to spoofing, the CensorSpoofer authors propose a obfuscating the downstream with a SIP-based steganographic channel.
+In addition to spoofing, the CensorSpoofer authors propose to obfuscate the downstream with a SIP-based steganographic channel.
 A recent study~\cite{nodirectionhome} on AS
@@
 blocks them for the future.
-(At the time, the firewall identified connections for future probing by looking for a distinctive
-list of ciphersuites sent by a Tor client in its TLS client hello---a failure of obfuscation.) %\cite{bug4744}
+(At the time, the firewall identified potential Tor connections for future probing by looking for a distinctive
+list of TLS ciphersuites---a failure of obfuscation.) %\cite{bug4744}
 The discovery of Chinese active probing was the motivation for probing resistance in ScrambleSuit
@@
 According to a May 2013 survey~\cite{collateral-freedom},
-GoAgent was then the circumvention tool most used in
+GoAgent was the circumvention tool most used in
 China, with 35\% of survey respondents having used it in the previous month.

### 2014-03-09 docs/paper.tex
Some notes on CloudFlare.

@@
 
+\section{Other third-party services}
+
+A censor can block meek by blocking access to Google entirely.
+To take such a step is extreme, because of its high collateral damage,
+but it is not outside the realm of possibility.
+% Cite when Google and Gmail were completely blocked temporarily.
+We investigated how easily our system can be adapted to hard-to-block systems other than Google,
+and found that CloudFlare, a content delivery network, in principle supports domain fronting.
+
+CloudFlare provides the frontend of $X$ web sites, $Y$ of them supporting HTTPS~\cite{something}.
+CloudFlare supports the domain fronting trick;
+that is, it is possible that a request has one domain in the TLS layer
+and another in the HTTP layer, and the CloudFlare server will transparently redirect it to proper place.
+While we verified that domain fronting would work on CloudFlare,
+we did not test deployment,
+because when we asked we were told that our planned use would be against CloudFlare's terms of service.
+CloudFlare hosts a number of HTTPS sites.
+Choosing just one of them to be the front in TLS connections could cause
+the innocent third-party domain to be censored even though it is not itself carrying any circumvention traffic.
+To avoid this problem, the front can be simply a CloudFlare IP address,
+with no SNI at all.
+The censor then faces the choice of allowing circumvention traffic,
+or else blocking a large number of popular unrelated web sites.
+
+We were not able to make the system work with Amazon CloudFront nor Akamai.
+
 \bibliographystyle{plain}  

### 2014-03-10 docs/paper.tex
Note of some stuff to write about.
meek-server 0.2 suports HTTPS. But using HTTPS increases latency a lot.
https://people.torproject.org/~dcf/graphs/meek-server-0.2-https-latency.png
Outline some different usage scenarios.

@@
 
+\section{Usage scenarios}
+
+The default usage scenario has a single paid App Engine instance, publicly known and usable by anyone,
+with software configured to use the public instance by default.
+This way has the greatest usability because there is nothing to upload and nothing to configure.
+The number of parties able to analyze users' traffic patterns is somewhat increased:
+the path from user to bridge now includes Google and the app operators, not only the ISP and intermediate routers that were there before.
+On the other hand, the bridge no longer gets to see users' IP addresses.
+In effect, Google and the app become what Tor calls a ``guard node.''
+Because Tor is encrypted and integrity-protected, neither Google nor the app operators
+are able to read or alter users' communications, but being able to measure packet timings,
+for example, is necessary for certain linking attacks.
+
+Users are also free to upload their own personal copy of the App Engine code, as is done with GoAgent.
+App Engine imposes bandwidth quotas on unpaid apps, but they are high enough to allow daily web browsing.
+In this scenario, Google still has a privileged network position,
+but the user's traffic is no longer visible to the operators of the public app instance.
+% Outgoing HTTP requests include app id? As good as an IP address.
+
+The code that runs on App Engine is very simple.
+It just statelessly copies HTTP requests and responses.
+Another usage scenario has the App Engine code ported to another language such as PHP,
+so that it can be run in ordinary web hosting environments.
+What you lose with a PHP app is Google's unblockability;
+the censor may find and individually block the domains
+This scenario is still interesting because there are so many places
+where such an app can be run, with low cost and minimal setup.
+Installing a PHP file on a web host environment is easier than setting up a Tor bridge or SOCKS proxy.
+The URLs of PHP bridges could be distributed in a way like BridgeDB.
+
 \section{Other third-party services}
@@
 We were not able to make the system work with Amazon CloudFront nor Akamai.
+% Dreamhost? Other HTTPS webhosts with PHP bridge?
+
+%%%%%%%
+
+% HTTPS or not on the App Engine--bridge link.
+% HTTPS obscures session ids, equivalent to obscuring TCP connections in other transports.
+% Increases latency a lot: \approx 100 ms increased to \approx 350 ms when I tried it in March 2014.
 

### 2014-03-13 bro-diagrams.R
Flow-level analysis of meek's traffic

@@ -8,6 +8,9 @@ broClasses <- c("numeric", "factor", "factor",    "factor",    "factor",    "fac
 nongoog <- (read.table('non-goog.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
 goog <- (read.table('goog.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
 
+meek <- (read.table('non-goog.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
+meek <- meek[meek$id.resp_p==443,]
+
 y <- nongoog$duration
 png("diagrams/flowduration.png")
 qplot(y, geom="histogram", main="Flow duration", binwidth=2) + xlab("duration")
@@ -26,4 +29,14 @@ dev.off()
 y <- (goog$resp_ip_bytes) / (goog$orig_ip_bytes)
 png("diagrams/ratio-google.png")
 qplot(y, geom="histogram", main="Downstream/Upstream Ratio (Google only)", binwidth=2) + xlab("duration")
+dev.off()
+
+y <- meek$duration
+png("diagrams/flowduration-meek.png")
+qplot(y, geom="histogram", main="Flow duration (meek)", binwidth=2) + xlab("duration")
+dev.off()
+
+y <- (meek$resp_ip_bytes) / (meek$orig_ip_bytes)
+png("diagrams/ratio-meek.png")
+qplot(y, geom="histogram", main="Downstream/Upstream Ratio (meek)", binwidth=2) + xlab("ratio")
 dev.off()

### 2014-03-13 bro-diagrams.R
Read from meek.log for meek graphs, not non-goog.log.

@@ -8,7 +8,7 @@ broClasses <- c("numeric", "factor", "factor",    "factor",    "factor",    "fac
 nongoog <- (read.table('non-goog.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
 goog <- (read.table('goog.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
 
-meek <- (read.table('non-goog.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
+meek <- (read.table('meek.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
 meek <- meek[meek$id.resp_p==443,]
 
 y <- nongoog$duration

### 2014-03-13 bro-diagrams.R
Fix a label.

@@ -28,7 +28,7 @@ dev.off()
 
 y <- (goog$resp_ip_bytes) / (goog$orig_ip_bytes)
 png("diagrams/ratio-google.png")
-qplot(y, geom="histogram", main="Downstream/Upstream Ratio (Google only)", binwidth=2) + xlab("duration")
+qplot(y, geom="histogram", main="Downstream/Upstream Ratio (Google only)", binwidth=2) + xlab("ratio")
 dev.off()
 
 y <- meek$duration

### 2014-03-14 docs/paper.tex
Use correct bib in paper.tex.
Make it more clear, the two kinds of blocking.

@@
 
-Broadly speaking, there are two main challenges to proxy-based circumvention.
-The first is obfuscation: making circumvention traffic difficult to distinguish
-from traffic the censor wishes to allow. The second is proxy address
-unblockability: making it difficult for the censor simply to block proxies by
-address. Past works have considered one or both of these problems.
+Broadly speaking, there are two main challenges to proxy-based circumvention:
+blocking by content and blocking by endpoint.
+Blocking by content means that the censor inspect packet or flow payloads,
+looking, for example, for forbidden protocols or keywords.
+Content-based blocking is countered by obfuscation:
+making circumvention traffic difficult to distinguish
+from traffic the censor wishes to allow.
+Blocking by endpoint means that the censor forbids all communication with certain
+network addresses, whatever the content of the communication.
+The challenge of endpoint blocking is met by making it difficult for the censor to learn proxy addresses;
+by having sufficiently many proxies;
+or by colocating proxies with high-value services, to block which would incur collateral damage.
+Effective proxy-based circumvention requires that both these challenges be addressed.
 
@@
 \bibliographystyle{plain}  
-\bibliography{related-work}
+\bibliography{paper}
 

### 2014-03-14 docs/paper.tex
Mention scanning resistance earlier.

@@
 The challenge of endpoint blocking is met by making it difficult for the censor to learn proxy addresses;
+by making it difficult to scan for proxies;
 by having sufficiently many proxies;

### 2014-03-14 docs/paper.tex
More on BridgeDB.

@@
 
-The other grand challenge of proxy-based circumvention is proxy address unblockability,
-for which there have been a few approaches proposed.
+The other grand challenge of proxy-based circumvention is endpoint blocking,
+against which there have been a few approaches proposed.
 Tor has long faced the problem of its entry relays being blocked. The list of
@@
 provide a few secret bridges to anyone who asks, while at the same time making it
-difficult to learn the entire list. BridgeDB is capable of distributing
-the addresses of obfsproxy and ScrambleSuit bridges, and the combination
-of selective bridge distribution and traffic obfuscation has had some success as a comprehensive circumvention solution.
-It remains the case that there are simply not enough bridges to keep them all secret for long against a resourceful adversary.
+difficult to learn the entire list.
+The database is accessible over HTTPS and email.
+The HTTPS interface requires solving a captcha,
+and the email interface responds only to addresses from certain providers, like Gmail,
+that have defenses against bulk account creation.
+BridgeDB has the feature that repeated queries from the same address
+(IP subnet or email address) will receive the same small set of bridges.
+Its resistance to enumeration therefore depends both on
+having a large number of potential bridges,
+and on the censor not being able to control large numbers of IP and email addresses.
+BridgeDB is capable of distributing
+the addresses of obfsproxy and ScrambleSuit bridges.
+The combination
+of careful bridge address disbursement and obfuscated protocols
+gives Tor's system a realistic claim to addressing both challenges of proxy-based circumvention.
+Address distribution appears to be the weaker side of the defense,
+as evidenced by real-world censors' apparent preference for
+blocking bridge addresses over real-time deobfuscation~\cite{foci12-winter}.
 
-Flash proxy~\cite{flashproxy} attempts to address the problem  by
+Flash proxy~\cite{flashproxy} attempts to address endpoint blocking by
 conscripting web users as temporary proxies. Proxies last only as long as a web

### 2014-03-14 docs/paper.tex
Stuff on flash proxy.

@@
 conscripting web users as temporary proxies. Proxies last only as long as a web
-user stays on a page, so the pool of proxies is constantly changing and
-difficult to block.
-Flash proxy's approach to unblockability is in a sense
+user stays on a page, so the pool of proxies is constantly changing;
+even if one of them is blocked, there will soon be another to replace it.
+Flash proxy's approach to endpoint blocking is in a sense
 the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
@@
 infrastructure that is expensive to block.
+Flash proxy itself does nothing to defend against content blocking.
+Connections between censored clients and browser-based proxies use
+WebSocket, a meta-protocol running on TCP,
+but inside the WebSocket framing is the ordinary Tor protocol.
 There exists a prototype transport that attempts to get both
-obfuscation and address unblockability by combining flash proxy
-with obfsproxy~\cite{obfs-flash}, however it is limited because it is not
-possible to obfuscate flash proxy's outermost WebSocket layer.
+content-based and endpoint-based blocking resistance by obfuscating traffic
+with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
+However it is limited because it is not
+possible to obfuscate the outermost WebSocket layer;
+the censor could decide simply to block all WebSocket.
 

### 2014-03-14 docs/paper.tex
Use the fteproxy name.

@@
 and sends it over VoIP to a proxy which decodes and forwards it to the destination.
-Format-transforming encryption~\cite{fte} encodes data into strings that match a given regular expression,
+fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings that match a given regular expression,
 in order to match a firewall's whitelist or avoid matching a blacklist.

### 2014-03-14 docs/paper.tex
Some stuff on how stego is easier for us.

@@
 
+\section{Introduction}
+
 % VPN arms race We seek to build a system that remains difficult to block even
 % after it has many users.
+
+\ldots
+
+The fact that we tunnel inside HTTPS greatly eases the steganography problem.
+It's not necessary to generate plausible HTTP, only plausible TLS.
+TLS payloads are encrypted, and to a first approximation all encrypted payloads look alike.
+We need only make sure that the TLS handshake and other meta-attributes of the connection are not uniquely fingerprintable.
+Section~\ref{sec:browserextension} describes the use of a web browser extension as a instrument for making HTTPS requests,
+so things like the TLS handshake, DNS lookup, and TCP connection reuse match those of a browser as closely as possible.
+Of course, there are more subtle considerations that go into
+making a circumvention HTTPS stream look like an allowed HTTPS stream,
+things like packet size and timing, and duration of TCP connections.
+These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.
 
@@
 
+\section{Making the TLS handshake indistinguishable}
+\label{sec:browserextension}
+
+% Examples of how handshakes differ; e.g., OpenSSL versus NSS,
+% and non-browser NSS versus browser NSS.
+
+\section{Making traffic characteristics indistinguishable}
+\label{sec:trafficstatistics}
+
 \section{Usage scenarios}

### 2014-03-14 docs/paper.tex
Better discussion of OSS.

@@
 infrastructure that is expensive to block.
+A quirk of the browser proxy model is that the proxy connects to the client rather than the other way around.
+The client must be able to receive a TCP connection; in particular it
+may not be behind network address translation~(NAT), which limits flash proxy's usefulness.
 Flash proxy itself does nothing to defend against content blocking.
@@
 A technique known as OSS~\cite{oss} (for
-``online scanning service'') resembles ours in certain ways. OSS bounces data
+``online scanning service'') bounces data
 through third-party web services that are capable of making HTTP requests.
-Even though such services can fetch a web page, they do not in general
-preserve the contents of the page when it is returned to the requestor.
-(A translation service, for example,
-returns the page after translating it to another language.)
-For this reason, OSS does not rely on being able to send downstream data in HTTP response bodies,
-but rather requires the server to make a symmetric reflected HTTP request back to the client.
-The main ways in which this work differs is that we are effectively using an OSS that we fully control:
-we can ensure that reflected HTTP traffic is unmodified;
-and we make the OSS hard to block by hosting it on an important network resource.
+For example, a censored client may ask a translation service to
+translate a web page at \url{http://proxy.example.com/...}, where ``\url{...}''
+stands for the data payload that the client wishes to send---data are embedded in the URL.
+Simply by making the HTTP request, the service sends the client's message.
+The client cannot rely on being able to receive the response to its message in an HTTP response,
+because online scanning services do not in general
+return unmodified the contents of the page they are ordered to retrieve.
+The translation service, for example, returns the page in another language.
+For this reason, the server sends a response message by making
+another reflected HTTP request back to the client, through the same OSS or a different one.
+The need for the client to receive a connection means that OSS has the same problem with NAT that flash proxy does.
+The NAT aspect is the most important way in which our work improves on OSS.
+App Engine is effectively an unblockable OSS that we fully control.
+We can ensure that reflected HTTP bodies are unmodified, and therefore use them to carry traffic
+without having to connect to the client.
 

### 2014-03-15 docs/paper.tex
GAE could stand for other systems.

@@
 These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.
+
+Most of the discussion in this paper will use the specific example of the
+Google frontend server as a front for App Engine.
+App Engine is the system on which we have based our deployment,
+and it suffices to illustrate the concept of domain fronting.
+There are other systems, discussed in Section~\ref{sec:otherservices}
+that can be substituted for App Engine, with few or no modifications.
+When an example talks about ``App Engine,'' the reader may instead think
+of other systems such as the CloudFlare content delivery network.
 
@@
 \section{Other third-party services}
+\label{sec:otherservices}
 

### 2014-03-15 docs/paper.tex
Split Telex, better CensorSpoofer.

@@
 and toward the censored destination requested by the client.
+Telex is conceptually similar to our work.
+Both systems use a piece of network infrastructure as a decoy to redirect certain flows
+(for Telex it is an ISP router; for us it is the Google frontend server),
+and both tag flows in a way that is visible only to the decoy router
+(for Telex a tag is a hash embedded in the TLS client randomness;
+for us it is the HTTP Host header, hidden within an HTTPS stream).
+An important difference is that Telex requires some degree of buy-in from network operators
+whose incentives may not be aligned with circumventors'.
+We require no active participation on the part of the frontend operator,
+only a lack of active opposition.
+
 CensorSpoofer~\cite{censorspoofer}
 decouples the upstream and downstream channels.
-Upstream data are carried over a low-bandwidth covert channel such as email.
-The CensorSpoofer proxy protects its address by
-spoofing the source IP address of all downstream data sent back to the client.
-In addition to spoofing, the CensorSpoofer authors propose to obfuscate the downstream with a SIP-based steganographic channel.
+The client sends upstream data to the CensorSpoofer proxy over a low-bandwidth covert channel such as email.
+At the same time, the client pretends to have an innocuous communication (such as a VoIP call) with an unblocked dummy host.
+The CensorSpoofer proxy sends encrypted UDP data back downstream to the client,
+protecting its true IP address by spoofing the source of all its packets
+so that they appear to come from the dummy host.
+From the censor's point of view, the client is carrying on a conversation only with the dummy host.
+If the dummy is blocked, another can be used in its place,
+as the CensorSpoofer proxy's true IP address remains unknown.
+% Cirripede
+
+% Routing around decoys
 A recent study~\cite{nodirectionhome} on AS
@@
 can take advantage of.
-Of the decoy routing systems, Telex is the most similar to our work.
-Both systems use a piece of network infrastructure as a decoy to redirect certain flows
-(for Telex it is an ISP router; for us it is the Google frontend server),
-and both tag flows in a way that is visible only to the decoy router
-(for Telex a tag is a hash embedded in the TLS client randomness; for us it is the HTTP Host header).
-
-% Routing around decoys
-% Cirripede
 

### 2014-03-15 docs/paper.tex
Comments for stuff to write.
Lots more on GoAgent.

@@
 % Psiphon
+% Infranet
+% Freegate
+% Ultrasurf
 
@@
 GoAgent~\cite{goagent} is a direct inspiration for our system in its use of App
-Engine and Host header--based domain fronting. GoAgent requires users to upload
-a personal copy of the server code to App Engine, and works only with HTTP and HTTPS,
-not other TCP-based protocols.
+Engine and Host header--based domain fronting.
+As in our system, traffic is fronted by the Google frontend server
+and delivered to its destination by a specialized app running on App Engine.
+GoAgent requires users to upload a personal copy of the server code to App Engine,
+which harms usability but requires no central management
+and enables users to stay within bandwidth limits that exist for unpaid apps.
+GoAgent is an HTTP and HTTPS proxy only.
+It works by encapulating a desired HTTP request, including URL and POST body, if any,
+and uploading the request to App Engine.
+The app unpacks the encapsulated request and directly requests the desired URL using
+App Engine's URL-fetching API.
+The design is simple but has disadvantages, stemming from the web app's
+need to know what URL to request.
+In order to proxy HTTPS, the local GoAgent proxy program does a benign man-in-the-middle
+attack on the browser, which must have previously trusted the GoAgent CA certificate.
+The local proxy program decrypts the HTTPS in order to read from it the HTTP request including the URL.
+When the response comes back, the local proxy re-encrypts it under its own key.
+End-to-end security is lost; an attacker positioned at the web app
+is able to observe and modify all traffic.
+In our system, such an attacker may only deny service or perform traffic analysis on ciphertext.
+Additionally, we allow proxying of any TCP-based traffic, not only HTTP.
 According to a May 2013 survey~\cite{collateral-freedom},
@@
 
+\section{Future work}
+
+% Pipelining of requests.
+% Put a diagram here showing serialized requests.
+% Simple reliability layer, SEQ/ACK.
+% Would be useful for Iran-like session cutoff, independent of meek.
+
 %%%%%%%

### 2014-05-09 docs/paper.tex
Should discuss Google's visibility of the first and last hop.
Should mention Dust for traffic shaping.
Note about splitting challenges into three.
ACKs terminology "unobservability" and "unblockability."
Cite Cirripede and Routing Around Decoys.
More general decoy routing paragraph.

@@
 % which can pass data on to the true destination for the user.
+
+% I'm thinking of recasting this as three challenges:
+%  1. Content blocking.
+%  2. Endpoint blocking.
+%  3. Active scanning.
+% We have something to say for all three and related work falls into one or
+% more of those categories.
+%
+% "Cover your ACKs" talks about "unobservability" and "unblockability," maybe
+% isomorphic to our "blocking by content" and "blocking by endpoint."
 
@@
 % Ultrasurf
+% Dust
 
@@
 
-Decoy routing is
-a recently proposed anti-blocking approach. Telex~\cite{telex}
-asks friendly ISPs to deploy special software on routers between censored users and
-popular, uncensored Internet destinations.
-Circumvention traffic is marked with a special ``tag'' that is distinguishable from a random string only
-by Telex routers (not by the censor).
-On receiving such a tagged communication, the Telex router shunts it away from its apparent destination
+Decoy routing~\cite{decoyrouting} is a technique that puts
+proxies in the middle of network paths, rather than at the endpoints.
+Realizations of the decoy routing idea include Telex~\cite{telex}
+and Cirripede~\cite{cirripede}.
+Decoy routing asks friendly ISPs to deploy special software on routers that lie
+between censored users and uncensored Internet destinations.
+Circumvention traffic is ``tagged'' in a way that is detectable only
+by decoy routers, and not by the censor.
+On receiving a tagged communication, the decoy router shunts it away from its apparent destination
 and toward the censored destination requested by the client.
-Telex is conceptually similar to our work.
-Both systems use a piece of network infrastructure as a decoy to redirect certain flows
-(for Telex it is an ISP router; for us it is the Google frontend server),
-and both tag flows in a way that is visible only to the decoy router
-(for Telex a tag is a hash embedded in the TLS client randomness;
-for us it is the HTTP Host header, hidden within an HTTPS stream).
-An important difference is that Telex requires some degree of buy-in from network operators
-whose incentives may not be aligned with circumventors'.
-We require no active participation on the part of the frontend operator,
-only a lack of active opposition.
+Our work is conceptually similar to decoy routing,
+though the action happens at the application layer rather than the network layer.
+Both systems use a piece of network infrastructure as a decoy to redirect certain flows:
+in decoy routing it is an ISP router; for us it is the front domain.
+Both tag flows in a way that is visible only to the decoy router:
+in decoy routing a tag may be, for example, a hash embedded in the TLS client randomness;
+for us it is the HTTP Host header, encrypted within an HTTPS stream.
+Decoy routing generally requires the cooperation of large, centrally located
+router operators,
+whereas we only need to buy web application hosting.
 
@@
 as the CensorSpoofer proxy's true IP address remains unknown.
-% Cirripede
 
+\cite{ccs2012-decoys}
 % Routing around decoys
@@
 
+\section{Security}
+
+% Google can deanonymize you, because they are the first hop,
+% and also often the last hop because of their popularity.
+
 \section{Future work}

### 2014-05-12 docs/meek.tex
Rename paper.tex → meek.tex.
Title.

--- 2014-05-09 docs/paper.tex
@@
 \setlength{\parskip}{\baselineskip}
+
+\title{Blocking-resistant communication through high-value web services}
+\author{David Fifield, Chang Lan}
 
@@
 censors, if the decoy routers are strategically deployed. Despite that decoy
-routing is a sound technical approach, it is still questionable whether ISPs are
-willing to act against state-level censors. However, the takeaway is that the
+routing is a sound technical approach, it is not clear whether ISPs are
+willing to act against censors. However, the takeaway is that the
 censors are unwilling to completely block day-to-day Internet access, which we
@@
 \bibliographystyle{plain}  
-\bibliography{paper}
+\bibliography{meek}
 

### 2014-05-12 bro-diagrams.R
CDF

@@ -7,6 +7,7 @@ broClasses <- c("numeric", "factor", "factor",    "factor",    "factor",    "fac
 
 nongoog <- (read.table('non-goog.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
 goog <- (read.table('goog.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
+tbb <- (read.table('tbb.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
 
 y <- nongoog$duration
 png("diagrams/flowduration.png")
@@ -23,6 +24,19 @@ png("diagrams/flowduration-google.png")
 qplot(y, geom="histogram", main="Flow duration (Google only)", binwidth=2) + xlab("duration")
 dev.off()
 
+png("diagrams/flowduration-google-cdf.png")
+qplot(y, ecdf(y)(y), geom="step", ylim=c(0,1), main="Flow duration CDF (Google)") + xlab("length") + ylab("probability")
+dev.off()
+
+y <- tbb$duration
+png("diagrams/flowduration-tbb.png")
+qplot(y, geom="histogram", main="Flow duration (TBB)", binwidth=2) + xlab("duration")
+dev.off()
+
+png("diagrams/flowduration-tbb-cdf.png")
+qplot(y, ecdf(y)(y), geom="step", ylim=c(0,1), main="Flow duration CDF (Alexa 500 with TBB)") + xlab("length") + ylab("probability")
+dev.off()
+
 y <- (goog$resp_ip_bytes) / (goog$orig_ip_bytes)
 png("diagrams/ratio-google.png")
 qplot(y, geom="histogram", main="Downstream/Upstream Ratio (Google only)", binwidth=2) + xlab("ratio")
@@ -30,6 +44,6 @@ dev.off()
 
 y <- table(goog$id.orig_h)
 png("diagrams/connections-google.png")
-hist(y,breaks=1000,main="Connections per user in 5 mins", xlab="Connections")
+hist(y,breaks=1000,main="Connections per user in 10 mins", xlab="Connections")
 dev.off()
 

### 2014-05-12 diagrams.R

@@ -7,27 +7,39 @@ min.datalen <- min(x$datalen)
 max.datalen <- max(x$datalen)
 
 png("diagrams/datalen.png")
-qplot(x$datalen, geom="histogram", main="TCP payload length", binwidth=4) + xlab("length")
+qplot(x[x$type=="non-google",]$datalen, geom="histogram", main="TCP payload length", binwidth=2) + xlab("length")
 dev.off()
 
 png("diagrams/datalen-in.png")
-qplot(x[x$dir=="IN",]$datalen, main="TCP payload length (incoming)", binwidth=4) + xlab("length")
+qplot(x[x$type=="non-google" & x$dir=="IN",]$datalen, main="TCP payload length (incoming)", binwidth=2) + xlab("length")
 dev.off()
 
 png("diagrams/datalen-out.png")
-qplot(x[x$dir=="OUT",]$datalen, main="TCP payload length (outgoing)", binwidth=4) + xlab("length")
+qplot(x[x$type=="non-google" & x$dir=="OUT",]$datalen, main="TCP payload length (outgoing)", binwidth=2) + xlab("length")
 dev.off()
 
 png("diagrams/datalen-google.png")
-qplot(x[x$google,]$datalen, main="TCP payload length (Google only)", binwidth=4) + xlab("length")
+qplot(x[x$type=="google",]$datalen, main="TCP payload length (Google only)", binwidth=2) + xlab("length")
+dev.off()
+
+png("diagrams/datalen-google-cdf.png")
+qplot(x[x$type=="google",]$datalen, ecdf(x[x$type=="google",]$datalen)(x[x$type=="google",]$datalen), geom="step", ylim=c(0,1), main="TCP payload length CDF (Google only)") + xlab("length") + ylab("probability")
 dev.off()
 
 png("diagrams/datalen-google-in.png")
-qplot(x[x$google & x$dir=="IN",]$datalen, main="TCP payload length (incoming, Google only)", binwidth=4) + xlab("length")
+qplot(x[x$type=="google" & x$dir=="IN",]$datalen, main="TCP payload length (incoming, Google only)", binwidth=2) + xlab("length")
 dev.off()
 
 png("diagrams/datalen-google-out.png")
[…]

### 2014-05-12 docs/meek.tex
Start a list of acknowledgements.
Start an abstract.

@@
 \usepackage{url}
-
-\setlength{\parskip}{\baselineskip}
 
@@
 \begin{document}
+
+\maketitle
+
+\begin{abstract}
+We describe meek, a blocking-resistant Internet communication system for censorship circumvention.
+A key technique we use is ``domain fronting''---communicating with
+a forbidden domain name while appearing to communicate with one that is allowed.
+\end{abstract}
 
@@
 
+\section{Acknowledgements}
+
+tor-dev
+tor-qa
+George Kadianakis
+Georg Koppen
+Lunar
+Yawning Angel
+Vern Paxson
+Nick Weaver
+
 %%%%%%%

### 2014-05-12 bro-diagrams.R
output eps figures

@@ -10,40 +10,40 @@ goog <- (read.table('goog.log', col.names=broNames, colClasses=broClasses, na.st
 tbb <- (read.table('tbb.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
 
 y <- nongoog$duration
-png("diagrams/flowduration.png")
+postscript("diagrams/flowduration.eps")
 qplot(y, geom="histogram", main="Flow duration", binwidth=2) + xlab("duration")
 dev.off()
 
 y <- (nongoog$resp_ip_bytes) / (nongoog$orig_ip_bytes)
-png("diagrams/ratio.png")
+postscript("diagrams/ratio.eps")
 qplot(y, geom="histogram", main="Downstream/Upstream Ratio", binwidth=2) + xlab("ratio")
 dev.off()
 
 y <- goog$duration
-png("diagrams/flowduration-google.png")
+postscript("diagrams/flowduration-google.eps")
 qplot(y, geom="histogram", main="Flow duration (Google only)", binwidth=2) + xlab("duration")
 dev.off()
 
-png("diagrams/flowduration-google-cdf.png")
+postscript("diagrams/flowduration-google-cdf.eps")
 qplot(y, ecdf(y)(y), geom="step", ylim=c(0,1), main="Flow duration CDF (Google)") + xlab("length") + ylab("probability")
 dev.off()
 
 y <- tbb$duration
-png("diagrams/flowduration-tbb.png")
+postscript("diagrams/flowduration-tbb.eps")
 qplot(y, geom="histogram", main="Flow duration (TBB)", binwidth=2) + xlab("duration")
 dev.off()
 
-png("diagrams/flowduration-tbb-cdf.png")
+postscript("diagrams/flowduration-tbb-cdf.eps")
 qplot(y, ecdf(y)(y), geom="step", ylim=c(0,1), main="Flow duration CDF (Alexa 500 with TBB)") + xlab("length") + ylab("probability")
 dev.off()
 
 y <- (goog$resp_ip_bytes) / (goog$orig_ip_bytes)
-png("diagrams/ratio-google.png")
+postscript("diagrams/ratio-google.eps")
 qplot(y, geom="histogram", main="Downstream/Upstream Ratio (Google only)", binwidth=2) + xlab("ratio")
 dev.off()
 
 y <- table(goog$id.orig_h)
-png("diagrams/connections-google.png")
+postscript("diagrams/connections-google.eps")
[…]

### 2014-05-12 diagrams.R

@@ -6,39 +6,39 @@ x <- x[order(x$t),]
 min.datalen <- min(x$datalen)
 max.datalen <- max(x$datalen)
 
-png("diagrams/datalen.png")
+postscript("diagrams/datalen.eps")
 qplot(x[x$type=="non-google",]$datalen, geom="histogram", main="TCP payload length", binwidth=2) + xlab("length")
 dev.off()
 
-png("diagrams/datalen-in.png")
+postscript("diagrams/datalen-in.eps")
 qplot(x[x$type=="non-google" & x$dir=="IN",]$datalen, main="TCP payload length (incoming)", binwidth=2) + xlab("length")
 dev.off()
 
-png("diagrams/datalen-out.png")
+postscript("diagrams/datalen-out.eps")
 qplot(x[x$type=="non-google" & x$dir=="OUT",]$datalen, main="TCP payload length (outgoing)", binwidth=2) + xlab("length")
 dev.off()
 
-png("diagrams/datalen-google.png")
+postscript("diagrams/datalen-google.eps")
 qplot(x[x$type=="google",]$datalen, main="TCP payload length (Google only)", binwidth=2) + xlab("length")
 dev.off()
 
-png("diagrams/datalen-google-cdf.png")
+postscript("diagrams/datalen-google-cdf.eps")
 qplot(x[x$type=="google",]$datalen, ecdf(x[x$type=="google",]$datalen)(x[x$type=="google",]$datalen), geom="step", ylim=c(0,1), main="TCP payload length CDF (Google only)") + xlab("length") + ylab("probability")
 dev.off()
 
-png("diagrams/datalen-google-in.png")
+postscript("diagrams/datalen-google-in.eps")
 qplot(x[x$type=="google" & x$dir=="IN",]$datalen, main="TCP payload length (incoming, Google only)", binwidth=2) + xlab("length")
 dev.off()
 
-png("diagrams/datalen-google-out.png")
+postscript("diagrams/datalen-google-out.eps")
 qplot(x[x$type=="google" & x$dir=="OUT",]$datalen, main="TCP payload length (outgoing, Google only)", binwidth=2) + xlab("length")
 dev.off()
 
-png("diagrams/datalen-tbb.png")
+postscript("diagrams/datalen-tbb.eps")
 qplot(x[x$type=="tbb",]$datalen, main="TCP payload length (TBB meek)", binwidth=2) + xlab("length")
[…]

### 2014-05-12 docs/meek.tex
"Background and related work"
Bare cite for CloundTransport (PETS 2014).
Better abstract.

@@
 We describe meek, a blocking-resistant Internet communication system for censorship circumvention.
-A key technique we use is ``domain fronting''---communicating with
-a forbidden domain name while appearing to communicate with one that is allowed.
+meek uses HTTP as a mechanism for transporting data, but it is not a steganographic HTTP transport;
+rather, it relies on HTTPS to hide the contents of communications from a censor.
+Communications are proxied through a web service that may itself be blocked by the censor:
+``domain fronting''---in which the domain name used in the (censor-visible)
+DNS request and TLS server name extension doesn't match the name in the (censor-invisible)
+HTTP host header---enables communication that is apparently with an allowed host
+but actually with a forbidden host.
+
+Though HTTPS frustrates blocking by hiding the underlying communication,
+differences in TLS implementations give rise to distinguishing features
+that may be used to block circumvention traffic.
+We describe how we use a web browser as a tool for making HTTPS requests,
+so that the TLS signature of circumvention traffic resembles that of ordinary web browsing.
+We present other, more subtle traffic characteristics that may enable blocking,
+and identify potential countermeasures to such blocking.
+
+We describe our experience implementing meek as a pluggable transport for Tor,
+and the results of an initial experimental deployment.
 \end{abstract}
@@
 
-\section{Related work}
+\section{Background and related work}
 
@@
 
+CloudTransport~\cite{cloudtransport}
+
 Winter and Lindskog~\cite{foci12-winter} investigated how China's Great Firewall blocks Tor.

### 2014-05-12 docs/meek.tex
Better obfsproxy discussion.

@@
 payloads are indistinguishable from a uniformly random byte stream.
-The classic example of a look-like-nothing
-protocol is obfsproxy~\cite{obfsproxy}, long the go-to obfuscated
-transport used by Tor. ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the
+Classic example of look-like-nothing
+protocols are obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
+which have been Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
+ScrambleSuit~\cite{scramblesuit} is like obfs3 in the
 content of its payloads, but it takes additional steps to obscure its traffic signature

### 2014-05-13 docs/meek.tex
notes.
Users graph.

@@
 \documentclass{article}  
+\usepackage{graphicx}
 \usepackage{url}
@@
 of other systems such as the CloudFlare content delivery network.
+
+The confidentiality provided by HTTPS
+
+Alternate domain fronting: use just an IP (no DNS and no SNI).
 
@@
 
+\section{Threat model}
+
+Censor allows www.google.com (or an IP); forbids appspot.com.
+
+\section{Architecture}
+
 \section{Making the TLS handshake indistinguishable}
 \label{sec:browserextension}
+
+Two big things: list of ciphersuites and extensions.
 
@@
 
+\section{Deployment}
+
+\begin{figure}
+\includegraphics[width=\linewidth]{clients-meek}
+\caption{Number of concurrent users using the meek transport,
+as reported by the Tor Metrics Portal.
+Missing parts of the graph are caused by missing data at the metrics portal.
+}
+\label{fig:clients}
+\end{figure}
+
+Figure~\ref{fig:clients} shows the number of concurrent users of meek between January and May~2014,
+as reported by the Tor Metrics Portal~\cite{metrics-meek}.
+The number of concurrent users is estimated by counting directory requests made over the transport~\cite{counting-daily-bridge-users}.
+
 \section{Future work}

### 2014-05-13 docs/clients-meek.R

@@ -1,0 +1,11 @@
+library(ggplot2)
+library(scales)
+colClasses <- c(date="Date")
+data <- read.csv("clients-meek.csv", colClasses=colClasses)
+
+# Fill in missing dates with NA.
+# https://stackoverflow.com/questions/6058677/how-to-create-na-for-missing-data-in-a-time-series/6059113#6059113
+daterange <- seq(min(data$date), max(data$date), "1 day")
+data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
+ggplot(data, aes(x=date, y=clients)) + geom_line() + xlab("Date") + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NA) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8))
+ggsave("clients-meek.pdf", width=5, height=2, units="in")

### 2014-05-13 docs/clients-meek.R
Add some significant dates to the client graph but comment them out.

@@ -7,5 +7,19 @@ data <- read.csv("clients-meek.csv", colClasses=colClasses)
 # https://stackoverflow.com/questions/6058677/how-to-create-na-for-missing-data-in-a-time-series/6059113#6059113
 daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
-ggplot(data, aes(x=date, y=clients)) + geom_line() + xlab("Date") + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NA) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8))
+p <- ggplot(data, aes(x=date, y=clients))
+# p <- p + geom_vline(xintercept=as.numeric(as.Date(c("2014-02-18", "2014-04-11", "2014-04-18", "2014-04-25", "2014-05-07", "2014-05-08"))), color="red")
+p <- p + geom_line() + xlab("Date") + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NA) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8))
 ggsave("clients-meek.pdf", width=5, height=2, units="in")
+
+# 2014-02-18 [tor-qa] Please test experimental bundles with meek transport (3.5.2.1-meek-1)
+# https://lists.torproject.org/pipermail/tor-qa/2014-February/000340.html
+# 2014-04-11 [tor-qa] 3.5.4-meek-1 (meek bundles with browser TLS camouflage)
+# https://lists.torproject.org/pipermail/tor-qa/2014-April/000390.html
+# 2014-04-18 [tor-dev] Please try 3.5.4-meek-1 bundles (covert HTTPS pluggable transport)
+# https://lists.torproject.org/pipermail/tor-dev/2014-April/006718.html
+# 2014-04-25 [tor-dev] Q&A for meek pluggable transport tomorrow, 25 April, 18:30 UTC, #tor-dev
+# https://lists.torproject.org/pipermail/tor-dev/2014-April/006763.html
+# 2014-05-07 tor1 decommissioning
+# 2014-05-08 [tor-qa] 3.6.1-meek-1 bundles
+# https://lists.torproject.org/pipermail/tor-qa/2014-May/000410.html

### 2014-05-13 docs/meek.tex
Explain the dip to zero users.
Whee, hyperref.
Remove hyperlink on example URL.
https://tex.stackexchange.com/questions/118182/selectively-turn-off-hyperref-links-for-citations/118195#118195

@@
 \usepackage{url}
+\usepackage{hyperref}
 
@@
 For example, a censored client may ask a translation service to
-translate a web page at \url{http://proxy.example.com/...}, where ``\url{...}''
+translate a web page at \begin{NoHyper}\url{http://proxy.example.com/...}\end{NoHyper},
+where ``\begin{NoHyper}\url{...}\end{NoHyper}''
 stands for the data payload that the client wishes to send---data are embedded in the URL.
@@
 The number of concurrent users is estimated by counting directory requests made over the transport~\cite{counting-daily-bridge-users}.
+The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by meek.
 

### 2014-05-13 docs/meek.tex
larger text size

--- 2014-05-12 docs/meek.tex
@@
 We describe meek, a blocking-resistant Internet communication system for censorship circumvention.
-meek uses HTTP as a mechanism for transporting data, but it is not a steganographic HTTP transport;
-rather, it relies on HTTPS to hide the contents of communications from a censor.
-Communications are proxied through a web service that may itself be blocked by the censor:
-``domain fronting''---in which the domain name used in the (censor-visible)
-DNS request and TLS server name extension doesn't match the name in the (censor-invisible)
-HTTP host header---enables communication that is apparently with an allowed host
-but actually with a forbidden host.
-
-Though HTTPS frustrates blocking by hiding the underlying communication,
-differences in TLS implementations give rise to distinguishing features
-that may be used to block circumvention traffic.
-We describe how we use a web browser as a tool for making HTTPS requests,
-so that the TLS signature of circumvention traffic resembles that of ordinary web browsing.
-We present other, more subtle traffic characteristics that may enable blocking,
-and identify potential countermeasures to such blocking.
-
-We describe our experience implementing meek as a pluggable transport for Tor,
-and the results of an initial experimental deployment.
+A key technique we use is ``domain fronting''---communicating with
+a forbidden domain name while appearing to communicate with one that is allowed.
 \end{abstract}
@@
 payloads are indistinguishable from a uniformly random byte stream.
-Classic example of look-like-nothing
-protocols are obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
-which have been Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
-ScrambleSuit~\cite{scramblesuit} is like obfs3 in the
+The classic example of a look-like-nothing
+protocol is obfsproxy~\cite{obfsproxy}, long the go-to obfuscated
+transport used by Tor. ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the
 content of its payloads, but it takes additional steps to obscure its traffic signature
@@
 
+% 1. TCP payload length
+% 2. Number of concurrent connections
+% 3. Connection Lifetime
+
+% Conclusion:
+% 1. long-lived connections with bulk data transfer may be suspicious
+% 2. Distribution of packet sizes
+
 \section{Usage scenarios}

### 2014-05-13 bro-diagrams.R

@@ -1,4 +1,6 @@
 library(ggplot2)
+library(grid)
+theme_set(theme_bw(base_size = 24))
 
 #fields          ts         uid       id.orig_h    id.orig_p    id.resp_h    id.resp_p    proto     service    duration    orig_bytes    resp_bytes    conn_state    local_orig    missed_bytes    history      orig_pkts    orig_ip_bytes    resp_pkts    resp_ip_bytes    tunnel_parents
 broNames <-   c("ts",      "uid",    "id.orig_h", "id.orig_p", "id.resp_h", "id.resp_p", "proto",  "service", "duration", "orig_bytes", "resp_bytes", "conn_state", "local_orig", "missed_bytes", "history",   "orig_pkts", "orig_ip_bytes", "resp_pkts", "resp_ip_bytes", "tunnel_parents")
@@ -11,39 +13,45 @@ tbb <- (read.table('tbb.log', col.names=broNames, colClasses=broClasses, na.stri
 
 y <- nongoog$duration
 postscript("diagrams/flowduration.eps")
-qplot(y, geom="histogram", main="Flow duration", binwidth=2) + xlab("duration")
+qplot(y, geom="histogram", binwidth=2) + xlab("duration") 
+#+ theme(text = element_text(size = rel(5))) 
 dev.off()
 
 y <- (nongoog$resp_ip_bytes) / (nongoog$orig_ip_bytes)
 postscript("diagrams/ratio.eps")
-qplot(y, geom="histogram", main="Downstream/Upstream Ratio", binwidth=2) + xlab("ratio")
+qplot(y, geom="histogram", main="Downstream/Upstream Ratio", binwidth=2) + xlab("ratio") 
+#+ theme(text = element_text(size = rel(5)))
 dev.off()
 
 y <- goog$duration
 postscript("diagrams/flowduration-google.eps")
-qplot(y, geom="histogram", main="Flow duration (Google only)", binwidth=2) + xlab("duration")
+qplot(y, geom="histogram", main="Flow duration (Google only)", binwidth=2) + xlab("duration") 
+#+ theme(text = element_text(size = rel(5)))
 dev.off()
 
 postscript("diagrams/flowduration-google-cdf.eps")
-qplot(y, ecdf(y)(y), geom="step", ylim=c(0,1), main="Flow duration CDF (Google)") + xlab("length") + ylab("probability")
[…]

### 2014-05-13 diagrams.R

@@ -1,45 +1,48 @@
 library(ggplot2)
 
+theme_set(theme_bw(base_size = 16))
+
 x <- read.delim("table.dat")
 x <- x[order(x$t),]
 
 min.datalen <- min(x$datalen)
 max.datalen <- max(x$datalen)
 
-postscript("diagrams/datalen.eps")
-qplot(x[x$type=="non-google",]$datalen, geom="histogram", main="TCP payload length", binwidth=2) + xlab("length")
+png("diagrams/datalen.png")
+qplot(x[x$type=="non-google",]$datalen, geom="histogram", main="TCP payload length", binwidth=2) + xlab("length")  
+
 dev.off()
 
-postscript("diagrams/datalen-in.eps")
-qplot(x[x$type=="non-google" & x$dir=="IN",]$datalen, main="TCP payload length (incoming)", binwidth=2) + xlab("length")
+png("diagrams/datalen-in.png")
+qplot(x[x$type=="non-google" & x$dir=="IN",]$datalen, main="TCP payload length (incoming)", binwidth=2) + xlab("length") 
 dev.off()
 
-postscript("diagrams/datalen-out.eps")
-qplot(x[x$type=="non-google" & x$dir=="OUT",]$datalen, main="TCP payload length (outgoing)", binwidth=2) + xlab("length")
+png("diagrams/datalen-out.png")
+qplot(x[x$type=="non-google" & x$dir=="OUT",]$datalen, main="TCP payload length (outgoing)", binwidth=2) + xlab("length") 
 dev.off()
 
-postscript("diagrams/datalen-google.eps")
-qplot(x[x$type=="google",]$datalen, main="TCP payload length (Google only)", binwidth=2) + xlab("length")
+png("diagrams/datalen-google.png")
+qplot(x[x$type=="google",]$datalen, main="TCP payload length (Google only)", binwidth=2) + xlab("length") 
 dev.off()
 
-postscript("diagrams/datalen-google-cdf.eps")
-qplot(x[x$type=="google",]$datalen, ecdf(x[x$type=="google",]$datalen)(x[x$type=="google",]$datalen), geom="step", ylim=c(0,1), main="TCP payload length CDF (Google only)") + xlab("length") + ylab("probability")
+png("diagrams/datalen-google-cdf.png")
[…]

### 2014-05-13 docs/meek.tex
Include architecture diagram.
Turns out missing data is due to Heartbleed.
https://lists.torproject.org/pipermail/tor-dev/2014-May/006863.html

--- 2014-05-13 docs/meek.tex
@@
 
+\begin{figure}
+\includegraphics[width=\linewidth]{architecture}
+\caption{
+System architecture.
+The Google frontend server is the server that dispatches requests to different services depending on the Host header.
+Components that are new in our system are outlined in blue.
+The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
+}
+\label{fig:architecture}
+\end{figure}
+
 \section{Making the TLS handshake indistinguishable}
@@
 \label{sec:trafficstatistics}
+
+% 1. TCP payload length
+% 2. Number of concurrent connections
+% 3. Connection Lifetime
+
+% Conclusion:
+% 1. long-lived connections with bulk data transfer may be suspicious
+% 2. Distribution of packet sizes
 
@@
 as reported by the Tor Metrics Portal.
-Missing parts of the graph are caused by missing data at the metrics portal.
-}
+The gap between April~14 and April~22 is when the Tor bridge authority
+was down because of the Heartbleed OpenSSL vulnerability~\cite{heartbleed}, and wasn't collecting statistics.}
 \label{fig:clients}

### 2014-05-13 docs/meek.tex
Include browser-architecture diagram.
Headless browser is invisible.

@@
 
+\begin{figure}
+\includegraphics{browser-architecture}
+\caption{
+Client architecture including a browser extension for TLS camouflage.
+Dashed lines show the process hierarchy.
+Solid lines show the flow of outgoing communication.
+The headless instance of the browser runs in the background and is invisible to the user.
+This figure is a detailed view of the ``User's PC'' component of Figure~\ref{fig:architecture}.
+}
+\label{fig:architecture}
+\end{figure}
+
 \section{Making traffic characteristics indistinguishable}

### 2014-05-13 docs/meek.tex
Fix figure label.
traffic characteristics figures

--- 2014-05-13 docs/meek.tex
@@
 \usepackage{url}
+\usepackage{caption}
+\usepackage{subcaption}
 \usepackage{hyperref}
@@
 
-\begin{figure}
-\includegraphics[width=\linewidth]{architecture}
-\caption{
-System architecture.
-The Google frontend server is the server that dispatches requests to different services depending on the Host header.
-Components that are new in our system are outlined in blue.
-The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
-}
-\label{fig:architecture}
-\end{figure}
-
 \section{Making the TLS handshake indistinguishable}
@@
 
+The censor cannot sniff the content of communications or infer the existence of meek traffic 
+from packet \emph{data}, 
+since the communication is encrypted inside the TLS session, and we have devoted large efforts 
+in hiding TLS handshake fingerprints. However, it is still possible that the censor can detect 
+the existence of meek traffic according to the \emph{metadata}, i.e. traffic characteristics. 
+We studied a collection of traffic characteristics and evaluated their possibilities of becoming
+the censor's interest. Specifically, we considered three characteristics: 1) payload length of
+TCP packets, 2) number of concurrent HTTPS connections, 3) HTTPS connection lifetime. To collect 
+the traffic trace of meek, we browsed the Alexa top 500 websites sequentially using the Tor Browser Bundle
+and dumped the traffic trace from 
+the network interface. We ensured only the browser can successfully access the network by setting
+up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
+obtained a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983 MB in total. We also
+specifically extracted the traffic between LBL and Google. Since the trace only has packet headers, we 
+cannot extract the domain information. However, the \texttt{TXT} DNS records of the domain 
+\texttt{\_netblocks.google.com} shows the IP address blocks that belongs to Google. Therefore, we 
+determine whether a flow is from or to Google by examining the address in the IP header. For this
+study we are only interested in Google traffic, because the censor will be mostly likely to compare
+suspected meek traffic with normal Google traffic. This part of the trace is 312 MB in size.
+
 % 1. TCP payload length
@@
 % 2. Distribution of packet sizes
+
+\begin{figure}
+\centering
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figs/datalen-google-cdf.png}
+\caption{Normal Google Traffic}
+\label{fig:len:lbl}
+\end{subfigure}%
+%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
+%(or a blank line to force the subfigure onto a new line)
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics[width=\textwidth]{figs/datalen-tbb-cdf.png}
+\caption{Traffic Using meek}
+\label{fig:len:meek}
+\end{subfigure}
+
+\caption{TCP packet payload size distribution}
+\label{fig:len}
+\end{figure}
+
+\paragraph{TCP payload length}
+Figure \ref{fig:len} shows the payload size distribution of normal Google traffic and meek traffic. Both
+figures exhibit a significant amount of packets with no payload. Most likely these packets are TCP SYN and ACK
+packets. Figure \ref{fig:len:lbl} is the distribution of normal traffic, which indicates a large portion
+of small-sized packets. While in the distribution of meek traffic shown in Figure \ref{fig:len:meek}, most packets
+are large packets ranging from 1400B to 1500B.
+
+Recall that we use browsers to handle HTTPS connections for meek in order to hide TLS handshake characteristics.
+Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
+the same Google frontend server, the browser will keep the persistant TLS connection. In addition, small requests 
+can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the meek trace.
+In contract, normal users may not have persistent connections to Google. For example, a user may search a keyword on
+Google, click a result, and then close the tab that displays search results. The browser may close the 
+connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
+opens a new connection. In this case, small requests do not have such opportunity for batching.
+
+These browser techniques improve performance, but also lead to unexpected results. The censor may be aware of the 
+deviation from the distribution of normal traffic. Additionally, the persistent connection itself can be a problem.
+We thus investigated other related characteristics.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth, angle=270]{figs/connections-google.eps}
+\caption{Histogram of each user's connections in the 10-minute window}
+\label{fig:connections}
+\end{figure}
+%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
+%(or a blank line to force the subfigure onto a new line)
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figs/conns.eps}
+\caption{Concurrent HTTPS connections over time. We measure the trace for the Tor Browser Bundle and Firefox/Chrome extensions.}
+\label{fig:len:meek}
+\end{figure}
+
+\paragraph{Concurrent connections}
+
+\begin{figure}
+\centering
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics[height=\textwidth, angle=270]{figs/flowduration-google-cdf.eps}
+\caption{Normal Google Traffic}
+\label{fig:len:lbl}
+\end{subfigure}%
+%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
+%(or a blank line to force the subfigure onto a new line)
+\begin{subfigure}[b]{0.5\textwidth}
+\includegraphics[height=\textwidth, angle=270]{figs/flowduration-tbb-cdf.eps}
+\caption{Traffic Using meek}
+\label{fig:len:meek}
+\end{subfigure}
+
+\caption{Connection lifetime distribution}
+\label{fig:len}
+\end{figure}
+
+\paragraph{Connection lifetime}
+
+\paragraph{Conclusion}
 
@@
 as reported by the Tor Metrics Portal.
-The gap between April~14 and April~22 is when the Tor bridge authority
-was down because of the Heartbleed OpenSSL vulnerability~\cite{heartbleed}, and wasn't collecting statistics.}
+Missing parts of the graph are caused by missing data at the metrics portal.
+}
 \label{fig:clients}

### 2014-05-13 bro-diagrams.R

@@ -30,7 +30,7 @@ qplot(y, geom="histogram", main="Flow duration (Google only)", binwidth=2) + xla
 dev.off()
 
 postscript("diagrams/flowduration-google-cdf.eps")
-qplot(y, ecdf(y)(y), geom="step", ylim=c(0,1), main="Flow duration CDF (Google)") + xlab("length (sec)") + ylab("probability")
+qplot(y, ecdf(y)(y), geom="step", ylim=c(0,1), main="Flow duration CDF (Google)") + xlab("Length (Seconds)") + ylab("Probability")
 #+ theme(text = element_text(size = rel(5)))
 dev.off()
 
@@ -41,7 +41,7 @@ qplot(y, geom="histogram", main="Flow duration (TBB)", binwidth=2) + xlab("durat
 dev.off()
 
 postscript("diagrams/flowduration-tbb-cdf.eps")
-qplot(y, ecdf(y)(y), geom="step", ylim=c(0,1), main="Flow duration CDF (Alexa 500 with TBB)") + xlab("length (sec)") + ylab("probability")  
+qplot(y, ecdf(y)(y), geom="step", ylim=c(0,1), main="Flow duration CDF (Alexa 500 with TBB)") + xlab("Length (Seconds)") + ylab("Probability")  
 #+ theme(axis.title = element_text(size = rel(2)), axis.text = element_text(size = rel(2)), plot.title = element_text(size = rel(2)), axis.ticks.margin = unit(10, "lines"))
 dev.off()
 

### 2014-05-13 diagrams.R

@@ -26,7 +26,7 @@ qplot(x[x$type=="google",]$datalen, main="TCP payload length (Google only)", bin
 dev.off()
 
 png("diagrams/datalen-google-cdf.png")
-qplot(x[x$type=="google",]$datalen, ecdf(x[x$type=="google",]$datalen)(x[x$type=="google",]$datalen), geom="step", ylim=c(0,1), main="TCP payload length CDF (Google only)") + xlab("length") + ylab("probability") 
+qplot(x[x$type=="google",]$datalen, ecdf(x[x$type=="google",]$datalen)(x[x$type=="google",]$datalen), geom="step", ylim=c(0,1), main="TCP payload length CDF (Google only)") + xlab("Length (Bytes)") + ylab("Probability") 
 dev.off()
 
 png("diagrams/datalen-google-in.png")
@@ -38,11 +38,11 @@ qplot(x[x$type=="google" & x$dir=="OUT",]$datalen, main="TCP payload length (out
 dev.off()
 
 png("diagrams/datalen-tbb.png")
-qplot(x[x$type=="tbb",]$datalen, main="TCP payload length (TBB meek)", binwidth=2) + xlab("length") 
+qplot(x[x$type=="tbb",]$datalen, main="TCP payload length (TBB meek)", binwidth=2) + xlab("Length") 
 dev.off()
 
 png("diagrams/datalen-tbb-cdf.png")
-qplot(x[x$type=="tbb",]$datalen, ecdf(x[x$type=="tbb",]$datalen)(x[x$type=="tbb",]$datalen), geom="step", ylim=c(0,1), main="TCP payload length CDF (Alexa 500 with TBB)") + xlab("length") + ylab("probability") 
+qplot(x[x$type=="tbb",]$datalen, ecdf(x[x$type=="tbb",]$datalen)(x[x$type=="tbb",]$datalen), geom="step", ylim=c(0,1), main="TCP payload length CDF (Alexa 500 with TBB)") + xlab("Length (Bytes)") + ylab("Probability") 
 dev.off()
 
 syn.out <- x[x$syn & x$dir=="OUT",]

### 2014-05-13 docs/meek.tex

@@
 % and non-browser NSS versus browser NSS.
+
+\begin{figure}
+\includegraphics{browser-architecture}
+\caption{
+Client architecture including a browser extension for TLS camouflage.
+Dashed lines show the process hierarchy.
+Solid lines show the flow of outgoing communication.
+The headless instance of the browser runs in the background and is invisible to the user.
+This figure is a detailed view of the ``User's PC'' component of Figure~\ref{fig:architecture}.
+}
+\label{fig:browser-architecture}
+\end{figure}
 

### 2014-05-13 docs/meek.tex
characteristics

@@
 in hiding TLS handshake fingerprints. However, it is still possible that the censor can detect 
-the existence of meek traffic according to the \emph{metadata}, i.e. traffic characteristics. 
+the existence of meek traffic according to the \emph{meta-data}, i.e. traffic characteristics. 
 We studied a collection of traffic characteristics and evaluated their possibilities of becoming
@@
 Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
-the same Google frontend server, the browser will keep the persistant TLS connection. In addition, small requests 
+the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
 can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the meek trace.
@@
 
-These browser techniques improve performance, but also lead to unexpected results. The censor may be aware of the 
+These browser techniques improve performance, but also lead to unexpected risks. The censor may be aware of the 
 deviation from the distribution of normal traffic. Additionally, the persistent connection itself can be a problem.
@@
 \caption{Concurrent HTTPS connections over time. We measure the trace for the Tor Browser Bundle and Firefox/Chrome extensions.}
-\label{fig:len:meek}
+\label{fig:conconns}
 \end{figure}
@@
 \paragraph{Concurrent connections}
+Figure \ref{fig:connections} shows how many HTTPS connections to Google did a user make 
+during the 10-minute measurement window.
+There are 34,732 connections in total from 2,745 unique IPs. We observe that the majority of users have less than 
+50 connections to the Google frontend server, and most of the numbers concentrate on 1 ~ 10. This is not unexpected
+because a typical pattern of using Google is using the Google search as a stepping stone for other websites.
+
+We measure the number of concurrent HTTPS connections during the automated browsing of Alexa
+top 500 sites using three platforms: Tor Browser Bundle, Safari + Firefox extension, and Safari + Chrome extension.
+Figure \ref{fig:conconns} shows the number over time. We can see that most of the time
+the browser has one HTTPS connection to Google. Sometimes the browser may have more than one connection
+due to background activities such as statistics reporting. In all cases the number of connections is always 
+less than 5. We can conclude that the number of concurrent connections does not show distinct characteristics, as 
+a small number of connections can be considered as a normal behavior.
 
@@
 \caption{Normal Google Traffic}
-\label{fig:len:lbl}
+\label{fig:duration:lbl}
 \end{subfigure}%
@@
 \includegraphics[height=\textwidth, angle=270]{figs/flowduration-tbb-cdf.eps}
-\caption{Traffic Using meek}
-\label{fig:len:meek}
+\caption{Traffic Using meek (Notice the x-axis)}
+\label{fig:duration:meek}
 \end{subfigure}
@@
 \caption{Connection lifetime distribution}
-\label{fig:len}
+\label{fig:duration}
 \end{figure}
@@
 \paragraph{Connection lifetime}
+We consider the connection lifetime as a potential weakness. Figure \ref{fig:duration:lbl} shows the 
+connection lifetime distribution of normal traffic. Interestingly we can see the concentration on 
+several discrete values: 60s, 120s, 180s, 240s. We hypothesize that it is due to the HTTP Keep-Alive 
+timeout of different browsers and web services. Another important observation is the concentration on 
+durations that exceed 600 seconds. Note that our trace only contains 10 minutes' data, therefore the concentration 
+on 600 seconds does not reflect that these connections' actual duration is 600 seconds. Rather, 600 seconds
+is the lower bound of their actual duration. Thus, we can conclude that only about 10\% connections last 
+longer than 600 seconds.
 
-\paragraph{Conclusion}
+The distribution of meek traffic, in contrast, is totally different. First, there are much fewer connections, which is 
+consistent with the discussions above.
+Second, the durations are much longer if we notice the x-axis in Figure \ref{fig:duration:meek}.
+If there is not a case in which normal users also have such long connections when browsing Google, the
+censor can potentially block any long connections between users and Google. Even if this is the case, the
+censor has to wait until a time threshold is reached. The user may already obtained the forbidden data she wants, or 
+meek could simply restart a connection.
+
+\paragraph{Conclusion} So far we have found two potential weaknesses: long-lived connections with bulk data transfer, 
+and deviated distribution of packet sizes.
+To fundamentally fix these weaknesses we need to transform to the traffic into the normal-looking traffic.
+The problem is inherently difficult, because we need to know \emph{what} is normal traffic, i.e.
+what
+is the model of normal traffic, which is an open problem. However, the arm-race game is symmetric; since finding a right
+model is a difficult task for us, it is also difficult for the censor. Therefore, the censor can only find ad-hoc 
+characteristics to block forbidden traffic, which are relatively easy to defend against.
 

### 2014-05-13 docs/meek.tex
Pluggable transport cite.
Source code.

@@
 
+\cite{pt}
+
 \begin{figure}
@@
 
+meek has a home page at
+\url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
+Our source code is in the Git repository at
+\url{https://git.torproject.org/pluggable-transports/meek.git}.
+As of version 0.5 (May~7, 2014), the source code consists of
+about 800 lines of Go for the client programs,
+400 lines for the server, and
+100 lines for the intermediary web app.
+Each of the browser extensions
+(one for Firefox, one for Chrome)
+is about 300 lines of JavaScript.
+
 \section{Future work}

### 2014-05-13 docs/meek.tex
Bundles.

@@
 
+We implemented meek as a Tor pluggable transport~\cite{pt}
+and built experimental releases of the Tor Browser Bundle featuring meek.
+The browser bundle includes Tor and a version of Firefox
+called Tor Browser that is patched to defend against application-layer identity leaks.
+Users need to download and run the bundle and select meek from the list of transports,
+and then a browser window appears,
+configured to use meek for circumvention and Tor for anonymity.
+We announced our prototype bundles on Tor development mailing lists,
+and from there they were picked up by Tor Weekly News on the Tor blog.
+
 \begin{figure}

### 2014-05-13 docs/meek.tex
App Engine costs.
Threat model.

@@
 
-Censor allows www.google.com (or an IP); forbids appspot.com.
+The censor is able to inspect all traffic that passes through
+the censorship boundary and block or allow it at will.
+The censor is able to actively scan for proxies, and issue followup
+connections to hosts that clients connect to, in order to determine
+whether they are proxies.
+The censor may block the web host on which the reflector web app runs,
+but it must allow access to some domain that can front for it.
+In our deployment using App Engine, the censor may block appspot.com,
+but must allow www.google.com (or its IP address, or some other domain
+that goes through the frontend server).
+
+The censor must operate at line rate; that is,
+it must not delay traffic unduly while deciding whether to allow it.
+This consideration is one facet of the censor's sensistivity to
+collateral damage caused by false positives:
+mistakenly blocking or degrading non-circumvention traffic causes the censor
+to incur some penalty, just as mistakenly allowing circumvention traffic does.
+The censor must allow TLS connections; meek does not try to look like plaintext.
+
+The user's computer, the third-party infrastructure (e.g., Google), and the Tor bridge
+are all uncontrolled and uncompromised by the censor.
+The user has a way to get a copy of the necessary client programs.
 
@@
 
+We are running a paid instance of the web app on App Engine for use by the public.
+The cost for bandwidth on App Engine is \$0.12 per gigabyte,
+with one gigabyte free each day.
+The total cost has so far been \$1.11, with bills of
+\$0.09 in March,
+\$0.73 in April,
+and \$0.29 in May through May~12.
+
 meek has a home page at

### 2014-05-13 docs/meek.tex
Better phrasing.
Some stuff about browser extension.

@@
 \usepackage{hyperref}
+
+% Avoid line breaks in program names.
+\def\meekclient{\mbox{meek-client}}
+\def\meekserver{\mbox{meek-server}}
 
@@
 
+We implemented two versions of a browser extension, one for Firefox and one for Chrome.
+They both work similarly: they open a TCP port on localhost,
+await instructions from \meekclient\ on what HTTP requests to make,
+issue the requests, and return the responses.
+
+Figure~\ref{fig:browser-architecture} shows the interaction of components
+on the user's computer.
+Rather than starting \meekclient\ directly, the tor
+process starts a helper process that starts both \meekclient\
+and a headless browser instance.
+The headless browser runs our extension in a separate
+process and separate browser profile from the browser the
+user interacts with; the two browser instances share no state.
+\meekclient\ is configured to issue its requests through the browser extension;
+in this configuration, the headless browser is the only thing that ever touches the network.
+
+The use of a browser extension offers benefits beyond its TLS signature.
+We inherit other characteristics of the browser:
+how often it resolves DNS names,
+its connection reuse,
+and HTTP keepalive behavior.
+The Firefox extension has special usability advantages because the Tor Browser Bundle
+uses a modified Firefox.
+We can include a small extension in the browser bundle and reuse the existing
+Firefox executable without increasing the download size of the bundle much,
+and without requiring users to separately configure a browser to run the extension.
+
 \section{Making traffic characteristics indistinguishable}
@@
 \$0.73 in April,
-and \$0.29 in May through May~12.
+and \$0.29 in the first half of May.
 

### 2014-05-13 docs/meek.tex
Use \meekserver macro.

@@
 about 800 lines of Go for the client programs,
-400 lines for the server, and
+400 lines for \meekserver, and
 100 lines for the intermediary web app.

### 2014-05-13 docs/meek.tex
TLS handshake.

@@
 
-Two big things: list of ciphersuites and extensions.
+The practice of routing traffic through a web service with domain fronting
+defeats both endpoint-based blocking and active scanning.
+The endpoint (which appears to be the front domain; e.g. www.google.com)
+cannot be blocked because to block it would cause collateral damage.
+Active scanning is defeated because if the censor accesses the same
+endpoint as the client, all they see is a web page served by the front domain.
+Even though the censor knows some traffic is being fronted,
+by looking only at IP addresses and domain names, it cannot determine which.
 
-% Examples of how handshakes differ; e.g., OpenSSL versus NSS,
-% and non-browser NSS versus browser NSS.
+However, a savvy censor may also use content-based blocking
+(deep packet inspection) as a basis for blocking.
+Anything that reliably distinguishes meek's traffic from that of normal allowed traffic
+(presumably web browsing) must be eliminated.
+In this section we demonstrate how the client part of the TLS handshake can be used
+to fingerprint different TLS implementations,
+and how we use a web browser to camouflage meek's TLS.
+
+There are many parts of the TLS handshake, but the two that
+most distinguish the client are the list of ciphersuites and the
+list of TLS extensions in the Client Hello.
+Figure~\ref{fig:ciphersuites} shows how the list of ciphersuites
+differs in different client implementations.
+Figure~\ref{fig:ciphersuites:meek-client} is how our first prototype of \meekclient\ appeared on the wire,
+using the built-in crypto/tls library of the Go programming language.
+The list of ciphersuites is unlike that of a web browser,
+and could be used as a fingerprint for blocking.
+Tor itself was blocked by China in 2011 in exactly this way~\cite{bug4744}.
+Similarly the list of TLS extensions (not shown)
+differed between \meekclient\ and popular browsers.
+
+\begin{figure}
+
+\begin{subfigure}[t]{0.30\textwidth}
+\begin{minipage}[t][17ex][t]{0.30\textwidth}
+\tiny
+\begin{verbatim}
+TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
+TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
+TLS_ECDHE_RSA_WITH_RC4_128_SHA
+TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
+TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
+TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
+TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
+TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
+TLS_RSA_WITH_RC4_128_SHA
+TLS_RSA_WITH_AES_128_CBC_SHA
+TLS_RSA_WITH_AES_256_CBC_SHA
+TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
+TLS_RSA_WITH_3DES_EDE_CBC_SHA
+\end{verbatim}
+\end{minipage}
+\caption{meek-client}
+\label{fig:ciphersuites:meek-client}
+\end{subfigure}
+%
+\begin{subfigure}[t]{0.30\textwidth}
+\begin{minipage}[t][48ex][t]{0.30\textwidth}
+\tiny
+\begin{verbatim}
+TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
+TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
+TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
+TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
+TLS_ECDHE_ECDSA_WITH_3DES_EDE_CBC_SHA
+TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
+TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
+TLS_ECDHE_RSA_WITH_RC4_128_SHA
+TLS_DHE_RSA_WITH_AES_128_CBC_SHA
+TLS_DHE_DSS_WITH_AES_128_CBC_SHA
+TLS_DHE_RSA_WITH_CAMELLIA_128_CBC_SHA
+TLS_DHE_DSS_WITH_CAMELLIA_128_CBC_SHA
+TLS_DHE_RSA_WITH_AES_256_CBC_SHA
+TLS_DHE_DSS_WITH_AES_256_CBC_SHA
+TLS_DHE_RSA_WITH_CAMELLIA_256_CBC_SHA
+TLS_DHE_DSS_WITH_CAMELLIA_256_CBC_SHA
+TLS_DHE_RSA_WITH_3DES_EDE_CBC_SHA
+TLS_DHE_DSS_WITH_3DES_EDE_CBC_SHA
+TLS_ECDH_ECDSA_WITH_AES_128_CBC_SHA
+TLS_ECDH_RSA_WITH_AES_128_CBC_SHA
+TLS_ECDH_ECDSA_WITH_AES_256_CBC_SHA
+TLS_ECDH_RSA_WITH_AES_256_CBC_SHA
+TLS_ECDH_ECDSA_WITH_3DES_EDE_CBC_SHA
+TLS_ECDH_RSA_WITH_3DES_EDE_CBC_SHA
+TLS_ECDH_ECDSA_WITH_RC4_128_SHA
+TLS_ECDH_RSA_WITH_RC4_128_SHA
+TLS_RSA_WITH_AES_128_CBC_SHA
+TLS_RSA_WITH_CAMELLIA_128_CBC_SHA
+TLS_RSA_WITH_AES_256_CBC_SHA
+TLS_RSA_WITH_CAMELLIA_256_CBC_SHA
+TLS_RSA_WITH_SEED_CBC_SHA
+SSL_RSA_FIPS_WITH_3DES_EDE_CBC_SHA
+TLS_RSA_WITH_3DES_EDE_CBC_SHA
+TLS_RSA_WITH_RC4_128_SHA
+TLS_RSA_WITH_RC4_128_MD5
+\end{verbatim}
+\end{minipage}
+\caption{Firefox 24}
+\label{fig:ciphersuites:firefox}
+\end{subfigure}
+%
+\begin{subfigure}[t]{0.30\textwidth}
+\begin{minipage}[t][27ex][t]{0.30\textwidth}
+\tiny
+\begin{verbatim}
+TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
+TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
+TLS_DHE_RSA_WITH_AES_128_GCM_SHA256
+TLS_ECDHE_ECDSA_WITH_CHACHA20_POLY1305_SHA256
+TLS_ECDHE_RSA_WITH_CHACHA20_POLY1305_SHA256
+TLS_RSA_WITH_AES_128_GCM_SHA256
+TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
+TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
+TLS_DHE_RSA_WITH_AES_256_CBC_SHA
+TLS_RSA_WITH_AES_256_CBC_SHA
+TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
+TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
+TLS_ECDHE_RSA_WITH_RC4_128_SHA
+TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
+TLS_DHE_RSA_WITH_AES_128_CBC_SHA
+TLS_DHE_DSS_WITH_AES_128_CBC_SHA
+TLS_RSA_WITH_RC4_128_SHA
+TLS_RSA_WITH_RC4_128_MD5
+TLS_RSA_WITH_AES_128_CBC_SHA
+TLS_RSA_WITH_3DES_EDE_CBC_SHA
+\end{verbatim}
+\end{minipage}
+\caption{Chrome 33}
+\label{fig:ciphersuites:chrome}
+\end{subfigure}
+
+\caption{Differences in ciphersuites offered by
+our \meekclient\ program when it accesses the network directly,
+and by two web browsers.
+The distinctive ciphersuites offered by \meekclient\ can be used as part of a blocking fingerprint.
+As a remedy we have \meekclient\ proxy its TLS through a web browser extension.
+}
+\label{fig:ciphersuites}
+\end{figure}
+
+In response to the threat of TLS fingerprinting,
+we modified \meekclient\ to proxy its HTTP requests through a local web browser extension.
+\meekclient\ tells the extension what URLs to fetch, and the extension fetches them.
+The TLS fingerprint looks like that of a browser, because it is that of a browser.
+We implemented two versions of the extension, one for Firefox and one for Chrome.
+They work similarly: they open a TCP port on localhost,
+await instructions from \meekclient\ on what HTTP requests to make,
+issue the requests, and return the responses.
 
@@
 
-We implemented two versions of a browser extension, one for Firefox and one for Chrome.
-They both work similarly: they open a TCP port on localhost,
-await instructions from \meekclient\ on what HTTP requests to make,
-issue the requests, and return the responses.
-
 Figure~\ref{fig:browser-architecture} shows the interaction of components
 on the user's computer.
-Rather than starting \meekclient\ directly, the tor
+Rather than starting \meekclient\ as a pluggable transport directly, the tor
 process starts a helper process that starts both \meekclient\
@@
 in this configuration, the headless browser is the only thing that ever touches the network.
+When run with a browser extension, meek has the same TLS signature
+as Firefox (Figure~\ref{fig:ciphersuites:firefox}) or
+Chrome (Figure~\ref{fig:ciphersuites:chrome}).
 
@@
 uses a modified Firefox.
-We can include a small extension in the browser bundle and reuse the existing
-Firefox executable without increasing the download size of the bundle much,
+We can include a small extension in the browser bundle, reusing the existing
+Firefox executable, without increasing the download size of the bundle much,
 and without requiring users to separately configure a browser to run the extension.
+
+The development of the browser extensions posed some unexpected challenges.
+Tor Browser disables TLS session tickets because they can be used as linking identifiers,
+but the lack of session tickets shows up as a missing TLS extension,
+so we had to reenable them in the headless browser.
+(Doing so doesn't harm Tor Browser's anonymity:
+if session tickets are used, they are used only on the circumvention layer
+between the user and the frontend server. Tor Browser's own TLS is tunneled
+within the circumvention layer, and session tickets are still disabled at that level.)
+The Chrome extension needed to be split into two pieces, an extension and an app,
+because an extension cannot open a listening socket and an app cannot make HTTP requests.
 

### 2014-05-13 docs/meek.tex
Architecture.

@@
 
-\cite{pt}
+The components of the system are shown in Figure~\ref{fig:architecture}.
+The three parts that are new in our system are:
+\begin{enumerate}
+\item The client program \meekclient.
+Using the pluggable transports protocol, tor treats \meekclient\ as a SOCKS proxy.
+When \meekclient\ receives data from tor, it bundles it up in an HTTP POST
+request and sends it to the web app,
+using HTTPS to hide the contents and the domain fronting trick to hide the true destination.
+Downstream data are returned in HTTP responses, which \meekclient\ decodes and sends back to tor.
+\item The ``reflector'' web app, running on App Engine.
+Its domain name \mbox{meek-reflect.appspot.com} is protected by domain fronting.
+It is called a reflector because it doesn't do anything intelligent:
+it merely copies the HTTP requests it receives and forwards them
+to \meekserver\ running on the Tor bridge.
+\item The server program \meekserver, which acts as an HTTP server.
+It receives reflected requests from the web app, decodes their bodies,
+and forwards the contents to an instance of tor running on the same host.
+If there is anything pending to be sent back to the client,
+\meekserver\ sends it along with its HTTP response.
+\meekserver\ also takes care of stringing together multiple HTTP requests
+into one logical stream and multiplexing multiple concurrent connections,
+both using the technique of session IDs described in this section.
+\end{enumerate}
 
@@
 \end{figure}
+
+The main technical challenge in making this system work
+is in encoding a TCP stream as a sequence of HTTP requests and responses.
+\meekserver\ handles many clients at once, and their data streams
+are split across multiple HTTP transactions.
+In TCP, different streams are distinguished by their
+(source~IP, source port, dest~IP, dest~port) tuple,
+but we cannot do that because streams are split across multiple TCP sessions.
+Rather, each instance of \meekclient\ generates at startup a random 32-byte
+session ID, which is sent along with its requests in a special
+X-Session-ID HTTP header.
+\meekserver, when it sees a particular session ID for the first time,
+opens up a new connection to the local tor process,
+and stores the session ID in a cache. Subsequent requests with the
+same session ID will reuse the same tor connection.
+Entries are removed from the cache after a period of inactivity.
+
+HTTP is fundamentally a pull-based protocol.
+There is no way for the server to send data to the client without
+the client first making a request.
+The same applies to meek: when \meekserver\ has data to send back to
+a client with a particular session ID, it cannot do so until it
+receives a request from that client.
+For this reason, \meekclient\ polls the server,
+sending an empty request if necessary, every so often.
+The polling interval starts short (100~ms) and grows exponentially
+up to a maximum of 5~s.
+Alternative techniques for push-like behavior,
+such as HTTP long polling,
+don't work well with App Engine,
+because App Engine requires requests to finish within 60 seconds.
+
+We implemented meek as a pluggable transport~\cite{pt} for Tor.
+Although it is possible to use the system with proxies other than Tor,
+using Tor has some attractive features.
+The pluggable transports infrastructure makes it relatively easy to prototype
+a circumvention technique and connect it to a global proxy network.
+We can treat confidentiality and integrity of tunnelled communication
+as a problem solved by Tor, which we don't need to solve separately.
+Tor's extra proxy hops mean that the HTTP reflector (App Engine)
+and the entry bridge do not have to be trusted.
 

### 2014-05-13 docs/meek.tex
Change section title; we're not indistinguishable yet.
Performance measurements for future work.
Put active scanning earlier in background.

@@
 
-% I'm thinking of recasting this as three challenges:
-%  1. Content blocking.
-%  2. Endpoint blocking.
-%  3. Active scanning.
-% We have something to say for all three and related work falls into one or
-% more of those categories.
-%
-% "Cover your ACKs" talks about "unobservability" and "unblockability," maybe
-% isomorphic to our "blocking by content" and "blocking by endpoint."
-
 Broadly speaking, there are two main challenges to proxy-based circumvention:
 blocking by content and blocking by endpoint.
-Blocking by content means that the censor inspect packet or flow payloads,
+A content-blocking censor inspects packets and payloads,
 looking, for example, for forbidden protocols or keywords.
@@
 from traffic the censor wishes to allow.
-Blocking by endpoint means that the censor forbids all communication with certain
-network addresses, whatever the content of the communication.
+Blocking by endpoint is based on \emph{whom you are speaking to},
+and blocking by content is based on \emph{what you are saying}.
+A skilled censor will do both, and effective circumvention requires meeting both challenges.
+An endpoint-blocking censor forbids all communication with certain
+addresses, for example IP addresses and domain names, whatever the contents may be.
 The challenge of endpoint blocking is met by making it difficult for the censor to learn proxy addresses;
-by making it difficult to scan for proxies;
-by having sufficiently many proxies;
-or by colocating proxies with high-value services, to block which would incur collateral damage.
-Effective proxy-based circumvention requires that both these challenges be addressed.
+by having overwhelmingly many proxies;
+or by colocating proxies with high-value services so that both must be blocked or both allowed.
+
+To the above challenges we may add the related challenge of active scanning for proxies.
+Though a circumvention protocol may be difficult to identify on the wire,
+it may nevertheless be easy to scan for servers that speak the protocol,
+and thereafter block the server by its address.
+Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
+Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
+by actively scanning destination addresses to see if they speak the Tor protocol.
+The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
+and in this work.
 
@@
 CloudTransport~\cite{cloudtransport}
-
-Winter and Lindskog~\cite{foci12-winter} investigated how China's Great Firewall blocks Tor.
-They confirmed an earlier discovery of Wilde~\cite{wilde} that the firewall identifies Tor relays using more than passive monitoring:
-it actively probes destination addresses to see if they speak the Tor protocol, and if so,
-blocks them for the future.
-(At the time, the firewall identified potential Tor connections for future probing by looking for a distinctive
-list of TLS ciphersuites---a failure of obfuscation.) %\cite{bug4744}
-The discovery of Chinese active probing was the motivation for probing resistance in ScrambleSuit
-and in our work.
 
@@
 
-\section{Making traffic characteristics indistinguishable}
+\section{Camouflage of traffic characteristics}
 \label{sec:trafficstatistics}
@@
 
+% Performance measurements
+
 \section{Acknowledgements}

### 2014-05-13 docs/meek.tex
Rewrite deployment scenarios.

@@
 
-\section{Usage scenarios}
-
-The default usage scenario has a single paid App Engine instance, publicly known and usable by anyone,
-with software configured to use the public instance by default.
-This way has the greatest usability because there is nothing to upload and nothing to configure.
-The number of parties able to analyze users' traffic patterns is somewhat increased:
-the path from user to bridge now includes Google and the app operators, not only the ISP and intermediate routers that were there before.
-On the other hand, the bridge no longer gets to see users' IP addresses.
-In effect, Google and the app become what Tor calls a ``guard node.''
-Because Tor is encrypted and integrity-protected, neither Google nor the app operators
-are able to read or alter users' communications, but being able to measure packet timings,
-for example, is necessary for certain linking attacks.
-
-Users are also free to upload their own personal copy of the App Engine code, as is done with GoAgent.
-App Engine imposes bandwidth quotas on unpaid apps, but they are high enough to allow daily web browsing.
-In this scenario, Google still has a privileged network position,
-but the user's traffic is no longer visible to the operators of the public app instance.
-% Outgoing HTTP requests include app id? As good as an IP address.
-
-The code that runs on App Engine is very simple.
-It just statelessly copies HTTP requests and responses.
-Another usage scenario has the App Engine code ported to another language such as PHP,
-so that it can be run in ordinary web hosting environments.
-What you lose with a PHP app is Google's unblockability;
-the censor may find and individually block the domains
-This scenario is still interesting because there are so many places
-where such an app can be run, with low cost and minimal setup.
-Installing a PHP file on a web host environment is easier than setting up a Tor bridge or SOCKS proxy.
-The URLs of PHP bridges could be distributed in a way like BridgeDB.
-
 \section{Other third-party services}
@@
 
+\subsection{Other deployment scenarios}
+
+The deployment we envision and have started to implement
+uses a single paid App Engine instance, which is publicly known and usable by anyone.
+Client software is configured to use this public instance by default.
+A preconfigured public instance has great usability advantages
+because there is nothing for the user to upload and nothing to configure.
+The number of parties able to analyze users' traffic patterns is somewhat increased:
+the path from user to Tor bridge now includes App Engine and the web app operators,
+in addition to the ISP and intermediate routers that were there before.
+On the other hand, the Tor bridge no longer gets to see users' IP addresses:
+all it sees are many connections from the App Engine.
+In effect, App Engine and the web app become what Tor calls a ``guard node,''
+a privileged relay that takes the first hop in the chain of relays.
+Because Tor is encrypted and integrity-protected, neither App Engine nor the app operators
+are able to read or alter users' communications, but being on path enables them
+to do things like measure packet timing patterns.
+
+Users are also free to upload their own personal copy of the App Engine code, as is done with GoAgent.
+App Engine imposes bandwidth quotas on unpaid apps, but they are high enough to allow daily web browsing.
+In this scenario, Google still has a privileged network position,
+but the user's traffic patterns are no longer visible to the operators of a public app instance.
+% Outgoing HTTP requests include app id? As good as an IP address.
+
+The code that runs on App Engine is very simple.
+It just statelessly copies HTTP requests and responses.
+Another possible deployment scenario uses a PHP implementation of the reflector,
+deployed on an ordinary web hosting service other than App Engine.
+In this scenario, domain fronting is not used;
+instead unblockability depends on there being many (individually blockable) PHP reflectors.
+In other words, it is roughly the same situation as exists today with Tor bridges,
+except that it can be much easier for a volunteer to upload a PHP file to a web host
+than to set up Tor bridge or other proxy.
+Such PHP bridges could potentially automatically report their own URLs,
+which could be distributed using a system like BridgeDB.
+
 \section{Future work}

### 2014-05-13 docs/meek.tex
comment on threat model; minor change on packet size distribution

--- 2014-05-13 docs/meek.tex
@@
 The censor must allow TLS connections; meek does not try to look like plaintext.
+% but the censor may look at TLS characteristics and block suspicious connections.
 
@@
 \item The client program \meekclient.
-Using the pluggable transports protocol, tor treats \meekclient\ as a SOCKS proxy.
-When \meekclient\ receives data from tor, it bundles it up in an HTTP POST
+Using the pluggable transports protocol, Tor treats \meekclient\ as a SOCKS proxy.
+When \meekclient\ receives data from Tor, it bundles it up in an HTTP POST
 request and sends it to the web app,
 using HTTPS to hide the contents and the domain fronting trick to hide the true destination.
-Downstream data are returned in HTTP responses, which \meekclient\ decodes and sends back to tor.
+Downstream data are returned in HTTP responses, which \meekclient\ decodes and sends back to Tor.
 \item The ``reflector'' web app, running on App Engine.
@@
 It receives reflected requests from the web app, decodes their bodies,
-and forwards the contents to an instance of tor running on the same host.
+and forwards the contents to an instance of Tor running on the same host.
 If there is anything pending to be sent back to the client,
@@
 \meekserver, when it sees a particular session ID for the first time,
-opens up a new connection to the local tor process,
+opens up a new connection to the local Tor process,
 and stores the session ID in a cache. Subsequent requests with the
-same session ID will reuse the same tor connection.
+same session ID will reuse the same Tor connection.
 Entries are removed from the cache after a period of inactivity.
@@
 
-% 1. TCP payload length
-% 2. Number of concurrent connections
-% 3. Connection Lifetime
-
-% Conclusion:
-% 1. long-lived connections with bulk data transfer may be suspicious
-% 2. Distribution of packet sizes
-
 \begin{figure}
@@
 Figure \ref{fig:len} shows the payload size distribution of normal Google traffic and meek traffic. Both
-figures exhibit a significant amount of packets with no payload. Most likely these packets are TCP SYN and ACK
-packets. Figure \ref{fig:len:lbl} is the distribution of normal traffic, which indicates a large portion
-of small-sized packets. While in the distribution of meek traffic shown in Figure \ref{fig:len:meek}, most packets
-are large packets ranging from 1400B to 1500B.
+figures exhibit a significant amount of packets with no payload. These packets are mostly TCP SYN and ACK
+packets. Figure \ref{fig:len:lbl} shows the distribution of normal traffic, which indicates a large portion
+of small-sized packets. However, in the meek traffic shown in Figure \ref{fig:len:meek}, most packets
+are large packets ranging from 1400 bytes to 1500 bytes. This result is unexpected, because the underlying packets 
+in the TLS session are sent from Tor. By default, each Tor cell is 512 bytes, but meek changes the packet size 
+distribution. Therefore, meek provides traffic shaping without additional efforts.
 
@@
 
-These browser techniques improve performance, but also lead to unexpected risks. The censor may be aware of the 
-deviation from the distribution of normal traffic. Additionally, the persistent connection itself can be a problem.
+These browser techniques improve performance, but may also lead to unexpected consequences. 
+Although meek alters the packet size distribution of underlying Tor traffic, 
+the censor may be aware of the distribution of meek itself. 
+Additionally, the persistent connection itself can be a problem.
 We thus investigated other related characteristics.
@@
 censor can potentially block any long connections between users and Google. Even if this is the case, the
-censor has to wait until a time threshold is reached. The user may already obtained the forbidden data she wants, or 
+censor has to wait until a time threshold is reached. The user might have already obtained the forbidden data she wants, or 
 meek could simply restart a connection.
 
-\paragraph{Conclusion} So far we have found two potential weaknesses: long-lived connections with bulk data transfer, 
-and deviated distribution of packet sizes.
-To fundamentally fix these weaknesses we need to transform to the traffic into the normal-looking traffic.
+\paragraph{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
+distinguishing the meek traffic. But admittedly there two potential weaknesses: long-lived connections 
+with bulk data transfer, and deviated distribution of packet sizes. To fundamentally fix these weaknesses 
+we need to transform to the traffic into the normal-looking traffic.
 The problem is inherently difficult, because we need to know \emph{what} is normal traffic, i.e.
-what
-is the model of normal traffic, which is an open problem. However, the arm-race game is symmetric; since finding a right
-model is a difficult task for us, it is also difficult for the censor. Therefore, the censor can only find ad-hoc 
-characteristics to block forbidden traffic, which are relatively easy to defend against.
+what is the model of normal traffic, which is an open problem.
+However,
+the arm-race game is symmetric; since finding a right model is a difficult task for us, it is also difficult for 
+the censor. Therefore, the censor can only find ad-hoc features to block forbidden traffic, which are relatively 
+easy to defend against.
 

### 2014-05-13 docs/meek.tex
traffic characteristics section

@@
 
-The censor cannot sniff the content of communications or infer the existence of meek traffic 
+The censor cannot sniff the content of communications or infer the usage of meek 
 from packet \emph{data}, 
@@
 in hiding TLS handshake fingerprints. However, it is still possible that the censor can detect 
-the existence of meek traffic according to the \emph{meta-data}, i.e. traffic characteristics. 
-We studied a collection of traffic characteristics and evaluated their possibilities of becoming
-the censor's interest. Specifically, we considered three characteristics: 1) payload length of
-TCP packets, 2) number of concurrent HTTPS connections, 3) HTTPS connection lifetime. To collect 
-the traffic trace of meek, we browsed the Alexa top 500 websites sequentially using the Tor Browser Bundle
-and dumped the traffic trace from 
-the network interface. We ensured only the browser can successfully access the network by setting
+the existence of meek according to the \emph{meta-data}, i.e. traffic characteristics. 
+In this section we study a collection of traffic characteristics and evaluate their possibilities of becoming
+the censor's interest. Specifically, we consider three characteristics: 1) payload length of
+TCP packets, 2) number of concurrent HTTPS connections, 3) HTTPS connection lifetime.
+
+To collect the traffic trace of meek, we browses the Alexa top 500 websites sequentially using 
+the Tor Browser Bundle and dump the traffic trace from the network interface. We ensured only
+the browser can successfully access the network by setting
 up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
-obtained a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983 MB in total. We also
-specifically extracted the traffic between LBL and Google. Since the trace only has packet headers, we 
-cannot extract the domain information. However, the \texttt{TXT} DNS records of the domain 
-\texttt{\_netblocks.google.com} shows the IP address blocks that belongs to Google. Therefore, we 
-determine whether a flow is from or to Google by examining the address in the IP header. For this
-study we are only interested in Google traffic, because the censor will be mostly likely to compare
-suspected meek traffic with normal Google traffic. This part of the trace is 312 MB in size.
+obtain a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983 MB in total. 
+We also specifically extracted the traffic between LBL and Google from the trace. Since the trace 
+only has packet headers, we cannot extract the domain information. However, the \texttt{TXT} DNS
+records of the domain \texttt{\_netblocks.google.com} shows the IP address blocks that belongs to
+Google. Therefore, we determine whether a flow is from or to Google by examining the address in the 
+IP header. We only interested in the Google traffic only, because the censor who wants to defeat meek
+will be mostly likely to compare suspicious traffic with normal Google traffic. The size of the 
+Google trace is 312 MB.
 
@@
 
-Recall that we use browsers to handle HTTPS connections for meek in order to hide TLS handshake characteristics.
+To explain the phenomenon, recall that we use browsers to handle HTTPS connections for meek in order
+to hide TLS handshake characteristics.
 Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
@@
 
-These browser techniques improve performance, but may also lead to unexpected consequences. 
+These browser techniques improve performance, but also pose unexpected consequences. 
 Although meek alters the packet size distribution of underlying Tor traffic, 
 the censor may be aware of the distribution of meek itself. 
-Additionally, the persistent connection itself can be a problem.
+Additionally, the persistent connection itself can be an issue.
 We thus investigated other related characteristics.

### 2014-05-13 docs/meek.tex
Domain fronting.

@@
 
-Most of the discussion in this paper will use the specific example of the
-Google frontend server as a front for App Engine.
-App Engine is the system on which we have based our deployment,
-and it suffices to illustrate the concept of domain fronting.
-There are other systems, discussed in Section~\ref{sec:otherservices}
-that can be substituted for App Engine, with few or no modifications.
-When an example talks about ``App Engine,'' the reader may instead think
-of other systems such as the CloudFlare content delivery network.
+``Domain fronting'' is the term we use for one of the key techniques used by meek.
+Domain fronting is the use of different domain names at different layers of the network stack.
+In the DNS query and TLS server name indication (SNI)~\cite[Section~3]{rfc6066},
+which are visible to the censor, one domain name (the ``front domain'') appears;
+while in the HTTP Host header~\cite[Section~14.23]{rfc2616},
+which is hidden from censor by HTTPS encryption,
+a different name (the actual destination) appears.
+Domain fronting works in systems that use the Host header in order to
+multiplex many domain names behind one HTTPS frontend;
+among these systems are Google's infrastructure and the
+CloudFlare content delivery network.
+Domain fronting can also work using only an IP address in place of
+a front domain. In this case there is no DNS query and no SNI in the TLS layer,
+but the actual destination still appears in the Host header.
+Domain fronting has been used successfully for years by GoAgent~\cite{goagent}
+(which uses a bare IP address without SNI)
+and by one of the rendezvous methods of flash proxy~\cite{flashproxy}.
+In the examples in this paper, the front domain is www.google.com
+and the actual hidden destination domain is meek-reflect.appspot.com,
+which is our custom web app that aids in circumvention.
 
-The confidentiality provided by HTTPS
-
-Alternate domain fronting: use just an IP (no DNS and no SNI).
+For concreteness, and because it is what we have deployed so far,
+the examples in this paper will use Google and App Engine as the specific
+third-party web service used for circumvention.
+Other systems that support domain fronting may be substituted for Google,
+and other alternative deployments are discussed in Section~\ref{sec:otherdeployment}.
 
@@
 \section{Deployment}
+\label{sec:deployment}
 
@@
 \subsection{Other deployment scenarios}
+\label{sec:otherdeployment}
 

### 2014-05-13 docs/meek.tex
Small changes.

@@
 % after it has many users.
-
-\ldots
 
@@
 content of its payloads, but it takes additional steps to obscure its traffic signature
-(packet lengths and timing), and is designed to resist active scanning for proxies
+(packet lengths and timing), and is designed to resist active scanning
 (the proxy server remains silent until the client proves knowledge of a shared
@@
 
-\cite{ccs2012-decoys}
+% \cite{ccs2012-decoys}
 % Routing around decoys
@@
 
-CloudTransport~\cite{cloudtransport}
+% CloudTransport~\cite{cloudtransport}
 
@@
 
-\section{Security}
+% \section{Security}
 

### 2014-05-13 docs/meek.tex
make figures appear in the center
Move CloudFront to other deployment.

@@
 \begin{figure}
+\centering
 \includegraphics[width=\linewidth]{architecture}
@@
 \begin{figure}
+\centering
 \includegraphics{browser-architecture}
@@
 
-\section{Other third-party services}
-\label{sec:otherservices}
-
-A censor can block meek by blocking access to Google entirely.
-To take such a step is extreme, because of its high collateral damage,
-but it is not outside the realm of possibility.
-% Cite when Google and Gmail were completely blocked temporarily.
-We investigated how easily our system can be adapted to hard-to-block systems other than Google,
-and found that CloudFlare, a content delivery network, in principle supports domain fronting.
-
-CloudFlare provides the frontend of $X$ web sites, $Y$ of them supporting HTTPS~\cite{something}.
-CloudFlare supports the domain fronting trick;
-that is, it is possible that a request has one domain in the TLS layer
-and another in the HTTP layer, and the CloudFlare server will transparently redirect it to proper place.
-While we verified that domain fronting would work on CloudFlare,
-we did not test deployment,
-because when we asked we were told that our planned use would be against CloudFlare's terms of service.
-CloudFlare hosts a number of HTTPS sites.
-Choosing just one of them to be the front in TLS connections could cause
-the innocent third-party domain to be censored even though it is not itself carrying any circumvention traffic.
-To avoid this problem, the front can be simply a CloudFlare IP address,
-with no SNI at all.
-The censor then faces the choice of allowing circumvention traffic,
-or else blocking a large number of popular unrelated web sites.
-
-We were not able to make the system work with Amazon CloudFront nor Akamai.
-% Dreamhost? Other HTTPS webhosts with PHP bridge?
-
 % \section{Security}
@@
 
+A censor can block meek by blocking access to Google entirely,
+but other systems can take the place of Google.
+An attractive alternative is CloudFlare, a large content delivery network,
+which supports domain fronting, dispatching requests based on the Host header
+rather than IP or SNI.
+We did not test deployment on CloudFlare,
+because their terms of service are not clear on whether this kind of use is allowed,
+and we got an ambiguous answer when we asked for clarification.
+A particular concern when using CloudFlare or other content delivery networks is the choice of front domain.
+If one domain is being used particularly as a front for circumvention traffic,
+it may find itself blocked by the censor, even though it is not itself
+involved in any circumvention.
+One good solution to this problem may be not to use a domain name at all,
+but only the IP address of one of CloudFlare's servers.
+The censor will then face the choice of allowing circumvention traffic,
+or else blocking a large number of unrelated web sites.
+
+% We were not able to make the system work with Amazon CloudFront nor Akamai.
+% Dreamhost? Other HTTPS webhosts with PHP bridge?
+
 The code that runs on App Engine is very simple.

### 2014-05-13 docs/meek.tex
Ensmallen extension diagram.
grammar fix

--- 2014-05-13 docs/meek.tex
@@
 \paragraph{TCP payload length}
-Figure \ref{fig:len} shows the payload size distribution of normal Google traffic and meek traffic. Both
+Figure \ref{fig:len} shows the payload size distribution of normal traffic and meek's traffic. Both
 figures exhibit a significant amount of packets with no payload. These packets are mostly TCP SYN and ACK
 packets. Figure \ref{fig:len:lbl} shows the distribution of normal traffic, which indicates a large portion
-of small-sized packets. However, in the meek traffic shown in Figure \ref{fig:len:meek}, most packets
+of small-sized packets. However, in the meek's traffic shown in Figure \ref{fig:len:meek}, most packets
 are large packets ranging from 1400 bytes to 1500 bytes. This result is unexpected, because the underlying packets 
@@
 the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
-can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the meek trace.
+can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
+records meek's traffic.
 In contract, normal users may not have persistent connections to Google. For example, a user may search a keyword on
@@
 
-The distribution of meek traffic, in contrast, is totally different. First, there are much fewer connections, which is 
+The distribution of meek's traffic, in contrast, is totally different. First, there are much fewer connections, which is 
 consistent with the discussions above.
@@
 \paragraph{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
-distinguishing the meek traffic. But admittedly there two potential weaknesses: long-lived connections 
+distinguishing meek's traffic. But admittedly there two potential weaknesses: long-lived connections 
 with bulk data transfer, and deviated distribution of packet sizes. To fundamentally fix these weaknesses 

### 2014-05-13 docs/meek.tex

--- 2014-05-13 docs/meek.tex
@@
 \centering
-\includegraphics{browser-architecture}
+\includegraphics[height=1.5in]{browser-architecture}
 \caption{

### 2014-05-13 docs/meek.tex
Introduction.

@@
 
-The fact that we tunnel inside HTTPS greatly eases the steganography problem.
-It's not necessary to generate plausible HTTP, only plausible TLS.
-TLS payloads are encrypted, and to a first approximation all encrypted payloads look alike.
-We need only make sure that the TLS handshake and other meta-attributes of the connection are not uniquely fingerprintable.
-Section~\ref{sec:browserextension} describes the use of a web browser extension as a instrument for making HTTPS requests,
-so things like the TLS handshake, DNS lookup, and TCP connection reuse match those of a browser as closely as possible.
-Of course, there are more subtle considerations that go into
-making a circumvention HTTPS stream look like an allowed HTTPS stream,
-things like packet size and timing, and duration of TCP connections.
-These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.
+Censorship is a daily reality for many Internet users.
+Workplaces, schools, and governments use technical and social means
+to prevent access to certain information by the network users under their control.
+In response, those users use technical and social means
+to gain access to the forbidden information.
+What has emerged is an ongoing conflict between censor and censored,
+with advances on both sides, more subtle evasion being countered by more powerful detection.
+
+In this paper we describe the design and deployment of meek,
+a censorship-resistant communication system that aims at defeating
+known technical means of censorship.
+meek tunnels traffic through HTTP, but does not attempt to look like plaintext HTTP;
+it uses HTTPS to hide the contents of communications
+while relaying them through a third-party web services that it itself hard to block.
+meek is implemented as a Tor pluggable transport~\cite{pt}.
+We have done an initial deployment of the system and it is in use
+by a small number of users.
 
@@
 which is our custom web app that aids in circumvention.
+
+meek may be regarded as a steganographic transport only in that it must blend in with other HTTPS traffic.
+Tunnelling inside HTTPS greatly eases the steganography problem:
+It's not necessary to generate plausible HTTP, only plausible TLS,
+because TLS payloads are encrypted, and to a first approximation all encrypted payloads look alike.
+We need only make sure that the TLS handshake and other meta-attributes of the connection are not uniquely fingerprintable.
+Section~\ref{sec:browserextension} describes the use of a web browser extension as a instrument for making HTTPS requests,
+so things like the TLS handshake, DNS lookup, and TCP connection reuse match those of a browser as closely as possible.
+Of course, there are more subtle considerations that go into
+making a circumvention HTTPS stream look like an allowed HTTPS stream,
+things like packet size and timing, and duration of TCP connections.
+These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.
 

### 2014-05-13 docs/meek.tex
Future work.

@@
 \paragraph{TCP payload length}
-Figure \ref{fig:len} shows the payload size distribution of normal traffic and meek's traffic. Both
+Figure ~\ref{fig:len} shows the payload size distribution of normal traffic and meek's traffic. Both
 figures exhibit a significant amount of packets with no payload. These packets are mostly TCP SYN and ACK
-packets. Figure \ref{fig:len:lbl} shows the distribution of normal traffic, which indicates a large portion
-of small-sized packets. However, in the meek's traffic shown in Figure \ref{fig:len:meek}, most packets
+packets. Figure ~\ref{fig:len:lbl} shows the distribution of normal traffic, which indicates a large portion
+of small-sized packets. However, in the meek's traffic shown in Figure ~\ref{fig:len:meek}, most packets
 are large packets ranging from 1400 bytes to 1500 bytes. This result is unexpected, because the underlying packets 
@@
 \paragraph{Concurrent connections}
-Figure \ref{fig:connections} shows how many HTTPS connections to Google did a user make 
+Figure ~\ref{fig:connections} shows how many HTTPS connections to Google did a user make 
 during the 10-minute measurement window.
@@
 top 500 sites using three platforms: Tor Browser Bundle, Safari + Firefox extension, and Safari + Chrome extension.
-Figure \ref{fig:conconns} shows the number over time. We can see that most of the time
+Figure ~\ref{fig:conconns} shows the number over time. We can see that most of the time
 the browser has one HTTPS connection to Google. Sometimes the browser may have more than one connection
@@
 \paragraph{Connection lifetime}
-We consider the connection lifetime as a potential weakness. Figure \ref{fig:duration:lbl} shows the 
+We consider the connection lifetime as a potential weakness. Figure ~\ref{fig:duration:lbl} shows the 
 connection lifetime distribution of normal traffic. Interestingly we can see the concentration on 
@@
 consistent with the discussions above.
-Second, the durations are much longer if we notice the x-axis in Figure \ref{fig:duration:meek}.
+Second, the durations are much longer if we notice the x-axis in Figure ~\ref{fig:duration:meek}.
 If there is not a case in which normal users also have such long connections when browsing Google, the
@@
 
-% Pipelining of requests.
-% Put a diagram here showing serialized requests.
-% Simple reliability layer, SEQ/ACK.
+In future work we would like to implement pipelining of requests,
+so that more than one HTTP request can be outstanding at a time.
+This would have better performance compared to the current system,
+which serializes requests and responses in order to keep the
+underlying TCP stream in order.
+A system of sequence numbers and acknowledgments as used in OSS~\cite{oss}
+could make this possible.
 % Would be useful for Iran-like session cutoff, independent of meek.
@@
 % Performance measurements
+We would like to do more quantitative performance measurements,
+in order to measure the overhead in bandwidth and latency that meek has over plain Tor.
+We have done informal tests, such as browsing YouTube,
+but have not yet put numbers to our measurements.
+
+% Load balancing
 

### 2014-05-13 docs/meek.tex
Acknowledgements.

@@
 
-tor-dev
-tor-qa
-George Kadianakis
-Georg Koppen
-Lunar
-Yawning Angel
-Vern Paxson
-Nick Weaver
+We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
+Special thanks go to the members of the tor-qa and tor-dev mailing lists
+who responded to our design ideas, reviewed source code, and tested our prototypes.
+% George Kadianakis
+% Georg Koppen
+% Lunar
+% Yawning Angel
 

### 2014-05-13 docs/meek.tex
load balancing as future work?

--- 2014-05-13 docs/meek.tex
@@
 
-Censorship is a daily reality for many Internet users.
-Workplaces, schools, and governments use technical and social means
-to prevent access to certain information by the network users under their control.
-In response, those users use technical and social means
-to gain access to the forbidden information.
-What has emerged is an ongoing conflict between censor and censored,
-with advances on both sides, more subtle evasion being countered by more powerful detection.
-
-In this paper we describe the design and deployment of meek,
-a censorship-resistant communication system that aims at defeating
-known technical means of censorship.
-meek tunnels traffic through HTTP, but does not attempt to look like plaintext HTTP;
-it uses HTTPS to hide the contents of communications
-while relaying them through a third-party web services that it itself hard to block.
-meek is implemented as a Tor pluggable transport~\cite{pt}.
-We have done an initial deployment of the system and it is in use
-by a small number of users.
+The fact that we tunnel inside HTTPS greatly eases the steganography problem.
+It's not necessary to generate plausible HTTP, only plausible TLS.
+TLS payloads are encrypted, and to a first approximation all encrypted payloads look alike.
+We need only make sure that the TLS handshake and other meta-attributes of the connection are not uniquely fingerprintable.
+Section~\ref{sec:browserextension} describes the use of a web browser extension as a instrument for making HTTPS requests,
+so things like the TLS handshake, DNS lookup, and TCP connection reuse match those of a browser as closely as possible.
+Of course, there are more subtle considerations that go into
+making a circumvention HTTPS stream look like an allowed HTTPS stream,
+things like packet size and timing, and duration of TCP connections.
+These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.
 
@@
 which is our custom web app that aids in circumvention.
-
-meek may be regarded as a steganographic transport only in that it must blend in with other HTTPS traffic.
-Tunnelling inside HTTPS greatly eases the steganography problem:
-It's not necessary to generate plausible HTTP, only plausible TLS,
-because TLS payloads are encrypted, and to a first approximation all encrypted payloads look alike.
-We need only make sure that the TLS handshake and other meta-attributes of the connection are not uniquely fingerprintable.
-Section~\ref{sec:browserextension} describes the use of a web browser extension as a instrument for making HTTPS requests,
-so things like the TLS handshake, DNS lookup, and TCP connection reuse match those of a browser as closely as possible.
-Of course, there are more subtle considerations that go into
-making a circumvention HTTPS stream look like an allowed HTTPS stream,
-things like packet size and timing, and duration of TCP connections.
-These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.
 
@@
 
-In future work we would like to implement pipelining of requests,
-so that more than one HTTP request can be outstanding at a time.
-This would have better performance compared to the current system,
-which serializes requests and responses in order to keep the
-underlying TCP stream in order.
-A system of sequence numbers and acknowledgments as used in OSS~\cite{oss}
-could make this possible.
+% Pipelining of requests.
+% Put a diagram here showing serialized requests.
+% Simple reliability layer, SEQ/ACK.
 % Would be useful for Iran-like session cutoff, independent of meek.
@@
 % Performance measurements
-We would like to do more quantitative performance measurements,
-in order to measure the overhead in bandwidth and latency that meek has over plain Tor.
-We have done informal tests, such as browsing YouTube,
-but have not yet put numbers to our measurements.
-
 % Load balancing

### 2014-05-13 docs/meek.tex
Spell check.

--- 2014-05-13 docs/meek.tex
@@
 meek may be regarded as a steganographic transport only in that it must blend in with other HTTPS traffic.
-Tunnelling inside HTTPS greatly eases the steganography problem:
+Tunneling inside HTTPS greatly eases the steganography problem:
 It's not necessary to generate plausible HTTP, only plausible TLS,
@@
 GoAgent is an HTTP and HTTPS proxy only.
-It works by encapulating a desired HTTP request, including URL and POST body, if any,
+It works by encapsulating a desired HTTP request, including URL and POST body, if any,
 and uploading the request to App Engine.
@@
 it must not delay traffic unduly while deciding whether to allow it.
-This consideration is one facet of the censor's sensistivity to
+This consideration is one facet of the censor's sensitivity to
 collateral damage caused by false positives:
@@
 a circumvention technique and connect it to a global proxy network.
-We can treat confidentiality and integrity of tunnelled communication
+We can treat confidentiality and integrity of tunneled communication
 as a problem solved by Tor, which we don't need to solve separately.
@@
 
-\section{Acknowledgements}
+\section{Acknowledgments}
 

### 2014-05-13 docs/meek.tex
tor→Tor in one more place.
The distinction between little-t tor and big-T Tor is potentially
confusing here.

@@
 on the user's computer.
-Rather than starting \meekclient\ as a pluggable transport directly, the tor
+Rather than starting \meekclient\ as a pluggable transport directly, the Tor
 process starts a helper process that starts both \meekclient\

### 2014-05-13 docs/meek.tex
Stick with the "reflector" terminology.

@@
 400 lines for \meekserver, and
-100 lines for the intermediary web app.
+100 lines for the reflector web app.
 Each of the browser extensions

### 2014-05-13 docs/meek.tex
Words.

@@
 On the other hand, the Tor bridge no longer gets to see users' IP addresses:
-all it sees are many connections from the App Engine.
+all it sees are many connections from App Engine.
 In effect, App Engine and the web app become what Tor calls a ``guard node,''
@@
 except that it can be much easier for a volunteer to upload a PHP file to a web host
-than to set up Tor bridge or other proxy.
+than to set up Tor bridge.
 Such PHP bridges could potentially automatically report their own URLs,

### 2014-07-07 docs/meek.tex
Remember to ack Psiphon.
Revise decoy routing coverage.

@@
 Decoy routing~\cite{decoyrouting} is a technique that puts
-proxies in the middle of network paths, rather than at the endpoints.
-Realizations of the decoy routing idea include Telex~\cite{telex}
+proxies in the middle of network paths, rather than at the ends.
+Realizations of decoy routing include Telex~\cite{telex}
 and Cirripede~\cite{cirripede}.
-Decoy routing asks friendly ISPs to deploy special software on routers that lie
-between censored users and uncensored Internet destinations.
+In decoy routing, friendly ISPs deploy special \emph{decoy} routers that lie
+on network paths between censored users and uncensored Internet destinations.
 Circumvention traffic is ``tagged'' in a way that is detectable only
 by decoy routers, and not by the censor.
-On receiving a tagged communication, the decoy router shunts it away from its apparent destination
-and toward the censored destination requested by the client.
-Our work is conceptually similar to decoy routing,
-though the action happens at the application layer rather than the network layer.
-Both systems use a piece of network infrastructure as a decoy to redirect certain flows:
-in decoy routing it is an ISP router; for us it is the front domain.
-Both tag flows in a way that is visible only to the decoy router:
-in decoy routing a tag may be, for example, a hash embedded in the TLS client randomness;
-for us it is the HTTP Host header, encrypted within an HTTPS stream.
-Decoy routing generally requires the cooperation of large, centrally located
-router operators,
-whereas we only need to buy web application hosting.
+On receiving a tagged communication, the decoy shunts it away from its apparent, \emph{overt destination}
+and toward a censored, \emph{covert destination}.
+Domain fronting is similar to decoy routing;
+think of domain fronting as decoy routing at the application layer.
+In place of a decoy router, domain fronting has a CDN edge server;
+in place of the overt destination is the front domain.
+Both systems tag flows in a way that is invisible to the censor:
+decoy routing uses, for example, a hash embedded in a client nonce,
+while domain fronting uses the HTTP Host header, encrypted within HTTPS.
+
+Schuhard et~al.~\cite{ccs2012-decoys}
+introduce the idea of a \emph{routing adversary} against decoy routing,
+and show that the connectivity of the Internet enables
+censors to force network users onto paths that do not include decoys.
+Simulations by Houmansadr et~al.~\cite{nodirectionhome}
+show that even though such alternate paths exist,
+they are many times more costly to the censor,
+especially when decoys are placed strategically.
 
@@
 as the CensorSpoofer proxy's true IP address remains unknown.
-
-% \cite{ccs2012-decoys}
-% Routing around decoys
-A recent study~\cite{nodirectionhome} on AS
-topology suggests that defeating decoy routing is likely to be expensive for the
-censors, if the decoy routers are strategically deployed. Despite that decoy
-routing is a sound technical approach, it is not clear whether ISPs are
-willing to act against censors. However, the takeaway is that the
-censors are unwilling to completely block day-to-day Internet access, which we
-can take advantage of.
 
@@
 % Yawning Angel
+% Rod Hynes and Michael Hull of Psiphon.
 

### 2014-07-08 docs/meek.tex
Latency measurement attack.

@@
 
-% \section{Security}
+\section{Security}
 
-% Google can deanonymize you, because they are the first hop,
-% and also often the last hop because of their popularity.
+Domain fronting shares a weakness with decoy routing,
+which is that the overt and covert destinations lie on different
+network paths.
+The difference in paths may create side channels---latency measurements for instance---that
+enable the censor to
+distinguish fronted traffic from traffic that is truly destined
+to the front domain.
+For example, a CDN can be expected to have responses
+to some fraction of requests already in cache,
+and respond to those requests with low latency.
+Fronted traffic, on the other hand, always continues all the way
+to the origin server after reaching the CDN (as if nothing were ever cached),
+resulting in a higher latency.
+Latency measurement was applied to decoy routing by Schuhard et~al.~\cite[Section~5]{ccs2012-decoys},
+who compared empirical round-trip-time distributions using a
+Kolmogorov--Smirnov test.
+% time between ChangeCipherSpec and ApplicationData
+
+% Edge servers within the censored region.
+% Censor could block on the way to the origin server,
+% if the censor has visibility to it.
+% Maybe the CDN has its own private high-speed cables,
+% or it VPNs its own stuff or something.
+
+% Firefox plugin uses normal browser trust store.
+% Adversary controls CAs. Can MITM and read your tag and block you.
+% Maybe not willing to risk getting caught in MITM.
+% Could conceivably send cover traffic if MITM detected, but blah.
 

### 2014-07-08 docs/meek.tex
Remember Psiphon.
Entry+exit observation.

@@
 
+When domain fronting is combined with Tor,
+the CDN or web service effectively becomes
+what Tor calls a ``guard node,''
+a host with a privileged network position that can observe
+the ciphertext entering the network.
+One consequence of this fact is that Google (for example)
+knows the IP addresses of everyone using the circumvention system,
+just as if it were those users' ISP.
+Another consequence is that the CDN or web service gets
+to observe and correlate both entry and exit traffic,
+in the special case where the target of the communication
+also lies on the same CDN or web service.
+For example, a user fronting through App Engine and
+browsing YouTube reveals both their entry and exit traffic to Google,
+which may attempt through traffic analysis to determine
+which entry packets correspond to which exit packets.
+The problem is hard to counter, because the front domain needs
+to be a popular destination in order to have high collateral damage,
+but popular destinations by definition tend to be visited a lot.
+% Possible countermeasure is traffic fingerprinting resistance
+% like what mjuarez is working on, mostly orthogonal to circumvention.
+
 % Edge servers within the censored region.
@@
 
+% Psiphon
+
 \subsection{Other deployment scenarios}
@@
 all it sees are many connections from App Engine.
-In effect, App Engine and the web app become what Tor calls a ``guard node,''
-a privileged relay that takes the first hop in the chain of relays.
-Because Tor is encrypted and integrity-protected, neither App Engine nor the app operators
-are able to read or alter users' communications, but being on path enables them
-to do things like measure packet timing patterns.
 

### 2014-07-08 docs/meek.tex
Put "domain fronting" in the title.
Use IEEE style.
Line break in title.
Nobody will care about the Heartbleed gap.

@@
-\documentclass{article}  
+\documentclass[conference]{IEEEtran}
 \usepackage{graphicx}
@@
 
-\title{Blocking-resistant communication through high-value web services}
+\begin{document}
+
+\title{Blocking-resistant communication\\through domain fronting}
+
 \author{David Fifield, Chang Lan}
-
-\begin{document}
+\author{
+\IEEEauthorblockN{David Fifield and Chang Lan}
+\IEEEauthorblockA{University of California, Berkeley}
+}
 
@@
 \caption{Number of concurrent users using the meek transport,
-as reported by the Tor Metrics Portal.
-The gap between April~14 and April~22 is when the Tor bridge authority
-was down because of the Heartbleed OpenSSL vulnerability~\cite{heartbleed}, and wasn't collecting statistics.}
+as reported by the Tor Metrics Portal.}
 \label{fig:clients}
@@
 
-\section{Acknowledgments}
+\section*{Acknowledgments}
 
@@
 
-\bibliographystyle{plain}  
+\bibliographystyle{IEEEtran}
 \bibliography{meek}

### 2014-07-14 docs/clients-meek.R
Use points, not lines, in the client graph.

@@ -9,7 +9,7 @@ daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
 p <- ggplot(data, aes(x=date, y=clients))
 # p <- p + geom_vline(xintercept=as.numeric(as.Date(c("2014-02-18", "2014-04-11", "2014-04-18", "2014-04-25", "2014-05-07", "2014-05-08"))), color="red")
-p <- p + geom_line() + xlab("Date") + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NA) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8))
+p <- p + geom_point() + xlab("Date") + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NA) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8))
 ggsave("clients-meek.pdf", width=5, height=2, units="in")
 
 # 2014-02-18 [tor-qa] Please test experimental bundles with meek transport (3.5.2.1-meek-1)

### 2014-07-15 docs/meek.tex
Ack Johanna from ICSI Notary.
Rewrite abstract with more emphasis on fronting.

@@
 \begin{abstract}
-We describe meek, a blocking-resistant Internet communication system for censorship circumvention.
-meek uses HTTP as a mechanism for transporting data, but it is not a steganographic HTTP transport;
-rather, it relies on HTTPS to hide the contents of communications from a censor.
-Communications are proxied through a web service that may itself be blocked by the censor:
-``domain fronting''---in which the domain name used in the (censor-visible)
-DNS request and TLS server name extension doesn't match the name in the (censor-invisible)
-HTTP host header---enables communication that is apparently with an allowed host
-but actually with a forbidden host.
+We describe ``domain fronting,'' an application-layer technique
+for HTTPS
+that hides the remote endpoint of a communication
+for the purpose of censorship circumvention.
+Fronting enables a communication stream that is apparently with an allowed domain,
+but actually with a forbidden domain.
+The technique uses different domain names are used in different
+parts of an HTTP request.
+One domain is used on the ``outside''---in the DNS request and
+TLS Server Name Indication---while another domain is used
+on the ``inside''---the HTTP Host header, invisible to the
+censor under HTTPS encryption.
+A variety of difficult-to-block web services, such as content delivery networks
+and Google App Engine, ignore the outside of an HTTPS request
+and dispatch it internally according to the Host header:
+their frontend servers effectively provide a front,
+behind which any domain on their network may be accessed
+without revealing the destination to the censor.
+If a censor is unable to identify which traffic is fronted,
+then blocking the traffic means blocking a content delivery network wholesale,
+with resulting expensive collateral damage.
+Fronting has been used successfully for a few years by a circumvention system called GoAgent;
+we provide a systematic examination of its potential and limitations,
+and the results of building an implementation.
 
-Though HTTPS frustrates blocking by hiding the underlying communication,
-differences in TLS implementations give rise to distinguishing features
-that may be used to block circumvention traffic.
-We describe how we use a web browser as a tool for making HTTPS requests,
-so that the TLS signature of circumvention traffic resembles that of ordinary web browsing.
-We present other, more subtle traffic characteristics that may enable blocking,
-and identify potential countermeasures to such blocking.
+We have implemented a system called meek,
+a pluggable transport for Tor.
+meek combines domain fronting with a simple encoding of a bidirectional byte stream
+as HTTPS requests and responses.
+A censored client using meek makes a series of HTTPS requests
+that appear to be destined to an allowed domain,
+but which actually arrive at a special web server on a Tor relay.
+The web server decodes the requests, feeds their data into the Tor network,
+and sends back any downstream data encoded as HTTPS responses.
+We describe our experience deploying meek to Tor users.
+meek, or systems inspired by it,
+has been adopted by other circumvention systems including Lantern and Psiphon.
 
-We describe our experience implementing meek as a pluggable transport for Tor,
-and the results of an initial experimental deployment.
+Hiding the endpoint and obscuring byte patterns are important parts of blocking-resistant communication,
+but there are other, more subtle considerations.
+We describe what we have done to disguise other traffic ``tells'' in meek,
+such as using a web browser to make HTTPS requests
+for a believable TLS fingerprint.
+We argue that these measures increase the censor's effort
+beyond simple one-shot techniques such as IP address blocking, and into
+the realm of more expensive, less reliable statistical tests.
 \end{abstract}
@@
 % Rod Hynes and Michael Hull of Psiphon.
+% Johanna Amann for getting the fraction of SNI from ICSI notary:
+%   https://trac.torproject.org/projects/tor/ticket/12208#comment:5
 

### 2014-07-15 docs/meek.tex
Note on why you have to be a CDN customer.
Make the arch diagram use the whole width.
Say "address blocking" instead of "endpoint blocking."

@@
 
+% CDNs don't route just anywhere---you have to be a customer.
+
 \section{Background and related work}
@@
 Broadly speaking, there are two main challenges to proxy-based circumvention:
-blocking by content and blocking by endpoint.
+blocking by content and blocking by address.
+Blocking by content is based on \emph{what you are saying},
+and blocking by address is based on \emph{whom you are speaking to},
+A skilled censor will do both, and effective circumvention requires meeting both challenges.
 A content-blocking censor inspects packets and payloads,
@@
 from traffic the censor wishes to allow.
-Blocking by endpoint is based on \emph{whom you are speaking to},
-and blocking by content is based on \emph{what you are saying}.
-A skilled censor will do both, and effective circumvention requires meeting both challenges.
-An endpoint-blocking censor forbids all communication with certain
+An address-blocking censor forbids all communication with certain
 addresses, for example IP addresses and domain names, whatever the contents may be.
-The challenge of endpoint blocking is met by making it difficult for the censor to learn proxy addresses;
+The challenge of address blocking is met by making it difficult for the censor to learn proxy addresses;
 by having overwhelmingly many proxies;
@@
 
-The other grand challenge of proxy-based circumvention is endpoint blocking,
+The other grand challenge of proxy-based circumvention is address blocking,
 against which there have been a few approaches proposed.
@@
 
-Flash proxy~\cite{flashproxy} attempts to address endpoint blocking by
+Flash proxy~\cite{flashproxy} resists address blocking by
 conscripting web users as temporary proxies. Proxies last only as long as a web
@@
 even if one of them is blocked, there will soon be another to replace it.
-Flash proxy's approach to endpoint blocking is in a sense
+Flash proxy's approach to address blocking is in a sense
 the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
@@
 There exists a prototype transport that attempts to get both
-content-based and endpoint-based blocking resistance by obfuscating traffic
+content-based and address-based blocking resistance by obfuscating traffic
 with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \label{fig:architecture}
-\end{figure}
+\end{figure*}
 
@@
 The practice of routing traffic through a web service with domain fronting
-defeats both endpoint-based blocking and active scanning.
+defeats both address-based blocking and active scanning.
 The endpoint (which appears to be the front domain; e.g. www.google.com)
@@
 Active scanning is defeated because if the censor accesses the same
-endpoint as the client, all they see is a web page served by the front domain.
+domain as does the client, all they see is a web page served by the front domain.
 Even though the censor knows some traffic is being fronted,

### 2014-07-15 docs/meek.tex
Comment out obfs-flash.

@@
 but inside the WebSocket framing is the ordinary Tor protocol.
-There exists a prototype transport that attempts to get both
-content-based and address-based blocking resistance by obfuscating traffic
-with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
-However it is limited because it is not
-possible to obfuscate the outermost WebSocket layer;
-the censor could decide simply to block all WebSocket.
+% There exists a prototype transport that attempts to get both
+% content-based and address-based blocking resistance by obfuscating traffic
+% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
+% However it is limited because it is not
+% possible to obfuscate the outermost WebSocket layer;
+% the censor could decide simply to block all WebSocket.
 

### 2014-07-15 docs/meek.tex
CloudTransport.

@@
 
-% CloudTransport~\cite{cloudtransport}
+CloudTransport~\cite{cloudtransport} uses cloud storage, for example Amazon~S3,
+as a communication channel by encoding sends and receives as reads and writes to shared remote files.
+CloudTransport has much in common with domain fronting:
+it hides the true endpoint of a communication with HTTPS,
+and sends traffic through a domain with high collateral damage.
+In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
+is hidden in the path rather than the Host header.
+For example, in an example S3 URL
+\begin{NoHyper}\url{https://s3.amazonaws.com/bucketname/filename}\end{NoHyper},
+the censor only gets to ``see'' the generic domain part, \begin{NoHyper}\url{s3.amazonaws.com}\end{NoHyper}.
+The path component \begin{NoHyper}\url{/bucketname/filename}\end{NoHyper},
+which would reveal that CloudTransport is being used,
+cannot be used for blocking because it is encrypted in HTTPS.
 

### 2014-07-16 docs/meek.tex
Typo.
Make the ciphersuite figure take the whole width.
Might cut this figure.
Psiphon.

@@
 
+Psiphon~\cite{psiphon} is a network of many one-hop proxies,
+with encryption and traffic obfuscation between client and server.
+Psiphon uses domain fronting based on meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
+
 % Lantern
-% Psiphon
 % Infranet
@@
 
-\begin{figure}
-
+\begin{figure*}
+\centering
 \begin{subfigure}[t]{0.30\textwidth}
@@
 \label{fig:ciphersuites}
-\end{figure}
+\end{figure*}
 
@@
 records meek's traffic.
-In contract, normal users may not have persistent connections to Google. For example, a user may search a keyword on
+In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
 Google, click a result, and then close the tab that displays search results. The browser may close the 

### 2014-07-16 docs/meek.tex
Lantern.
Start a paragraph on Akamai.

@@
 Psiphon uses domain fronting based on meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
-
-% Lantern
+Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
+proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
+Lantern~1.4 is planned to use domain fronting inspired by meek~\cite{lantern-1.3.1}.
+
 % Infranet
@@
 
+The collateral damage of blocking Akamai is enormous: in 2010 it carried 15--20\% of all web traffic~\cite{akamai}.
+
 The code that runs on App Engine is very simple.

### 2014-07-16 docs/meek.tex
Typo.

@@
 payloads are indistinguishable from a uniformly random byte stream.
-Classic example of look-like-nothing
+Classic examples of look-like-nothing
 protocols are obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},

### 2014-07-16 docs/meek.tex
Note to note GoAgent's non-workingness.
Some more on active probing.

@@
 looking, for example, for forbidden protocols or keywords.
+Content-based blocking is sometimes called deep packet inspection (DPI).
 Content-based blocking is countered by obfuscation:
@@
 
-To the above challenges we may add the related challenge of active scanning for proxies.
-Though a circumvention protocol may be difficult to identify on the wire,
-it may nevertheless be easy to scan for servers that speak the protocol,
-and thereafter block the server by its address.
+To the above challenges we may add the related challenge of active probing.
+An active-probing censor tries to connect to a server using a circumvention tool
+as if it were an ordinary client.
+If the connection is successful, the server can be blacklisted.
+Active probing is a very precise means of identifying a server as belonging to a circumvention system.
 Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
 Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
-by actively scanning destination addresses to see if they speak the Tor protocol.
+by issuing followup scans to observed client connections to see
+whether a server speaks the Tor protocol.
 The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
@@
 Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.
+
+% GoAgent not working since June 2014.
 

### 2014-07-16 docs/meek.tex
Better phrasing.

@@
 blocking by content and blocking by address.
-Blocking by content is based on \emph{what you are saying},
-and blocking by address is based on \emph{whom you are speaking to},
+Blocking by content is based on \emph{what you say},
+and blocking by address is based on \emph{whom you talk to}.
 A skilled censor will do both, and effective circumvention requires meeting both challenges.

### 2014-07-16 docs/meek.tex
Dust.
Cite TapDance.

@@
 and sends it over VoIP to a proxy which decodes and forwards it to the destination.
+Dust~\cite{dust} uses encryption to hide static byte patterns and then
+shapes statistical features such as packet length and byte frequency to
+match given distributions.
 fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings that match a given regular expression,
@@
 % Ultrasurf
-% Dust
 
@@
 
-Decoy routing~\cite{decoyrouting} is a technique that puts
+Decoy routing~\cite{decoyrouting}, also called end-to-middle proxying,
+is a technique that puts
 proxies in the middle of network paths, rather than at the ends.
-Realizations of decoy routing include Telex~\cite{telex}
-and Cirripede~\cite{cirripede}.
-In decoy routing, friendly ISPs deploy special \emph{decoy} routers that lie
+Realizations of decoy routing include Telex~\cite{telex},
+Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
+In decoy routing, friendly ISPs deploy special routers that lie
 on network paths between censored users and uncensored Internet destinations.

### 2014-07-17 docs/meek.tex
Make the traffic characteristic graphs fit again.
Still need some work.
Fix some wording.

@@
 but actually with a forbidden domain.
-The technique uses different domain names are used in different
-parts of an HTTP request.
+The technique uses different domain names at different communication layers.
 One domain is used on the ``outside''---in the DNS request and
-TLS Server Name Indication---while another domain is used
+TLS Server Name Indication---while another is used
 on the ``inside''---the HTTP Host header, invisible to the
@@
 \label{fig:len}
-\end{figure}
+\end{figure*}
 
@@
 \centering
-\includegraphics[width=0.7\textwidth, angle=270]{figs/connections-google.eps}
+\includegraphics[height=\linewidth, angle=270]{figs/connections-google.eps}
 \caption{Histogram of each user's connections in the 10-minute window}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figs/conns.eps}
+\includegraphics[width=\linewidth]{figs/conns.eps}
 \caption{Concurrent HTTPS connections over time. We measure the trace for the Tor Browser Bundle and Firefox/Chrome extensions.}
@@
 \label{fig:duration}
-\end{figure}
+\end{figure*}
 

### 2014-07-17 docs/meek.tex
Include fronting figure.

@@
 which is our custom web app that aids in circumvention.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth]{fronting}
+\caption{
+Domain fronting uses different domain names at different layers of communication.
+At the plaintext layers visible to the censor---the DNS request and the
+TLS Server Name Indication---appears
+the front domain \mbox{\textbf{allowed.example}}.
+At the HTTP layer, unreadable to the censor but meaningful to the CDN or web service,
+is the actual destination \mbox{\textbf{forbidden.example}}.
+}
+\label{fig:fronting}
+\end{figure}
 

### 2014-07-21 docs/meek.tex
Wording.
More abstract tweaking.

@@
 censor under HTTPS encryption.
-A variety of difficult-to-block web services, such as content delivery networks
-and Google App Engine, ignore the outside of an HTTPS request
-and dispatch it internally according to the Host header:
-their frontend servers effectively provide a front,
-behind which any domain on their network may be accessed
-without revealing the destination to the censor.
-If a censor is unable to identify which traffic is fronted,
-then blocking the traffic means blocking a content delivery network wholesale,
+We identify a number of hard-to-block web services,
+like content delivery networks and Google's infrastructure,
+that ignore the outside of an HTTPS request
+and dispatch it internally according to the Host header.
+The effect is that a user may communicate with any domain within the web service,
+while appearing to communicate with any other domain.
+If a censor is unable otherwise to distinguish fronted and non-fronted traffic,
+then blocking circumvention traffic means blocking the whole web service,
 with resulting expensive collateral damage.
-Fronting has been used successfully for a few years by a circumvention system called GoAgent;
-we provide a systematic examination of its potential and limitations,
-and the results of building an implementation.
-
-We have implemented a system called meek,
+
+We have implemented domain fronting in a system called meek,
 a pluggable transport for Tor.
-meek combines domain fronting with a simple encoding of a bidirectional byte stream
-as HTTPS requests and responses.
-A censored client using meek makes a series of HTTPS requests
-that appear to be destined to an allowed domain,
+meek combines fronting with a proxy server that encodes a TCP stream
+as a sequence of HTTP requests and responses.
+The meek server's external interface is that of an ordinary web server.
+Communication with it is enabled through domain fronting.
+The server receives requests, decodes them, and feeds their payloads into a Tor relay,
+and returns downstream data in the HTTP response.
+A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
 but which actually arrive at a special web server on a Tor relay.
-The web server decodes the requests, feeds their data into the Tor network,
-and sends back any downstream data encoded as HTTPS responses.
-We describe our experience deploying meek to Tor users.
-meek, or systems inspired by it,
+meek, or something based on it,
 has been adopted by other circumvention systems including Lantern and Psiphon.

### 2014-07-22 docs/meek.tex
Ack Arlo.
Big revision of introduction.
Might move some of this into a later section.

@@
 \def\meekserver{\mbox{meek-server}}
+\def\urll#1{\begin{NoHyper}\url{#1}\end{NoHyper}}
 
@@
 We describe what we have done to disguise other traffic ``tells'' in meek,
-such as using a web browser to make HTTPS requests
+such as using a real web browser to make HTTPS requests
 for a believable TLS fingerprint.
@@
 Workplaces, schools, and governments use technical and social means
-to prevent access to certain information by the network users under their control.
+to prevent access to information by the network users under their control.
 In response, those users use technical and social means
@@
 
-In this paper we describe the design and deployment of meek,
-a censorship-resistant communication system that aims at defeating
-known technical means of censorship.
-meek tunnels traffic through HTTP, but does not attempt to look like plaintext HTTP;
-it uses HTTPS to hide the contents of communications
-while relaying them through a third-party web services that it itself hard to block.
-meek is implemented as a Tor pluggable transport~\cite{pt}.
-We have done an initial deployment of the system and it is in use
-by a small number of users.
-
-``Domain fronting'' is the term we use for one of the key techniques used by meek.
-Domain fronting is the use of different domain names at different layers of the network stack.
-In the DNS query and TLS server name indication (SNI)~\cite[Section~3]{rfc6066},
-which are visible to the censor, one domain name (the ``front domain'') appears;
-while in the HTTP Host header~\cite[Section~14.23]{rfc2616},
+What we as circumventors have in our favor is the censor's
+distaste for ``collateral damage,''
+accidental overblocking committed in the course of trying to censor something else.
+One way to win against the censor is to entangle circumvention traffic
+with ordinary Internet traffic in a way that both must be blocked together
+or not at all.
+If the ordinary traffic is important enough,
+above the censor's tolerance for overblocking,
+then the circumvention traffic will get through.
+
+In this paper we describe ``domain fronting,'' a general-purpose technique
+based on HTTPS that hides the true destination of a communication
+from a censor.
+Fronting works with many web services that host multiple domain names
+behind an HTTPS frontend server.
+These include such high--collateral damage infrastructure as
+big content delivery networks (CDNs)
+and Google's panoply of services---a nontrivial fraction of the web.
+Domain fronting can be used as a means of tunneling traffic
+to a general-purpose proxy,
+so it is not limited to HTTPS, nor to the domains of any specific web service.
+
+The key idea of domain fronting is using
+different domain names at different layers of communication.
+In an HTTPS request, the destination domain name appears
+in three places relevant to the discussion:
+the DNS query,
+the TLS Server Name Indication (SNI) extension~\cite[Section~3]{rfc6066},
+and the HTTP Host header~\cite[Section~14.23]{rfc2616}.
+Normally, the same domain name appears in all three places.
+In a domain-fronted request,
+the DNS query and SNI carry one name (the ``front domain''),
+while the HTTP Host header,
 which is hidden from censor by HTTPS encryption,
-a different name (the actual destination) appears.
-Domain fronting works in systems that use the Host header in order to
-multiplex many domain names behind one HTTPS frontend;
-among these systems are Google's infrastructure and the
-CloudFlare content delivery network.
-Domain fronting can also work using only an IP address in place of
-a front domain. In this case there is no DNS query and no SNI in the TLS layer,
-but the actual destination still appears in the Host header.
-Domain fronting has been used successfully for years by GoAgent~\cite{goagent}
-(which uses a bare IP address without SNI)
-and by one of the rendezvous methods of flash proxy~\cite{flashproxy}.
-In the examples in this paper, the front domain is www.google.com
-and the actual hidden destination domain is meek-reflect.appspot.com,
-which is our custom web app that aids in circumvention.
+has a different name (the actual destination).
 
@@
 
-meek may be regarded as a steganographic transport only in that it must blend in with other HTTPS traffic.
-Tunneling inside HTTPS greatly eases the steganography problem:
-It's not necessary to generate plausible HTTP, only plausible TLS,
-because TLS payloads are encrypted, and to a first approximation all encrypted payloads look alike.
-We need only make sure that the TLS handshake and other meta-attributes of the connection are not uniquely fingerprintable.
-Section~\ref{sec:browserextension} describes the use of a web browser extension as a instrument for making HTTPS requests,
-so things like the TLS handshake, DNS lookup, and TCP connection reuse match those of a browser as closely as possible.
-Of course, there are more subtle considerations that go into
-making a circumvention HTTPS stream look like an allowed HTTPS stream,
-things like packet size and timing, and duration of TCP connections.
-These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.
-
-For concreteness, and because it is what we have deployed so far,
-the examples in this paper will use Google and App Engine as the specific
-third-party web service used for circumvention.
-Other systems that support domain fronting may be substituted for Google,
-and other alternative deployments are discussed in Section~\ref{sec:otherdeployment}.
-
-% CDNs don't route just anywhere---you have to be a customer.
+Neither the DNS nor the SNI can be blocked without
+collaterally blocking the front domain.
+The Host header is unknown to the censor,
+but known to the server receiving the HTTPS request,
+which uses the header to internally route the request to its destination.
+No traffic ever reaches the front domain,
+which may be oblivious to the circumvention.
+
+A Wget command shows domain fronting in action
+on Google's infrastructure.
+An HTTPS request for \urll{www.google.com} has a Host header for
+\urll{maps.google.com}, and the HTML in the response is that of Google Maps.
+
+\noindent
+\begin{quote}
+\usefont{U}{cmtt}{m}{n}%
+\$ wget -q -O - https://www.google.com/ \char`\\\\
+\strut~~~~--header 'Host: maps.google.com' | \char`\\\\
+\strut~~~~grep -o '<title>.*</title>'\\
+<title>Google Maps</title>
+\end{quote}
+
+Domain fronting works with CDNs because a CDN's frontend server
+(called an ``edge server''),
+on receiving a request for a resource not already cached,
+forwards the request to the domain in the Host header
+(the ``origin server'').
+(There are other ways for CDNs to work, but this ``origin pull''
+configuration is common.)
+% The certificate you get may be that of the front domain,
+% or may be a generic shared domain.~\cite{httpsincdn}
+The CDN's edge server won't forward requests just anywhere---it
+has to be to the domain of a customer.
+This means that in order to host a proxy,
+one has to create an account and pay for bandwidth.
+
+Fronting works with Google because Google App Engine, a web application platform,
+can host a simple ``reflector'' application that emulates
+an origin-pull CDN, simply forwarding every request to another server.
+Though App Engine's domain \urll{appspot.com}
+may be blocked because it can trivially be used to host a proxy,
+it can be fronted by essentially any Google domain, for example
+\urll{google.com}, \urll{gmail.com}, or \urll{googleapis.com}.
+App Engine charges for bandwidth,
+though it has a low-bandwidth free tier.
+% See Section~\ref{sec:deployment} for more discussion on deployment.
+
+A variation is ``domainless'' fronting,
+in which there is no DNS request and no SNI extension.
+It looks to the censor
+like the user is browsing an HTTPS site by its IP address,
+or using an old browser that doesn't support SNI.
+Domainless fronting can be useful when there is no front domain
+with sufficiently high collateral damage.
+The censor is faced with the choice of blocking an entire IP address,
+blocking requests without SNI,
+or finding some more subtle and expensive test to distinguish
+circumvention traffic.
+
+To our knowledge,
+the earliest application of domain fronting to circumvention
+was by GoAgent~\cite{goagent},
+a tool based on App Engine and
+once widely used in China.
+Fronting has been used with success since 2013~\cite{flashproxy-reg-appspot}
+for the rendezvous component of another transport called flash proxy.
+GoAgent and the flash proxy rendezvous are the most direct
+inspirations of this work.
+
+We have developed domain fronting into a system called meek,
+a full-fledged circumvention transport,
+implemented as a pluggable transport~\cite{pt} for Tor.
+meek combines fronting with an HTTP-based tunneling proxy:
+upstream data are transformed into a sequence of HTTP requests,
+which are fronted in order to reach a proxy server.
+The server decodes the requests and feeds their payloads
+into a local Tor relay.
+Downstream data received from the Tor relay
+are returned to the client as HTTP responses
+through the same fronted channel.
+meek's architecture appears in Figure~\ref{fig:architecture}.
+Section~\ref{sec:architecture} describes meek's workings in detail.
+
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{architecture}
+\caption{
+System architecture.
+The Google frontend server is the server that dispatches requests to different services depending on the Host header.
+Components that are new in our system are outlined in blue.
+The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
+}
+\label{fig:architecture}
+\end{figure*}
+
+meek has been built into an alpha version of Tor Browser,
+and has seen use by a small number of users.
+Our deployment uses Google App Engine,
+with the hidden actual domain \urll{meek-reflect.appspot.com}
+hidden by the front \urll{www.google.com}.
+Section~\ref{sec:deployment} discusses other systems meek can work with
+and other deployment scenarios.
+In addition to the Tor pluggable transport,
+systems based on meek are now in use by other circumvention systems
+including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.
+
+% meek is designed to have features attractive in a circumvention transport.
+% It is easy to use, not requiring the configuration of any bridge addresses.
+% In Tor Browser, users need only select ``meek''
+% from a pulldown menu in order to use it.
+% It resists blocking by address and by content,
+% Section~\ref{sec:security}
+
+Domain fronting and HTTPS take care of two big circumvention challenges,
+namely hiding the destination and obscuring the contents of the message.
+There remain other, more subtle, meta-attributes of communication
+that could serve as a basis for blocking.
+For example, the handshake is a fingerprintable part of TLS.
+Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
+in order that meek's TLS and HTTPS characteristics
+match those of a browser as closely as possible.
+One of our goals for meek is to force the censor
+to employ more sophisticated, expensive, and error-prone statistical tests
+to classify traffic as allowed or prohibited,
+rather than simple domain blacklists or deep packet inspection;
+to force the frontier of censorship
+to be a frontier not of simple in-line packet filters,
+but of probabilities and false positives.
+A preliminary analysis of meek's resistance to detection
+based on traffic characteristics like packet size and timing
+appears in Section~\ref{sec:trafficstatistics}.
+The analysis is based on comparing traffic traces of meek
+with samples of HTTPS traffic at an Internet router.
 
 \section{Background and related work}
-
-% In response to Internet censorship, many research papers and pragmatic systems
-% such Freegate, Psiphon, and Lantern have explored the design space of censorship
-% circumvention. All these schemes are based on a simple idea: deploy a set of
-% proxies outside the censor's domain, and let the user connect to one of them
-% which can pass data on to the true destination for the user.
 
@@
 and delivered to its destination by a specialized app running on App Engine.
+GoAgent uses the ``domainless'' fronting model without SNI for most target domains.
 GoAgent requires users to upload a personal copy of the server code to App Engine,
@@
 
+We assume that the censor cannot observe the communication
+once it reaches the third-party infrastructure; i.e.,
+that no further obfuscation is needed once fronting is accomplished.
+% What about in-country edge servers; seems to work.
+
 \section{Architecture}
+\label{sec:architecture}
 
@@
 \end{enumerate}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{architecture}
-\caption{
-System architecture.
-The Google frontend server is the server that dispatches requests to different services depending on the Host header.
-Components that are new in our system are outlined in blue.
-The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
-}
-\label{fig:architecture}
-\end{figure*}
 
@@
 \section{Security}
+\label{sec:security}
 
@@
 % Rod Hynes and Michael Hull of Psiphon.
+% Ox from Lantern.
 % Johanna Amann for getting the fraction of SNI from ICSI notary:
 %   https://trac.torproject.org/projects/tor/ticket/12208#comment:5
+% Arlo Breault (flashproxy-reg-appspot)
 

### 2014-07-22 docs/meek.tex
Use my NoHyper macro.

@@
 For example, a censored client may ask a translation service to
-translate a web page at \begin{NoHyper}\url{http://proxy.example.com/...}\end{NoHyper},
-where ``\begin{NoHyper}\url{...}\end{NoHyper}''
+translate a web page at \urll{http://proxy.example.com/...},
+where ``\urll{...}''
 stands for the data payload that the client wishes to send---data are embedded in the URL.
@@
 For example, in an example S3 URL
-\begin{NoHyper}\url{https://s3.amazonaws.com/bucketname/filename}\end{NoHyper},
-the censor only gets to ``see'' the generic domain part, \begin{NoHyper}\url{s3.amazonaws.com}\end{NoHyper}.
-The path component \begin{NoHyper}\url{/bucketname/filename}\end{NoHyper},
+\urll{https://s3.amazonaws.com/bucketname/filename},
+the censor only gets to ``see'' the generic domain part, \urll{s3.amazonaws.com}.
+The path component \urll{/bucketname/filename},
 which would reveal that CloudTransport is being used,

### 2014-07-22 docs/meek.tex
Straight apostrophes in shell command.
Cite obfs4.

@@
 \usepackage{hyperref}
+\usepackage{textcomp}
 
@@
 \$ wget -q -O - https://www.google.com/ \char`\\\\
-\strut~~~~--header 'Host: maps.google.com' | \char`\\\\
-\strut~~~~grep -o '<title>.*</title>'\\
+\strut~~~~--header \textquotesingle{}Host: maps.google.com\textquotesingle{} | \char`\\\\
+\strut~~~~grep -o \textquotesingle{}<title>.*</title>\textquotesingle{}\\
 <title>Google Maps</title>
@@
 whether a server speaks the Tor protocol.
-The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
-and in this work.
+The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit},
+obfs4~\cite{obfs4},
+and this work.
 

### 2014-07-23 docs/meek.tex
Big revision of related work.

@@
 
+For those familiar with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance},
+domain fronting can be understood as
+``decoy routing at the application layer.''
+A fuller comparison with decoy routing appears in Section~\ref{sec:related-work}.
+
 A Wget command shows domain fronting in action
@@
 
-A variation is ``domainless'' fronting,
+A variation on fronting is ``domainless'' fronting,
 in which there is no DNS request and no SNI extension.
@@
 once widely used in China.
-Fronting has been used with success since 2013~\cite{flashproxy-reg-appspot}
-for the rendezvous component of another transport called flash proxy.
+Fronting has been used with success since 2013
+for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
 GoAgent and the flash proxy rendezvous are the most direct
@@
 \caption{
-System architecture.
+Architecture of meek.
 The Google frontend server is the server that dispatches requests to different services depending on the Host header.
@@
 \section{Background and related work}
-
-Broadly speaking, there are two main challenges to proxy-based circumvention:
+\label{sec:related-work}
+
+Broadly speaking, there are two main challenges in circumvention:
 blocking by content and blocking by address.
@@
 and blocking by address is based on \emph{whom you talk to}.
-A skilled censor will do both, and effective circumvention requires meeting both challenges.
 A content-blocking censor inspects packets and payloads,
@@
 Content-based blocking is sometimes called deep packet inspection (DPI).
-Content-based blocking is countered by obfuscation:
-making circumvention traffic difficult to distinguish
-from traffic the censor wishes to allow.
 An address-blocking censor forbids all communication with certain
 addresses, for example IP addresses and domain names, whatever the contents may be.
-The challenge of address blocking is met by making it difficult for the censor to learn proxy addresses;
-by having overwhelmingly many proxies;
-or by colocating proxies with high-value services so that both must be blocked or both allowed.
-
-To the above challenges we may add the related challenge of active probing.
-An active-probing censor tries to connect to a server using a circumvention tool
-as if it were an ordinary client.
-If the connection is successful, the server can be blacklisted.
-Active probing is a very precise means of identifying a server as belonging to a circumvention system.
+A skilled censor will use both means of censorship,
+and effective circumvention requires countering both.
+
+To the above challenges we may add a related one, active probing.
+An active-probing censor does not merely passively observe traffic;
+it injects its own traffic,
+acting as if it were an ordinary client and connecting to suspected
+proxy servers to see how they respond.
+If the connection is successful, the server can then be blacklisted.
+Active probing is a precise means of identifying a server as belonging to a circumvention system,
+even when a protocol is hard to classify on the wire.
 Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
@@
 whether a server speaks the Tor protocol.
-The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit},
-obfs4~\cite{obfs4},
-and this work.
-
-Traffic obfuscation has been approached in many different ways,
-which may be classified into two general techniques.
-The first technique is to look unlike
+The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
+and obfs4~\cite{obfs4},
+
+There are two general strategies for countering DPI.
+The first is to make traffic look unlike
 anything forbidden by the censor; that is, fail to match a blacklist. The second is
@@
 payloads are indistinguishable from a uniformly random byte stream.
-Classic examples of look-like-nothing
+Well-traveled look-like-nothing
 protocols are obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
 which have been Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
+They both work by superenciphering a stream, using a key exchange that has no plaintext components.
 ScrambleSuit~\cite{scramblesuit} is like obfs3 in the
-content of its payloads, but it takes additional steps to obscure its traffic signature
-(packet lengths and timing), and is designed to resist active scanning
-(the proxy server remains silent until the client proves knowledge of a shared
-secret).
-
-The other category of obfuscation contains transports that take the steganographic approach: look like
-something the censor doesn't block. StegoTorus~\cite{stegotorus}
-encodes traffic to look like a cover protocol, such as unencrypted HTTP,
-using special-purpose encoders.
+content of its payloads, but additionally obscures its traffic signature
+(packet lengths and timing), and is designed to resist active probing.
+A ScrambleSuit server will accept a TCP connection but not send anything
+until the client proves knowledge of shared secret, depriving the censor
+of an easy distinguisher.
+obfs4~\cite{obfs4}
+(which despite the name has more in common with ScrambleSuit than with obfs2 and obfs3)
+builds on ScrambleSuit with more efficient cryptography and an authenticated handshake.
+
+The other strategy against content blocking is the steganographic approach: look like
+something the censor doesn't block.
+fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings
+that match a given regular expression,
+for example a regular-expression approximation of HTTP,
+in order to match a firewall's whitelist.
+StegoTorus~\cite{stegotorus}
+encodes traffic to look like a cover protocol
+using a variety of special-purpose encoders.
 Code Talker
 Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
-FreeWave~\cite{freewave} encodes a digital stream into an acoustic signal
-and sends it over VoIP to a proxy which decodes and forwards it to the destination.
+FreeWave~\cite{freewave} encodes a stream as an acoustic signal
+and sends it over VoIP to a proxy, which decodes it and forwards it to the destination.
 Dust~\cite{dust} uses encryption to hide static byte patterns and then
-shapes statistical features such as packet length and byte frequency to
+shapes statistical features such as packet lengths and byte frequencies so that they
 match given distributions.
-fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings that match a given regular expression,
-in order to match a firewall's whitelist or avoid matching a blacklist.
-
-Houmansadr et~al.~\cite{parrot} evaluate ``parrot'' systems that imitate a particular implementation of a protocol
-and conclude that unobservability by imitation is a ``fundamentally
-flawed approach.''
+
+Houmansadr et~al.~\cite{parrot} evaluate ``parrot'' systems that imitate another protocol
+and conclude that unobservability by imitation is fundamentally flawed.
 To fully mimic a complex and sometimes proprietary protocol like Skype
-is difficult in that the system must imitate not only the protocol's normal operation, but also its reaction to errors,
-its typical traffic patterns, and quirks of common implementations.
+is difficult,
+because the system must imitate not only the normal operation of the protocol,
+but also its reaction to errors,
+its typical traffic patterns, and quirks of implementations.
 Geddes et~al.~\cite{acks}
 demonstrate that even non-parrot systems may be vulnerable to
-attacks that disrupt covert communication while having little effect
-on legitimate traffic. Their examination is specific to VoIP protocols,
-where packet loss and duplication are acceptable. The censor may
-deliberately drop or inject ACKs in order to disrupt the covert channel, without causing
-much collateral damage.
-
-The other grand challenge of proxy-based circumvention is address blocking,
-against which there have been a few approaches proposed.
-Tor has long faced the problem of its entry relays being blocked. The list of
-relays is public, so it easy to block all of them by IP address. Tor
-bridges~\cite{tor-blocking} are relays that are not universally known, intended
-to serve as entry points for censored users. A database of bridges (BridgeDB) seeks to
-provide a few secret bridges to anyone who asks, while at the same time making it
-difficult to learn the entire list.
-The database is accessible over HTTPS and email.
-The HTTPS interface requires solving a captcha,
-and the email interface responds only to addresses from certain providers, like Gmail,
-that have defenses against bulk account creation.
-BridgeDB has the feature that repeated queries from the same address
-(IP subnet or email address) will receive the same small set of bridges.
-Its resistance to enumeration therefore depends both on
-having a large number of potential bridges,
-and on the censor not being able to control large numbers of IP and email addresses.
-BridgeDB is capable of distributing
-the addresses of obfsproxy and ScrambleSuit bridges.
-The combination
-of careful bridge address disbursement and obfuscated protocols
-gives Tor's system a realistic claim to addressing both challenges of proxy-based circumvention.
+attacks that disrupt circumvention while having little effect
+on ordinary traffic.
+Their examination includes VoIP protocols,
+in which packet loss and duplication are acceptable.
+The censor may, for example, strategically drop certain packets
+in order to disrupt a covert channel, without much harming ordinary VoIP calls.
+
+The other grand challenge of proxy-based circumvention is address-based blocking.
+Tor has long faced the blocking of its entry relays,
+the addresses of which are in a public directory.
+In response, Tor began to reserve a portion of its
+new relays as secret ``bridges''~\cite{tor-blocking}
+whose addresses are not publicly known.
+BridgeDB, the database of secret bridges,
+carefully distributes bridge addresses
+so that anyone can learn a few bridges, but it is hard to learn all of them.
+BridgeDB uses captchas and other rate-limiting measures,
+and over short time periods,
+always returns the same set of bridges to the same requester,
+preventing enumeration by simple repeated querying.
+BridgeDB is also capable of distributing the addresses
+of obfuscated bridges (obfs3 or ScrambleSuit);
+the combination
+of careful bridge address dispersal and obfuscated protocols
+gives Tor's system a realistic claim to addressing both main challenges of circumvention.
 Address distribution appears to be the weaker side of the defense,
 as evidenced by real-world censors' apparent preference for
-blocking bridge addresses over real-time deobfuscation~\cite{foci12-winter}.
+blocking bridge addresses over real-time DPI-based blocking~\cite{foci12-winter}.
 
@@
 conscripting web users as temporary proxies. Proxies last only as long as a web
-user stays on a page, so the pool of proxies is constantly changing;
-even if one of them is blocked, there will soon be another to replace it.
+user stays on a page, so the pool of proxies is constantly changing.
+If one of them is blocked, there is soon another to replace it.
 Flash proxy's approach to address blocking is in a sense
-the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
-we use just one high-value proxy, which shares its fate with network
-infrastructure that is expensive to block.
-A quirk of the browser proxy model is that the proxy connects to the client rather than the other way around.
-The client must be able to receive a TCP connection; in particular it
-may not be behind network address translation~(NAT), which limits flash proxy's usefulness.
-Flash proxy itself does nothing to defend against content blocking.
+the opposite of meek's:
+where flash proxy uses many cheap, disposable, individually blockable proxies,
+meek uses just a few high-value front domains on hard-to-block network infrastructure.
+A quirk of the browser proxy model is that
+the client must be able to receive a TCP connection; in particular it
+must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
+Part of the flash proxy protocol requires the client to send
+a small amount of unblockable data in a process called rendezvous.
+The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
+Flash proxy itself does nothing to defend against DPI.
 Connections between censored clients and browser-based proxies use
-WebSocket, a meta-protocol running on TCP,
+WebSocket, a meta-protocol running on HTTP,
 but inside the WebSocket framing is the ordinary Tor protocol.
@@
 
-Psiphon~\cite{psiphon} is a network of many one-hop proxies,
-with encryption and traffic obfuscation between client and server.
-Psiphon uses domain fronting based on meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
-Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
-proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
-Lantern~1.4 is planned to use domain fronting inspired by meek~\cite{lantern-1.3.1}.
-
-% Infranet
-% Freegate
-% Ultrasurf
-
 A technique known as OSS~\cite{oss} (for
-``online scanning service'') bounces data
-through third-party web services that are capable of making HTTP requests.
-For example, a censored client may ask a translation service to
-translate a web page at \urll{http://proxy.example.com/...},
-where ``\urll{...}''
-stands for the data payload that the client wishes to send---data are embedded in the URL.
-Simply by making the HTTP request, the service sends the client's message.
-The client cannot rely on being able to receive the response to its message in an HTTP response,
-because online scanning services do not in general
-return unmodified the contents of the page they are ordered to retrieve.
-The translation service, for example, returns the page in another language.
-For this reason, the server sends a response message by making
-another reflected HTTP request back to the client, through the same OSS or a different one.
-The need for the client to receive a connection means that OSS has the same problem with NAT that flash proxy does.
-The NAT aspect is the most important way in which our work improves on OSS.
-App Engine is effectively an unblockable OSS that we fully control.
-We can ensure that reflected HTTP bodies are unmodified, and therefore use them to carry traffic
-without having to connect to the client.
+``online scanning service'') bounces messages
+through web services that are capable of making HTTP requests.
+For example, a censored client may ask an HTTPS-based online translation service to
+translate the web page at \urll{http://forbidden.example/}\textsl{data...},
+where ``\textsl{data...}'' is the message the client wishes to send,
+embedded in the URL.
+The translation service requests the URL,
+unwittingly sending the message on behalf of the client.
+OSS shares certain similarities with domain fronting:
+the web service takes the place of the front domain,
+and the destination of the communication is embedded somewhere in an HTTPS query
+rather than in the Host header.
 
@@
 Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
-In decoy routing, friendly ISPs deploy special routers that lie
-on network paths between censored users and uncensored Internet destinations.
+Decoy routing asks friendly ISPs to deploy special routers that lie
+on network paths between censored users and uncensored ``decoy'' Internet destinations.
 Circumvention traffic is ``tagged'' in a way that is detectable only
-by decoy routers, and not by the censor.
-On receiving a tagged communication, the decoy shunts it away from its apparent, \emph{overt destination}
+by the special routers, and not by the censor.
+On receiving a tagged communication, the router shunts it away from its apparent, \emph{overt destination}
 and toward a censored, \emph{covert destination}.
-Domain fronting is similar to decoy routing;
+Domain fronting is similar in spirit to decoy routing;
 think of domain fronting as decoy routing at the application layer.
-In place of a decoy router, domain fronting has a CDN edge server;
+In place of a router, domain fronting has a web service's frontend server;
 in place of the overt destination is the front domain.
@@
 decoy routing uses, for example, a hash embedded in a client nonce,
-while domain fronting uses the HTTP Host header, encrypted within HTTPS.
+while fronting uses the HTTP Host header, encrypted within HTTPS.
+Fronting has the advantage that it doesn't require knowing cooperation by network intermediaries.
 
@@
 and show that the connectivity of the Internet enables
-censors to force network users onto paths that do not include decoys.
+censors to force network users onto paths that do not include participating routers.
 Simulations by Houmansadr et~al.~\cite{nodirectionhome}
@@
 they are many times more costly to the censor,
-especially when decoys are placed strategically.
+especially when participating routers are placed strategically.
 
 CensorSpoofer~\cite{censorspoofer}
-decouples the upstream and downstream channels.
-The client sends upstream data to the CensorSpoofer proxy over a low-bandwidth covert channel such as email.
-At the same time, the client pretends to have an innocuous communication (such as a VoIP call) with an unblocked dummy host.
-The CensorSpoofer proxy sends encrypted UDP data back downstream to the client,
-protecting its true IP address by spoofing the source of all its packets
-so that they appear to come from the dummy host.
-From the censor's point of view, the client is carrying on a conversation only with the dummy host.
-If the dummy is blocked, another can be used in its place,
-as the CensorSpoofer proxy's true IP address remains unknown.
+decouples upstream and downstream data channels.
+The client sends data to a CensorSpoofer proxy over a low-bandwidth covert channel such as email.
+The proxy sends data back over a UDP channel, all the time
+spoofing its source address so the packets appear to originate from some other ``dummy'' host.
+The censor has no IP address to block, because the proxy's true address never appears on the wire.
+Client and server have the challenge of agreeing on a dependable covert upstream channel
+that must itself remain unblocked,
+and the client must carry on a believable UDP conversation with the dummy host
+(the authors suggest a VoIP call).
 
@@
 
-GoAgent~\cite{goagent} is a direct inspiration for our system in its use of App
+GoAgent~\cite{goagent} is a direct inspiration for meek in its use of App
 Engine and Host header--based domain fronting.
-As in our system, traffic is fronted by the Google frontend server
+Traffic is fronted by the Google frontend server
 and delivered to its destination by a specialized app running on App Engine.
 GoAgent uses the ``domainless'' fronting model without SNI for most target domains.
-GoAgent requires users to upload a personal copy of the server code to App Engine,
-which harms usability but requires no central management
-and enables users to stay within bandwidth limits that exist for unpaid apps.
-GoAgent is an HTTP and HTTPS proxy only.
-It works by encapsulating a desired HTTP request, including URL and POST body, if any,
-and uploading the request to App Engine.
-The app unpacks the encapsulated request and directly requests the desired URL using
-App Engine's URL-fetching API.
-The design is simple but has disadvantages, stemming from the web app's
-need to know what URL to request.
-In order to proxy HTTPS, the local GoAgent proxy program does a benign man-in-the-middle
-attack on the browser, which must have previously trusted the GoAgent CA certificate.
-The local proxy program decrypts the HTTPS in order to read from it the HTTP request including the URL.
-When the response comes back, the local proxy re-encrypts it under its own key.
-End-to-end security is lost; an attacker positioned at the web app
-is able to observe and modify all traffic.
-In our system, such an attacker may only deny service or perform traffic analysis on ciphertext.
-Additionally, we allow proxying of any TCP-based traffic, not only HTTP.
+GoAgent doesn't use an additional general-purpose proxy after fronting;
+rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers,
+meaning that GoAgent is limited to carrying HTTP and HTTPS traffic,
+and the contents of all communications are revealed to App Engine.
+Users of GoAgent upload their own personal copy of the proxy code to App Engine,
+which is free of charge as long as they do not exceed a bandwidth quota.
+Use of GoAgent in China was disrupted starting in the beginning of June~2014
+when all Google services (including GoAgent's front domains) were blocked.
+meek over App Engine was similarly affected.
 According to a May 2013 survey~\cite{collateral-freedom},
@@
 
-% GoAgent not working since June 2014.
+Cloud-Entry~\cite{cloud-entry} is somewhat similar to GoAgent.
+It also uses App Engine, but uses a socket API rather than a URL fetch API
+in order to support protocols other than HTTP and HTTPS.
+Cloud-Entry has the same problem with NAT that flash proxy does,
+because the proxy tries to connect back to the client with a socket.
+App Engine kills web requests (and their associated socket connections)
+that take longer than 60~seconds,
+so users must reconnect at least every 60~seconds.
+
+Psiphon~\cite{psiphon} is a network of many one-hop proxies,
+with encryption and traffic obfuscation between client and server.
+Psiphon uses domain fronting based on meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
+Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
+proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
+Lantern~1.4 is planned to use domain fronting inspired by meek~\cite{lantern-1.3.1}.
+
+% Infranet
+% Freegate
+% Ultrasurf
 
@@
 
-\section{Architecture}
+\section{Architecture and protocol of meek}
 \label{sec:architecture}

### 2014-07-23 docs/clients-meek.R
Fix a deprecated R usage.
"Error: Please use minor_breaks = NULL to remove minor breaks in the scale. (Defunct; last used in version 0.8.9)"

@@ -9,7 +9,7 @@ daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
 p <- ggplot(data, aes(x=date, y=clients))
 # p <- p + geom_vline(xintercept=as.numeric(as.Date(c("2014-02-18", "2014-04-11", "2014-04-18", "2014-04-25", "2014-05-07", "2014-05-08"))), color="red")
-p <- p + geom_point() + xlab("Date") + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NA) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8))
+p <- p + geom_point() + xlab("Date") + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NULL) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8))
 ggsave("clients-meek.pdf", width=5, height=2, units="in")
 
 # 2014-02-18 [tor-qa] Please test experimental bundles with meek transport (3.5.2.1-meek-1)

### 2014-07-23 docs/clients-meek.R
Remove "Date" label from clients-meek graph.

@@ -9,7 +9,7 @@ daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
 p <- ggplot(data, aes(x=date, y=clients))
 # p <- p + geom_vline(xintercept=as.numeric(as.Date(c("2014-02-18", "2014-04-11", "2014-04-18", "2014-04-25", "2014-05-07", "2014-05-08"))), color="red")
-p <- p + geom_point() + xlab("Date") + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NULL) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8))
+p <- p + geom_point() + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NULL) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8), axis.title.x=element_blank())
 ggsave("clients-meek.pdf", width=5, height=2, units="in")
 
 # 2014-02-18 [tor-qa] Please test experimental bundles with meek transport (3.5.2.1-meek-1)

### 2014-07-24 docs/meek.tex
Note to talk about Psiphon's long-polling design.
Note to add a figure.
Put GoAgent GFW disruption after Collateral Freedom survey.
Threat model revisions.

@@
 with samples of HTTPS traffic at an Internet router.
+
+% We measure the performance...
 
@@
 which is free of charge as long as they do not exceed a bandwidth quota.
-Use of GoAgent in China was disrupted starting in the beginning of June~2014
-when all Google services (including GoAgent's front domains) were blocked.
-meek over App Engine was similarly affected.
 According to a May 2013 survey~\cite{collateral-freedom},
@@
 above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
-Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.
+Use of GoAgent in China was disrupted starting in the beginning of June~2014
+when all Google services (including GoAgent's front domains) were blocked.
+meek over App Engine was similarly affected.
+% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.
 
@@
 
-The censor is able to inspect all traffic that passes through
-the censorship boundary and block or allow it at will.
-The censor is able to actively scan for proxies, and issue followup
-connections to hosts that clients connect to, in order to determine
-whether they are proxies.
-The censor may block the web host on which the reflector web app runs,
-but it must allow access to some domain that can front for it.
-In our deployment using App Engine, the censor may block appspot.com,
-but must allow www.google.com (or its IP address, or some other domain
-that goes through the frontend server).
-
-The censor must operate at line rate; that is,
-it must not delay traffic unduly while deciding whether to allow it.
-This consideration is one facet of the censor's sensitivity to
-collateral damage caused by false positives:
-mistakenly blocking or degrading non-circumvention traffic causes the censor
-to incur some penalty, just as mistakenly allowing circumvention traffic does.
-The censor must allow TLS connections; meek does not try to look like plaintext.
-% but the censor may look at TLS characteristics and block suspicious connections.
-
-The user's computer, the third-party infrastructure (e.g., Google), and the Tor bridge
-are all uncontrolled and uncompromised by the censor.
-The user has a way to get a copy of the necessary client programs.
-
-We assume that the censor cannot observe the communication
-once it reaches the third-party infrastructure; i.e.,
-that no further obfuscation is needed once fronting is accomplished.
+The model includes four actors:
+the censor,
+the censored client,
+the intermediate web service's frontend server (CDN edge server),
+and the destination proxy (Tor bridge).
+Circumvention is achieved when the client evades the censor to reach
+the destination proxy,
+because the proxy provides access to anywhere.
+The client and destination proxy cooperate with each other.
+The intermediate web service does not cooperate with either,
+except to the extent that it doesn't collude with the censor.
+% The censor's goal is to prevent circumvention.
+
+The censor controls a network and the into and within it.
+The censor is able to inspect traffic flowing across all links under its control
+and may block or allow any packet.
+The censor may inject and replay traffic, and
+operate its own clients and servers.
+The client lies within the censor's network,
+while the intermediate web service and destination proxy lie outside the network.
+The censor blocks direct communication between the client and the destination proxy,
+but allows HTTPS between the client and at least one front domain or IP address
+on the intermediate web service.
+
+% The censor must operate at line rate; that is,
+% it must not delay traffic unduly while deciding whether to allow it.
+% This consideration is one facet of the censor's sensitivity to
+% collateral damage caused by false positives:
+% mistakenly blocking or degrading non-circumvention traffic causes the censor
+% to incur some penalty, just as mistakenly allowing circumvention traffic does.
+
+The client,
+intermediate web service,
+and destination proxy
+are uncontrolled by the censor.
+The censor does not control a TLS certificate authority;
+specifically it cannot man-in-the-middle an HTTPS session
+without being caught by ordinary certificate verification.
+The client has a way to get a copy of the necessary client programs.
+
+See Section~\ref{sec:security} for what happens when some
+of these assumptions are violated;
+specifically what happens
+when the intermediate web service's frontend server is inside the censor's network
+and when the censor controls a certificate authority.
+
 % What about in-country edge servers; seems to work.
@@
 Entries are removed from the cache after a period of inactivity.
+
+% Use a child's garden--like figure of the HTTP protocol here.
+% "concatenates successive bodies"
 
@@
 
+% Psiphon idea: use long-polling for downstream data.
+% Works with CDNs, not with App Engine.
+
 \section{Future work}

### 2014-07-25 docs/meek.tex
More generic caption for architecture diagram.

@@
 Architecture of meek.
-The Google frontend server is the server that dispatches requests to different services depending on the Host header.
-Components that are new in our system are outlined in blue.
-The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
+The client sends an HTTP request to the Tor bridge by way of an intermediate web service such as a CDN.
+The client protects the bridge's domain name \textbf{forbidden.example} from the censor
+by fronting it with another name, here \textbf{allowed.example}.
+The intermediate web server decrypts the TLS layer and forwards the request to the bridge
+according to the Host header.
+The bridge sends data back to the client in the HTTP response.
+\meekclient\ and \meekserver\ are transport plugins, the interface between Tor and meek.
+The host actually at allowed.example does not participate in the communication.
 }

### 2014-07-25 docs/meek.tex
More model revisions.

@@
 the censored client,
-the intermediate web service's frontend server (CDN edge server),
-and the destination proxy (Tor bridge).
+the intermediate web service (CDN),
+and the destination Tor bridge.
 Circumvention is achieved when the client evades the censor to reach
-the destination proxy,
-because the proxy provides access to anywhere.
-The client and destination proxy cooperate with each other.
+the bridge,
+because the bridge proxies to anywhere.
+The client and bridge cooperate with each other.
 The intermediate web service does not cooperate with either,
@@
 The client lies within the censor's network,
-while the intermediate web service and destination proxy lie outside the network.
-The censor blocks direct communication between the client and the destination proxy,
+while the intermediate web service and bridge lie outside the network.
+The censor blocks direct communication between the client and the bridge,
 but allows HTTPS between the client and at least one front domain or IP address
 on the intermediate web service.
+% In examples, we will use the \textbf{allowed.example} as the front domain
+% and \textbf{forbidden.example} as the domain name of the Tor bridge.
 
@@
 
-See Section~\ref{sec:security} for what happens when some
+Section~\ref{sec:security} shows what happens when some
 of these assumptions are violated;
@@
 and when the censor controls a certificate authority.
+That section also describes the use of meek apart from Tor.
 

### 2014-07-25 docs/meek.tex
Update caption.
Partial revision of architecture section.

@@
 The components of the system are shown in Figure~\ref{fig:architecture}.
-The three parts that are new in our system are:
-\begin{enumerate}
-\item The client program \meekclient.
-Using the pluggable transports protocol, Tor treats \meekclient\ as a SOCKS proxy.
-When \meekclient\ receives data from Tor, it bundles it up in an HTTP POST
-request and sends it to the web app,
-using HTTPS to hide the contents and the domain fronting trick to hide the true destination.
-Downstream data are returned in HTTP responses, which \meekclient\ decodes and sends back to Tor.
-\item The ``reflector'' web app, running on App Engine.
-Its domain name \mbox{meek-reflect.appspot.com} is protected by domain fronting.
-It is called a reflector because it doesn't do anything intelligent:
-it merely copies the HTTP requests it receives and forwards them
-to \meekserver\ running on the Tor bridge.
-\item The server program \meekserver, which acts as an HTTP server.
-It receives reflected requests from the web app, decodes their bodies,
-and forwards the contents to an instance of Tor running on the same host.
-If there is anything pending to be sent back to the client,
-\meekserver\ sends it along with its HTTP response.
-\meekserver\ also takes care of stringing together multiple HTTP requests
-into one logical stream and multiplexing multiple concurrent connections,
-both using the technique of session IDs described in this section.
-\end{enumerate}
-
-The main technical challenge in making this system work
-is in encoding a TCP stream as a sequence of HTTP requests and responses.
-\meekserver\ handles many clients at once, and their data streams
-are split across multiple HTTP transactions.
+The parts that are new in meek
+are the programs \meekclient\ and \meekserver,
+which are the pluggable-transports~\cite{pt} interface between Tor and meek.
+% All the programs are free software, naturally,
+% and may be downloaded from the meek home page at
+% \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
+
+\meekclient\ is essentially a web client that knows how to front HTTPS requests.
+When \meekclient\ receives data from a client Tor process, it bundles it up into a POST request
+and fronts the request through the web service
+(which in turn forwards it to \meekserver\ on the bridge).
+If the response contains any payload, \meekclient\ decodes it and returns it back to Tor.
+\meekclient\ takes pains to make its TLS fingerprint
+look like that of a browser; see Section~\ref{sec:browserextension}.
+
+\meekserver\ is a special-purpose web server.
+When \meekserver\ receives a request, it extracts the body and feeds it into
+a local Tor running as a bridge.
+If there are any data pending to be sent back to the client from Tor,
+\meekserver\ includes it in the body of the HTTP response.
+\meekserver\ also handles session management:
+as there may be many clients using the service at once,
+the server must determine which client session each incoming request belongs to.
+% It does this by means of an X-Session-ID header,
+% described in this section.
+
+When meek is used with Google App Engine, one other component is needed.
+It is a small ``reflector'' web app that simply copies any request
+it receives and forwards it to an instance of \meekserver\ running on a bridge.
+App Engine cannot directly run a Tor bridge,
+so we bounce the requests to somewhere that can.
+The reflector app emulates the behavior of an origin-pull CDN,
+which also simply copies and forwards a request to the origin server
+when the response is not already cached.
+
+The main technical challenge is handling a TCP stream
+that has been split up into a sequence of HTTP requests and responses.
+The body of each HTTP request and HTTP response carries
+a small chunk of upstream or downstream communication.
+\meekserver\ must handle many clients at once,
+and therefore maintains many open connections to the local Tor process,
+one for each active client.
+When a new request arrives, the server must determine which
+open session it belongs to
+(or whether it is a brand-new client needing a new session).
 In TCP, different streams are distinguished by their
 (source~IP, source port, dest~IP, dest~port) tuple,
-but we cannot do that because streams are split across multiple TCP sessions.
-Rather, each instance of \meekclient\ generates at startup a random 32-byte
-session ID, which is sent along with its requests in a special
-X-Session-ID HTTP header.
-\meekserver, when it sees a particular session ID for the first time,
-opens up a new connection to the local Tor process,
-and stores the session ID in a cache. Subsequent requests with the
+but that doesn't work for meek for two reasons:
+the source IP of the requests is that of the intermediate web service,
+not that of the client;
+and a logical stream is chopped into multiple independent HTTP requests,
+so the source port is always changing.
+Rather, each client generates a random 256-bit session ID,
+which it sends with each of its requests in a special
+X-Session-ID header.
+\meekserver, when it sees a session ID for the first time,
+opens up a new connection to the local Tor process
+and associates the connection and ID in a cache.
+Subsequent requests with the
 same session ID will reuse the same Tor connection.
-Entries are removed from the cache after a period of inactivity.
-
+Sessions are closed after a period of inactivity.
+Figure~\ref{fig:protocol} shows an sample of the protocol.
+
+\begin{figure}
 % Use a child's garden--like figure of the HTTP protocol here.
+\caption{
+The meek protocol.
+The session ID is randomly generated by the client.
+The protocol shown here is encrypted inside HTTPS until after
+it has been fronted,
+so the censor is unable to classify the traffic based on the
+Host or X-Session-ID headers.
+}
+\label{fig:protocol}
+\end{figure}
+
+% out of order, blah blah.
 % "concatenates successive bodies"
+% handle it by strict serialization, has performance issues, see ...
 
@@
 because App Engine requires requests to finish within 60 seconds.
-
-We implemented meek as a pluggable transport~\cite{pt} for Tor.
-Although it is possible to use the system with proxies other than Tor,
-using Tor has some attractive features.
-The pluggable transports infrastructure makes it relatively easy to prototype
-a circumvention technique and connect it to a global proxy network.
-We can treat confidentiality and integrity of tunneled communication
-as a problem solved by Tor, which we don't need to solve separately.
-Tor's extra proxy hops mean that the HTTP reflector (App Engine)
-and the entry bridge do not have to be trusted.
+% Psiphon did it.
 
@@
 The headless instance of the browser runs in the background and is invisible to the user.
-This figure is a detailed view of the ``User's PC'' component of Figure~\ref{fig:architecture}.
+This figure is a detailed view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
 }
@@
 
+We implemented meek as a pluggable transport~\cite{pt} for Tor.
+Although it is possible to use the system with proxies other than Tor,
+using Tor has some attractive features.
+The pluggable transports infrastructure makes it relatively easy to prototype
+a circumvention technique and connect it to a global proxy network.
+We can treat confidentiality and integrity of tunneled communication
+as a problem solved by Tor, which we don't need to solve separately.
+Tor's extra proxy hops mean that the HTTP reflector (App Engine)
+and the entry bridge do not have to be trusted.
+
 % Edge servers within the censored region.
@@
 % Could conceivably send cover traffic if MITM detected, but blah.
+
+% meek apart from Tor.
+% more risk for the proxy operator
+% can require people to run their own proxies à la GoAgent.
+% "Censorship implies surveillance"
 

### 2014-07-25 docs/meek.tex
Protocol sample.
Cribbed from
https://trac.torproject.org/projects/tor/wiki/doc/AChildsGardenOfPluggableTransports#meek.

@@
 Sessions are closed after a period of inactivity.
-Figure~\ref{fig:protocol} shows an sample of the protocol.
+Figure~\ref{fig:protocol} shows a sample of the protocol.
 
@@
 % Use a child's garden--like figure of the HTTP protocol here.
+\tiny
+\usefont{U}{cmtt}{m}{n}%
+\begin{verbatim}
+POST / HTTP/1.1
+Host: forbidden.example
+X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
+Content-Length: 517
+
+\x16\x03\x01\x02\x00\x01\x00\x01\xfc\x03\x03\x9b\xa9\x9f\xf5\xbb
+...
+\end{verbatim}
+\begin{quote}
+\begin{verbatim}
+HTTP/1.1 200 OK
+Content-Length: 739
+
+\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75\xa2\x78\x7d
+...
+\end{verbatim}
+\end{quote}
+\begin{verbatim}
+POST / HTTP/1.1
+Host: forbidden.example
+X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
+Content-Length: 0
+
+\end{verbatim}
+\begin{quote}
+\begin{verbatim}
+HTTP/1.1 200 OK
+Content-Length: 75\r\n
+
+\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25\x72\x1e
+...
+\end{verbatim}
+\end{quote}
 \caption{
@@
 The session ID is randomly generated by the client.
-The protocol shown here is encrypted inside HTTPS until after
+Request/response bodies contain successive chunks of a Tor TLS stream
+(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02...}
+is the beginning of a TLS handshake).
+The messages shown here is encrypted inside HTTPS until after
 it has been fronted,
-so the censor is unable to classify the traffic based on the
-Host or X-Session-ID headers.
+so the censor cannot use the
+Host and X-Session-ID headers for classification.
 }

### 2014-07-25 docs/clients-meek.R
Use a barchart for the clients graph.
This loses information: you can't tell the difference between a missing
day and a day with 0 users. But it looks better.

@@ -9,7 +9,7 @@ daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
 p <- ggplot(data, aes(x=date, y=clients))
 # p <- p + geom_vline(xintercept=as.numeric(as.Date(c("2014-02-18", "2014-04-11", "2014-04-18", "2014-04-25", "2014-05-07", "2014-05-08"))), color="red")
-p <- p + geom_point() + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NULL) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8), axis.title.x=element_blank())
+p <- p + geom_bar(stat="identity", width=1.1) + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NULL) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8), axis.title.x=element_blank())
 ggsave("clients-meek.pdf", width=5, height=2, units="in")
 
 # 2014-02-18 [tor-qa] Please test experimental bundles with meek transport (3.5.2.1-meek-1)

### 2014-07-25 docs/meek.tex
Add wire diagrams.
Tweak protocol figure.

@@
 \def\urll#1{\begin{NoHyper}\url{#1}\end{NoHyper}}
+
+% https://tex.stackexchange.com/questions/113338/use-sans-serif-in-a-verbatim-environment/113339#113339
+\makeatletter
+\def\verbatim@font{\usefont{U}{cmtt}{m}{n}}
+\makeatother
 
@@
 \begin{figure}
-% Use a child's garden--like figure of the HTTP protocol here.
-\tiny
-\usefont{U}{cmtt}{m}{n}%
+\scriptsize
 \begin{verbatim}
@@
 
-\x16\x03\x01\x02\x00\x01\x00\x01\xfc\x03\x03\x9b\xa9\x9f\xf5\xbb
-...
+\x16\x03\x01\x02\x00\x01\x00\x01\xfc\x03\x03\x9b\xa9\x9f...
 \end{verbatim}
+\smallskip
 \begin{quote}
@@
 
-\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75\xa2\x78\x7d
-...
+\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75\xa2...
 \end{verbatim}
 \end{quote}
+\smallskip
 \begin{verbatim}
@@
 \end{verbatim}
+\smallskip
 \begin{quote}
@@
 HTTP/1.1 200 OK
-Content-Length: 75\r\n
-
-\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25\x72\x1e
-...
+Content-Length: 75
+
+\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
 \end{verbatim}
@@
 \caption{
-The meek protocol.
+Requests and responses in the meek HTTP protocol.
 The session ID is randomly generated by the client.
 Request/response bodies contain successive chunks of a Tor TLS stream
-(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02...}
-is the beginning of a TLS handshake).
+(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
+is the beginning of a TLS ClientHello message).
+The second POST request is an empty polling request.
 The messages shown here is encrypted inside HTTPS until after
@@
 
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.40\linewidth}
+\includegraphics[width=\linewidth]{wire-sequential}
+\caption{Sequential}
+\label{fig:wire-sequential}
+\end{subfigure}
+\qquad
+\begin{subfigure}[t]{0.40\linewidth}
+\includegraphics[width=\linewidth]{wire-parallel}
+\caption{Parallel}
+\label{fig:wire-parallel}
+\end{subfigure}
+
+\caption{
+The nature of potential performance gain
+from sending fronted requests in parallel.
+}
+\label{fig:wire}
+\end{figure}
+
 % Performance measurements

### 2014-07-25 docs/meek.tex
Comment out acknowledgements.
More revisions to architecture.

@@
 
-% out of order, blah blah.
-% "concatenates successive bodies"
-% handle it by strict serialization, has performance issues, see ...
-
-HTTP is fundamentally a pull-based protocol.
-There is no way for the server to send data to the client without
-the client first making a request.
-The same applies to meek: when \meekserver\ has data to send back to
-a client with a particular session ID, it cannot do so until it
-receives a request from that client.
-For this reason, \meekclient\ polls the server,
-sending an empty request if necessary, every so often.
+The underlying TCP stream is broken into chunks so that
+There must therefore be some way of making sure that chunks
+are correctly reassembled at the other end,
+in order and without gaps and duplicates.
+meek takes a naive approach: requests and responses are strictly serialized.
+The client doesn't send a second chunk of data
+(i.e, make another HTTPS request) until it has
+receive the response to the first request.
+The underlying stream is simply the concatenation
+of chunks in the order they arrive.
+Doing it this way is simple and guarantees correctness,
+but has performance drawbacks because there is a full round-trip
+between every send.
+The performance drawbacks are not inherent to the design:
+it is domain fronting, not HTTP encoding, that is the fundamental strength of the system.
+Section~\ref{sec:futurework} describes more efficient encodings
+that enable multiple requests in parallel.
+
+HTTP is fundamentally a request-based protocol.
+There is no way for the server to ``push'' data to the client without
+having first received a request.
+In order to enable the server to send back data,
+meek uses one of two techniques.
+The first is polling:
+every so often the client sends a request with an empty payload
+if it has nothing else to send.
 The polling interval starts short (100~ms) and grows exponentially
 up to a maximum of 5~s.
-Alternative techniques for push-like behavior,
-such as HTTP long polling,
-don't work well with App Engine,
-because App Engine requires requests to finish within 60 seconds.
-% Psiphon did it.
+% Implemented in Psiphon's version.
+The other technique is to use
+long-lived persistent HTTP connections.
+When the server sends a response, it keeps the connection open,
+continually appending data to the response body while it has anything to send.
+When the server receives a new request from the same client,
+it closes any response it has open to the client and starts a new response.
+See Section~\ref{sec:otherdeployment} for more details
+on when each technique may be used.
 
@@
 % Works with CDNs, not with App Engine.
+% Alternative techniques for push-like behavior,
+% such as HTTP long polling,
+% don't work well with App Engine,
+% because App Engine requires requests to finish within 60 seconds.
 
 \section{Future work}
+\label{sec:futurework}
 
@@
 
-\section*{Acknowledgments}
-
-We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
-Special thanks go to the members of the tor-qa and tor-dev mailing lists
-who responded to our design ideas, reviewed source code, and tested our prototypes.
+% \section*{Acknowledgments}
+
+% We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
+% Special thanks go to the members of the tor-qa and tor-dev mailing lists
+% who responded to our design ideas, reviewed source code, and tested our prototypes.
 % George Kadianakis

### 2014-07-25 docs/meek.tex
Miscellaneous revisions.

@@
 which may be oblivious to the circumvention.
-
 For those familiar with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance},
@@
 addresses, for example IP addresses and domain names, whatever the contents may be.
-A skilled censor will use both means of censorship,
-and effective circumvention requires countering both.
+A savvy censor will use both means of censorship---therefore
+effective circumvention requires countering both.
 
@@
 to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
-Falling into the first category are ``look-like-nothing'' transports whose
+Following the first strategy are the ``look-like-nothing'' transports whose
 payloads are indistinguishable from a uniformly random byte stream.
@@
 
-The other strategy against content blocking is the steganographic approach: look like
+The other strategy against DPI is the steganographic approach: look like
 something the censor doesn't block.
@@
 the server must determine which client session each incoming request belongs to.
-% It does this by means of an X-Session-ID header,
+% It does this by means of an X-Session-Id header,
 % described in this section.
@@
 which it sends with each of its requests in a special
-X-Session-ID header.
+X-Session-Id header.
 \meekserver, when it sees a session ID for the first time,
@@
 so the censor cannot use the
-Host and X-Session-ID headers for classification.
+Host and X-Session-Id headers for classification.
 }
@@
 most distinguish the client are the list of ciphersuites and the
-list of TLS extensions in the Client Hello.
+list of TLS extensions in the ClientHello.
 Figure~\ref{fig:ciphersuites} shows how the list of ciphersuites
@@
 The headless instance of the browser runs in the background and is invisible to the user.
-This figure is a detailed view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
+This figure is a zoomed-in view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
 }
@@
 
+% Censor could lean on the CDN to block the actual destination internally.
+
 % Firefox plugin uses normal browser trust store.
@@
 \includegraphics[width=\linewidth]{clients-meek}
-\caption{Number of concurrent users using the meek transport,
-as reported by the Tor Metrics Portal.}
+\caption{Concurrent users of meek with Tor.}
 \label{fig:clients}
@@
 
-Figure~\ref{fig:clients} shows the number of concurrent users of meek between January and May~2014,
+Figure~\ref{fig:clients} shows the average number of concurrent users of meek with Tor
+since close to the beginning of development,
 as reported by the Tor Metrics Portal~\cite{metrics-meek}.
-The number of concurrent users is estimated by counting directory requests made over the transport~\cite{counting-daily-bridge-users}.
-The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by meek.
+The number of users is estimated by counting the number
+of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
+% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by meek.
 

### 2014-07-25 docs/meek.tex
Minor revisions.

@@
 once widely used in China.
-Fronting has been used with success since 2013
+Fronting has also been used with success since 2013
 for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
-GoAgent and the flash proxy rendezvous are the most direct
+GoAgent and flash proxy's rendezvous are the most direct
 inspirations of this work.
 
-We have developed domain fronting into a system called meek,
-a full-fledged circumvention transport,
-implemented as a pluggable transport~\cite{pt} for Tor.
+We have developed domain fronting into a full-fledged circumvention system called meek,
+implemented as a Tor pluggable transport~\cite{pt}.
 meek combines fronting with an HTTP-based tunneling proxy:
@@
 meek's architecture appears in Figure~\ref{fig:architecture}.
-Section~\ref{sec:architecture} describes meek's workings in detail.
+Section~\ref{sec:architecture} describes its workings in detail.
 

### 2014-07-26 docs/meek.tex
TLS camouflage revisions.

@@
 See Section~\ref{sec:otherdeployment} for more details
-on when each technique may be used.
-
-\section{Making the TLS handshake indistinguishable}
+on when each technique may be used;
+it depends on the intermediate web service.
+
+\section{Camouflage for the TLS layer}
 \label{sec:browserextension}
 
-The practice of routing traffic through a web service with domain fronting
-defeats both address-based blocking and active scanning.
-The endpoint (which appears to be the front domain; e.g. www.google.com)
-cannot be blocked because to block it would cause collateral damage.
-Active scanning is defeated because if the censor accesses the same
-domain as does the client, all they see is a web page served by the front domain.
-Even though the censor knows some traffic is being fronted,
-by looking only at IP addresses and domain names, it cannot determine which.
-
-However, a savvy censor may also use content-based blocking
-(deep packet inspection) as a basis for blocking.
-Anything that reliably distinguishes meek's traffic from that of normal allowed traffic
-(presumably web browsing) must be eliminated.
-In this section we demonstrate how the client part of the TLS handshake can be used
-to fingerprint different TLS implementations,
-and how we use a web browser to camouflage meek's TLS.
-
-There are many parts of the TLS handshake, but the two that
-most distinguish the client are the list of ciphersuites and the
-list of TLS extensions in the ClientHello.
-Figure~\ref{fig:ciphersuites} shows how the list of ciphersuites
-differs in different client implementations.
-Figure~\ref{fig:ciphersuites:meek-client} is how our first prototype of \meekclient\ appeared on the wire,
-using the built-in crypto/tls library of the Go programming language.
-The list of ciphersuites is unlike that of a web browser,
-and could be used as a fingerprint for blocking.
-Tor itself was blocked by China in 2011 in exactly this way~\cite{bug4744}.
-Similarly the list of TLS extensions (not shown)
-differed between \meekclient\ and popular browsers.
+Domain fronting defeats address-based blocking and active probing.
+HTTPS foils the most straightforward DPI,
+hiding byte patterns in the underlying stream.
+The censor may try to apply more careful DPI in order to
+distinguish fronted and non-fronted traffic.
+This section is about TLS fingerprinting,
+which is the censor's remaining easy distinguisher,
+and how we use a web browser with an unremarkable TLS fingerprint
+to disguise the HTTPS tunnel.
+The next section is about more subtle and hard-to-apply forms of DPI.
+
+The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}.
+The plaintext SNI extension, for instance, has to be protected by domain fronting.
+There is enough room for variation in other fields,
+such as the client's lists of ciphersuites and extensions,
+that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}.
+(We are only concerned with fingerprinting the client,
+because the server's TLS that the censor can observe
+comes from the intermediate web service;
+i.e., it is what you would expect when connecting to the front domain.)
+Tor itself was blocked by China in 2011
+because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
+
+Figure~\ref{fig:ciphersuites} shows examples of how TLS client
+implementations may differ.
+Figure~\ref{fig:ciphersuites:golang} is from the Go programming languages
+built-in net/http library~\cite{golang-net/http},
+which has a custom TLS implementation;
+it is how \meekclient\ would appear with no TLS camouflage.
+It is unlike Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
+which are browsers; the browsers are also unlike each other.
+A censor could block an uncamouflaged meek using Go's fingerprint,
+if it considered the collateral damage resulting from blocking other Go programs to be slight enough.
 
@@
 \begin{subfigure}[t]{0.30\textwidth}
-\begin{minipage}[t][17ex][t]{0.30\textwidth}
+\caption{Go 1.2's net/http library}
+\begin{minipage}[t][25.5ex][t]{\textwidth}
 \tiny
 \begin{verbatim}
+Ciphersuites:
   TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
@@
   TLS_RSA_WITH_3DES_EDE_CBC_SHA
+Extensions:
+  server_name
+  status_request
+  elliptic_curves
+  ec_point_formats
+  signature_algorithms
 \end{verbatim}
 \end{minipage}
-\caption{meek-client}
-\label{fig:ciphersuites:meek-client}
+\label{fig:ciphersuites:golang}
 \end{subfigure}
@@
 \begin{subfigure}[t]{0.30\textwidth}
-\begin{minipage}[t][48ex][t]{0.30\textwidth}
+\caption{Firefox 24}
+\begin{minipage}[t][57ex][t]{\textwidth}
 \tiny
 \begin{verbatim}
+Ciphersuites:
   TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
@@
   TLS_RSA_WITH_RC4_128_MD5
+Extensions:
+  server_name
+  renegotiation_info
+  elliptic_curves
+  ec_point_formats
+  SessionTicket TLS
+  next_protocol_negotiation
 \end{verbatim}
 \end{minipage}
-\caption{Firefox 24}
 \label{fig:ciphersuites:firefox}
@@
 \begin{subfigure}[t]{0.30\textwidth}
-\begin{minipage}[t][27ex][t]{0.30\textwidth}
+\caption{Chrome 33}
+\begin{minipage}[t][42.5ex][t]{\textwidth}
 \tiny
 \begin{verbatim}
+Ciphersuites:
   TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
@@
   TLS_RSA_WITH_3DES_EDE_CBC_SHA
+Extensions:
+  server_name
+  renegotiation_info
+  elliptic_curves
+  ec_point_formats
+  SessionTicket TLS
+  next_protocol_negotiation
+  application_layer_protocol_negotiation
+  Channel ID
+  status_request
+  signature_algorithms
+  Signed Certificate Timestamp
 \end{verbatim}
 \end{minipage}
-\caption{Chrome 33}
 \label{fig:ciphersuites:chrome}
@@
 
-\caption{Differences in ciphersuites offered by
-our \meekclient\ program when it accesses the network directly,
-and by two web browsers.
-The distinctive ciphersuites offered by \meekclient\ can be used as part of a blocking fingerprint.
-As a remedy we have \meekclient\ proxy its TLS through a web browser extension.
+\caption{
+Selected differences in ClientHello messages in three different TLS implementations.
 }
@@
 
-In response to the threat of TLS fingerprinting,
-we modified \meekclient\ to proxy its HTTP requests through a local web browser extension.
-\meekclient\ tells the extension what URLs to fetch, and the extension fetches them.
+In order to disguise its TLS fingerprint,
+\meekclient\ proxies all its HTTPS requests through an actual web browser.
+We implemented extensions for two web browsers,
+Firefox and Chrome,
+that enable them to make HTTPS requests on behalf of \meekclient.
 The TLS fingerprint looks like that of a browser, because it is that of a browser.
-We implemented two versions of the extension, one for Firefox and one for Chrome.
-They work similarly: they open a TCP port on localhost,
-await instructions from \meekclient\ on what HTTP requests to make,
-issue the requests, and return the responses.
+The browser instance with the extension is completely separate
+from the browser the user interacts with.
+It runs invisibly in the background in a separate process,
+doesn't display a user interface,
+and shares no state with the user's browser.
 
@@
 Solid lines show the flow of outgoing communication.
-The headless instance of the browser runs in the background and is invisible to the user.
+The headless browser runs in the background and is invisible to the user.
 This figure is a zoomed-in view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
@@
 Figure~\ref{fig:browser-architecture} shows the interaction of components
-on the user's computer.
-Rather than starting \meekclient\ as a pluggable transport directly, the Tor
-process starts a helper process that starts both \meekclient\
-and a headless browser instance.
-The headless browser runs our extension in a separate
-process and separate browser profile from the browser the
-user interacts with; the two browser instances share no state.
-\meekclient\ is configured to issue its requests through the browser extension;
-in this configuration, the headless browser is the only thing that ever touches the network.
-When run with a browser extension, meek has the same TLS signature
-as Firefox (Figure~\ref{fig:ciphersuites:firefox}) or
-Chrome (Figure~\ref{fig:ciphersuites:chrome}).
-
-The use of a browser extension offers benefits beyond its TLS signature.
-We inherit other characteristics of the browser:
+on the client's computer.
+The local Tor process starts a helper process that starts both \meekclient\
+and the headless browser,
+then configures \meekclient\ to proxy its requests through the browser extension.
+The user's browser proxies through Tor;
+Tor proxies through \meekclient,
+and \meekclient\ proxies through the headless browser.
+The headless browser is the only thing that ever actually touches the network.
+It should be emphasized that the URLs requested by the headless browser extension
+have no relation to the URLs the user actually browses;
+the extension only ever makes requests to the front domain.
+
+The use of a browser extension brings benefits beyond TLS camouflage.
+It means meek inherits other traffic characteristics of the browser:
+for instance
 how often it resolves DNS names,
 its connection reuse,
-and HTTP keepalive behavior.
-The Firefox extension has special usability advantages because the Tor Browser Bundle
-uses a modified Firefox.
-We can include a small extension in the browser bundle, reusing the existing
-Firefox executable, without increasing the download size of the bundle much,
-and without requiring users to separately configure a browser to run the extension.
-
-The development of the browser extensions posed some unexpected challenges.
-Tor Browser disables TLS session tickets because they can be used as linking identifiers,
-but the lack of session tickets shows up as a missing TLS extension,
-so we had to reenable them in the headless browser.
-(Doing so doesn't harm Tor Browser's anonymity:
-if session tickets are used, they are used only on the circumvention layer
-between the user and the frontend server. Tor Browser's own TLS is tunneled
-within the circumvention layer, and session tickets are still disabled at that level.)
-The Chrome extension needed to be split into two pieces, an extension and an app,
-because an extension cannot open a listening socket and an app cannot make HTTP requests.
+and its HTTP keepalive behavior.
+The Firefox extension has special advantages
+when meek is used with Tor Browser
+because Tor Browser
+is a modified version of Firefox.
+We can use the same browser executable for both the browser the user interacts with (Tor Browser)
+and the one providing TLS camouflage (a headless Firefox),
+saving space in distribution packages
+and sparing the user from having to separately configure a browser to run the extension.
+In Tor Browser,
+the headless Firefox is started and stopped transparently
+when meek is activated and deactivated.
+
+% The development of the browser extensions posed some unexpected challenges.
+% Tor Browser disables TLS session tickets because they can be used as linking identifiers,
+% but the lack of session tickets shows up as a missing TLS extension,
+% so we had to reenable them in the headless browser.
+% (Doing so doesn't harm Tor Browser's anonymity:
+% if session tickets are used, they are used only on the circumvention layer
+% between the user and the frontend server. Tor Browser's own TLS is tunneled
+% within the circumvention layer, and session tickets are still disabled at that level.)
+% The Chrome extension needed to be split into two pieces, an extension and an app,
+% because an extension cannot open a listening socket and an app cannot make HTTP requests.
+
+No TLS camouflage is needed between the intermediate web service and \meekserver,
+because that portion of the communication flow is not observed by the censor.
+
+Appropriate TLS camouflage may differ according to circumstances.
+On a traditional desktop PC, using a browser is probably the right choice.
+When Psiphon ported \meekclient\ to Android,
+they didn't use a browser as camouflage,
+but rather made all HTTPS requests with the standard Android HTTP API.
+This decision makes sense because typical Android applications
+also use the standard API and share the same TLS fingerprint.
 
@@
 \label{sec:trafficstatistics}
+
+% Advantage is that we are probably proxying web traffic.
 

### 2014-07-26 docs/meek.tex
Related-work JumpBox if they get it online.
Cite Google Transparency Report.

@@
 Use of GoAgent in China was disrupted starting in the beginning of June~2014
-when all Google services (including GoAgent's front domains) were blocked.
+when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
 meek over App Engine was similarly affected.
@@
 % CORDON? Say how meek would be classified in it?
+
+% Section~\ref{sec:browserextension}, JumpBox
+% http://securecomm.org/2014/show/tutorials
 

### 2014-07-28 docs/clients-psiphon3.R
clients-psiphon3 graph.

@@ -1,0 +1,10 @@
+library(ggplot2)
+library(scales)
+data <- read.csv("psiphon3-fronted-meek-unique-users-all-regions.csv", skip=2, col.names=c("date", "clients"))
+data$date <- as.Date(data$date, format="%b %d, %Y")
+
+daterange <- seq(min(data$date), max(data$date), "1 day")
+data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
+p <- ggplot(data, aes(x=date, y=clients))
+p <- p + geom_bar(stat="identity", width=1.1) + ylab("Daily unique users") + scale_x_date(labels=date_format("%b %Y")) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8), axis.title.x=element_blank())
+ggsave("clients-psiphon3.pdf", width=5, height=2, units="in")

### 2014-07-28 docs/clients-meek.R
Adjust dims of client graphs a bit.

@@ -9,8 +9,8 @@ daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
 p <- ggplot(data, aes(x=date, y=clients))
 # p <- p + geom_vline(xintercept=as.numeric(as.Date(c("2014-02-18", "2014-04-11", "2014-04-18", "2014-04-25", "2014-05-07", "2014-05-08"))), color="red")
-p <- p + geom_bar(stat="identity", width=1.1) + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NULL) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8), axis.title.x=element_blank())
-ggsave("clients-meek.pdf", width=5, height=2, units="in")
+p <- p + geom_bar(stat="identity", width=1.1) + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NULL) + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
+ggsave("clients-meek.pdf", width=4, height=1.5, units="in")
 
 # 2014-02-18 [tor-qa] Please test experimental bundles with meek transport (3.5.2.1-meek-1)
 # https://lists.torproject.org/pipermail/tor-qa/2014-February/000340.html

### 2014-07-28 docs/clients-psiphon3.R

@@ -6,5 +6,5 @@ data$date <- as.Date(data$date, format="%b %d, %Y")
 daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
 p <- ggplot(data, aes(x=date, y=clients))
-p <- p + geom_bar(stat="identity", width=1.1) + ylab("Daily unique users") + scale_x_date(labels=date_format("%b %Y")) + theme(axis.text=element_text(size=8), axis.title=element_text(size=8), axis.title.x=element_blank())
-ggsave("clients-psiphon3.pdf", width=5, height=2, units="in")
+p <- p + geom_bar(stat="identity", width=1.1) + ylab("Daily unique users") + scale_x_date(labels=date_format("%b %Y")) + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
+ggsave("clients-psiphon3.pdf", width=4, height=1.5, units="in")

### 2014-07-29 diagrams.R
Parse pcap files with Bro.
Scapy is so so slow.

@@ -2,7 +2,12 @@ library(ggplot2)
 
 theme_set(theme_bw(base_size = 16))
 
-x <- read.delim("table.dat")
+col.names <- c("t", "src", "dst", "dir", "iplen", "datalen", "syn")
+
+x <- cbind(read.table("traces/lbl.https.goog.dpriv.tcp.log", col.names=col.names), type="google")
+x <- rbind(x, cbind(read.table("traces/lbl.https.non-goog.dpriv.tcp.log", col.names=col.names), type="non-google"))
+x <- rbind(x, cbind(read.table("traces/meek_tbb_extension_tcp.pcap.tcp.log", col.names=col.names), type="tbb"))
+
 x <- x[order(x$t),]
 
 min.datalen <- min(x$datalen)

### 2014-07-29 diagrams.R
Use stat="ecdf".
This is loads faster because you don't have to index the data twice.

@@ -31,7 +31,7 @@ qplot(x[x$type=="google",]$datalen, main="TCP payload length (Google only)", bin
 dev.off()
 
 png("diagrams/datalen-google-cdf.png")
-qplot(x[x$type=="google",]$datalen, ecdf(x[x$type=="google",]$datalen)(x[x$type=="google",]$datalen), geom="step", ylim=c(0,1), main="TCP payload length CDF (Google only)") + xlab("Length (Bytes)") + ylab("Probability") 
+qplot(x[x$type=="google",]$datalen, stat="ecdf", geom="step", ylim=c(0,1), main="TCP payload length CDF (Google only)") + xlab("Length (Bytes)") + ylab("Probability") 
 dev.off()
 
 png("diagrams/datalen-google-in.png")
@@ -47,7 +47,7 @@ qplot(x[x$type=="tbb",]$datalen, main="TCP payload length (TBB meek)", binwidth=
 dev.off()
 
 png("diagrams/datalen-tbb-cdf.png")
-qplot(x[x$type=="tbb",]$datalen, ecdf(x[x$type=="tbb",]$datalen)(x[x$type=="tbb",]$datalen), geom="step", ylim=c(0,1), main="TCP payload length CDF (Alexa 500 with TBB)") + xlab("Length (Bytes)") + ylab("Probability") 
+qplot(x[x$type=="tbb",]$datalen, stat="ecdf", geom="step", ylim=c(0,1), main="TCP payload length CDF (Alexa 500 with TBB)") + xlab("Length (Bytes)") + ylab("Probability") 
 dev.off()
 
 syn.out <- x[x$syn & x$dir=="OUT",]

### 2014-07-29 diagrams.R
Fix the google+non-google LBL plots.
They were meant to represent all LBL traffic, not just the non-google
portion of it. The google graphs are a subset of the whole LBL data.

@@ -4,53 +4,55 @@ theme_set(theme_bw(base_size = 16))
 
 col.names <- c("t", "src", "dst", "dir", "iplen", "datalen", "syn")
 
-x <- cbind(read.table("traces/lbl.https.goog.dpriv.tcp.log", col.names=col.names), type="google")
-x <- rbind(x, cbind(read.table("traces/lbl.https.non-goog.dpriv.tcp.log", col.names=col.names), type="non-google"))
-x <- rbind(x, cbind(read.table("traces/meek_tbb_extension_tcp.pcap.tcp.log", col.names=col.names), type="tbb"))
+x <- cbind(read.table("traces/lbl.https.goog.dpriv.tcp.log", col.names=col.names), google=T, source="lbl")
+x <- rbind(x, cbind(read.table("traces/lbl.https.non-goog.dpriv.tcp.log", col.names=col.names), google=F, source="lbl"))
+x <- rbind(x, cbind(read.table("traces/meek_tbb_extension_tcp.pcap.tcp.log", col.names=col.names), google=T, source="tbb"))
 
 x <- x[order(x$t),]
 
 min.datalen <- min(x$datalen)
 max.datalen <- max(x$datalen)
 
+lbl = x[x$source=="lbl",]
+
 png("diagrams/datalen.png")
-qplot(x[x$type=="non-google",]$datalen, geom="histogram", main="TCP payload length", binwidth=2) + xlab("length")  
+qplot(lbl$datalen, geom="histogram", main="TCP payload length", binwidth=2) + xlab("length")  
 
 dev.off()
 
 png("diagrams/datalen-in.png")
-qplot(x[x$type=="non-google" & x$dir=="IN",]$datalen, main="TCP payload length (incoming)", binwidth=2) + xlab("length") 
+qplot(lbl[lbl$dir=="IN",]$datalen, main="TCP payload length (incoming)", binwidth=2) + xlab("length") 
 dev.off()
 
 png("diagrams/datalen-out.png")
-qplot(x[x$type=="non-google" & x$dir=="OUT",]$datalen, main="TCP payload length (outgoing)", binwidth=2) + xlab("length") 
+qplot(lbl[lbl$dir=="OUT",]$datalen, main="TCP payload length (outgoing)", binwidth=2) + xlab("length") 
 dev.off()
 
 png("diagrams/datalen-google.png")
[…]

### 2014-07-29 docs/clients-meek.R
xlab(NULL) for more space.

@@ -9,8 +9,8 @@ daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
 p <- ggplot(data, aes(x=date, y=clients))
 # p <- p + geom_vline(xintercept=as.numeric(as.Date(c("2014-02-18", "2014-04-11", "2014-04-18", "2014-04-25", "2014-05-07", "2014-05-08"))), color="red")
-p <- p + geom_bar(stat="identity", width=1.1) + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NULL) + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
-ggsave("clients-meek.pdf", width=4, height=1.5, units="in")
+p <- p + geom_bar(stat="identity", width=1.1) + xlab(NULL) + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NULL) + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
+ggsave("clients-meek.pdf", width=4, height=1.4, units="in")
 
 # 2014-02-18 [tor-qa] Please test experimental bundles with meek transport (3.5.2.1-meek-1)
 # https://lists.torproject.org/pipermail/tor-qa/2014-February/000340.html

### 2014-07-29 docs/clients-psiphon3.R

@@ -6,5 +6,5 @@ data$date <- as.Date(data$date, format="%b %d, %Y")
 daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
 p <- ggplot(data, aes(x=date, y=clients))
-p <- p + geom_bar(stat="identity", width=1.1) + ylab("Daily unique users") + scale_x_date(labels=date_format("%b %Y")) + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
-ggsave("clients-psiphon3.pdf", width=4, height=1.5, units="in")
+p <- p + geom_bar(stat="identity", width=1.1) + xlab(NULL) + ylab("Daily unique users") + scale_x_date(labels=date_format("%b %Y")) + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
+ggsave("clients-psiphon3.pdf", width=4, height=1.4, units="in")

### 2014-07-29 diagrams.R
Undo theme in diagrams.R.

@@ -1,7 +1,5 @@
 library(ggplot2)
 
-theme_set(theme_bw(base_size = 16))
-
 col.names <- c("t", "src", "dst", "dir", "iplen", "datalen", "syn")
 
 x <- cbind(read.table("traces/lbl.https.goog.dpriv.tcp.log", col.names=col.names), google=T, source="lbl")

### 2014-07-29 diagrams.R
xlim for CDF plots.

@@ -31,7 +31,7 @@ qplot(lbl[lbl$google,]$datalen, main="TCP payload length (Google only)", binwidt
 dev.off()
 
 png("diagrams/datalen-google-cdf.png")
-qplot(lbl[lbl$google,]$datalen, stat="ecdf", geom="step", ylim=c(0,1), main="TCP payload length CDF (Google only)") + xlab("Length (Bytes)") + ylab("Probability") 
+qplot(lbl[lbl$google,]$datalen, stat="ecdf", geom="step", xlim=range(lbl$datalen), ylim=c(0,1), main="TCP payload length CDF (Google only)") + xlab("Length (Bytes)") + ylab("Probability") 
 dev.off()
 
 png("diagrams/datalen-google-in.png")
@@ -47,7 +47,7 @@ qplot(x[x$source=="tbb",]$datalen, main="TCP payload length (TBB meek)", binwidt
 dev.off()
 
 png("diagrams/datalen-tbb-cdf.png")
-qplot(x[x$source=="tbb",]$datalen, stat="ecdf", geom="step", ylim=c(0,1), main="TCP payload length CDF (Alexa 500 with TBB)") + xlab("Length (Bytes)") + ylab("Probability") 
+qplot(x[x$source=="tbb",]$datalen, stat="ecdf", geom="step", xlim=range(lbl$datalen), ylim=c(0,1), main="TCP payload length CDF (Alexa 500 with TBB)") + xlab("Length (Bytes)") + ylab("Probability") 
 dev.off()
 
 syn.out <- lbl[lbl$syn & lbl$dir=="OUT",]

### 2014-07-29 diagrams.R
Remove unused variables.

@@ -8,9 +8,6 @@ x <- rbind(x, cbind(read.table("traces/meek_tbb_extension_tcp.pcap.tcp.log", col
 
 x <- x[order(x$t),]
 
-min.datalen <- min(x$datalen)
-max.datalen <- max(x$datalen)
-
 lbl = x[x$source=="lbl",]
 
 png("diagrams/datalen.png")

### 2014-07-29 docs/datalen.R
Redo the TCP payload length chart.

@@ -1,0 +1,27 @@
+library(ggplot2)
+
+col.names <- c("t", "src", "dst", "dir", "iplen", "datalen", "syn")
+
+# http://www.cookbook-r.com/Graphs/Facets_%28ggplot2%29/#modifying-facet-label-text
+label = function(variable, value) {
+	if (as.character(variable) != "source") {
+		stop()
+	}
+	value <- as.character(value)
+	value[value == "lbl"] <- "LBL Google HTTPS"
+	value[value == "tbb"] <- "meek on App Engine"
+	return(value)
+}
+
+x <- cbind(read.table("../traces/lbl.https.goog.dpriv.tcp.log", col.names=col.names), google=T, source="lbl")
+x <- rbind(x, cbind(read.table("../traces/lbl.https.non-goog.dpriv.tcp.log", col.names=col.names), google=F, source="lbl"))
+x <- rbind(x, cbind(read.table("../traces/meek_tbb_extension_tcp.pcap.tcp.log", col.names=col.names), google=T, source="tbb"))
+
+binwidth = 5
+
+p <- ggplot(x[x$google, ], aes(datalen))
+p <- p + geom_histogram(aes(y=..density..), binwidth=binwidth)
+p <- p + xlab("TCP payload length") + ylab("Fraction of TCP segments")
+p <- p + scale_y_continuous(labels = function(y) binwidth * y)
+p <- p + facet_grid(source ~ ., labeller = label)
+ggsave("datalen.pdf", width=4, height=4, units="in")

### 2014-07-29 docs/meek.tex
Note about appspot.
Add Psiphon3 graph.
UTF-8 input.
Survey of fronting-capable services.

@@
 \documentclass[conference]{IEEEtran}
+\usepackage[utf8]{inputenc}
 \usepackage{graphicx}
@@
 one has to create an account and pay for bandwidth.
-
 Fronting works with Google because Google App Engine, a web application platform,
 can host a simple ``reflector'' application that emulates
-an origin-pull CDN, simply forwarding every request to another server.
-Though App Engine's domain \urll{appspot.com}
-may be blocked because it can trivially be used to host a proxy,
-it can be fronted by essentially any Google domain, for example
-\urll{google.com}, \urll{gmail.com}, or \urll{googleapis.com}.
-App Engine charges for bandwidth,
-though it has a low-bandwidth free tier.
-% See Section~\ref{sec:deployment} for more discussion on deployment.
+an origin-pull CDN, simply forwarding every request to an origin server.
 
@@
 
+\section{A survey of fronting-capable web services}
+\label{sec:survey}
+
+This section contains a brief survey of the fronting-capable
+web services we have found, each with its pros and cons.
+The list is not exhaustive and is meant to illustrate the broad
+support that exists for fronting.
+Of the services listed, we have deployed meek
+only on Google App Engine and Amazon CloudFront.
+We have only checked that fronting works on the others.
+Recall that even web services that support fronting
+will front only for their own customers,
+so each deployment typically requires an investment of time and money.
+
+Google App Engine (\url{https://developers.google.com/appengine/})
+is a web application platform.
+Each application gets a subdomain of \urll{appspot.com},
+which can be fronted through almost any Google domain,
+including google.com, gmail.com, googleapis.com, and many others.
+App Engine can run only web applications,
+not a full Tor bridge;
+for that reason we use a tiny ``reflector'' application
+that merely copies incoming requests to a Tor bridge hosted elsewhere.
+Fronting through App Engine is attractive in the case where
+\urll{appspot.com} is blocked---not unlikely,
+because of the ease of building a proxy there---but
+at least one other Google service is reachable.
+Applications that use less than one gigabyte of bandwidth daily
+are free of charge,
+making possible an upload-your-own-app model
+à la GoAgent.
+
+Amazon CloudFront (\url{https://aws.amazon.com/cloudfront/}),
+not to be confused with CloudFlare,
+is the CDN of Amazon Web Services.
+A CloudFront ``distribution'' associates
+a randomly generated subdomain of \urll{cloudflare.net}
+with an origin server,
+which in our case is an instance of \meekserver.
+The front domain may be any other randomly generated subdomain---all
+of which support HTTPS through a wildcard certificate---or
+certain domain aliases like \urll{a0.awsstatic.com}.
+CloudFront has a usage tier that is free of charge for a year,
+subject to a bandwidth limit of 50 gigabytes per month.
+
+CloudFlare (\url{https://www.cloudflare.com/}),
+not to be confused with CloudFront,
+is a CDN also marketed as protection against
+denial-of-service attacks.
+It appears that any domain name on CloudFlare
+can front for any other, even custom domains;
+however it is not obvious which one is best to use as a front.
+The front domain needs to be popular
+(causing high collateral damage if blocked),
+or else the censor may call our bluff and simply block the domain entirely.
+It is doubly bad if that happens because not only is circumvention foiled,
+some unsuspecting third part has just had their web site blocked.
+A solution may be to round-robin through
+a pool of domain names;
+or to use ``domainless'' fronting that doesn't send SNI.
+Though CloudFlare supports domain fronting,
+its terms of service~\cite{cloudflare-terms}
+seem to prohibit the kind of tunneled proxying that meek does:
+\begin{quote}
+\textsc{Section 10: Limitation on non-HTML caching}\\
+You acknowledge that CloudFlare's Service is offered as a platform to cache and
+serve web pages and websites and is not offered for other purposes
+\ldots\ you understand and agree to use the Service solely
+for the purpose of hosting and serving web pages\ldots
+\end{quote}
+
+Akamai (\url{http://www.akamai.com/}) is a large CDN.
+Requests may be fronted through the special domain
+\urll{a248.e.akamai.net},
+which serves a certificate also good for \urll{*.akamaihd.net}.
+The collateral damage of blocking Akamai is enormous:
+in 2010 it carried 15--20\% of all web traffic~\cite{akamai}.
+Akamai costs more than other CDNs;
+it would likely require institutional support
+to keep a circumvention system running in the long term.
+
+Microsoft Azure (\url{http://azure.microsoft.com/})
+is a cloud computing platform that features a CDN.
+Similarly to CloudFront, users get a subdomain
+of \urll{vo.msecnd.net},
+all of which subdomains can front for each other.
+There are other fronting domain names, like \urll{ajax.aspnetcdn.com},
+that may offer enough collateral damage.
+
+Fastly (\url{http://www.fastly.com/}) is a CDN.
+It is unique among the the services we tested in that
+it is the only one that appears to enforce the SNI:
+if the SNI and Host do not match,
+the Fastly edge server returns an HTTP 400 error.
+It is thus the only service for which the ``domainless'' fronting style is required.
+
 \section{Camouflage of traffic characteristics}
@@
 
+\begin{figure}
+\includegraphics[width=\linewidth]{clients-psiphon3}
+\caption{Daily unique users of meek with Psiphon3.}
+\label{fig:clients}
+\end{figure}
+
 Figure~\ref{fig:clients} shows the average number of concurrent users of meek with Tor
@@
 % The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by meek.
+
+% Psiphon. Drop in July is due to an unblocking event.
+% Different counting method. Client self-reporting of last connection date.
 
@@
 
-% Psiphon
-
 \subsection{Other deployment scenarios}
@@
 rather than IP or SNI.
-We did not test deployment on CloudFlare,
-because their terms of service are not clear on whether this kind of use is allowed,
-and we got an ambiguous answer when we asked for clarification.
-A particular concern when using CloudFlare or other content delivery networks is the choice of front domain.
-If one domain is being used particularly as a front for circumvention traffic,
-it may find itself blocked by the censor, even though it is not itself
-involved in any circumvention.
-One good solution to this problem may be not to use a domain name at all,
-but only the IP address of one of CloudFlare's servers.
-The censor will then face the choice of allowing circumvention traffic,
-or else blocking a large number of unrelated web sites.
-
-% We were not able to make the system work with Amazon CloudFront nor Akamai.
+
 % Dreamhost? Other HTTPS webhosts with PHP bridge?
-
-The collateral damage of blocking Akamai is enormous: in 2010 it carried 15--20\% of all web traffic~\cite{akamai}.
 
@@
 % because App Engine requires requests to finish within 60 seconds.
+
+% App Engine works when appspot.com is blocked but google.com is not.
 
@@
 % who responded to our design ideas, reviewed source code, and tested our prototypes.
+% Thanks to Psiphon~Inc. for help with design and development, and for providing user count estimates.
 % George Kadianakis
@@
 % Yawning Angel
-% Rod Hynes and Michael Hull of Psiphon.
 % Ox from Lantern.

### 2014-07-29 docs/meek.tex
Miscellaneous revisions.

@@
 and Google's panoply of services---a nontrivial fraction of the web.
+See Section~\ref{sec:survey} for a listing of some suitable services.
 Domain fronting can be used as a means of tunneling traffic
@@
 circumvention traffic.
-
-To our knowledge,
-the earliest application of domain fronting to circumvention
-was by GoAgent~\cite{goagent},
-a tool based on App Engine and
-once widely used in China.
-Fronting has also been used with success since 2013
-for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
-GoAgent and flash proxy's rendezvous are the most direct
-inspirations of this work.
 
@@
 based on traffic characteristics like packet size and timing
-appears in Section~\ref{sec:trafficstatistics}.
+appears in Section~\ref{sec:analysis}.
 The analysis is based on comparing traffic traces of meek
 with samples of HTTPS traffic at an Internet router.
+
+To our knowledge,
+the earliest application of domain fronting to circumvention
+was by GoAgent~\cite{goagent},
+a tool based on App Engine and
+once widely used in China.
+Fronting has also been used with success since 2013
+for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
+GoAgent and flash proxy's rendezvous are the most direct
+inspirations of this work.
 
@@
 % Implemented in Psiphon's version.
-The other technique is to use
-long-lived persistent HTTP connections.
+The other technique,
+implemented in Psiphon's version of meek,
+uses long-lived persistent HTTP connections.
 When the server sends a response, it keeps the connection open,
@@
 it closes any response it has open to the client and starts a new response.
-See Section~\ref{sec:otherdeployment} for more details
-on when each technique may be used;
-it depends on the intermediate web service.
+This second technique doesn't work on all services:
+notably Google App Engine doesn't support streaming downloads of this kind.
 
@@
 to disguise the HTTPS tunnel.
-The next section is about more subtle and hard-to-apply forms of DPI.
+Section~\ref{sec:analysis} is about more subtle and hard-to-apply forms of DPI.
 
@@
 
-\section{Camouflage of traffic characteristics}
-\label{sec:trafficstatistics}
+\section{Analysis}
+\label{sec:analysis}
 
@@
 up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
-obtain a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983 MB in total. 
+obtain a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983~megabytes in total. 
 We also specifically extracted the traffic between LBL and Google from the trace. Since the trace 
@@
 will be mostly likely to compare suspicious traffic with normal Google traffic. The size of the 
-Google trace is 312 MB.
+Google trace is 312~megabytes.
 
@@
 \label{sec:security}
+
+% Censors that know no bounds: China on Google, Egypt.
 
@@
 
+% Prevalence of no SNI.
+
 \section{Deployment}

### 2014-07-29 docs/meek.tex
Revisions on packet length.

@@
 
+One of our goals in developing meek is to force
+the censor to use relatively expensive statistical classifiers
+to effect blocking---generally, to increase the cost of censorship.
+We believe meek as described is resistant to the ``easy''
+forms of blocking, namely IP address and DNS blocking,
+simple pattern-based DPI,
+and active probing.
+We hope that the censor will have to resort to measuring
+more subtle features of the communication like
+the packet length distribution and interpacket timing,
+or injecting traffic at the risk of causing collateral damage.
+In this section we provide a preliminary analysis
+of meek's resistance to such attacks.
+Specifically, we consider three traffic features:
+packet length distribution,
+number of simultaneous connections,
+and connection lifetime.
+
+The issue of statistical traffic anaysis is a general one~\cite{trafficmorphing},
+and mostly orthogonal to meek's main idea, domain fronting.
+It may be that the problem is
+best solved by a modular component not
+specifically designed for meek.
+
 % Advantage is that we are probably proxying web traffic.
-
-The censor cannot sniff the content of communications or infer the usage of meek 
-from packet \emph{data}, 
-since the communication is encrypted inside the TLS session, and we have devoted large efforts 
-in hiding TLS handshake fingerprints. However, it is still possible that the censor can detect 
-the existence of meek according to the \emph{meta-data}, i.e. traffic characteristics. 
-In this section we study a collection of traffic characteristics and evaluate their possibilities of becoming
-the censor's interest. Specifically, we consider three characteristics: 1) payload length of
-TCP packets, 2) number of concurrent HTTPS connections, 3) HTTPS connection lifetime.
-
-To collect the traffic trace of meek, we browses the Alexa top 500 websites sequentially using 
-the Tor Browser Bundle and dump the traffic trace from the network interface. We ensured only
-the browser can successfully access the network by setting
-up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
-obtain a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983~megabytes in total. 
-We also specifically extracted the traffic between LBL and Google from the trace. Since the trace 
-only has packet headers, we cannot extract the domain information. However, the \texttt{TXT} DNS
-records of the domain \texttt{\_netblocks.google.com} shows the IP address blocks that belongs to
-Google. Therefore, we determine whether a flow is from or to Google by examining the address in the 
-IP header. We only interested in the Google traffic only, because the censor who wants to defeat meek
-will be mostly likely to compare suspicious traffic with normal Google traffic. The size of the 
-Google trace is 312~megabytes.
-
-\begin{figure*}
+As meek is based on HTTPS,
+we compare traffic traces of meek against
+traces of ``ordinary'' HTTPS traffic.
+We did a packet capture
+automatically browsing the home pages
+of the top 500 Alexa web sites using meek,
+with a firewall in place so that no extraneous traffic was included.
+The browser used was Tor Browser,
+with the browser camouflage for meek described in Section~\ref{sec:browserextension},
+using Google App Engine as the intermediate web service.
+The meek trace is 687~megabytes in all.
+Our representative of ordinary HTTPS traffic
+is a sanitized trace of 10 minutes of HTTPS traffic
+% anon
+originating at Lawrence Berkeley National Laboratory (LBL).
+The LBL trace consists 313~megabytes of packet headers,
+not payloads, destined for TCP port 443 on any Google server.
+% Mention the non-google if it appears in a figure.
+The original IP addresses were replaced with a counter.
+
+\begin{figure}
 \centering
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figs/datalen-google-cdf.png}
-\caption{Normal Google Traffic}
-\label{fig:len:lbl}
-\end{subfigure}%
-%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
-%(or a blank line to force the subfigure onto a new line)
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics[width=\textwidth]{figs/datalen-tbb-cdf.png}
-\caption{Traffic Using meek}
-\label{fig:len:meek}
-\end{subfigure}
-
-\caption{TCP packet payload size distribution}
-\label{fig:len}
-\end{figure*}
-
-\paragraph{TCP payload length}
-Figure ~\ref{fig:len} shows the payload size distribution of normal traffic and meek's traffic. Both
-figures exhibit a significant amount of packets with no payload. These packets are mostly TCP SYN and ACK
-packets. Figure ~\ref{fig:len:lbl} shows the distribution of normal traffic, which indicates a large portion
-of small-sized packets. However, in the meek's traffic shown in Figure ~\ref{fig:len:meek}, most packets
-are large packets ranging from 1400 bytes to 1500 bytes. This result is unexpected, because the underlying packets 
-in the TLS session are sent from Tor. By default, each Tor cell is 512 bytes, but meek changes the packet size 
-distribution. Therefore, meek provides traffic shaping without additional efforts.
+\includegraphics[width=\linewidth]{datalen.pdf}
+\caption{
+Comparison of TCP payload length distributions
+between ordinary HTTPS connections to Google services
+from the LBL traffic trace,
+and meek running on App Engine, fronted through www.google.com.
+The histogram's bin width is 5~bytes.
+}
+\label{fig:datalen}
+\end{figure}
+
+\subsection{Packet length}
+Figure~\ref{fig:datalen}
+compares the packet length distribution of both traces in both directions.
+A few similarities are noticeable:
+roughly 37\% of packets have no payload; these are mostly ACKs.
+There is a small peak at the usual TCP Maximum Segment Size
+of 1460 bytes.
+% Other peaks near the max are probably near 1400, TLS maximum record size.
+The meek trace is missing a small peak of small packets
+present in the LBL trace.
+In its place, there are minor peaks at fairly distinct values,
+probably a reflection of Tor's fixed cell size
+and the fixed overhead of an encrypted HTTP header added
+to each transmission by meek.
+% Maybe mention apparent residue of a doubling of the three peaks at around 750.
+meek's trace is tends more overall to larger packets.
 
@@
 
-\paragraph{Concurrent connections}
+\subsection{Concurrent connections}
 Figure ~\ref{fig:connections} shows how many HTTPS connections to Google did a user make 
@@
 
-\paragraph{Connection lifetime}
+\subsection{Connection lifetime}
 We consider the connection lifetime as a potential weakness. Figure ~\ref{fig:duration:lbl} shows the 
@@
 
-\paragraph{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
+\subsection{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
 distinguishing meek's traffic. But admittedly there two potential weaknesses: long-lived connections 
@@
 
-% Censors that know no bounds: China on Google, Egypt.
+% Censors that know no bounds: China on Google, Egypt, Pakistan with YouTube.
 

### 2014-07-29 docs/datalen.R
Have datalen.R print out the most common values.

@@ -17,6 +17,12 @@ x <- cbind(read.table("../traces/lbl.https.goog.dpriv.tcp.log", col.names=col.na
 x <- rbind(x, cbind(read.table("../traces/lbl.https.non-goog.dpriv.tcp.log", col.names=col.names), google=F, source="lbl"))
 x <- rbind(x, cbind(read.table("../traces/meek_tbb_extension_tcp.pcap.tcp.log", col.names=col.names), google=T, source="tbb"))
 
+# Print the heavy hitters.
+t <- table(x[x$google & x$source=="lbl", ]$datalen)
+(t[order(t, decreasing=TRUE)] / sum(t))[1:15]
+t <- table(x[x$google & x$source=="tbb", ]$datalen)
+(t[order(t, decreasing=TRUE)] / sum(t))[1:15]
+
 binwidth = 5
 
 p <- ggplot(x[x$google, ], aes(datalen))

### 2014-07-29 diagrams.R
binwidth=5 in diagrams.

@@ -11,20 +11,20 @@ x <- x[order(x$t),]
 lbl = x[x$source=="lbl",]
 
 png("diagrams/datalen.png")
-qplot(lbl$datalen, geom="histogram", main="TCP payload length", binwidth=2) + xlab("length")  
+qplot(lbl$datalen, geom="histogram", main="TCP payload length", binwidth=5) + xlab("length")  
 
 dev.off()
 
 png("diagrams/datalen-in.png")
-qplot(lbl[lbl$dir=="IN",]$datalen, main="TCP payload length (incoming)", binwidth=2) + xlab("length") 
+qplot(lbl[lbl$dir=="IN",]$datalen, main="TCP payload length (incoming)", binwidth=5) + xlab("length") 
 dev.off()
 
 png("diagrams/datalen-out.png")
-qplot(lbl[lbl$dir=="OUT",]$datalen, main="TCP payload length (outgoing)", binwidth=2) + xlab("length") 
+qplot(lbl[lbl$dir=="OUT",]$datalen, main="TCP payload length (outgoing)", binwidth=5) + xlab("length") 
 dev.off()
 
 png("diagrams/datalen-google.png")
-qplot(lbl[lbl$google,]$datalen, main="TCP payload length (Google only)", binwidth=2) + xlab("length") 
+qplot(lbl[lbl$google,]$datalen, main="TCP payload length (Google only)", binwidth=5) + xlab("length") 
 dev.off()
 
 png("diagrams/datalen-google-cdf.png")
@@ -32,15 +32,15 @@ qplot(lbl[lbl$google,]$datalen, stat="ecdf", geom="step", xlim=range(lbl$datalen
 dev.off()
 
 png("diagrams/datalen-google-in.png")
-qplot(lbl[lbl$google & lbl$dir=="IN",]$datalen, main="TCP payload length (incoming, Google only)", binwidth=2) + xlab("length") 
+qplot(lbl[lbl$google & lbl$dir=="IN",]$datalen, main="TCP payload length (incoming, Google only)", binwidth=5) + xlab("length") 
 dev.off()
 
 png("diagrams/datalen-google-out.png")
-qplot(lbl[lbl$google & lbl$dir=="OUT",]$datalen, main="TCP payload length (outgoing, Google only)", binwidth=2) + xlab("length") 
+qplot(lbl[lbl$google & lbl$dir=="OUT",]$datalen, main="TCP payload length (outgoing, Google only)", binwidth=5) + xlab("length") 
[…]

### 2014-07-29 docs/datalen.R
Futzing with datalen.R.
I tried adding inbound/outbound to the graph, but it didn't look good.

@@ -4,12 +4,14 @@ col.names <- c("t", "src", "dst", "dir", "iplen", "datalen", "syn")
 
 # http://www.cookbook-r.com/Graphs/Facets_%28ggplot2%29/#modifying-facet-label-text
 label = function(variable, value) {
-	if (as.character(variable) != "source") {
-		stop()
-	}
 	value <- as.character(value)
-	value[value == "lbl"] <- "LBL Google HTTPS"
-	value[value == "tbb"] <- "meek on App Engine"
+	if (variable == "source") {
+		value[value == "lbl"] <- "LBL Google HTTPS"
+		value[value == "tbb"] <- "meek on App Engine"
+	} else if (variable == "dir") {
+		value[value == "IN"] <- "inbound"
+		value[value == "OUT"] <- "outbound"
+	}
 	return(value)
 }
 
@@ -19,9 +21,18 @@ x <- rbind(x, cbind(read.table("../traces/meek_tbb_extension_tcp.pcap.tcp.log", 
 
 # Print the heavy hitters.
 t <- table(x[x$google & x$source=="lbl", ]$datalen)
-(t[order(t, decreasing=TRUE)] / sum(t))[1:15]
+(t[order(t, decreasing=TRUE)] / sum(t))[1:10]
 t <- table(x[x$google & x$source=="tbb", ]$datalen)
-(t[order(t, decreasing=TRUE)] / sum(t))[1:15]
+(t[order(t, decreasing=TRUE)] / sum(t))[1:10]
+
+# t <- table(x[x$google & x$source=="lbl" & x$dir=="IN", ]$datalen)
+# (t[order(t, decreasing=TRUE)] / sum(t))[1:10]
+# t <- table(x[x$google & x$source=="lbl" & x$dir=="OUT", ]$datalen)
+# (t[order(t, decreasing=TRUE)] / sum(t))[1:10]
+# t <- table(x[x$google & x$source=="tbb" & x$dir=="IN", ]$datalen)
+# (t[order(t, decreasing=TRUE)] / sum(t))[1:10]
+# t <- table(x[x$google & x$source=="tbb" & x$dir=="OUT", ]$datalen)
+# (t[order(t, decreasing=TRUE)] / sum(t))[1:10]
 
 binwidth = 5
 

### 2014-07-29 docs/datalen.R
Shorter datalen graph.

@@ -41,4 +41,4 @@ p <- p + geom_histogram(aes(y=..density..), binwidth=binwidth)
 p <- p + xlab("TCP payload length") + ylab("Fraction of TCP segments")
 p <- p + scale_y_continuous(labels = function(y) binwidth * y)
 p <- p + facet_grid(source ~ ., labeller = label)
-ggsave("datalen.pdf", width=4, height=4, units="in")
+ggsave("datalen.pdf", width=4, height=3.75, units="in")

### 2014-07-29 docs/meek.tex
Remove extraneous.
More revisions on packet length.
I'm not sure about the speculation that I've just commented out--I've
been thinking about it and I'm not sure it's because of the browser
extension. I think the peak at 1418 bytes in the meek trace is caused by
something the Google frontend does to keep TLS records within a TCP
segment:

https://www.igvita.com/2013/10/24/optimizing-tls-record-size-and-buffering-latency/
http://chimera.labs.oreilly.com/books/1230000000545/ch04.html
"...leaves us with 1,400 bytes for each TLS record payload—adjust as needed
if your MTU is lower."

@@
 \usepackage[utf8]{inputenc}
+\usepackage{array}
 \usepackage{graphicx}
@@
 blocking requests without SNI,
-or finding some more subtle and expensive test to distinguish
+or finding some other, presumably more expensive, test to distinguish
 circumvention traffic.
@@
 % It resists blocking by address and by content,
-% Section~\ref{sec:security}
+% Section~\ref{sec:discussion}
 
@@
 based on traffic characteristics like packet size and timing
-appears in Section~\ref{sec:analysis}.
+appears in Section~\ref{sec:trafficanalysis}.
 The analysis is based on comparing traffic traces of meek
@@
 
-Section~\ref{sec:security} shows what happens when some
+Section~\ref{sec:discussion} shows what happens when some
 of these assumptions are violated;
@@
 to disguise the HTTPS tunnel.
-Section~\ref{sec:analysis} is about more subtle and hard-to-apply forms of DPI.
+Section~\ref{sec:trafficanalysis} is about more subtle and hard-to-apply forms of DPI.
 
@@
 the Fastly edge server returns an HTTP 400 error.
-It is thus the only service for which the ``domainless'' fronting style is required.
-
-\section{Analysis}
-\label{sec:analysis}
+It is thus the only service we have found
+for which the ``domainless'' fronting style is required.
+
+\section{Resistance to traffic analysis}
+\label{sec:trafficanalysis}
 
@@
 with a firewall in place so that no extraneous traffic was included.
-The browser used was Tor Browser,
-with the browser camouflage for meek described in Section~\ref{sec:browserextension},
-using Google App Engine as the intermediate web service.
+The used meek in Tor Browser,
+with the browser camouflage described in Section~\ref{sec:browserextension},
+and Google App Engine as the intermediate web service.
 The meek trace is 687~megabytes in all.
@@
 % anon
-originating at Lawrence Berkeley National Laboratory (LBL).
+from Lawrence Berkeley National Laboratory (LBL),
+comprising data to and from TCP port 443 on any Google server.
+% Mention the non-google if it appears in a figure.
+The trace contains packet headers only, not payloads
+were replaced by an incrementing counter.
 The LBL trace consists 313~megabytes of packet headers,
 not payloads, destined for TCP port 443 on any Google server.
-% Mention the non-google if it appears in a figure.
-The original IP addresses were replaced with a counter.
+The original IP addresses were masked by being
+replaced by a counter before we received the trace.
 
@@
 and meek running on App Engine, fronted through www.google.com.
-The histogram's bin width is 5~bytes.
+% The histogram's bin width is 5~bytes.
 }
@@
 compares the packet length distribution of both traces in both directions.
-A few similarities are noticeable:
-roughly 37\% of packets have no payload; these are mostly ACKs.
+Table~\ref{tab:datalen} summarizes the most common values.
+In both traces, about 38\% of packets have an empty payload, mostly ACKs.
 There is a small peak at the usual TCP Maximum Segment Size
 of 1460 bytes.
-% Other peaks near the max are probably near 1400, TLS maximum record size.
-The meek trace is missing a small peak of small packets
-present in the LBL trace.
-In its place, there are minor peaks at fairly distinct values,
-probably a reflection of Tor's fixed cell size
-and the fixed overhead of an encrypted HTTP header added
-to each transmission by meek.
-% Maybe mention apparent residue of a doubling of the three peaks at around 750.
-meek's trace is tends more overall to larger packets.
-
-To explain the phenomenon, recall that we use browsers to handle HTTPS connections for meek in order
-to hide TLS handshake characteristics.
-Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
-the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
-can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
-records meek's traffic.
-In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
-Google, click a result, and then close the tab that displays search results. The browser may close the 
-connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
-opens a new connection. In this case, small requests do not have such opportunity for batching.
-
-These browser techniques improve performance, but also pose unexpected consequences. 
-Although meek alters the packet size distribution of underlying Tor traffic, 
-the censor may be aware of the distribution of meek itself. 
-Additionally, the persistent connection itself can be an issue.
-We thus investigated other related characteristics.
+The concentration of values near 1418 bytes
+may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
+% https://github.com/joyent/node/issues/6889
+% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
+Conspicuous in the meek trace are a small number of
+likely packet sizes,
+and the lack of a cluster of small payload lengths of around 50 bytes.
+Both of these characteristics are probably artifacts
+of Tor's fixed cell size and the nearly fixed-size HTTP headers
+added by \meekclient\ and \meekserver.
+
+% Output of datalen.R.
+%
+% LBL
+%          0       1430       1418         41       1416       1460       1260
+% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
+%       1400       1359         33
+% 0.01673740 0.01126137 0.01100281
+%
+% meek
+%        1418           0        1460         396         196        1024
+% 0.405263438 0.376721457 0.071558122 0.019904635 0.018484229 0.014867466
+%         811         783         151        1263
+% 0.012312158 0.007811639 0.007030949 0.006568932
+\begin{table}[h]
+\normalsize
+\centering
+\begin{tabular}{r r >{\qquad} r r}
+\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{meek on App Engine} \\
+0 bytes & 37.7\% & 1418 bytes & 40.5\% \\
+1430 bytes & 9.1\% & 0 bytes & 37.8\% \\
+1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
+41 bytes & 6.1\% & 396 bytes & 2.0\% \\
+1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
+1460 bytes & 3.0\% & 1024 bytes & 1.5\%
+\end{tabular}
+\caption{The most common TCP payload lengths.}
+\label{tab:datalen}
+\end{table}
+
+% David: I don't think the following paragraph is true.
+% Almost all the length>1400 packets are Google→client, not client→Google,
+% as you can see if you split the histogram up by direction.
+%
+% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for meek in order
+% to hide TLS handshake characteristics.
+% Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
+% the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
+% can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
+% records meek's traffic.
+% In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
+% Google, click a result, and then close the tab that displays search results. The browser may close the 
+% connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
+% opens a new connection. In this case, small requests do not have such opportunity for batching.
+
+% These browser techniques improve performance, but also pose unexpected consequences. 
+% Although meek alters the packet size distribution of underlying Tor traffic, 
+% the censor may be aware of the distribution of meek itself. 
+% Additionally, the persistent connection itself can be an issue.
+% We thus investigated other related characteristics.
 
@@
 
-\section{Security}
-\label{sec:security}
+\section{Discussion}
+\label{sec:discussion}
 
@@
 
-A censor can block meek by blocking access to Google entirely,
-but other systems can take the place of Google.
-An attractive alternative is CloudFlare, a large content delivery network,
-which supports domain fronting, dispatching requests based on the Host header
-rather than IP or SNI.
-
 % Dreamhost? Other HTTPS webhosts with PHP bridge?

### 2014-07-29 bro-diagrams.R
Use a common naming convention for conn.logs.

@@ -7,9 +7,9 @@ broNames <-   c("ts",      "uid",    "id.orig_h", "id.orig_p", "id.resp_h", "id.
 #types           time       string    addr         port         addr         port         enum      string     interval    count         count         string        bool          count           string       count        count            count        count            table[string]
 broClasses <- c("numeric", "factor", "factor",    "factor",    "factor",    "factor",    "factor", "factor",  "numeric",  "integer",    "integer",    "character",  "logical",    "integer",      "character", "integer",   "integer",       "integer",   "integer",       "character")
 
-nongoog <- (read.table('non-goog.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
-goog <- (read.table('goog.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
-tbb <- (read.table('tbb.log', col.names=broNames, colClasses=broClasses, na.strings=c("-")))
+nongoog <- (read.table("traces/lbl.https.non-goog.dpriv.conn.log", col.names=broNames, colClasses=broClasses, na.strings=c("-")))
+goog <- (read.table("traces/lbl.https.goog.dpriv.conn.log", col.names=broNames, colClasses=broClasses, na.strings=c("-")))
+tbb <- (read.table("traces/meek_tbb_extension_tcp.pcap.conn.log", col.names=broNames, colClasses=broClasses, na.strings=c("-")))
 
 y <- nongoog$duration
 postscript("diagrams/flowduration.eps")

### 2014-07-29 docs/flowduration.R
Add flowduration.R script.

@@ -1,0 +1,25 @@
+library(ggplot2)
+
+#fields           ts         uid       id.orig_h    id.orig_p    id.resp_h    id.resp_p    proto     service    duration    orig_bytes    resp_bytes    conn_state    local_orig    missed_bytes    history      orig_pkts    orig_ip_bytes    resp_pkts    resp_ip_bytes    tunnel_parents
+bro.names <-   c("ts",      "uid",    "id.orig_h", "id.orig_p", "id.resp_h", "id.resp_p", "proto",  "service", "duration", "orig_bytes", "resp_bytes", "conn_state", "local_orig", "missed_bytes", "history",   "orig_pkts", "orig_ip_bytes", "resp_pkts", "resp_ip_bytes", "tunnel_parents")
+#types            time       string    addr         port         addr         port         enum      string     interval    count         count         string        bool          count           string       count        count            count        count            table[string]
+bro.classes <- c("numeric", "factor", "factor",    "factor",    "factor",    "factor",    "factor", "factor",  "numeric",  "integer",    "integer",    "character",  "logical",    "integer",      "character", "integer",   "integer",       "integer",   "integer",       "character")
+
+x <- cbind(read.table("../traces/lbl.https.goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=T, source="lbl")
+x <- rbind(x, cbind(read.table("../traces/lbl.https.non-goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=F, source="lbl"))
+x <- rbind(x, cbind(read.table("../traces/meek_tbb_extension_tcp.pcap.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=T, source="tbb"))
+
+p <- ggplot(x[x$google, ], aes(duration, colour=source))
+p <- p + stat_ecdf()
+p <- p + scale_x_log10(breaks=c( 1,  5,  10,  20, 24, 60,  120,  180, 240,  300,  600,  900,  1800,  3000, 3600),
+                       labels=c("1","5","10","20","","60","120","180", "", "300","600","900","1800",   "","3600"))
+# https://stackoverflow.com/questions/20167613/ggplot-plotting-cutout-of-cdf-while-maintaining-nomalization-according-to-whole
[…]

### 2014-07-29 docs/meek.tex
Use new flowduration graph.

@@
 \subsection{Concurrent connections}
-Figure ~\ref{fig:connections} shows how many HTTPS connections to Google did a user make 
+Figure ~\ref{fig:connections} shows how many HTTPS connections to Google user made
 during the 10-minute measurement window.
 There are 34,732 connections in total from 2,745 unique IPs. We observe that the majority of users have less than 
-50 connections to the Google frontend server, and most of the numbers concentrate on 1 ~ 10. This is not unexpected
-because a typical pattern of using Google is using the Google search as a stepping stone for other websites.
+50 connections to the Google frontend server, and most of the numbers concentrate on 1--10.
+
+% David: I think this needs to be justified. Leaving Gmail open all day is a common use case,
+% as is YouTube, as is finding +1 buttons and Google-source JavaScript on unrelated web sites.
+% This is not unexpected
+% because a typical pattern of using Google is using the Google search as a stepping stone for other websites.
 
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics[height=\textwidth, angle=270]{figs/flowduration-google-cdf.eps}
-\caption{Normal Google Traffic}
-\label{fig:duration:lbl}
-\end{subfigure}%
-%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
-%(or a blank line to force the subfigure onto a new line)
-\begin{subfigure}[b]{0.5\textwidth}
-\includegraphics[height=\textwidth, angle=270]{figs/flowduration-tbb-cdf.eps}
-\caption{Traffic Using meek (Notice the x-axis)}
-\label{fig:duration:meek}
-\end{subfigure}
-
-\caption{Connection lifetime distribution}
+\includegraphics[width=\linewidth]{flowduration}
+\caption{CDF of connection lifetime.}
 \label{fig:duration}
-\end{figure*}
+\end{figure}
 
 \subsection{Connection lifetime}
-We consider the connection lifetime as a potential weakness. Figure ~\ref{fig:duration:lbl} shows the 
+We consider the connection lifetime as a potential weakness. Figure~\ref{fig:duration} shows the 
 connection lifetime distribution of normal traffic. Interestingly we can see the concentration on 
@@
 consistent with the discussions above.
-Second, the durations are much longer if we notice the x-axis in Figure ~\ref{fig:duration:meek}.
+Second, the durations are much longer if we notice the x-axis in Figure~\ref{fig:duration}.
 If there is not a case in which normal users also have such long connections when browsing Google, the

### 2014-07-30 docs/datalen.R
Add source and dest ports to tcp.bro.

@@ -1,6 +1,6 @@
 library(ggplot2)
 
-col.names <- c("t", "src", "dst", "dir", "iplen", "datalen", "syn")
+col.names <- c("t", "src", "sport", "dst", "dport", "dir", "iplen", "datalen", "syn")
 
 # http://www.cookbook-r.com/Graphs/Facets_%28ggplot2%29/#modifying-facet-label-text
 label = function(variable, value) {

### 2014-07-30 docs/meek.tex
Note vertical axis.
Change 'h' float specifier to 'ht'.
LaTeX was doing it anyway:
LaTeX Warning: `h' float specifier changed to `ht'.
Filter out non-HTTPS traffic from the meek trace.

@@
 \def\meekserver{\mbox{meek-server}}
+\def\meek{meek}
 \def\urll#1{\begin{NoHyper}\url{#1}\end{NoHyper}}
@@
 
-We have implemented domain fronting in a system called meek,
+We have implemented domain fronting in a system called \meek,
 a pluggable transport for Tor.
-meek combines fronting with a proxy server that encodes a TCP stream
+\meek combines fronting with a proxy server that encodes a TCP stream
 as a sequence of HTTP requests and responses.
-The meek server's external interface is that of an ordinary web server.
+The \meek server's external interface is that of an ordinary web server.
 Communication with it is enabled through domain fronting.
@@
 but which actually arrive at a special web server on a Tor relay.
-meek, or something based on it,
+\meek, or something based on it,
 has been adopted by other circumvention systems including Lantern and Psiphon.
@@
 but there are other, more subtle considerations.
-We describe what we have done to disguise other traffic ``tells'' in meek,
+We describe what we have done to disguise other traffic ``tells'' in \meek,
 such as using a real web browser to make HTTPS requests
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
@@
 
-We have developed domain fronting into a full-fledged circumvention system called meek,
+We have developed domain fronting into a full-fledged circumvention system called \meek,
 implemented as a Tor pluggable transport~\cite{pt}.
-meek combines fronting with an HTTP-based tunneling proxy:
+\meek combines fronting with an HTTP-based tunneling proxy:
 upstream data are transformed into a sequence of HTTP requests,
@@
 through the same fronted channel.
-meek's architecture appears in Figure~\ref{fig:architecture}.
+\meek's architecture appears in Figure~\ref{fig:architecture}.
 Section~\ref{sec:architecture} describes its workings in detail.
@@
 \caption{
-Architecture of meek.
+Architecture of \meek.
 The client sends an HTTP request to the Tor bridge by way of an intermediate web service such as a CDN.
@@
 The bridge sends data back to the client in the HTTP response.
-\meekclient\ and \meekserver\ are transport plugins, the interface between Tor and meek.
+\meekclient\ and \meekserver\ are transport plugins, the interface between Tor and \meek.
 The host actually at allowed.example does not participate in the communication.
@@
 
-meek has been built into an alpha version of Tor Browser,
+\meek has been built into an alpha version of Tor Browser,
 and has seen use by a small number of users.
@@
 hidden by the front \urll{www.google.com}.
-Section~\ref{sec:deployment} discusses other systems meek can work with
+Section~\ref{sec:deployment} discusses other systems \meek can work with
 and other deployment scenarios.
 In addition to the Tor pluggable transport,
-systems based on meek are now in use by other circumvention systems
+systems based on \meek are now in use by other circumvention systems
 including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.
 
-% meek is designed to have features attractive in a circumvention transport.
+% \meek is designed to have features attractive in a circumvention transport.
 % It is easy to use, not requiring the configuration of any bridge addresses.
@@
 Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
-in order that meek's TLS and HTTPS characteristics
+in order that \meek's TLS and HTTPS characteristics
 match those of a browser as closely as possible.
-One of our goals for meek is to force the censor
+One of our goals for \meek is to force the censor
 to employ more sophisticated, expensive, and error-prone statistical tests
@@
 but of probabilities and false positives.
-A preliminary analysis of meek's resistance to detection
+A preliminary analysis of \meek's resistance to detection
 based on traffic characteristics like packet size and timing
 appears in Section~\ref{sec:trafficanalysis}.
-The analysis is based on comparing traffic traces of meek
+The analysis is based on comparing traffic traces of \meek
 with samples of HTTPS traffic at an Internet router.
@@
 Flash proxy's approach to address blocking is in a sense
-the opposite of meek's:
+the opposite of \meek's:
 where flash proxy uses many cheap, disposable, individually blockable proxies,
-meek uses just a few high-value front domains on hard-to-block network infrastructure.
+\meek uses just a few high-value front domains on hard-to-block network infrastructure.
 A quirk of the browser proxy model is that
@@
 
-GoAgent~\cite{goagent} is a direct inspiration for meek in its use of App
+GoAgent~\cite{goagent} is a direct inspiration for \meek in its use of App
 Engine and Host header--based domain fronting.
@@
 when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
-meek over App Engine was similarly affected.
+\meek over App Engine was similarly affected.
 % Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.
@@
 with encryption and traffic obfuscation between client and server.
-Psiphon uses domain fronting based on meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
+Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
 Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
 proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
-Lantern~1.4 is planned to use domain fronting inspired by meek~\cite{lantern-1.3.1}.
+Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.
 
@@
 
-% CORDON? Say how meek would be classified in it?
+% CORDON? Say how \meek would be classified in it?
 
@@
 and when the censor controls a certificate authority.
-That section also describes the use of meek apart from Tor.
+That section also describes the use of \meek apart from Tor.
 
@@
 
-\section{Architecture and protocol of meek}
+\section{Architecture and protocol of \meek}
 \label{sec:architecture}
@@
 The components of the system are shown in Figure~\ref{fig:architecture}.
-The parts that are new in meek
+The parts that are new in \meek
 are the programs \meekclient\ and \meekserver,
-which are the pluggable-transports~\cite{pt} interface between Tor and meek.
+which are the pluggable-transports~\cite{pt} interface between Tor and \meek.
 % All the programs are free software, naturally,
-% and may be downloaded from the meek home page at
+% and may be downloaded from the \meek home page at
 % \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
@@
 
-When meek is used with Google App Engine, one other component is needed.
+When \meek is used with Google App Engine, one other component is needed.
 It is a small ``reflector'' web app that simply copies any request
@@
 (source~IP, source port, dest~IP, dest~port) tuple,
-but that doesn't work for meek for two reasons:
+but that doesn't work for \meek for two reasons:
 the source IP of the requests is that of the intermediate web service,
@@
 \caption{
-Requests and responses in the meek HTTP protocol.
+Requests and responses in the \meek HTTP protocol.
 The session ID is randomly generated by the client.
@@
 in order and without gaps and duplicates.
-meek takes a naive approach: requests and responses are strictly serialized.
+\meek takes a naive approach: requests and responses are strictly serialized.
 The client doesn't send a second chunk of data
@@
 In order to enable the server to send back data,
-meek uses one of two techniques.
+\meek uses one of two techniques.
 The first is polling:
@@
 The other technique,
-implemented in Psiphon's version of meek,
+implemented in Psiphon's version of \meek,
 uses long-lived persistent HTTP connections.
@@
 which are browsers; the browsers are also unlike each other.
-A censor could block an uncamouflaged meek using Go's fingerprint,
+A censor could block an uncamouflaged \meek using Go's fingerprint,
 if it considered the collateral damage resulting from blocking other Go programs to be slight enough.
@@
 The use of a browser extension brings benefits beyond TLS camouflage.
-It means meek inherits other traffic characteristics of the browser:
+It means \meek inherits other traffic characteristics of the browser:
 for instance
@@
 The Firefox extension has special advantages
-when meek is used with Tor Browser
+when \meek is used with Tor Browser
 because Tor Browser
@@
 the headless Firefox is started and stopped transparently
-when meek is activated and deactivated.
+when \meek is activated and deactivated.
 
@@
 support that exists for fronting.
-Of the services listed, we have deployed meek
+Of the services listed, we have deployed \meek
 only on Google App Engine and Amazon CloudFront.
@@
 its terms of service~\cite{cloudflare-terms}
-seem to prohibit the kind of tunneled proxying that meek does:
+seem to prohibit the kind of tunneled proxying that \meek does:
 \begin{quote}
@@
 
-One of our goals in developing meek is to force
+One of our goals in developing \meek is to force
 the censor to use relatively expensive statistical classifiers
 to effect blocking---generally, to increase the cost of censorship.
-We believe meek as described is resistant to the ``easy''
+We believe \meek as described is resistant to the ``easy''
 forms of blocking, namely IP address and DNS blocking,
@@
 In this section we provide a preliminary analysis
-of meek's resistance to such attacks.
+of \meek's resistance to such attacks.
 Specifically, we consider three traffic features:
@@
 The issue of statistical traffic anaysis is a general one~\cite{trafficmorphing},
-and mostly orthogonal to meek's main idea, domain fronting.
+and mostly orthogonal to \meek's main idea, domain fronting.
 It may be that the problem is
 best solved by a modular component not
-specifically designed for meek.
+specifically designed for \meek.
 
 % Advantage is that we are probably proxying web traffic.
-As meek is based on HTTPS,
-we compare traffic traces of meek against
+As \meek is based on HTTPS,
+we compare traffic traces of \meek against
 traces of ``ordinary'' HTTPS traffic.
@@
 automatically browsing the home pages
-of the top 500 Alexa web sites using meek,
+of the top 500 Alexa web sites using \meek,
 with a firewall in place so that no extraneous traffic was included.
-The used meek in Tor Browser,
+The used \meek in Tor Browser,
 with the browser camouflage described in Section~\ref{sec:browserextension},
 and Google App Engine as the intermediate web service.
-The meek trace is 687~megabytes in all.
+The \meek trace is 687~megabytes in all.
 Our representative of ordinary HTTPS traffic
@@
 from the LBL traffic trace,
-and meek running on App Engine, fronted through www.google.com.
+and \meek running on App Engine, fronted through www.google.com.
 % The histogram's bin width is 5~bytes.
@@
 % http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
-Conspicuous in the meek trace are a small number of
+Conspicuous in the \meek trace are a small number of
 likely packet sizes,
@@
 %        1418           0        1460         396         196        1024
-% 0.405263438 0.376721457 0.071558122 0.019904635 0.018484229 0.014867466
+% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
 %         811         783         151        1263
-% 0.012312158 0.007811639 0.007030949 0.006568932
-\begin{table}[h]
+% 0.012312668 0.007811963 0.007031241 0.006569205
+\begin{table}[ht]
 \normalsize
@@
 \begin{tabular}{r r >{\qquad} r r}
-\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{meek on App Engine} \\
-0 bytes & 37.7\% & 1418 bytes & 40.5\% \\
-1430 bytes & 9.1\% & 0 bytes & 37.8\% \\
+\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
+0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
+1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
 1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
@@
 1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
-1460 bytes & 3.0\% & 1024 bytes & 1.5\%
+1460 bytes & 2.9\% & 1024 bytes & 1.5\%
 \end{tabular}
@@
 %
-% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for meek in order
+% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for \meek in order
 % to hide TLS handshake characteristics.
-% Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
+% Browsers also apply techniques like HTTP pipelining to improve performance. Since \meek is always communicating with
 % the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
 % can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
-% records meek's traffic.
+% records \meek's traffic.
 % In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
@@
 % These browser techniques improve performance, but also pose unexpected consequences. 
-% Although meek alters the packet size distribution of underlying Tor traffic, 
-% the censor may be aware of the distribution of meek itself. 
+% Although \meek alters the packet size distribution of underlying Tor traffic, 
+% the censor may be aware of the distribution of \meek itself. 
 % Additionally, the persistent connection itself can be an issue.
@@
 
-The distribution of meek's traffic, in contrast, is totally different. First, there are much fewer connections, which is 
+The distribution of \meek's traffic, in contrast, is totally different. First, there are much fewer connections, which is 
 consistent with the discussions above.
@@
 censor has to wait until a time threshold is reached. The user might have already obtained the forbidden data she wants, or 
-meek could simply restart a connection.
+\meek could simply restart a connection.
 
 \subsection{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
-distinguishing meek's traffic. But admittedly there two potential weaknesses: long-lived connections 
+distinguishing \meek's traffic. But admittedly there two potential weaknesses: long-lived connections 
 with bulk data transfer, and deviated distribution of packet sizes. To fundamentally fix these weaknesses 
@@
 
-We implemented meek as a pluggable transport~\cite{pt} for Tor.
+We implemented \meek as a pluggable transport~\cite{pt} for Tor.
 Although it is possible to use the system with proxies other than Tor,
@@
 
-% meek apart from Tor.
+% \meek apart from Tor.
 % more risk for the proxy operator
@@
 
-We implemented meek as a Tor pluggable transport~\cite{pt}
-and built experimental releases of the Tor Browser Bundle featuring meek.
+We implemented \meek as a Tor pluggable transport~\cite{pt}
+and built experimental releases of the Tor Browser Bundle featuring \meek.
 The browser bundle includes Tor and a version of Firefox
 called Tor Browser that is patched to defend against application-layer identity leaks.
-Users need to download and run the bundle and select meek from the list of transports,
+Users need to download and run the bundle and select \meek from the list of transports,
 and then a browser window appears,
-configured to use meek for circumvention and Tor for anonymity.
+configured to use \meek for circumvention and Tor for anonymity.
 We announced our prototype bundles on Tor development mailing lists,
@@
 \includegraphics[width=\linewidth]{clients-meek}
-\caption{Concurrent users of meek with Tor.}
+\caption{Concurrent users of \meek with Tor.}
 \label{fig:clients}
@@
 \includegraphics[width=\linewidth]{clients-psiphon3}
-\caption{Daily unique users of meek with Psiphon3.}
+\caption{Daily unique users of \meek with Psiphon3 (note vertical axis).}
 \label{fig:clients}
@@
 
-Figure~\ref{fig:clients} shows the average number of concurrent users of meek with Tor
+Figure~\ref{fig:clients} shows the average number of concurrent users of \meek with Tor
 since close to the beginning of development,
@@
 of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
-% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by meek.
+% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by \meek.
 
@@
 
-meek has a home page at
+\meek has a home page at
 \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
@@
 could make this possible.
-% Would be useful for Iran-like session cutoff, independent of meek.
+% Would be useful for Iran-like session cutoff, independent of \meek.
 
@@
 We would like to do more quantitative performance measurements,
-in order to measure the overhead in bandwidth and latency that meek has over plain Tor.
+in order to measure the overhead in bandwidth and latency that \meek has over plain Tor.
 We have done informal tests, such as browsing YouTube,

### 2014-07-30 docs/datalen.R

@@ -17,7 +17,7 @@ label = function(variable, value) {
 
 x <- cbind(read.table("../traces/lbl.https.goog.dpriv.tcp.log", col.names=col.names), google=T, source="lbl")
 x <- rbind(x, cbind(read.table("../traces/lbl.https.non-goog.dpriv.tcp.log", col.names=col.names), google=F, source="lbl"))
-x <- rbind(x, cbind(read.table("../traces/meek_tbb_extension_tcp.pcap.tcp.log", col.names=col.names), google=T, source="tbb"))
+x <- rbind(x, cbind(subset(read.table("../traces/meek_tbb_extension_tcp.pcap.tcp.log", col.names=col.names), dport==443), google=T, source="tbb"))
 
 # Print the heavy hitters.
 t <- table(x[x$google & x$source=="lbl", ]$datalen)

### 2014-07-30 docs/flowduration.R

@@ -7,7 +7,7 @@ bro.classes <- c("numeric", "factor", "factor",    "factor",    "factor",    "fa
 
 x <- cbind(read.table("../traces/lbl.https.goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=T, source="lbl")
 x <- rbind(x, cbind(read.table("../traces/lbl.https.non-goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=F, source="lbl"))
-x <- rbind(x, cbind(read.table("../traces/meek_tbb_extension_tcp.pcap.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=T, source="tbb"))
+x <- rbind(x, cbind(subset(read.table("../traces/meek_tbb_extension_tcp.pcap.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), id.resp_p==443), google=T, source="tbb"))
 
 p <- ggplot(x[x$google, ], aes(duration, colour=source))
 p <- p + stat_ecdf()

### 2014-07-30 docs/flowduration.R
Tweaks to flowduration.

@@ -3,23 +3,27 @@ library(ggplot2)
 #fields           ts         uid       id.orig_h    id.orig_p    id.resp_h    id.resp_p    proto     service    duration    orig_bytes    resp_bytes    conn_state    local_orig    missed_bytes    history      orig_pkts    orig_ip_bytes    resp_pkts    resp_ip_bytes    tunnel_parents
 bro.names <-   c("ts",      "uid",    "id.orig_h", "id.orig_p", "id.resp_h", "id.resp_p", "proto",  "service", "duration", "orig_bytes", "resp_bytes", "conn_state", "local_orig", "missed_bytes", "history",   "orig_pkts", "orig_ip_bytes", "resp_pkts", "resp_ip_bytes", "tunnel_parents")
 #types            time       string    addr         port         addr         port         enum      string     interval    count         count         string        bool          count           string       count        count            count        count            table[string]
-bro.classes <- c("numeric", "factor", "factor",    "factor",    "factor",    "factor",    "factor", "factor",  "numeric",  "integer",    "integer",    "character",  "logical",    "integer",      "character", "integer",   "integer",       "integer",   "integer",       "character")
+bro.classes <- c("numeric", "factor", "factor",    "factor",    "factor",    "factor",    "factor", "factor",  "numeric",  "integer",    "integer",    "factor",     "logical",    "integer",      "character", "integer",   "integer",       "integer",   "integer",       "character")
 
 x <- cbind(read.table("../traces/lbl.https.goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=T, source="lbl")
 x <- rbind(x, cbind(read.table("../traces/lbl.https.non-goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=F, source="lbl"))
 x <- rbind(x, cbind(subset(read.table("../traces/meek_tbb_extension_tcp.pcap.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), id.resp_p==443), google=T, source="tbb"))
 
+# Read some values off the LBL graph.
+print(sprintf("%.1f%%", 100*ecdf(x[x$google & x$source=="lbl", ]$duration)(c(24, 300, 600))))
[…]

### 2014-07-30 docs/meek.tex
Misc. revisions.

@@
 implementations may differ.
-Figure~\ref{fig:ciphersuites:golang} is from the Go programming languages
-built-in net/http library~\cite{golang-net/http},
-which has a custom TLS implementation;
-it is how \meekclient\ would appear with no TLS camouflage.
-It is unlike Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
-which are browsers; the browsers are also unlike each other.
+\meekclient\ is written in the Go programming language,
+which has a custom TLS library~\cite{golang-crypto/tls};
+Figure~\ref{fig:ciphersuites:golang}
+shows how it would appear with no TLS camouflage.
+Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
+which are browsers, are different; the browsers are also unlike each other.
 A censor could block an uncamouflaged \meek using Go's fingerprint,
@@
 the Fastly edge server returns an HTTP 400 error.
-It is thus the only service we have found
-for which the ``domainless'' fronting style is required.
+It is the only service we have found
+that requires the ``domainless'' fronting style.
 
@@
 best solved by a modular component not
-specifically designed for \meek.
+necessarily specifically designed for \meek.
 
@@
 and Google App Engine as the intermediate web service.
-The \meek trace is 687~megabytes in all.
+The \meek trace is 687~megabytes in all
+and covers about 4.5 hours of network activity.
 Our representative of ordinary HTTPS traffic

### 2014-07-30 docs/meek.tex
Replace "meek" with "\meek"
In case we want to change the font or style.

--- 2014-07-30 docs/meek.tex
@@
 %        1418           0        1460         396         196        1024
-% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
+% 0.405263438 0.376721457 0.071558122 0.019904635 0.018484229 0.014867466
 %         811         783         151        1263
-% 0.012312668 0.007811963 0.007031241 0.006569205
+% 0.012312158 0.007811639 0.007030949 0.006568932
 \begin{table}[ht]
@@
 \multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
-0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
-1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
+0 bytes & 37.7\% & 1418 bytes & 40.5\% \\
+1430 bytes & 9.1\% & 0 bytes & 37.8\% \\
 1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
@@
 1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
-1460 bytes & 2.9\% & 1024 bytes & 1.5\%
+1460 bytes & 3.0\% & 1024 bytes & 1.5\%
 \end{tabular}

### 2014-07-30 docs/meek.tex
Connection duration revisions.

--- 2014-07-30 docs/meek.tex
@@
 
+\subsection{Connection lifetime}
+
 \begin{figure}
@@
 \includegraphics[width=\linewidth]{flowduration}
-\caption{CDF of connection lifetime.}
+\caption{
+CDF of connection lifetime.
+The horizontal axis is logarithmic.
+meek's connections tend to last longer than those of ordinary HTTPS traffic.
+}
 \label{fig:duration}
@@
 
-\subsection{Connection lifetime}
-We consider the connection lifetime as a potential weakness. Figure~\ref{fig:duration} shows the 
-connection lifetime distribution of normal traffic. Interestingly we can see the concentration on 
-several discrete values: 60s, 120s, 180s, 240s. We hypothesize that it is due to the HTTP Keep-Alive 
-timeout of different browsers and web services. Another important observation is the concentration on 
-durations that exceed 600 seconds. Note that our trace only contains 10 minutes' data, therefore the concentration 
-on 600 seconds does not reflect that these connections' actual duration is 600 seconds. Rather, 600 seconds
-is the lower bound of their actual duration. Thus, we can conclude that only about 10\% connections last 
-longer than 600 seconds.
-
-The distribution of \meek's traffic, in contrast, is totally different. First, there are much fewer connections, which is 
-consistent with the discussions above.
-Second, the durations are much longer if we notice the x-axis in Figure~\ref{fig:duration}.
-If there is not a case in which normal users also have such long connections when browsing Google, the
-censor can potentially block any long connections between users and Google. Even if this is the case, the
-censor has to wait until a time threshold is reached. The user might have already obtained the forbidden data she wants, or 
-\meek could simply restart a connection.
+% Output of flowduration.R.
+% LBL
+% [1] "42.6%" "87.0%" "92.2%"
+% meek
+% [1] "10.0%" "30.0%" "40.0%"
+
+We consider the duration of TCP connections as a potential distinguisher.
+Figure~\ref{fig:duration} shows the cumulative probability
+of connection duration in our two traces.
+Considering the LBL trace first,
+we see interesting probability concentrations on
+some round numbers: 10~s, 60~s, 120~s, 180~s, and 240~s.
+We hypothesize that this phenomenon is caused by
+keepalive timeouts in web browsers and servers,
+and polling behavior of web apps.
+The small rise at 600 seconds is an artifact caused
+by the fact that the trace is only 10 minutes long.
+Connections lasting longer than 10 minutes are not accurately reflected,
+however we can say that only about 8\% of connections lasted longer than 10 minutes.
+
+The \meek trace shows a propensity for longer connections.
+Over 4.5 hours, there were only 10 connections,
+three of them lasting for an hour.
+The long connections are caused by the client browser extension's
+use of long-lived HTTP keepalive connections,
+combined with \meekclient's polling requests,
+which keep the connection from becoming idle.
+The traffic trace represents the browsing of hundreds of web sites
+and thousands of HTTPS transactions, but they all
+occurred over just a few TCP/TLS connections.
+60\% of \meek connections lasts five minutes or longer,
+while only 13\% of those of ordinary traffic does.
+\meek has essentially no connections lasting less than 24 seconds,
+but such short connections account for over 42\% of the LBL HTTPS connections.
+30\% (3 out of 10) of \meek's connections lasted almost exactly one hour,
+evidently reflecting a built-in time limit in either the client browser extension
+or in App Engine.
+
+The censor may decide to block any long-lived HTTPS connections between
+a client and a web service.
+According to our traffic trace, doing so will not disrupt more than 8\% of ordinary connections;
+whether that is an acceptable cost depends on the censor's
+tolerance for collateral damage.
+The censor can lower the timing threshold, at the cost of more false positives.
+Duration-based blocking is favorable for the circumventor,
+because if the censor terminates connections after, say, 10 minutes,
+that's 10 minutes of circumvention achieved,
+after which \meek can start a new connection
+and allow Tor to rebuild its circuits.
+Future enhancements may even allow reconnecting using the same session ID,
+so there will be no effect on the client other than a brief delay
+while a new HTTPS connection is established.
+
+% meek is fairly robust against connection termination.
+% Well, not really for long-lived TCP connections.
+% But it could be.
+% Can reconnect and make a new circuit.
 

### 2014-07-30 docs/meek.tex
Don't confuse CloudFlare and CloudFront.

@@
 A CloudFront ``distribution'' associates
-a randomly generated subdomain of \urll{cloudflare.net}
+a randomly generated subdomain of \urll{cloudfront.net}
 with an origin server,

### 2014-07-30 docs/meek.tex
Typo.
Escape spaces after "\meek".
You need this, otherwise the escape sequence eats the space. I.e.,
	\meek combines fronting with a proxy server
renders as
	meekcombines fronting with a proxy server

@@
 a pluggable transport for Tor.
-\meek combines fronting with a proxy server that encodes a TCP stream
+\meek\ combines fronting with a proxy server that encodes a TCP stream
 as a sequence of HTTP requests and responses.
-The \meek server's external interface is that of an ordinary web server.
+The \meek\ server's external interface is that of an ordinary web server.
 Communication with it is enabled through domain fronting.
@@
 implemented as a Tor pluggable transport~\cite{pt}.
-\meek combines fronting with an HTTP-based tunneling proxy:
+\meek\ combines fronting with an HTTP-based tunneling proxy:
 upstream data are transformed into a sequence of HTTP requests,
@@
 
-\meek has been built into an alpha version of Tor Browser,
+\meek\ has been built into an alpha version of Tor Browser,
 and has seen use by a small number of users.
@@
 hidden by the front \urll{www.google.com}.
-Section~\ref{sec:deployment} discusses other systems \meek can work with
+Section~\ref{sec:deployment} discusses other systems \meek\ can work with
 and other deployment scenarios.
 In addition to the Tor pluggable transport,
-systems based on \meek are now in use by other circumvention systems
+systems based on \meek\ are now in use by other circumvention systems
 including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.
 
-% \meek is designed to have features attractive in a circumvention transport.
+% \meek\ is designed to have features attractive in a circumvention transport.
 % It is easy to use, not requiring the configuration of any bridge addresses.
@@
 match those of a browser as closely as possible.
-One of our goals for \meek is to force the censor
+One of our goals for \meek\ is to force the censor
 to employ more sophisticated, expensive, and error-prone statistical tests
@@
 where flash proxy uses many cheap, disposable, individually blockable proxies,
-\meek uses just a few high-value front domains on hard-to-block network infrastructure.
+\meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
 A quirk of the browser proxy model is that
@@
 
-GoAgent~\cite{goagent} is a direct inspiration for \meek in its use of App
+GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of App
 Engine and Host header--based domain fronting.
@@
 when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
-\meek over App Engine was similarly affected.
+\meek\ over App Engine was similarly affected.
 % Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.
@@
 with encryption and traffic obfuscation between client and server.
-Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
+Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
 Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
@@
 
-% CORDON? Say how \meek would be classified in it?
+% CORDON? Say how \meek\ would be classified in it?
 
@@
 and when the censor controls a certificate authority.
-That section also describes the use of \meek apart from Tor.
+That section also describes the use of \meek\ apart from Tor.
 
@@
 % All the programs are free software, naturally,
-% and may be downloaded from the \meek home page at
+% and may be downloaded from the \meek\ home page at
 % \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
@@
 
-When \meek is used with Google App Engine, one other component is needed.
+When \meek\ is used with Google App Engine, one other component is needed.
 It is a small ``reflector'' web app that simply copies any request
@@
 (source~IP, source port, dest~IP, dest~port) tuple,
-but that doesn't work for \meek for two reasons:
+but that doesn't work for \meek\ for two reasons:
 the source IP of the requests is that of the intermediate web service,
@@
 \caption{
-Requests and responses in the \meek HTTP protocol.
+Requests and responses in the \meek\ HTTP protocol.
 The session ID is randomly generated by the client.
@@
 in order and without gaps and duplicates.
-\meek takes a naive approach: requests and responses are strictly serialized.
+\meek\ takes a naive approach: requests and responses are strictly serialized.
 The client doesn't send a second chunk of data
@@
 In order to enable the server to send back data,
-\meek uses one of two techniques.
+\meek\ uses one of two techniques.
 The first is polling:
@@
 which are browsers, are different; the browsers are also unlike each other.
-A censor could block an uncamouflaged \meek using Go's fingerprint,
+A censor could block an uncamouflaged \meek\ using Go's fingerprint,
 if it considered the collateral damage resulting from blocking other Go programs to be slight enough.
@@
 The use of a browser extension brings benefits beyond TLS camouflage.
-It means \meek inherits other traffic characteristics of the browser:
+It means \meek\ inherits other traffic characteristics of the browser:
 for instance
@@
 The Firefox extension has special advantages
-when \meek is used with Tor Browser
+when \meek\ is used with Tor Browser
 because Tor Browser
@@
 the headless Firefox is started and stopped transparently
-when \meek is activated and deactivated.
+when \meek\ is activated and deactivated.
 
@@
 its terms of service~\cite{cloudflare-terms}
-seem to prohibit the kind of tunneled proxying that \meek does:
+seem to prohibit the kind of tunneled proxying that \meek\ does:
 \begin{quote}
@@
 
-One of our goals in developing \meek is to force
+One of our goals in developing \meek\ is to force
 the censor to use relatively expensive statistical classifiers
 to effect blocking---generally, to increase the cost of censorship.
-We believe \meek as described is resistant to the ``easy''
+We believe \meek\ as described is resistant to the ``easy''
 forms of blocking, namely IP address and DNS blocking,
@@
 
-The issue of statistical traffic anaysis is a general one~\cite{trafficmorphing},
+The issue of statistical traffic analysis is a general one~\cite{trafficmorphing},
 and mostly orthogonal to \meek's main idea, domain fronting.
@@
 % Advantage is that we are probably proxying web traffic.
-As \meek is based on HTTPS,
-we compare traffic traces of \meek against
+As \meek\ is based on HTTPS,
+we compare traffic traces of \meek\ against
 traces of ``ordinary'' HTTPS traffic.
@@
 with a firewall in place so that no extraneous traffic was included.
-The used \meek in Tor Browser,
+The used \meek\ in Tor Browser,
 with the browser camouflage described in Section~\ref{sec:browserextension},
 and Google App Engine as the intermediate web service.
-The \meek trace is 687~megabytes in all
+The \meek\ trace is 687~megabytes in all
 and covers about 4.5 hours of network activity.
@@
 from the LBL traffic trace,
-and \meek running on App Engine, fronted through www.google.com.
+and \meek\ running on App Engine, fronted through www.google.com.
 % The histogram's bin width is 5~bytes.
@@
 % http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
-Conspicuous in the \meek trace are a small number of
+Conspicuous in the \meek\ trace are a small number of
 likely packet sizes,
@@
 \begin{tabular}{r r >{\qquad} r r}
-\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
+\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
 0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
@@
 %
-% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for \meek in order
+% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for \meek\ in order
 % to hide TLS handshake characteristics.
-% Browsers also apply techniques like HTTP pipelining to improve performance. Since \meek is always communicating with
+% Browsers also apply techniques like HTTP pipelining to improve performance. Since \meek\ is always communicating with
 % the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
@@
 % These browser techniques improve performance, but also pose unexpected consequences. 
-% Although \meek alters the packet size distribution of underlying Tor traffic, 
-% the censor may be aware of the distribution of \meek itself. 
+% Although \meek\ alters the packet size distribution of underlying Tor traffic, 
+% the censor may be aware of the distribution of \meek\ itself. 
 % Additionally, the persistent connection itself can be an issue.
@@
 
-The \meek trace shows a propensity for longer connections.
+The \meek\ trace shows a propensity for longer connections.
 Over 4.5 hours, there were only 10 connections,
@@
 occurred over just a few TCP/TLS connections.
-60\% of \meek connections lasts five minutes or longer,
+60\% of \meek\ connections lasts five minutes or longer,
 while only 13\% of those of ordinary traffic does.
-\meek has essentially no connections lasting less than 24 seconds,
+\meek\ has essentially no connections lasting less than 24 seconds,
 but such short connections account for over 42\% of the LBL HTTPS connections.
@@
 that's 10 minutes of circumvention achieved,
-after which \meek can start a new connection
+after which \meek\ can start a new connection
 and allow Tor to rebuild its circuits.
@@
 
-We implemented \meek as a pluggable transport~\cite{pt} for Tor.
+We implemented \meek\ as a pluggable transport~\cite{pt} for Tor.
 Although it is possible to use the system with proxies other than Tor,
@@
 
-% \meek apart from Tor.
+% \meek\ apart from Tor.
 % more risk for the proxy operator
@@
 
-We implemented \meek as a Tor pluggable transport~\cite{pt}
+We implemented \meek\ as a Tor pluggable transport~\cite{pt}
 and built experimental releases of the Tor Browser Bundle featuring \meek.
@@
 called Tor Browser that is patched to defend against application-layer identity leaks.
-Users need to download and run the bundle and select \meek from the list of transports,
+Users need to download and run the bundle and select \meek\ from the list of transports,
 and then a browser window appears,
-configured to use \meek for circumvention and Tor for anonymity.
+configured to use \meek\ for circumvention and Tor for anonymity.
 We announced our prototype bundles on Tor development mailing lists,
@@
 \includegraphics[width=\linewidth]{clients-meek}
-\caption{Concurrent users of \meek with Tor.}
+\caption{Concurrent users of \meek\ with Tor.}
 \label{fig:clients}
@@
 \includegraphics[width=\linewidth]{clients-psiphon3}
-\caption{Daily unique users of \meek with Psiphon3 (note vertical axis).}
+\caption{Daily unique users of \meek\ with Psiphon3 (note vertical axis).}
 \label{fig:clients}
@@
 
-Figure~\ref{fig:clients} shows the average number of concurrent users of \meek with Tor
+Figure~\ref{fig:clients} shows the average number of concurrent users of \meek\ with Tor
 since close to the beginning of development,
@@
 
-\meek has a home page at
+\meek\ has a home page at
 \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
@@
 We would like to do more quantitative performance measurements,
-in order to measure the overhead in bandwidth and latency that \meek has over plain Tor.
+in order to measure the overhead in bandwidth and latency that \meek\ has over plain Tor.
 We have done informal tests, such as browsing YouTube,

### 2014-07-30 docs/flowduration.R
Restore horizontal minors on flowduration chart.
Vertical minors are disabled because they get drawn halfway between
breaks, which is weird with a log axis.

@@ -21,7 +21,7 @@ p <- p + scale_x_log10(breaks=c( 1,  5,  10,  24,  60,  120,  180, 240,  300,  6
 p <- p + coord_cartesian(xlim=c(5, 3800))
 p <- p + xlab("Duration (seconds)") + ylab("Fraction of connections")
 p <- p + theme(axis.text=element_text(size=7), axis.title=element_text(size=8))
-p <- p + theme(panel.grid.minor=element_blank())
+p <- p + theme(panel.grid.minor.x=element_blank())
 p <- p + theme(legend.position="none")
 p <- p + annotate("text", x=220, y=0.82, label="LBL Google HTTPS", hjust=1, size=2.5)
 p <- p + annotate("text", x=800, y=0.44, label="meek on App Engine", hjust=1, size=2.5)

### 2014-07-30 docs/concurrent.R
concurrent graph.

@@ -1,0 +1,66 @@
+library(ggplot2)
+
+#fields           ts         uid       id.orig_h    id.orig_p    id.resp_h    id.resp_p    proto     service    duration    orig_bytes    resp_bytes    conn_state    local_orig    missed_bytes    history      orig_pkts    orig_ip_bytes    resp_pkts    resp_ip_bytes    tunnel_parents
+bro.names <-   c("ts",      "uid",    "id.orig_h", "id.orig_p", "id.resp_h", "id.resp_p", "proto",  "service", "duration", "orig_bytes", "resp_bytes", "conn_state", "local_orig", "missed_bytes", "history",   "orig_pkts", "orig_ip_bytes", "resp_pkts", "resp_ip_bytes", "tunnel_parents")
+#types            time       string    addr         port         addr         port         enum      string     interval    count         count         string        bool          count           string       count        count            count        count            table[string]
+bro.classes <- c("numeric", "factor", "factor",    "factor",    "factor",    "factor",    "factor", "factor",  "numeric",  "integer",    "integer",    "factor",     "logical",    "integer",      "character", "integer",   "integer",       "integer",   "integer",       "character")
+
+x <- cbind(read.table("../traces/lbl.https.goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=T, source="lbl")
+x <- rbind(x, cbind(read.table("../traces/lbl.https.non-goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=F, source="lbl"))
+x <- rbind(x, cbind(subset(read.table("../traces/meek_tbb_extension_tcp.pcap.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), id.resp_p==443), google=T, source="tbb"))
+
+# Some RSTOS0 have duration==0, not sure what that's about.
+x <- x[!is.na(x$duration), ]
+
+# Get the number of connections open at every timestamp.
[…]

### 2014-07-30 diagrams.R
Add sport and dport to diagrams.R.

@@ -1,6 +1,6 @@
 library(ggplot2)
 
-col.names <- c("t", "src", "dst", "dir", "iplen", "datalen", "syn")
+col.names <- c("t", "src", "sport", "dst", "dport", "dir", "iplen", "datalen", "syn")
 
 x <- cbind(read.table("traces/lbl.https.goog.dpriv.tcp.log", col.names=col.names), google=T, source="lbl")
 x <- rbind(x, cbind(read.table("traces/lbl.https.non-goog.dpriv.tcp.log", col.names=col.names), google=F, source="lbl"))

### 2014-07-30 docs/datalen.R
Use facet_wrap for datalen.R.

@@ -2,19 +2,6 @@ library(ggplot2)
 
 col.names <- c("t", "src", "sport", "dst", "dport", "dir", "iplen", "datalen", "syn")
 
-# http://www.cookbook-r.com/Graphs/Facets_%28ggplot2%29/#modifying-facet-label-text
-label = function(variable, value) {
-	value <- as.character(value)
-	if (variable == "source") {
-		value[value == "lbl"] <- "LBL Google HTTPS"
-		value[value == "tbb"] <- "meek on App Engine"
-	} else if (variable == "dir") {
-		value[value == "IN"] <- "inbound"
-		value[value == "OUT"] <- "outbound"
-	}
-	return(value)
-}
-
 x <- cbind(read.table("../traces/lbl.https.goog.dpriv.tcp.log", col.names=col.names), google=T, source="lbl")
 x <- rbind(x, cbind(read.table("../traces/lbl.https.non-goog.dpriv.tcp.log", col.names=col.names), google=F, source="lbl"))
 x <- rbind(x, cbind(subset(read.table("../traces/meek_tbb_extension_tcp.pcap.tcp.log", col.names=col.names), dport==443), google=T, source="tbb"))
@@ -36,9 +23,11 @@ t <- table(x[x$google & x$source=="tbb", ]$datalen)
 
 binwidth = 5
 
+x <- cbind(x, label=ifelse(x$source=="lbl", "LBL Google HTTPS", "meek on App Engine"))
+
 p <- ggplot(x[x$google, ], aes(datalen))
 p <- p + geom_histogram(aes(y=..density..), binwidth=binwidth)
 p <- p + xlab("TCP payload length") + ylab("Fraction of TCP segments")
 p <- p + scale_y_continuous(labels = function(y) binwidth * y)
-p <- p + facet_grid(source ~ ., labeller = label)
+p <- p + facet_wrap(~ label, ncol=1, scales="fixed")
 ggsave("datalen.pdf", width=4, height=3.75, units="in")

### 2014-07-31 docs/meek.tex
Explain HTTP 400.

@@
 if the SNI and Host do not match,
-the Fastly edge server returns an HTTP 400 error.
+the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
 It is the only service we have found

### 2014-07-31 docs/concurrent.R
Flip backward-labeled connections.
It appears that Bro got the direction of some connections wrong: it has
them with client port 443. From inspecition of the trace, it is clear
that the host with the port of 443 is really the server, as other
connections have the same IP with port 443 being connected to by a
variety of IP addresses on ephemeral ports.

@@ -3,7 +3,7 @@ library(ggplot2)
 #fields           ts         uid       id.orig_h    id.orig_p    id.resp_h    id.resp_p    proto     service    duration    orig_bytes    resp_bytes    conn_state    local_orig    missed_bytes    history      orig_pkts    orig_ip_bytes    resp_pkts    resp_ip_bytes    tunnel_parents
 bro.names <-   c("ts",      "uid",    "id.orig_h", "id.orig_p", "id.resp_h", "id.resp_p", "proto",  "service", "duration", "orig_bytes", "resp_bytes", "conn_state", "local_orig", "missed_bytes", "history",   "orig_pkts", "orig_ip_bytes", "resp_pkts", "resp_ip_bytes", "tunnel_parents")
 #types            time       string    addr         port         addr         port         enum      string     interval    count         count         string        bool          count           string       count        count            count        count            table[string]
-bro.classes <- c("numeric", "factor", "factor",    "factor",    "factor",    "factor",    "factor", "factor",  "numeric",  "integer",    "integer",    "factor",     "logical",    "integer",      "character", "integer",   "integer",       "integer",   "integer",       "character")
+bro.classes <- c("numeric", "factor", "character", "integer",   "character", "integer",   "factor", "factor",  "numeric",  "integer",    "integer",    "factor",     "logical",    "integer",      "character", "integer",   "integer",       "integer",   "integer",       "character")
 
 x <- cbind(read.table("../traces/lbl.https.goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=T, source="lbl")
 x <- rbind(x, cbind(read.table("../traces/lbl.https.non-goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=F, source="lbl"))
@@ -11,6 +11,18 @@ x <- rbind(x, cbind(subset(read.table("../traces/meek_tbb_extension_tcp.pcap.con
 
 # Some RSTOS0 have duration==0, not sure what that's about.
 x <- x[!is.na(x$duration), ]
+# Flip connections that Bro got backwards because they
+# started before the beginning of the trace.
+for (i in 1:nrow(x)) {
+	if (x[i,"id.resp_p"] != 443) {
+		t <- x[i,"id.resp_p"];
[…]

### 2014-07-31 docs/flowduration.R

@@ -3,11 +3,26 @@ library(ggplot2)
 #fields           ts         uid       id.orig_h    id.orig_p    id.resp_h    id.resp_p    proto     service    duration    orig_bytes    resp_bytes    conn_state    local_orig    missed_bytes    history      orig_pkts    orig_ip_bytes    resp_pkts    resp_ip_bytes    tunnel_parents
 bro.names <-   c("ts",      "uid",    "id.orig_h", "id.orig_p", "id.resp_h", "id.resp_p", "proto",  "service", "duration", "orig_bytes", "resp_bytes", "conn_state", "local_orig", "missed_bytes", "history",   "orig_pkts", "orig_ip_bytes", "resp_pkts", "resp_ip_bytes", "tunnel_parents")
 #types            time       string    addr         port         addr         port         enum      string     interval    count         count         string        bool          count           string       count        count            count        count            table[string]
-bro.classes <- c("numeric", "factor", "factor",    "factor",    "factor",    "factor",    "factor", "factor",  "numeric",  "integer",    "integer",    "factor",     "logical",    "integer",      "character", "integer",   "integer",       "integer",   "integer",       "character")
+bro.classes <- c("numeric", "factor", "character", "integer",   "character", "integer",   "factor", "factor",  "numeric",  "integer",    "integer",    "factor",     "logical",    "integer",      "character", "integer",   "integer",       "integer",   "integer",       "character")
 
 x <- cbind(read.table("../traces/lbl.https.goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=T, source="lbl")
 x <- rbind(x, cbind(read.table("../traces/lbl.https.non-goog.dpriv.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), google=F, source="lbl"))
 x <- rbind(x, cbind(subset(read.table("../traces/meek_tbb_extension_tcp.pcap.conn.log", col.names=bro.names, colClasses=bro.classes, na.strings=c("-")), id.resp_p==443), google=T, source="tbb"))
+
+# Some RSTOS0 have duration==0, not sure what that's about.
+x <- x[!is.na(x$duration), ]
+# Flip connections that Bro got backwards because they
[…]

### 2014-07-31 docs/concurrent.R
Make the concurrent graph only depend on the client IP.
Not also the server.

@@ -17,25 +17,25 @@ x <- x[!is.na(x$duration), ]
 calc.numconns <- function(x) {
 	n <- nrow(x)
 	ts <- numeric(2*n)
-	srcdst <- character(2*n)
+	orig_h <- character(2*n)
 	dconns <- integer(2*n)
 	for (i in 1:n) {
 		# Connection begin
 		ts[2*(i-1) + 1] <- x$ts[i]
-		srcdst[2*(i-1) + 1] <- sprintf("%s-%s", x$id.orig_h[i], x$id.resp_h[i])
+		orig_h[2*(i-1) + 1] <- x$id.orig_h[i]
 		dconns[2*(i-1) + 1] <- +1
 		# Connection end
 		ts[2*(i-1) + 2] <- x$ts[i] + x$duration[i]
-		srcdst[2*(i-1) + 2] <- sprintf("%s-%s", x$id.orig_h[i], x$id.resp_h[i])
+		orig_h[2*(i-1) + 2] <- x$id.orig_h[i]
 		dconns[2*(i-1) + 2] <- -1
 	}
-	y <- data.frame(ts, srcdst, dconns, scale=length(unique(x$id.orig_h)))
-	y$srcdst <- factor(y$srcdst)
+	y <- data.frame(ts, orig_h, dconns, scale=length(unique(x$id.orig_h)))
+	y$orig_h <- factor(y$orig_h)
 	y <- y[order(y$ts), ]
 	y$ts <- y$ts - min(y$ts)
 	y$weight <- c(diff(y$ts), 0)
 	# https://stackoverflow.com/questions/7409138/combining-split-and-cumsum/7409310#7409310
-	y$numconns <- with(y, ave(dconns, srcdst, FUN=cumsum))
+	y$numconns <- with(y, ave(dconns, orig_h, FUN=cumsum))
 	y
 }
 
@@ -59,7 +59,7 @@ p <- ggplot(data=data)
 p <- p + scale_y_continuous(breaks=calc.breaks)
 p <- p + xlab("Time (seconds)") + ylab("Concurrent connections")
 p <- p + facet_wrap(~ label, ncol=1, scales="free")
-p <- p + geom_step(aes(ts, numconns, group=srcdst, alpha=data$alpha, colour="coral"))
+p <- p + geom_step(aes(ts, numconns, group=orig_h, alpha=data$alpha, colour="coral"))
[…]

### 2014-07-31 docs/concurrent.R
Change concurrent axis label.

@@ -69,7 +69,7 @@ calc.breaks <- function(v) {
 data <- numconns[numconns$google, ]
 p <- ggplot(data=data)
 p <- p + scale_y_continuous(breaks=calc.breaks)
-p <- p + xlab("Time (seconds)") + ylab("Concurrent connections")
+p <- p + xlab("Time (seconds)") + ylab("Concurrent HTTPS connections per client")
 p <- p + facet_wrap(~ label, ncol=1, scales="free")
 p <- p + geom_step(aes(ts, numconns, group=orig_h, alpha=data$alpha, colour="coral"))
 p <- p + geom_smooth(aes(ts, cumsum(dconns)/scale, weight=weight), size=0.4, colour="black", se=FALSE)

### 2014-07-31 docs/concurrent.R
Print out some stats in concurrent.R..

@@ -66,6 +66,14 @@ calc.breaks <- function(v) {
 	}
 }
 
+data <- x[x$google & x$source=="lbl", ]
+length(unique(data$id.orig_h))
+sum(data$duration)/(max(data$ts + data$duration) - min(data$ts))/length(unique(data$id.orig_h))
+
+data <- x[x$google & x$source=="tbb", ]
+length(unique(data$id.orig_h))
+sum(data$duration)/(max(data$ts + data$duration) - min(data$ts))/length(unique(data$id.orig_h))
+
 data <- numconns[numconns$google, ]
 p <- ggplot(data=data)
 p <- p + scale_y_continuous(breaks=calc.breaks)

### 2014-07-31 docs/datalen.R
Reorder ggplot commands.

@@ -26,8 +26,8 @@ binwidth = 5
 x <- cbind(x, label=ifelse(x$source=="lbl", "LBL Google HTTPS", "meek on App Engine"))
 
 p <- ggplot(x[x$google, ], aes(datalen))
-p <- p + geom_histogram(aes(y=..density..), binwidth=binwidth)
-p <- p + xlab("TCP payload length") + ylab("Fraction of TCP segments")
 p <- p + scale_y_continuous(labels = function(y) binwidth * y)
+p <- p + xlab("TCP payload length") + ylab("Fraction of TCP segments")
 p <- p + facet_wrap(~ label, ncol=1, scales="fixed")
+p <- p + geom_histogram(aes(y=..density..), binwidth=binwidth)
 ggsave("datalen.pdf", width=4, height=3.75, units="in")

### 2014-07-31 docs/meek.tex
Put the table inside the datalen figure.
Add concurrent graph to paper.

@@
 \includegraphics[width=\linewidth]{datalen.pdf}
+% Output of datalen.R.
+%
+% LBL
+%          0       1430       1418         41       1416       1460       1260
+% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
+%       1400       1359         33
+% 0.01673740 0.01126137 0.01100281
+%
+% meek
+%        1418           0        1460         396         196        1024
+% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
+%         811         783         151        1263
+% 0.012312668 0.007811963 0.007031241 0.006569205
+\begin{tabular}{r r >{\qquad} r r}
+\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
+0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
+1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
+1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
+41 bytes & 6.1\% & 396 bytes & 2.0\% \\
+1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
+1460 bytes & 2.9\% & 1024 bytes & 1.5\%
+\end{tabular}
 \caption{
@@
 compares the packet length distribution of both traces in both directions.
-Table~\ref{tab:datalen} summarizes the most common values.
 In both traces, about 38\% of packets have an empty payload, mostly ACKs.
@@
 added by \meekclient\ and \meekserver.
-
-% Output of datalen.R.
-%
-% LBL
-%          0       1430       1418         41       1416       1460       1260
-% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
-%       1400       1359         33
-% 0.01673740 0.01126137 0.01100281
-%
-% meek
-%        1418           0        1460         396         196        1024
-% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
-%         811         783         151        1263
-% 0.012312668 0.007811963 0.007031241 0.006569205
-\begin{table}[ht]
-\normalsize
-\centering
-\begin{tabular}{r r >{\qquad} r r}
-\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
-0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
-1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
-1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
-41 bytes & 6.1\% & 396 bytes & 2.0\% \\
-1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
-1460 bytes & 2.9\% & 1024 bytes & 1.5\%
-\end{tabular}
-\caption{The most common TCP payload lengths.}
-\label{tab:datalen}
-\end{table}
 
@@
 
+\subsection{Concurrent connections}
+
+% Output of concurrent.R.
+% [1] 2745
+% [1] 2.610621
+% [1] 1
+% [1] 1.002148
+
 \begin{figure}
 \centering
-\includegraphics[height=\linewidth, angle=270]{figs/connections-google.eps}
-\caption{Histogram of each user's connections in the 10-minute window}
-\label{fig:connections}
+\includegraphics[width=\linewidth]{concurrent.pdf}
+\caption{
+Number of simultaneous HTTPS connections to any Google server.
+Each pale line indicates the number of HTTPS connections
+of a single client IP address.
+The LBL trace shows 2,745 unique clients and the meek trace only one.
+The dark line is a smoothed average number of connections per client.
+The meek count stays close to~1 throughout, only momentarily
+jumping to 0 or~2.
+The average number of connections per user in the LBL trace is 2.61,
+and in the meek trace is 1.002.
+}
+\label{fig:concurrent}
 \end{figure}
-%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
-%(or a blank line to force the subfigure onto a new line)
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{figs/conns.eps}
-\caption{Concurrent HTTPS connections over time. We measure the trace for the Tor Browser Bundle and Firefox/Chrome extensions.}
-\label{fig:conconns}
-\end{figure}
-
-\subsection{Concurrent connections}
-Figure ~\ref{fig:connections} shows how many HTTPS connections to Google user made
-during the 10-minute measurement window.
-There are 34,732 connections in total from 2,745 unique IPs. We observe that the majority of users have less than 
-50 connections to the Google frontend server, and most of the numbers concentrate on 1--10.
-
-% David: I think this needs to be justified. Leaving Gmail open all day is a common use case,
-% as is YouTube, as is finding +1 buttons and Google-source JavaScript on unrelated web sites.
-% This is not unexpected
-% because a typical pattern of using Google is using the Google search as a stepping stone for other websites.
-
-We measure the number of concurrent HTTPS connections during the automated browsing of Alexa
-top 500 sites using three platforms: Tor Browser Bundle, Safari + Firefox extension, and Safari + Chrome extension.
-Figure ~\ref{fig:conconns} shows the number over time. We can see that most of the time
-the browser has one HTTPS connection to Google. Sometimes the browser may have more than one connection
-due to background activities such as statistics reporting. In all cases the number of connections is always 
-less than 5. We can conclude that the number of concurrent connections does not show distinct characteristics, as 
-a small number of connections can be considered as a normal behavior.
+
+The number of concurrent connections is another potential distinguisher.
+We have seen how meek tends to use one long-lived connection
+through which it tunnels all its requests.
+Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
+Google per client in both traces.
+The number of connections in the LBL trace is variable,
+with some hosts briefly spiking up above 50 connections,
+but the average case if very heavily skewed to smaller numbers.
+The average number of connections in the LBL trace is 2.61,
+while that in the meek trace is almost exactly 1, only briefly
+deviating when one connection ends and another begins.
+We conclude that a small number of concurrent connections is unremarkable.
 

### 2014-07-31 docs/meek.tex
Minor edits.

@@
 \subsection{Packet length}
+
+Protocols vary in their packet lengths;
+a censor may block a circumvention protocol if its length distribution
+is distinct enough.
 Figure~\ref{fig:datalen}
-compares the packet length distribution of both traces in both directions.
-In both traces, about 38\% of packets have an empty payload, mostly ACKs.
+compares the packet length distribution of both sample traffic traces in both directions.
+In both cases, about 38\% of packets have an empty payload, mostly ACKs.
 There is a small peak at the usual TCP Maximum Segment Size
@@
 Conspicuous in the \meek\ trace are a small number of
-likely packet sizes,
+frequent packet sizes,
 and the lack of a cluster of small payload lengths of around 50 bytes.

### 2014-07-31 docs/meek.tex
Swap order of concurrent connections and connection lifetime.
Call the section just "Traffic analysis."
Revise conclusion to traffic analysis.

@@
 
-\section{Resistance to traffic analysis}
+\section{Traffic analysis}
 \label{sec:trafficanalysis}
@@
 We hope that the censor will have to resort to measuring
-more subtle features of the communication like
-the packet length distribution and interpacket timing,
-or injecting traffic at the risk of causing collateral damage.
+more subtle features of the communication.
 In this section we provide a preliminary analysis
@@
 
-\subsection{Concurrent connections}
-
-% Output of concurrent.R.
-% [1] 2745
-% [1] 2.610621
-% [1] 1
-% [1] 1.002148
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{concurrent.pdf}
-\caption{
-Number of simultaneous HTTPS connections to any Google server.
-Each pale line indicates the number of HTTPS connections
-of a single client IP address.
-The LBL trace shows 2,745 unique clients and the meek trace only one.
-The dark line is a smoothed average number of connections per client.
-The meek count stays close to~1 throughout, only momentarily
-jumping to 0 or~2.
-The average number of connections per user in the LBL trace is 2.61,
-and in the meek trace is 1.002.
-}
-\label{fig:concurrent}
-\end{figure}
-
-The number of concurrent connections is another potential distinguisher.
-We have seen how meek tends to use one long-lived connection
-through which it tunnels all its requests.
-Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
-Google per client in both traces.
-The number of connections in the LBL trace is variable,
-with some hosts briefly spiking up above 50 connections,
-but the average case if very heavily skewed to smaller numbers.
-The average number of connections in the LBL trace is 2.61,
-while that in the meek trace is almost exactly 1, only briefly
-deviating when one connection ends and another begins.
-We conclude that a small number of concurrent connections is unremarkable.
-
 \subsection{Connection lifetime}
@@
 
-\subsection{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
-distinguishing \meek's traffic. But admittedly there two potential weaknesses: long-lived connections 
-with bulk data transfer, and deviated distribution of packet sizes. To fundamentally fix these weaknesses 
-we need to transform to the traffic into the normal-looking traffic.
-The problem is inherently difficult, because we need to know \emph{what} is normal traffic, i.e.
-what is the model of normal traffic, which is an open problem.
-However,
-the arm-race game is symmetric; since finding a right model is a difficult task for us, it is also difficult for 
-the censor. Therefore, the censor can only find ad-hoc features to block forbidden traffic, which are relatively 
-easy to defend against.
+\subsection{Concurrent connections}
+
+% Output of concurrent.R.
+% [1] 2745
+% [1] 2.610621
+% [1] 1
+% [1] 1.002148
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{concurrent.pdf}
+\caption{
+Number of simultaneous HTTPS connections to any Google server.
+Each pale line indicates the number of HTTPS connections
+of a single client IP address.
+The LBL trace shows 2,745 unique clients and the meek trace only one.
+The dark line is a smoothed average number of connections per client.
+The meek count stays close to~1 throughout, only momentarily
+jumping to 0 or~2.
+The average number of connections per user in the LBL trace is 2.61,
+and in the meek trace is 1.002.
+}
+\label{fig:concurrent}
+\end{figure}
+
+The number of concurrent connections is another potential distinguisher.
+We have seen how meek tends to use one long-lived connection
+through which it tunnels all its requests.
+Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
+Google per client in both traces.
+The number of connections in the LBL trace is variable,
+with some hosts briefly spiking up above 50 connections,
+but the average case if very heavily skewed to smaller numbers.
+The average number of connections in the LBL trace is 2.61,
+while that in the meek trace is almost exactly 1, only briefly
+deviating when one connection ends and another begins.
+We conclude that a small number of concurrent connections is unremarkable.
+
+$$\diamondsuit$$
+
+So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish meek
+from other HTTPS traffic.
+The long-lived connections and few common packet sizes are
+potential targets for a more concerted attack.
+The fundamental problem we face is essentially that of steganography,
+the need to make our traffic fit some model of ``normal'' traffic.
+The problem is inherently difficult,
+because it's difficult to say just what normal traffic \emph{is}.
+It depends on the network environment;
+it also depends on the endpoint.
+Google is likely to be different than Akamai,
+and it's hard to characterize what normal use of a CDN is:
+they provide access to ordinary web sites,
+but also video streams and software updates,
+and not all clients are browsers.
+The difficulty is symmetric;
+if finding the right model is difficult task for us,
+it is also difficult for the censor.
+We have seen that censors prefer to use easy classifiers when they exist.
+By removing the easy ways, we increase the cost to the censor.
 

### 2014-07-31 docs/meek.tex
Censor talks to CDN directly and PHP bridges.

@@
 
+A censor could attack domain fronting by
+going directly to the operators of the intermediate web service
+and asking them either to break fronting
+(i.e., require SNI to be present and SNI and Host header to agree),
+or merely to get rid of their customers who are
+engaged in fronting in the support of circumvention.
+The censor could threaten to block the web service entirely otherwise.
+Whether the attack will succeed depends on the censor's
+and the web service's specific motivations,
+so we cannot make any general statements.
+It is ultimately a question of who needs whom more:
+whether it hurts the web service or the censor more
+when a web service is blocked.
+Nothing works against a censor with sufficiently high tolerance for
+collateral damage,
+but we also don't have to defeat the world's
+most powerful censor in order to be successful.
+What doesn't work in one place may work in another.
+
 % Edge servers within the censored region.
@@
 
-% Censor could lean on the CDN to block the actual destination internally.
-
 % Firefox plugin uses normal browser trust store.
@@
 % Prevalence of no SNI.
+
+The key idea of meek is domain fronting,
+but its HTTPS tunnel has independent utility.
+Another idea for deployment is to use
+thousands of simple HTTP reflectors on cheap web hosting
+(in place of domain fronting on a big CDN).
+The request-reflecting role of a CDN could
+be played by a PHP script, for example,
+or a special web server configuration.
+Their URLs unprotected by domain fronting,
+each reflector would be easily blockable,
+so there would need to be sufficiently many that
+a censor could not block them all.
+This deployment model is essentially the same as with
+ordinary Tor bridges: have lots of volunteer-operated bridges
+and make it hard to enumerate them all.
+The advantage that an HTTP transport would have
+is that it is easier for a volunteer to upload a PHP file to a web host
+than to set up and maintain a Tor bridge.
 
@@
 % Dreamhost? Other HTTPS webhosts with PHP bridge?
-
-The code that runs on App Engine is very simple.
-It just statelessly copies HTTP requests and responses.
-Another possible deployment scenario uses a PHP implementation of the reflector,
-deployed on an ordinary web hosting service other than App Engine.
-In this scenario, domain fronting is not used;
-instead unblockability depends on there being many (individually blockable) PHP reflectors.
-In other words, it is roughly the same situation as exists today with Tor bridges,
-except that it can be much easier for a volunteer to upload a PHP file to a web host
-than to set up Tor bridge.
-Such PHP bridges could potentially automatically report their own URLs,
-which could be distributed using a system like BridgeDB.
 

### 2014-07-31 docs/meek.tex
What happens if edge server is inside censor's network.

@@
 
-% Edge servers within the censored region.
-% Censor could block on the way to the origin server,
-% if the censor has visibility to it.
-% Maybe the CDN has its own private high-speed cables,
-% or it VPNs its own stuff or something.
+We have assumed that the intermediate web service is
+outside the censor's domain of control,
+so that communication between the web service and Tor bridge
+doesn't have to be protected.
+What happens when the web service---a CDN edge server, for instance---is
+inside the network controlled by the censor?
+If the edge server forwards the request to the Tor bridge
+as an ordinary HTTP request on the public Internet,
+then blocking it is as easy as blocking the IP address of the bridge.
+On the other hand, if the web service encapsulates
+the request and sends it encrypted, or over its own fast private network,
+to another server outside of the censor's control,
+then fronting will still work.
 

### 2014-07-31 docs/meek.tex
Edits.

@@
 up to a maximum of 5~s.
-% Implemented in Psiphon's version.
 The other technique,
@@
 notably Google App Engine doesn't support streaming downloads of this kind.
+
+% Overhead estimate.
+As discussed in Section~\ref{sec:trafficanalysis},
+the same TLS session is used for many requests,
+so the overhead of the TLS handshake is amortized.
 
@@
 
-Domain fronting shares a weakness with decoy routing,
+Domain fronting shares a potential weakness with decoy routing,
 which is that the overt and covert destinations lie on different
@@
 \includegraphics[width=\linewidth]{clients-meek}
-\caption{Concurrent users of \meek\ with Tor.}
+\caption{
+Concurrent users of \meek\ with Tor.
+}
 \label{fig:clients}
@@
 \includegraphics[width=\linewidth]{clients-psiphon3}
-\caption{Daily unique users of \meek\ with Psiphon3 (note vertical axis).}
+\caption{
+Daily unique users of \meek\ with Psiphon (note vertical axis).
+The decrease at the end of June
+was caused by an unblocking event that made meek unnecessary for some users.
+}
 \label{fig:clients}

### 2014-07-31 docs/meek.tex
Edits.

@@
 which are the pluggable-transports~\cite{pt} interface between Tor and \meek.
-% All the programs are free software, naturally,
-% and may be downloaded from the \meek\ home page at
-% \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
 
@@
 
-\subsection{Packet length}
+\subsection{Packet lengths}
 
@@
 
-% Prevalence of no SNI.
-
 The key idea of meek is domain fronting,
-but its HTTPS tunnel has independent utility.
+but its HTTP-tunneling ability is useful on its own.
 Another idea for deployment is to use
@@
 
-\section{Deployment}
-\label{sec:deployment}
-
-We implemented \meek\ as a Tor pluggable transport~\cite{pt}
-and built experimental releases of the Tor Browser Bundle featuring \meek.
-The browser bundle includes Tor and a version of Firefox
-called Tor Browser that is patched to defend against application-layer identity leaks.
-Users need to download and run the bundle and select \meek\ from the list of transports,
-and then a browser window appears,
-configured to use \meek\ for circumvention and Tor for anonymity.
-We announced our prototype bundles on Tor development mailing lists,
-and from there they were picked up by Tor Weekly News on the Tor blog.
-
-\begin{figure}
-\includegraphics[width=\linewidth]{clients-meek}
-\caption{
-Concurrent users of \meek\ with Tor.
-}
-\label{fig:clients}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\linewidth]{clients-psiphon3}
-\caption{
-Daily unique users of \meek\ with Psiphon (note vertical axis).
-The decrease at the end of June
-was caused by an unblocking event that made meek unnecessary for some users.
-}
-\label{fig:clients}
-\end{figure}
-
-Figure~\ref{fig:clients} shows the average number of concurrent users of \meek\ with Tor
-since close to the beginning of development,
-as reported by the Tor Metrics Portal~\cite{metrics-meek}.
-The number of users is estimated by counting the number
-of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
-% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by \meek.
-
-% Psiphon. Drop in July is due to an unblocking event.
-% Different counting method. Client self-reporting of last connection date.
-
-We are running a paid instance of the web app on App Engine for use by the public.
-The cost for bandwidth on App Engine is \$0.12 per gigabyte,
-with one gigabyte free each day.
-The total cost has so far been \$1.11, with bills of
-\$0.09 in March,
-\$0.73 in April,
-and \$0.29 in the first half of May.
-
-\meek\ has a home page at
-\url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
-Our source code is in the Git repository at
-\url{https://git.torproject.org/pluggable-transports/meek.git}.
-As of version 0.5 (May~7, 2014), the source code consists of
-about 800 lines of Go for the client programs,
-400 lines for \meekserver, and
-100 lines for the reflector web app.
-Each of the browser extensions
-(one for Firefox, one for Chrome)
-is about 300 lines of JavaScript.
-
-\subsection{Other deployment scenarios}
-\label{sec:otherdeployment}
+The ``domainless'' fronting style, which omits SNI,
+is useful when there is no good front domain known for a web service.
+At least one CDN, Fastly, requires the domainless style.
+All current web browsers support SNI,
+so it is possible that lack of SNI could be used as a distinguisher.
+According to our communication with
+a representative of the International Computer Science Institute's
+certificate notary~\cite{icsi-notary},
+which observes on the order of 50~million TLS connections daily,
+83.5\% of connections used SNI in June~2014.
+There are apparently enough connections without SNI
+that a censor will at least have to consider seriously
+the costs and benefits before deciding to block SNI outright.
 
@@
 
-% Dreamhost? Other HTTPS webhosts with PHP bridge?
-
-% Psiphon idea: use long-polling for downstream data.
-% Works with CDNs, not with App Engine.
-% Alternative techniques for push-like behavior,
-% such as HTTP long polling,
-% don't work well with App Engine,
-% because App Engine requires requests to finish within 60 seconds.
-
-% App Engine works when appspot.com is blocked but google.com is not.
+\section{Deployment}
+\label{sec:deployment}
+
+We implemented \meek\ as a Tor pluggable transport~\cite{pt}
+and built experimental releases of the Tor Browser Bundle featuring \meek.
+The browser bundle includes Tor and a version of Firefox
+called Tor Browser that is patched to defend against application-layer identity leaks.
+Users need to download and run the bundle and select \meek\ from the list of transports,
+and then a browser window appears,
+configured to use \meek\ for circumvention and Tor for anonymity.
+We announced our prototype bundles on Tor development mailing lists,
+and from there they were picked up by Tor Weekly News on the Tor blog.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{clients-meek}
+\caption{
+Concurrent users of \meek\ with Tor.
+}
+\label{fig:clients}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\linewidth]{clients-psiphon3}
+\caption{
+Daily unique users of \meek\ with Psiphon (note vertical axis).
+The decrease at the end of June
+was caused by an unblocking event that made meek unnecessary for some users.
+}
+\label{fig:clients}
+\end{figure}
+
+Figure~\ref{fig:clients} shows the average number of concurrent users of \meek\ with Tor
+since close to the beginning of development,
+as reported by the Tor Metrics Portal~\cite{metrics-meek}.
+The number of users is estimated by counting the number
+of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
+% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by \meek.
+
+% Psiphon. Drop in July is due to an unblocking event.
+% Different counting method. Client self-reporting of last connection date.
+
+We are running a paid instance of the web app on App Engine for use by the public.
+% The cost for bandwidth on App Engine is \$0.12 per gigabyte,
+% with one gigabyte free each day.
+% The total cost has so far been \$1.11, with bills of
+% \$0.09 in March,
+% \$0.73 in April,
+% and \$0.29 in the first half of May.
 
@@
 
+\section{Summary}
+\label{sec:summary}
+
+We have presented domain fronting,
+an HTTPS technique that uses different domain names
+at different communication layers in
+order to hide the remote endpoint of a communication.
+We implemented meek,
+a pluggable transport for Tor,
+show that it resists common methods of blocking,
+and begin an investigation into its
+resistance against more subtle and expensive means of traffic analysis.
+We discuss the results of an initial deployment of meek
+in both Tor and Psiphon.
+
+\meek\ has a home page at
+\url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
+Our source code is in the Git repository at
+\url{https://git.torproject.org/pluggable-transports/meek.git}.
+All our programs are free software.
+% As of version 0.9 (June~19, 2014), the source code consists of
+% about 1,100 lines of Go for the client programs,
+% 400 lines for \meekserver, and
+% 100 lines for the reflector application for App Engine.
+% Each of the browser extensions
+% (one for Firefox, one for Chrome)
+% is about 400 lines of JavaScript.
+
 % \section*{Acknowledgments}

### 2014-07-31 docs/meek.tex
Note size overhead.
Maybe shouldn't risk burning CloudFlare for other projects.

@@
 so the overhead of the TLS handshake is amortized.
+Tor uses fixed-size cells of 514 bytes~\cite[Section~0.2]{tor-spec}.
+% 514 → 543 → 957 → 1079
 
@@
 or to use ``domainless'' fronting that doesn't send SNI.
-Though CloudFlare supports domain fronting,
-its terms of service~\cite{cloudflare-terms}
-seem to prohibit the kind of tunneled proxying that \meek\ does:
-\begin{quote}
-\textsc{Section 10: Limitation on non-HTML caching}\\
-You acknowledge that CloudFlare's Service is offered as a platform to cache and
-serve web pages and websites and is not offered for other purposes
-\ldots\ you understand and agree to use the Service solely
-for the purpose of hosting and serving web pages\ldots
-\end{quote}
+% Though CloudFlare supports domain fronting,
+% its terms of service~\cite{cloudflare-terms}
+% seem to prohibit the kind of tunneled proxying that \meek\ does:
+% \begin{quote}
+% \textsc{Section 10: Limitation on non-HTML caching}\\
+% You acknowledge that CloudFlare's Service is offered as a platform to cache and
+% serve web pages and websites and is not offered for other purposes
+% \ldots\ you understand and agree to use the Service solely
+% for the purpose of hosting and serving web pages\ldots
+% \end{quote}
 
@@
 added by \meekclient\ and \meekserver.
+% In this trace, packets of 1024 bytes are probably single
+% Tor cells and those of 396 are probably empty polling requests.
 

### 2014-07-31 docs/meek.tex
Overhead discussion.

@@
 it is domain fronting, not HTTP encoding, that is the fundamental strength of the system.
-Section~\ref{sec:futurework} describes more efficient encodings
+Section~\ref{sec:discussion} describes more efficient encodings
 that enable multiple requests in parallel.
@@
 
-% Overhead estimate.
-As discussed in Section~\ref{sec:trafficanalysis},
-the same TLS session is used for many requests,
-so the overhead of the TLS handshake is amortized.
+As an encrypted tunneling protocol, meek adds some overhead.
+Each chunk of data gets an HTTP header, and then the HTTP
+request is wrapped in a TLS Application Data record.
+We estimate the overhead when meek is used to transport Tor.
 Tor uses fixed-size cells of 514 bytes~\cite[Section~0.2]{tor-spec}.
-% 514 → 543 → 957 → 1079
+Each cell is wrapped in a TLS Application Data record, which adds 29 bytes
+using a GCM ciphersuite.
+% (in Tor version~0.2.4.22 using a GCM ciphersuite).
+This 543-byte record is what is received by \meekclient,
+which adds an HTTP header whose length is about 400 bytes
+(varying slightly depending on the length of the Host field).
+The HTTP request goes into its own TLS Application Data record,
+which adds about 50~bytes
+(depending on how much padding is used by the ciphersuite selected by the web service).
+
+% 514 → 543 → 956 → 1013
+
+\begin{center}
+\begin{tabular}{r@{}r l}
+          &    514 & Tor cell \\
+          &  $+$29 & Tor TLS record \\
+$\approx$ & $+$400 & meek HTTP header \\
+$\approx$ &  $+$50 & meek TLS record \\
+\hline
+$\approx$ &   1000 & total
+\end{tabular}
+\end{center}
+
+% >>> (1*543+450.)/(1*543)
+% 1.828729281767956
+% >>> (2*543+450.)/(2*543)
+% 1.4143646408839778
+% >>> (3*543+450.)/(3*543)
+% 1.276243093922652
+\noindent
+The total overhead varies according to the length
+of the Host field and the specifics of the intermediate web service's TLS,
+but is somewhere in the neightborhood of $(543+450)/543-1\approx83$\%.
+This is the worst case, when Tor sends a single cell.
+Tor can bunch multiple cells into one transmission;
+if two cells are sent at once, the overhead drops to
+${\approx}41$\%; if three, it is ${\approx}28$\%.
+Bulk uploads and downloads tend to bunch many cells at once.
+Persistent HTTP connections as used by Psiphon reduce overhead further,
+because only one HTTP header is sent for a large number of transmissions.
+Empty polling requests also use bandwidth,
+but they are sent only when the connection is idle
+so they don't affect upload or download speed.
+As is discussed in Section~\ref{sec:trafficanalysis},
+\meekclient\ reuses the same TLS connection for many requests,
+so the fixed overhead of the initial TLS handshake is amortized.
+
+There is additional latency overhead caused by the extra network hop:
+rather than accessing the Tor bridge directly,
+the client first goes through the intermediate web service before
+reaching the bridge.
+How much latency this adds, of course depends on the network location
+of the client, web service, and Tor bridge.
+Strict serialization of requests and responses
+becomes a problem with large round-trip times,
+because bandwidth becomes a function of latency.
+Section~\ref{sec:discussion} describes ways to improve
+performance with high latencies;
+Psiphon's use of persistent connections as described in this section is one of them.
 

### 2014-07-31 docs/meek.tex
Discussion.

@@
 
-We implemented \meek\ as a pluggable transport~\cite{pt} for Tor.
-Although it is possible to use the system with proxies other than Tor,
-using Tor has some attractive features.
-The pluggable transports infrastructure makes it relatively easy to prototype
-a circumvention technique and connect it to a global proxy network.
-We can treat confidentiality and integrity of tunneled communication
-as a problem solved by Tor, which we don't need to solve separately.
-Tor's extra proxy hops mean that the HTTP reflector (App Engine)
-and the entry bridge do not have to be trusted.
+% We implemented \meek\ as a pluggable transport~\cite{pt} for Tor.
+% Although it is possible to use the system with proxies other than Tor,
+% using Tor has some attractive features.
+% The pluggable transports infrastructure makes it relatively easy to prototype
+% a circumvention technique and connect it to a global proxy network.
+% We can treat confidentiality and integrity of tunneled communication
+% as a problem solved by Tor, which we don't need to solve separately.
+% Tor's extra proxy hops mean that the HTTP reflector (App Engine)
+% and the entry bridge do not have to be trusted.
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.40\linewidth}
+\includegraphics[width=\linewidth]{wire-sequential}
+\caption{Sequential}
+\label{fig:wire-sequential}
+\end{subfigure}
+\qquad
+\begin{subfigure}[t]{0.40\linewidth}
+\includegraphics[width=\linewidth]{wire-parallel}
+\caption{Parallel}
+\label{fig:wire-parallel}
+\end{subfigure}
+
+\caption{
+The nature of potential performance gain
+from sending fronted requests in parallel.
+}
+\label{fig:wire}
+\end{figure}
+
+The current implementation of meek strictly serializes
+its HTTPS requests and responses,
+in order to keep the chunks of the underlying TCP stream
+in the proper order.
+The unfortunate side effect of this simple approach
+is delay that gets worse with higher round-trip times.
+In future work we plan to add an additional reliability layer,
+perhaps like the system of sequence numbers and acknowledgments used in OSS~\cite{oss},
+that would allow requests to be pipelined
+and cope with out-of-order delivery.
+Figure~\ref{fig:wire-sequential} shows the current implementation,
+and Figure~\ref{fig:wire-parallel} shows the nature of performance
+improvement that could be gained with a reliability layer.
+% Would be useful for Iran-like session cutoff, independent of \meek.
 
@@
 
-% Firefox plugin uses normal browser trust store.
-% Adversary controls CAs. Can MITM and read your tag and block you.
-% Maybe not willing to risk getting caught in MITM.
-% Could conceivably send cover traffic if MITM detected, but blah.
+meek's use of HTTPS is subject to the usual public key infrastructure
+and trust model.
+The browser running the HTTPS camouflage extension (Section~\ref{sec:browserextension})
+has a standard list of trusted certificate authorities.
+A censor that controls a certificate authority trusted by the browser
+would be able to do a man-in-the-middle attack
+between the client and the intermediate web service,
+and detect fronting by decrypting HTTP requests and checking for specific Host headers.
+Such a censor would be able to detect circumvention,
+but still not read the client's plaintext because of the
+additional encryption and authentication of the tunneled Tor layer.
+It seems risky for the censor to risk being detected in
+ia man-in-the-middle attack merely to confirm that a user is circumventing,
+but it is not impossible for a sufficiently powerful censor.
+The problem doesn't exist when the front domain is one
+that happens have its public key ``pinned'' in the headless browser,
+for instance when using the Chrome extension and fronting through
+\urll{www.google.com}.
 
@@
 
-\section{Future work}
-\label{sec:futurework}
-
-In future work we would like to implement pipelining of requests,
-so that more than one HTTP request can be outstanding at a time.
-This would have better performance compared to the current system,
-which serializes requests and responses in order to keep the
-underlying TCP stream in order.
-A system of sequence numbers and acknowledgments as used in OSS~\cite{oss}
-could make this possible.
-% Would be useful for Iran-like session cutoff, independent of \meek.
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.40\linewidth}
-\includegraphics[width=\linewidth]{wire-sequential}
-\caption{Sequential}
-\label{fig:wire-sequential}
-\end{subfigure}
-\qquad
-\begin{subfigure}[t]{0.40\linewidth}
-\includegraphics[width=\linewidth]{wire-parallel}
-\caption{Parallel}
-\label{fig:wire-parallel}
-\end{subfigure}
-
-\caption{
-The nature of potential performance gain
-from sending fronted requests in parallel.
-}
-\label{fig:wire}
-\end{figure}
-
-% Performance measurements
-We would like to do more quantitative performance measurements,
-in order to measure the overhead in bandwidth and latency that \meek\ has over plain Tor.
-We have done informal tests, such as browsing YouTube,
-but have not yet put numbers to our measurements.
-
-% Load balancing
-
 \section{Summary}

### 2014-08-01 docs/meek.tex
Deployment before Discussion.
(Except after C.)
Avoid breaking akamai domains across lines.
Deployment.

@@
 Akamai (\url{http://www.akamai.com/}) is a large CDN.
-Requests may be fronted through the special domain
+Requests may be fronted through the special HTTPS domain
 \urll{a248.e.akamai.net},
@@
 
+\section{Deployment}
+\label{sec:deployment}
+
+Development on meek as a Tor pluggable transport~\cite{pt} began in January~2014.
+Most users who use Tor use Tor Browser~\cite{torbrowser},
+a customized version of Firefox that is
+preconfigured to use a built-in Tor client.
+% and patched to defend against application-layer privacy and anonymity threats
+% like tracking cookies and web browser fingerprinting.
+Tor Browser has an easy interface for selecting a pluggable transport.
+We made a series experimental releases of Tor Browser featuring meek,
+releasing the first one on February~18.
+On April~18 we made the first release featuring the browser camouflage
+that is the subject of Section~\ref{sec:browserextension}.
+We announced our releases on Tor development mailing lists,
+whence they were picked up by Tor Weekly News on the Tor blog.
+Our code was merged by the Tor Browser maintainers
+in June and scheduled for an alpha release,
+which is still pending as of this writing.
+
+The experimental Tor Browser releases have all used Google as the intermediate web service.
+Support for CloudFront was not realized until late July.
+We are running the backends on paid accounts for use by the public.
+The cost for bandwidth on App Engine is \$0.12 per gigabyte,
+with one gigabyte free each day.
+The total App Engine bill so far has been \$2.07.
+There has not yet been enough use of CloudFront to cost any money.
+A longer-term goal is to find a way to fund continued operation
+if the system becomes popular.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{clients-meek}
+\caption{
+Concurrent users of the \meek\ pluggable transport for Tor.
+}
+\label{fig:clients-tor}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\linewidth]{clients-psiphon3}
+\caption{
+Daily unique users of \meek\ with Psiphon (note vertical axis).
+The decrease at the end of June
+was caused by an unblocking event that made meek unnecessary for some users.
+}
+\label{fig:clients-psiphon3}
+\end{figure}
+
+Figure~\ref{fig:clients-tor} shows the average number of concurrent users of \meek\ with Tor
+since close to the beginning of development.
+The measurements come from the Tor Metrics Portal~\cite{metrics-meek},
+which aggregates statistics self-reported by Tor relays.
+The number of users is estimated by counting the number
+of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
+% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by \meek.
+
+Psiphon began their deployment of meek in June~2014.
+Figure~\ref{fig:clients-psiphon3} shows the number
+of unique daily users of meek with Psiphon,
+estimated through clients' self-reporting of most recent connection date.
+The Psiphon developers tell us that the drop that occurs
+in the middle of June was not caused by a blocking event,
+but rather an unblocking event that made meek unnecessary for some users.
+Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
+are not directly comparable because they count slightly different things,
+it is clear that meek-with-Psiphon, with its thousands of daily users,
+is much more widely used than meek-with-Tor, which has not yet seen a formal release,
+
 \section{Discussion}
@@
 The problem is hard to counter, because the front domain needs
-to be a popular destination in order to have high collateral damage,
-but popular destinations by definition tend to be visited a lot.
+to be popular in order to have high collateral damage,
+but popular domains are also the ones people tend to want to go to.
 % Possible countermeasure is traffic fingerprinting resistance
@@
 and cope with out-of-order delivery.
-Figure~\ref{fig:wire-sequential} shows the current implementation,
-and Figure~\ref{fig:wire-parallel} shows the nature of performance
+Figure~\ref{fig:wire-sequential} shows how the current implementation works,
+and Figure~\ref{fig:wire-parallel} shows the nature of the performance
 improvement that could be gained with a reliability layer.
@@
 
-\section{Deployment}
-\label{sec:deployment}
-
-We implemented \meek\ as a Tor pluggable transport~\cite{pt}
-and built experimental releases of the Tor Browser Bundle featuring \meek.
-The browser bundle includes Tor and a version of Firefox
-called Tor Browser that is patched to defend against application-layer identity leaks.
-Users need to download and run the bundle and select \meek\ from the list of transports,
-and then a browser window appears,
-configured to use \meek\ for circumvention and Tor for anonymity.
-We announced our prototype bundles on Tor development mailing lists,
-and from there they were picked up by Tor Weekly News on the Tor blog.
-
-\begin{figure}
-\includegraphics[width=\linewidth]{clients-meek}
-\caption{
-Concurrent users of \meek\ with Tor.
-}
-\label{fig:clients}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\linewidth]{clients-psiphon3}
-\caption{
-Daily unique users of \meek\ with Psiphon (note vertical axis).
-The decrease at the end of June
-was caused by an unblocking event that made meek unnecessary for some users.
-}
-\label{fig:clients}
-\end{figure}
-
-Figure~\ref{fig:clients} shows the average number of concurrent users of \meek\ with Tor
-since close to the beginning of development,
-as reported by the Tor Metrics Portal~\cite{metrics-meek}.
-The number of users is estimated by counting the number
-of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
-% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by \meek.
-
-% Psiphon. Drop in July is due to an unblocking event.
-% Different counting method. Client self-reporting of last connection date.
-
-We are running a paid instance of the web app on App Engine for use by the public.
-% The cost for bandwidth on App Engine is \$0.12 per gigabyte,
-% with one gigabyte free each day.
-% The total cost has so far been \$1.11, with bills of
-% \$0.09 in March,
-% \$0.73 in April,
-% and \$0.29 in the first half of May.
-
 \section{Summary}

### 2014-08-01 docs/meek.tex
Check some more off.

@@
 The problem is inherently difficult,
-because it's difficult to say just what normal traffic \emph{is}.
+because it is difficult to say just what normal traffic \emph{is}.
 It depends on the network environment;
@@
 Google is likely to be different than Akamai,
-and it's hard to characterize what normal use of a CDN is:
+and it is hard to characterize what normal use of a CDN is:
 they provide access to ordinary web sites,

### 2014-08-01 docs/meek.tex
Devil-may-care censors.

@@
 
-% Censors that know no bounds: China on Google, Egypt, Pakistan with YouTube.
+Domain fronting derives part of its unblockability from the
+high collateral damage of blocking the domain fronted through.
+Fronting through \urll{www.google.com} to App Engine, for example,
+is betting that censor will lack the temerity to block Google.
+The Great Firewall of China called our bluff in June of 2014,
+when it blocked access to all Google services~\cite{cn-google-block}.
+In 2012, the government of Pakisten blocked to all of YouTube
+in order to restrict access to one video,
+and in 2011, the government of Egypt briefly ``turned off the net'' completely.
+% http://www.washingtonpost.com/business/economy/youtube-blocked-in-pakistan/2012/09/17/30081fa2-00ea-11e2-b257-e1c2b3548a4a_story.html
+% https://en.wikipedia.org/wiki/Internet_censorship_in_Egypt#2011_Internet_shutdown
+These examples show that blocking resistance is not an absolute,
+black-and-white security property;
+it can only be discussed in an economic context, relative to the costs borne
+by the censor and by users of a system.
+To block Google is an extreme measure,
+probably out of reach of most censors.
+Blocking all of the fronting-capable services listed in
+Section~\ref{sec:survey} would be even harder.
 

### 2014-08-01 docs/meek.tex
Edits.

@@
 
-The experimental Tor Browser releases have all used Google as the intermediate web service.
-Support for CloudFront was not realized until late July.
-We are running the backends on paid accounts for use by the public.
-The cost for bandwidth on App Engine is \$0.12 per gigabyte,
-with one gigabyte free each day.
-The total App Engine bill so far has been \$2.07.
-There has not yet been enough use of CloudFront to cost any money.
-A longer-term goal is to find a way to fund continued operation
-if the system becomes popular.
-
 \begin{figure}
@@
 is much more widely used than meek-with-Tor, which has not yet seen a formal release,
+
+The experimental Tor Browser releases have all used Google with App Engine as the intermediate web service.
+Support for CloudFront was not realized until late July.
+We are running the backends on paid accounts for use by the public.
+The cost for bandwidth on App Engine is \$0.12 per gigabyte,
+with one gigabyte free each day.
+The total App Engine bill so far has been \$2.07,
+with most days' usage being below the billable threshold.
+There has not yet been enough use of CloudFront to cost anything.
+
+A longer-term goal is to find a way to fund continued operation
+if the system becomes popular.
+Although some of the systems listed in Section~\ref{sec:survey}
+are inexpensive enough that some users could upload their own fronting backend,
+thereby diffusing costs,
+we believe that an organization operating a backend for the use of the public
+has compelling usability advantages.
+With client software can be configured to use the public backend by default,
+there is nothing for the user to upload and no out-of-band communication is needed before getting
+started---if everything works it offers no-configure circumvention.
+
+% The number of parties able to analyze users' traffic patterns is somewhat increased:
+% the path from user to Tor bridge now includes App Engine and the web app operators,
+% in addition to the ISP and intermediate routers that were there before.
+% On the other hand, the Tor bridge no longer gets to see users' IP addresses:
+% all it sees are many connections from App Engine.
 
@@
 
-Domain fronting shares a potential weakness with decoy routing,
-which is that the overt and covert destinations lie on different
-network paths.
-The difference in paths may create side channels---latency measurements for instance---that
-enable the censor to
-distinguish fronted traffic from traffic that is truly destined
-to the front domain.
-For example, a CDN can be expected to have responses
-to some fraction of requests already in cache,
-and respond to those requests with low latency.
-Fronted traffic, on the other hand, always continues all the way
-to the origin server after reaching the CDN (as if nothing were ever cached),
-resulting in a higher latency.
-Latency measurement was applied to decoy routing by Schuhard et~al.~\cite[Section~5]{ccs2012-decoys},
-who compared empirical round-trip-time distributions using a
-Kolmogorov--Smirnov test.
-% time between ChangeCipherSpec and ApplicationData
-
-When domain fronting is combined with Tor,
-the CDN or web service effectively becomes
-what Tor calls a ``guard node,''
-a host with a privileged network position that can observe
-the ciphertext entering the network.
-One consequence of this fact is that Google (for example)
-knows the IP addresses of everyone using the circumvention system,
-just as if it were those users' ISP.
-Another consequence is that the CDN or web service gets
-to observe and correlate both entry and exit traffic,
-in the special case where the target of the communication
-also lies on the same CDN or web service.
-For example, a user fronting through App Engine and
-browsing YouTube reveals both their entry and exit traffic to Google,
-which may attempt through traffic analysis to determine
-which entry packets correspond to which exit packets.
-The problem is hard to counter, because the front domain needs
-to be popular in order to have high collateral damage,
-but popular domains are also the ones people tend to want to go to.
-% Possible countermeasure is traffic fingerprinting resistance
-% like what mjuarez is working on, mostly orthogonal to circumvention.
-
-% We implemented \meek\ as a pluggable transport~\cite{pt} for Tor.
-% Although it is possible to use the system with proxies other than Tor,
-% using Tor has some attractive features.
-% The pluggable transports infrastructure makes it relatively easy to prototype
-% a circumvention technique and connect it to a global proxy network.
-% We can treat confidentiality and integrity of tunneled communication
-% as a problem solved by Tor, which we don't need to solve separately.
-% Tor's extra proxy hops mean that the HTTP reflector (App Engine)
-% and the entry bridge do not have to be trusted.
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.40\linewidth}
-\includegraphics[width=\linewidth]{wire-sequential}
-\caption{Sequential}
-\label{fig:wire-sequential}
-\end{subfigure}
-\qquad
-\begin{subfigure}[t]{0.40\linewidth}
-\includegraphics[width=\linewidth]{wire-parallel}
-\caption{Parallel}
-\label{fig:wire-parallel}
-\end{subfigure}
-
-\caption{
-The nature of potential performance gain
-from sending fronted requests in parallel.
-}
-\label{fig:wire}
-\end{figure}
-
-The current implementation of meek strictly serializes
-its HTTPS requests and responses,
-in order to keep the chunks of the underlying TCP stream
-in the proper order.
-The unfortunate side effect of this simple approach
-is delay that gets worse with higher round-trip times.
-In future work we plan to add an additional reliability layer,
-perhaps like the system of sequence numbers and acknowledgments used in OSS~\cite{oss},
-that would allow requests to be pipelined
-and cope with out-of-order delivery.
-Figure~\ref{fig:wire-sequential} shows how the current implementation works,
-and Figure~\ref{fig:wire-parallel} shows the nature of the performance
-improvement that could be gained with a reliability layer.
-% Would be useful for Iran-like session cutoff, independent of \meek.
-
 A censor could attack domain fronting by
@@
 
+Domain fronting shares a potential weakness with decoy routing,
+which is that the overt and covert destinations lie on different
+network paths.
+The difference in paths may create side channels---latency measurements for instance---that
+enable the censor to
+distinguish fronted traffic from traffic that is truly destined
+to the front domain.
+For example, a CDN can be expected to have responses
+to some fraction of requests already in cache,
+and respond to those requests with low latency.
+Fronted traffic, on the other hand, always continues all the way
+to the origin server after reaching the CDN (as if nothing were ever cached),
+resulting in a higher latency.
+Latency measurement was applied to decoy routing by Schuhard et~al.~\cite[Section~5]{ccs2012-decoys},
+who compared empirical round-trip-time distributions using a
+Kolmogorov--Smirnov test.
+% time between ChangeCipherSpec and ApplicationData
+
+The intermediate web service enjoys a privileged network position
+from which it is able to monitor all circumvention traffic.
+Even if the censor doesn't know who the users are, the CDN knows.
+The web service has basically the same network visibility
+as a client's ISP would have if the client were connecting to Tor directly.
+For this reason, domain fronting should be combined with another
+layer, for example Tor, that prevents the web service from
+observing the contents and destination of messages.
+There is additional risk when the client is browsing a web site
+controlled by the same service as that they are fronting through,
+for example browsing YouTube while fronting through \urll{www.google.com}.
+Even with Tor, in this case the web service gets to see
+both entry and exit traffic, and is in a position to
+perform traffic correlation attacks.
+The problem seems hard to counter, because the front domain needs
+to be popular in order to have high collateral damage,
+but popular domains are also the ones people tend to want to go to.
+A possible mitigation is traffic obfuscation that lasts all
+the way to the second hop of a three-hop Tor circuit,
+which would reduce the correlation between entry and exit traffic.
+% like what mjuarez is working on, mostly orthogonal to circumvention.
+
+% We implemented \meek\ as a pluggable transport~\cite{pt} for Tor.
+% Although it is possible to use the system with proxies other than Tor,
+% using Tor has some attractive features.
+% The pluggable transports infrastructure makes it relatively easy to prototype
+% a circumvention technique and connect it to a global proxy network.
+% We can treat confidentiality and integrity of tunneled communication
+% as a problem solved by Tor, which we don't need to solve separately.
+% Tor's extra proxy hops mean that the HTTP reflector (App Engine)
+% and the entry bridge do not have to be trusted.
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.40\linewidth}
+\includegraphics[width=\linewidth]{wire-sequential}
+\caption{Sequential}
+\label{fig:wire-sequential}
+\end{subfigure}
+\qquad
+\begin{subfigure}[t]{0.40\linewidth}
+\includegraphics[width=\linewidth]{wire-parallel}
+\caption{Parallel}
+\label{fig:wire-parallel}
+\end{subfigure}
+
+\caption{
+The nature of potential performance gain
+from sending fronted requests in parallel.
+}
+\label{fig:wire}
+\end{figure}
+
 We have assumed that the intermediate web service is
@@
 then fronting will still work.
+
+The ``domainless'' fronting style, which omits SNI,
+is useful when there is no good front domain known for a web service.
+At least one CDN, Fastly, requires the domainless style.
+All current web browsers support SNI,
+so it is possible that lack of SNI could be used as a distinguisher.
+According to our communication with
+a representative of the International Computer Science Institute's
+certificate notary~\cite{icsi-notary},
+which observes on the order of 50~million TLS connections daily,
+83.5\% of connections used SNI in June~2014.
+There are apparently enough connections without SNI
+that a censor will at least have to consider seriously
+the costs and benefits before deciding to block SNI outright.
+
+The current implementation of meek strictly serializes
+its HTTPS requests and responses,
+in order to keep the chunks of the underlying TCP stream
+in the proper order.
+The unfortunate side effect of this simple approach
+is delay that gets worse with higher round-trip times.
+In future work we plan to add an additional reliability layer,
+perhaps like the system of sequence numbers and acknowledgments used in OSS~\cite{oss},
+that would allow requests to be pipelined
+and cope with out-of-order delivery.
+Figure~\ref{fig:wire-sequential} shows how the current implementation works,
+and Figure~\ref{fig:wire-parallel} shows the nature of the performance
+improvement that could be gained with a reliability layer.
+% Would be useful for Iran-like session cutoff, independent of \meek.
 
@@
 The key idea of meek is domain fronting,
-but its HTTP-tunneling ability is useful on its own.
+but its HTTP tunneling ability is useful on its own.
 Another idea for deployment is to use
@@
 
-The ``domainless'' fronting style, which omits SNI,
-is useful when there is no good front domain known for a web service.
-At least one CDN, Fastly, requires the domainless style.
-All current web browsers support SNI,
-so it is possible that lack of SNI could be used as a distinguisher.
-According to our communication with
-a representative of the International Computer Science Institute's
-certificate notary~\cite{icsi-notary},
-which observes on the order of 50~million TLS connections daily,
-83.5\% of connections used SNI in June~2014.
-There are apparently enough connections without SNI
-that a censor will at least have to consider seriously
-the costs and benefits before deciding to block SNI outright.
-
-The deployment we envision and have started to implement
-uses a single paid App Engine instance, which is publicly known and usable by anyone.
-Client software is configured to use this public instance by default.
-A preconfigured public instance has great usability advantages
-because there is nothing for the user to upload and nothing to configure.
-The number of parties able to analyze users' traffic patterns is somewhat increased:
-the path from user to Tor bridge now includes App Engine and the web app operators,
-in addition to the ISP and intermediate routers that were there before.
-On the other hand, the Tor bridge no longer gets to see users' IP addresses:
-all it sees are many connections from App Engine.
-
-Users are also free to upload their own personal copy of the App Engine code, as is done with GoAgent.
-App Engine imposes bandwidth quotas on unpaid apps, but they are high enough to allow daily web browsing.
-In this scenario, Google still has a privileged network position,
-but the user's traffic patterns are no longer visible to the operators of a public app instance.
-% Outgoing HTTP requests include app id? As good as an IP address.
-
 \section{Summary}

### 2014-08-01 docs/meek.tex
Just have to be similar enough.

@@
 it also depends on the endpoint.
-Google is likely to be different than Akamai,
-and it is hard to characterize what normal use of a CDN is:
+Google's traffic is likely to be different than Akamai's.
+
+For the purposes of censorship circumvention,
+one doesn't need to match exactly a ``typical'' traffic profile;
+only not to deviate from it too much.
+Circumvention traffic must only be difficult enough to distinguish,
+that blocking requires a number of false positives unacceptable to the censor.
+Even 1\% of Google traffic accidentally blocked may exceed the collateral damage tolerance of some censors.
+Further, it is hard to characterize what normal use is, of, say, a CDN:
 they provide access to ordinary web sites,
-but also video streams and software updates,
+but also to video streams and software updates,
 and not all clients are browsers.
-The difficulty is symmetric;
+The difficulty we face is symmetric;
 if finding the right model is difficult task for us,

### 2014-08-01 docs/meek.tex
Spellcheck.

@@
 of the Host field and the specifics of the intermediate web service's TLS,
-but is somewhere in the neightborhood of $(543+450)/543-1\approx83$\%.
+but is somewhere in the neighborhood of $(543+450)/543-1\approx83$\%.
 This is the worst case, when Tor sends a single cell.
@@
 when it blocked access to all Google services~\cite{cn-google-block}.
-In 2012, the government of Pakisten blocked to all of YouTube
+In 2012, the government of Pakistan blocked to all of YouTube
 in order to restrict access to one video,
@@
 It seems risky for the censor to risk being detected in
-ia man-in-the-middle attack merely to confirm that a user is circumventing,
+a man-in-the-middle attack merely to confirm that a user is circumventing,
 but it is not impossible for a sufficiently powerful censor.

### 2014-08-01 docs/meek.tex
Comment out authors.
I think we also need to do the ISCI and LBL stuff.
Top-to-bottom proofreading.

@@
 
-\author{David Fifield, Chang Lan}
-\author{
-\IEEEauthorblockN{David Fifield and Chang Lan}
-\IEEEauthorblockA{University of California, Berkeley}
-}
+% ANON
+% \author{David Fifield, Chang Lan}
+% \author{
+% \IEEEauthorblockN{David Fifield and Chang Lan}
+% \IEEEauthorblockA{University of California, Berkeley}
+% }
 
@@
 for the purpose of censorship circumvention.
-Fronting enables a communication stream that is apparently with an allowed domain,
+Domain fronting enables communication that is apparently with an allowed domain,
 but actually with a forbidden domain.
-The technique uses different domain names at different communication layers.
-One domain is used on the ``outside''---in the DNS request and
+The key idea is the use of different domain names at different communication layers.
+One domain is used on the ``outside'' of an HTTPS request---in the DNS request and
 TLS Server Name Indication---while another is used
@@
 We identify a number of hard-to-block web services,
-like content delivery networks and Google's infrastructure,
-that ignore the outside of an HTTPS request
-and dispatch it internally according to the Host header.
-The effect is that a user may communicate with any domain within the web service,
-while appearing to communicate with any other domain.
+like content delivery networks and Google,
+that enable fronting by ignoring the outside of an HTTPS request
+and dispatching it internally according to the Host header.
+The effect of fronting is that a user may communicate with one domain,
+even one forbidden by the censor,
+while appearing to communicate with another.
 If a censor is unable otherwise to distinguish fronted and non-fronted traffic,
@@
 The \meek\ server's external interface is that of an ordinary web server.
-Communication with it is enabled through domain fronting.
+Domain fronting enables a client to reach the server.
 The server receives requests, decodes them, and feeds their payloads into a Tor relay,
@@
 A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
-but which actually arrive at a special web server on a Tor relay.
+We describe the results of an initial deployment.
 \meek, or something based on it,
@@
 We argue that these measures increase the censor's effort
-beyond simple one-shot techniques such as IP address blocking, and into
+beyond simple one-shot blocking techniques such as IP address blocking, and into
 the realm of more expensive, less reliable statistical tests.
@@
 accidental overblocking committed in the course of trying to censor something else.
-One way to win against the censor is to entangle circumvention traffic
-with ordinary Internet traffic in a way that both must be blocked together
+One way to win against censorship is to entangle circumvention traffic
+with ordinary Internet traffic in a way that either both must be blocked together,
 or not at all.
@@
 and Google's panoply of services---a nontrivial fraction of the web.
-See Section~\ref{sec:survey} for a listing of some suitable services.
-Domain fronting can be used as a means of tunneling traffic
+See Section~\ref{sec:survey} for a list of suitable services.
+Domain fronting can be used to tunnel traffic
 to a general-purpose proxy,
-so it is not limited to HTTPS, nor to the domains of any specific web service.
-
-The key idea of domain fronting is using
+so that circumvention is not limited to HTTPS, nor to the domains of any specific web service.
+
+The key idea of domain fronting is the use of
 different domain names at different layers of communication.
@@
 in three places relevant to the discussion:
-the DNS query,
+in the DNS query,
 the TLS Server Name Indication (SNI) extension~\cite[Section~3]{rfc6066},
 and the HTTP Host header~\cite[Section~14.23]{rfc2616}.
-Normally, the same domain name appears in all three places.
-In a domain-fronted request,
+Usually, the same domain name appears in all three places.
+But in a domain-fronted request,
 the DNS query and SNI carry one name (the ``front domain''),
@@
 which is hidden from censor by HTTPS encryption,
-has a different name (the actual destination).
+carries another (the actual destination).
 
@@
 the front domain \mbox{\textbf{allowed.example}}.
-At the HTTP layer, unreadable to the censor but meaningful to the CDN or web service,
+At the HTTP layer, unreadable to the censor but meaningful to the intermediate web service,
 is the actual destination \mbox{\textbf{forbidden.example}}.
@@
 
-Neither the DNS nor the SNI can be blocked without
+Neither the DNS request nor the SNI can be blocked without
 collaterally blocking the front domain.
-The Host header is unknown to the censor,
-but known to the server receiving the HTTPS request,
+The Host header is invisible to the censor,
+but visible to the server receiving the HTTPS request,
 which uses the header to internally route the request to its destination.
@@
 on Google's infrastructure.
-An HTTPS request for \urll{www.google.com} has a Host header for
-\urll{maps.google.com}, and the HTML in the response is that of Google Maps.
+Here, an HTTPS request for \urll{www.google.com} has a Host header for
+\urll{maps.google.com}. The HTML in the response is that of Google Maps.
 
@@
 % or may be a generic shared domain.~\cite{httpsincdn}
-The CDN's edge server won't forward requests just anywhere---it
-has to be to the domain of a customer.
-This means that in order to host a proxy,
-one has to create an account and pay for bandwidth.
 Fronting works with Google because Google App Engine, a web application platform,
@@
 an origin-pull CDN, simply forwarding every request to an origin server.
+In both cases, the intermediate web service does not forward requests just anywhere---it
+has to be to the domain of a customer.
+In order to run a fronting backend,
+one has to create an account and pay for bandwidth.
 
@@
 like the user is browsing an HTTPS site by its IP address,
-or using an old browser that doesn't support SNI.
+or using a web client that doesn't support SNI.
 Domainless fronting can be useful when there is no front domain
-with sufficiently high collateral damage.
+known to have sufficiently high collateral damage.
 The censor is faced with the choice of blocking an entire IP address,
 blocking requests without SNI,
-or finding some other, presumably more expensive, test to distinguish
+or finding some other, presumably more expensive, test to try to distinguish
 circumvention traffic.
@@
 We have developed domain fronting into a full-fledged circumvention system called \meek,
-implemented as a Tor pluggable transport~\cite{pt}.
+implemented as pluggable transport~\cite{pt} for Tor.
 \meek\ combines fronting with an HTTP-based tunneling proxy:
@@
 The server decodes the requests and feeds their payloads
-into a local Tor relay.
-Downstream data received from the Tor relay
-are returned to the client as HTTP responses
-through the same fronted channel.
+into the Tor network.
+Downstream data received from Tor
+are returned to the client as HTTP responses.
 \meek's architecture appears in Figure~\ref{fig:architecture}.
-Section~\ref{sec:architecture} describes its workings in detail.
+Section~\ref{sec:architecture} describes how it works in detail.
 
@@
 \meek\ has been built into an alpha version of Tor Browser,
-and has seen use by a small number of users.
-Our deployment uses Google App Engine,
-with the hidden actual domain \urll{meek-reflect.appspot.com}
-hidden by the front \urll{www.google.com}.
-Section~\ref{sec:deployment} discusses other systems \meek\ can work with
-and other deployment scenarios.
+and has a small number of users.
+Our deployment so far uses Google App Engine and Amazon CloudFront.
+% with the hidden actual domain \urll{meek-reflect.appspot.com}
+% hidden by the front \urll{www.google.com}.
+Section~\ref{sec:deployment} discusses other fronting-capable services
+and deployment scenarios.
 In addition to the Tor pluggable transport,
-systems based on \meek\ are now in use by other circumvention systems
+systems based on \meek\ are now used by other circumvention systems
 including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.
@@
 Domain fronting and HTTPS take care of two big circumvention challenges,
-namely hiding the destination and obscuring the contents of the message.
-There remain other, more subtle, meta-attributes of communication
+those of hiding the destination and of obscuring the contents of a message.
+There remain other, more subtle, attributes of communication
 that could serve as a basis for blocking.
-For example, the handshake is a fingerprintable part of TLS.
+For example, the plaintext handshake is a fingerprintable part of TLS.
 Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
-in order that \meek's TLS and HTTPS characteristics
+to make \meek's TLS and HTTPS characteristics
 match those of a browser as closely as possible.
-One of our goals for \meek\ is to force the censor
+One of our goals is to force the censor
 to employ more sophisticated, expensive, and error-prone statistical tests
@@
 rather than simple domain blacklists or deep packet inspection;
-to force the frontier of censorship
-to be a frontier not of simple in-line packet filters,
+to force the practice of censorship to exist in a world
+not of simple packet filters,
 but of probabilities and false positives.
 A preliminary analysis of \meek's resistance to detection
-based on traffic characteristics like packet size and timing
+based on traffic characteristics like packet length distribution
 appears in Section~\ref{sec:trafficanalysis}.
-The analysis is based on comparing traffic traces of \meek
+The analysis is based on comparing traffic traces of meek
 with samples of HTTPS traffic at an Internet router.
@@
 for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
-GoAgent and flash proxy's rendezvous are the most direct
-inspirations of this work.
+GoAgent and flash proxy are the systems that most directly
+inspire this work.
 
@@
 An address-blocking censor forbids all communication with certain
-addresses, for example IP addresses and domain names, whatever the contents may be.
-A savvy censor will use both means of censorship---therefore
+addresses, for example IP addresses and domain names, whatever the contents of the communication may be.
+A savvy censor will use both means of censorship, and
 effective circumvention requires countering both.
 
-To the above challenges we may add a related one, active probing.
-An active-probing censor does not merely passively observe traffic;
+To the above challenges we add a related one, active probing.
+An active-probing censor does not merely passively observe traffic:
 it injects its own traffic,
@@
 proxy servers to see how they respond.
-If the connection is successful, the server can then be blacklisted.
-Active probing is a precise means of identifying a server as belonging to a circumvention system,
+If the connection is successful, the server may be blacklisted.
+Active probing is a precise means of identifying whether a server as belongs to a circumvention system,
 even when a protocol is hard to classify on the wire.
@@
 Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
-by issuing followup scans to observed client connections to see
+by issuing scans that follow up observed client connections, to discover
 whether a server speaks the Tor protocol.
@@
 and obfs4~\cite{obfs4},
-
-There are two general strategies for countering DPI.
+described in this section.
+
+There are two general strategies for countering content-based blocking.
 The first is to make traffic look unlike
@@
 to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
-Following the first strategy are the ``look-like-nothing'' transports whose
-payloads are indistinguishable from a uniformly random byte stream.
-Well-traveled look-like-nothing
-protocols are obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
-which have been Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
-They both work by superenciphering a stream, using a key exchange that has no plaintext components.
-ScrambleSuit~\cite{scramblesuit} is like obfs3 in the
-content of its payloads, but additionally obscures its traffic signature
+Following the first strategy are the so-called ``look-like-nothing'' transports whose
+payloads are indistinguishable from a uniformly random byte stream,
+good examples of which are
+obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
+Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
+Both obfs2 and obfs3 work by superenciphering an underlying stream,
+using a key exchange that has no plaintext components.
+ScrambleSuit~\cite{scramblesuit} is like obfs3 in its
+payload obfuscation, but additionally obscures its traffic signature
 (packet lengths and timing), and is designed to resist active probing.
-A ScrambleSuit server will accept a TCP connection but not send anything
-until the client proves knowledge of shared secret, depriving the censor
-of an easy distinguisher.
+A ScrambleSuit server will accept a TCP connection but not send a reply
+until the client proves knowledge of a shared secret.
 obfs4~\cite{obfs4}
@@
 
-The other strategy against DPI is the steganographic approach: look like
+The other strategy against DPI is the steganographic one: look like
 something the censor doesn't block.
@@
 StegoTorus~\cite{stegotorus}
-encodes traffic to look like a cover protocol
+transforms traffic to look like a cover protocol
 using a variety of special-purpose encoders.
@@
 FreeWave~\cite{freewave} encodes a stream as an acoustic signal
-and sends it over VoIP to a proxy, which decodes it and forwards it to the destination.
+and sends it over VoIP to a proxy.
 Dust~\cite{dust} uses encryption to hide static byte patterns and then
@@
 The other grand challenge of proxy-based circumvention is address-based blocking.
-Tor has long faced the blocking of its entry relays,
-the addresses of which are in a public directory.
+Tor has long faced the problem of the blocking of its entry relays,
+the addresses of which appear in a public directory.
 In response, Tor began to reserve a portion of its
@@
 the combination
-of careful bridge address dispersal and obfuscated protocols
+of careful bridge address distribution and obfuscated protocols
 gives Tor's system a realistic claim to addressing both main challenges of circumvention.
@@
 
+CensorSpoofer~\cite{censorspoofer}
+decouples upstream and downstream data channels.
+The client sends data to a CensorSpoofer proxy over a low-bandwidth covert channel such as email.
+The proxy sends data back over a UDP channel, all the time
+spoofing its source address so the packets appear to originate from some other ``dummy'' host.
+The censor has no IP address to block, because the proxy's true address never appears on the wire.
+Client and server have the challenge of agreeing on a dependable covert upstream channel
+that must remain unblocked,
+and the client must carry on a believable UDP conversation with the dummy host
+(the authors suggest a VoIP call).
+
 Flash proxy~\cite{flashproxy} resists address blocking by
-conscripting web users as temporary proxies. Proxies last only as long as a web
-user stays on a page, so the pool of proxies is constantly changing.
+conscripting web users as temporary proxies.
+Each proxy lasts only as long as a
+user stays on a web page, so the pool of proxies is constantly changing.
 If one of them is blocked, there is soon another to replace it.
@@
 translate the web page at \urll{http://forbidden.example/}\textsl{data...},
-where ``\textsl{data...}'' is the message the client wishes to send,
-embedded in the URL.
+where ``\textsl{data...}'' is the URL-embedded message the client wants to send.
 The translation service requests the URL,
@@
 OSS shares certain similarities with domain fronting:
-the web service takes the place of the front domain,
+an unblockable web service takes the place of the front domain,
 and the destination of the communication is embedded somewhere in an HTTPS query
@@
 
-Decoy routing~\cite{decoyrouting}, also called end-to-middle proxying,
+Decoy routing~\cite{decoyrouting}
 is a technique that puts
 proxies in the middle of network paths, rather than at the ends.
+For this reason, it is also called end-to-middle proxying.
 Realizations of decoy routing include Telex~\cite{telex},
@@
 and toward a censored, \emph{covert destination}.
-Domain fronting is similar in spirit to decoy routing;
+Domain fronting is similar in spirit to decoy routing:
 think of domain fronting as decoy routing at the application layer.
-In place of a router, domain fronting has a web service's frontend server;
+In place of a router, domain fronting has a frontend server;
 in place of the overt destination is the front domain.
@@
 
-CensorSpoofer~\cite{censorspoofer}
-decouples upstream and downstream data channels.
-The client sends data to a CensorSpoofer proxy over a low-bandwidth covert channel such as email.
-The proxy sends data back over a UDP channel, all the time
-spoofing its source address so the packets appear to originate from some other ``dummy'' host.
-The censor has no IP address to block, because the proxy's true address never appears on the wire.
-Client and server have the challenge of agreeing on a dependable covert upstream channel
-that must itself remain unblocked,
-and the client must carry on a believable UDP conversation with the dummy host
-(the authors suggest a VoIP call).
-
 CloudTransport~\cite{cloudtransport} uses cloud storage, for example Amazon~S3,
@@
 In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
-is hidden in the path rather than the Host header.
+is hidden in the path component of the URL.
 For example, in an example S3 URL
@@
 which would reveal that CloudTransport is being used,
-cannot be used for blocking because it is encrypted in HTTPS.
-
-GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of App
-Engine and Host header--based domain fronting.
-Traffic is fronted by the Google frontend server
+cannot be used for blocking because it is encrypted inside HTTPS.
+
+GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of
+domain fronting with App Engine.
+Traffic is fronted by the Google frontend server,
+using the ``domainless'' fronting model without SNI,
 and delivered to its destination by a specialized app running on App Engine.
-GoAgent uses the ``domainless'' fronting model without SNI for most target domains.
 GoAgent doesn't use an additional general-purpose proxy after fronting;
-rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers,
-meaning that GoAgent is limited to carrying HTTP and HTTPS traffic,
-and the contents of all communications are revealed to App Engine.
-Users of GoAgent upload their own personal copy of the proxy code to App Engine,
-which is free of charge as long as they do not exceed a bandwidth quota.
+rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
+Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
+and the contents of all communications are revealed to Google.
+Users of GoAgent generally upload their own personal copy of the proxy code to App Engine,
+which is free of charge to use as long as they do not exceed a bandwidth quota.
 According to a May 2013 survey~\cite{collateral-freedom},
@@
 Cloud-Entry~\cite{cloud-entry} is somewhat similar to GoAgent.
-It also uses App Engine, but uses a socket API rather than a URL fetch API
+It also uses App Engine, but uses a socket API rather than a URL fetch API,
 in order to support protocols other than HTTP and HTTPS.
@@
 that take longer than 60~seconds,
-so users must reconnect at least every 60~seconds.
+so users must reconnect at least that often.
 
@@
 the censored client,
-the intermediate web service (CDN),
+the intermediate web service,
 and the destination Tor bridge.
@@
 the bridge,
-because the bridge proxies to anywhere.
+because the bridge can then proxy to anywhere.
 The client and bridge cooperate with each other.
-The intermediate web service does not cooperate with either,
+The intermediate web service does not need to cooperate with either,
 except to the extent that it doesn't collude with the censor.
@@
 The client lies within the censor's network,
-while the intermediate web service and bridge lie outside the network.
+while the intermediate web service and bridge lie outside.
 The censor blocks direct communication between the client and the bridge,
@@
 Section~\ref{sec:discussion} shows what happens when some
-of these assumptions are violated;
+of the threat model's assumptions are violated;
 specifically what happens
@@
 and when the censor controls a certificate authority.
-That section also describes the use of \meek\ apart from Tor.
-
-% What about in-country edge servers; seems to work.
 
@@
 The components of the system are shown in Figure~\ref{fig:architecture}.
-The parts that are new in \meek
+The parts that are new in meek
 are the programs \meekclient\ and \meekserver,
-which are the pluggable-transports~\cite{pt} interface between Tor and \meek.
+which are the pluggable-transports~\cite{pt} interface with Tor.
 
 \meekclient\ is essentially a web client that knows how to front HTTPS requests.
-When \meekclient\ receives data from a client Tor process, it bundles it up into a POST request
-and fronts the request through the web service
-(which in turn forwards it to \meekserver\ on the bridge).
-If the response contains any payload, \meekclient\ decodes it and returns it back to Tor.
+When \meekclient\ receives outgoing data from a client Tor process, it bundles them up into a POST request
+and fronts the request through the web service,
+which in turn forwards the request to \meekserver\ on the bridge.
+If the response contains any HTTP body, \meekclient\ decodes it and returns it back to Tor.
 \meekclient\ takes pains to make its TLS fingerprint
@@
 When \meekserver\ receives a request, it extracts the body and feeds it into
-a local Tor running as a bridge.
+a local Tor process running as a bridge.
 If there are any data pending to be sent back to the client from Tor,
@@
 \meekserver\ also handles session management:
-as there may be many clients using the service at once,
+because there may be many clients using the service at once,
 the server must determine which client session each incoming request belongs to.
@@
 
-When \meek\ is used with Google App Engine, one other component is needed.
-It is a small ``reflector'' web app that simply copies any request
-it receives and forwards it to an instance of \meekserver\ running on a bridge.
+When \meek\ is used with Google App Engine, one other component is needed:
+a small ``reflector'' web app that simply copies any request
+it receives and forwards it to a remote instance of \meekserver.
 App Engine cannot directly run a Tor bridge,
@@
 The reflector app emulates the behavior of an origin-pull CDN,
-which also simply copies and forwards a request to the origin server
+which also simply copies and forwards requests
 when the response is not already cached.
 
-The main technical challenge is handling a TCP stream
-that has been split up into a sequence of HTTP requests and responses.
+The main technical challenge of the protocol is splitting up a TCP stream
+into a sequence of HTTP requests and responses.
+The underlying TCP stream is broken into chunks so that
+it can be sent over HTTP.
 The body of each HTTP request and HTTP response carries
 a small chunk of upstream or downstream communication.
-\meekserver\ must handle many clients at once,
-and therefore maintains many open connections to the local Tor process,
-one for each active client.
-When a new request arrives, the server must determine which
-open session it belongs to
-(or whether it is a brand-new client needing a new session).
-In TCP, different streams are distinguished by their
-(source~IP, source port, dest~IP, dest~port) tuple,
-but that doesn't work for \meek\ for two reasons:
-the source IP of the requests is that of the intermediate web service,
-not that of the client;
-and a logical stream is chopped into multiple independent HTTP requests,
-so the source port is always changing.
-Rather, each client generates a random 256-bit session ID,
-which it sends with each of its requests in a special
-X-Session-Id header.
-\meekserver, when it sees a session ID for the first time,
-opens up a new connection to the local Tor process
-and associates the connection and ID in a cache.
-Subsequent requests with the
-same session ID will reuse the same Tor connection.
-Sessions are closed after a period of inactivity.
-Figure~\ref{fig:protocol} shows a sample of the protocol.
+There must therefore be some way of making sure that chunks
+are correctly reassembled at the other end,
+in order and without gaps and duplicates.
+\meek\ takes a naive approach: requests and responses are strictly serialized.
+The client doesn't send a second chunk of data
+(i.e, make another HTTPS request) until it has
+received the response to its first.
+The reconstructed stream is simply the concatenation
+of bodies in the order they arrive.
+Doing it this way is simple and guarantees correctness,
+but has performance drawbacks because there is a full round-trip
+between every send.
+Section~\ref{sec:discussion} proposes a more efficient encoding
+that would enable multiple requests in parallel.
 
@@
 
-The underlying TCP stream is broken into chunks so that
-There must therefore be some way of making sure that chunks
-are correctly reassembled at the other end,
-in order and without gaps and duplicates.
-\meek\ takes a naive approach: requests and responses are strictly serialized.
-The client doesn't send a second chunk of data
-(i.e, make another HTTPS request) until it has
-receive the response to the first request.
-The underlying stream is simply the concatenation
-of chunks in the order they arrive.
-Doing it this way is simple and guarantees correctness,
-but has performance drawbacks because there is a full round-trip
-between every send.
-The performance drawbacks are not inherent to the design:
-it is domain fronting, not HTTP encoding, that is the fundamental strength of the system.
-Section~\ref{sec:discussion} describes more efficient encodings
-that enable multiple requests in parallel.
+\meekserver\ must handle many clients at once,
+and therefore maintains many open connections to the local Tor process,
+one for each active client.
+When a new request arrives, the server must determine which
+open session it belongs to
+(or whether it is a brand-new client needing a new session).
+In TCP, different streams are distinguished by their
+(source~IP, source port, dest~IP, dest~port) tuple,
+but that doesn't work for \meek, for two reasons:
+the source IP of the requests is that of the intermediate web service,
+not that of the client;
+and a logical stream is chopped into multiple independent HTTP requests,
+so the source port is always changing.
+Instead, each client generates a random 256-bit session ID for each new Tor stream,
+which it sends with each of its requests in a special
+X-Session-Id HTTP header.
+\meekserver, when it sees a session ID for the first time,
+opens up a new connection to the local Tor process
+and associates the connection and ID in a cache.
+Subsequent requests with the
+same session ID will reuse the same Tor connection.
+Sessions are closed after a period of inactivity.
+Figure~\ref{fig:protocol} shows a sample of the protocol.
 
@@
 every so often the client sends a request with an empty payload
-if it has nothing else to send.
+if it has nothing else to send,
+simply to give the server an opportunity to reply.
 The polling interval starts short (100~ms) and grows exponentially
@@
 When the server receives a new request from the same client,
-it closes any response it has open to the client and starts a new response.
-This second technique doesn't work on all services:
-notably Google App Engine doesn't support streaming downloads of this kind.
-
-As an encrypted tunneling protocol, meek adds some overhead.
+it closes any response stream it has open to the client and starts a new one.
+This second technique is especially beneficial for bulk downloads,
+but doesn't work on all services:
+notably Google App Engine doesn't support streaming of this kind.
+
+As an encrypted tunneling protocol, meek necessarily adds overhead.
 Each chunk of data gets an HTTP header, and then the HTTP
-request is wrapped in a TLS Application Data record.
+request is wrapped in TLS.
 We estimate the overhead when meek is used to transport Tor.
@@
 Each cell is wrapped in a TLS Application Data record, which adds 29 bytes
-using a GCM ciphersuite.
+when using a GCM ciphersuite (the default in current versions of Tor).
 % (in Tor version~0.2.4.22 using a GCM ciphersuite).
@@
 ${\approx}41$\%; if three, it is ${\approx}28$\%.
-Bulk uploads and downloads tend to bunch many cells at once.
+Bulk uploads and downloads tend to have less overhead, bunching many cells at once.
 Persistent HTTP connections as used by Psiphon reduce overhead further,
-because only one HTTP header is sent for a large number of transmissions.
+because only one HTTP header is needed for a large number of transmissions.
 Empty polling requests also use bandwidth,
@@
 
-There is additional latency overhead caused by the extra network hop:
+% Mention server--client overhead?
+% The same except for HTTP header.
+
+There is additional latency overhead caused by meek's extra network hop:
 rather than accessing the Tor bridge directly,
-the client first goes through the intermediate web service before
-reaching the bridge.
-How much latency this adds, of course depends on the network location
+the client first goes to the intermediate web service.
+How much latency the extra hop adds depends, of course, on the network location
 of the client, web service, and Tor bridge.
@@
 becomes a problem with large round-trip times,
-because bandwidth becomes a function of latency.
+as throughput becomes limited by latency.
 Section~\ref{sec:discussion} describes ways to improve
@@
 Domain fronting defeats address-based blocking and active probing.
-HTTPS foils the most straightforward DPI,
-hiding byte patterns in the underlying stream.
-The censor may try to apply more careful DPI in order to
-distinguish fronted and non-fronted traffic.
+HTTPS foils simple DPI,
+hiding any byte patterns in the underlying stream.
+The censor may also apply DPI to the tunnel itself in order to try to
+distinguish fronted from non-fronted traffic.
 This section is about TLS fingerprinting,
@@
 to disguise the HTTPS tunnel.
-Section~\ref{sec:trafficanalysis} is about more subtle and hard-to-apply forms of DPI.
-
-The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}.
-The plaintext SNI extension, for instance, has to be protected by domain fronting.
-There is enough room for variation in other fields,
-such as the client's lists of ciphersuites and extensions,
-that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}.
+Section~\ref{sec:trafficanalysis} is about more subtle and hard-to-apply forms of traffic analysis.
+
+The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}, and leaves
+enough room for variation, for example in
+the client's lists of ciphersuites and extensions,
+that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
+based on the handshake.
 (We are only concerned with fingerprinting the client,
-because the server's TLS that the censor can observe
+because the server's TLS
 comes from the intermediate web service;
-i.e., it is what you would expect when connecting to the front domain.)
+i.e., it is what you would expect to see when connecting to the front domain.)
 Tor itself was blocked by China in 2011
 because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
-
 Figure~\ref{fig:ciphersuites} shows examples of how TLS client
-implementations may differ.
+implementations may detectably differ.
 \meekclient\ is written in the Go programming language,
@@
 Figure~\ref{fig:ciphersuites:golang}
-shows how it would appear with no TLS camouflage.
+shows how it would appear on the network with no TLS camouflage.
 Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
-which are browsers, are different; the browsers are also unlike each other.
+which are browsers, are different from Go's TLS; the browsers are also unlike each other.
 A censor could block an uncamouflaged \meek\ using Go's fingerprint,
@@
 \begin{subfigure}[t]{0.30\textwidth}
-\caption{Go 1.2's net/http library}
+\caption{Go 1.2's crypto/tls library}
 \begin{minipage}[t][25.5ex][t]{\textwidth}
@@
 The TLS fingerprint looks like that of a browser, because it is that of a browser.
-The browser instance with the extension is completely separate
+The browser instance running the extension is completely separate
 from the browser the user interacts with.
@@
 and \meekclient\ proxies through the headless browser.
-The headless browser is the only thing that ever actually touches the network.
+The headless browser is the only part that ever actually touches the network.
 It should be emphasized that the URLs requested by the headless browser extension
@@
 The use of a browser extension brings benefits beyond TLS camouflage.
-It means \meek\ inherits other traffic characteristics of the browser:
+It means \meek's HTTP tunnel inherits other characteristics of the browser:
 for instance
@@
 because Tor Browser
-is a modified version of Firefox.
-We can use the same browser executable for both the browser the user interacts with (Tor Browser)
-and the one providing TLS camouflage (a headless Firefox),
+is a modified version of Firefox:
+we can use the same browser executable for both the browser the user interacts with (Tor Browser)
+and the one providing TLS camouflage (headless Firefox),
 saving space in distribution packages
@@
 
-Appropriate TLS camouflage may differ according to circumstances.
+Appropriate TLS camouflage may differ depending on circumstances.
 On a traditional desktop PC, using a browser is probably the right choice.
@@
 but rather made all HTTPS requests with the standard Android HTTP API.
-This decision makes sense because typical Android applications
+This decision makes sense because other Android applications
 also use the standard API and share the same TLS fingerprint.
@@
 
-This section contains a brief survey of the fronting-capable
+This section contains a brief survey of fronting-capable
 web services we have found, each with its pros and cons.
 The list is not exhaustive and is meant to illustrate the broad
-support that exists for fronting.
-Of the services listed, we have deployed \meek
+support for fronting that exists.
+Of the services listed, we have so far deployed meek
 only on Google App Engine and Amazon CloudFront.
-We have only checked that fronting works on the others.
+For the others, we have only checked that fronting works.
 Recall that even web services that support fronting
 will front only for their own customers,
-so each deployment typically requires an investment of time and money.
+so new each deployment typically means becoming a customer and an investment of time and money.
 
@@
 is a web application platform.
-Each application gets a subdomain of \urll{appspot.com},
+Each application gets a user-specified subdomain of \urll{appspot.com},
 which can be fronted through almost any Google domain,
@@
 A CloudFront ``distribution'' associates
-a randomly generated subdomain of \urll{cloudfront.net}
+an automatically generated subdomain of \urll{cloudfront.net}
 with an origin server,
 which in our case is an instance of \meekserver.
-The front domain may be any other randomly generated subdomain---all
-of which support HTTPS through a wildcard certificate---or
-certain domain aliases like \urll{a0.awsstatic.com}.
+The front domain may be any other of CloudFront's automatically generated subdomains, all
+of which support HTTPS through a wildcard certificate.
 CloudFront has a usage tier that is free of charge for a year,
@@
 It appears that any domain name on CloudFlare
-can front for any other, even custom domains;
+can front for any other, even custom user-selected domains;
 however it is not obvious which one is best to use as a front.
@@
 (causing high collateral damage if blocked),
-or else the censor may call our bluff and simply block the domain entirely.
-It is doubly bad if that happens because not only is circumvention foiled,
-some unsuspecting third part has just had their web site blocked.
+or else the censor may simply block the domain entirely.
+It is doubly bad when a domain is blocked, because not only is circumvention foiled,
+but some unsuspecting third party has just had their web site blocked.
 A solution may be to round-robin through
-a pool of domain names;
+a pool of popular domain names;
 or to use ``domainless'' fronting that doesn't send SNI.
@@
 it would likely require institutional support
-to keep a circumvention system running in the long term.
+to keep a circumvention system running on it in the long term.
 
@@
 is a cloud computing platform that features a CDN.
-Similarly to CloudFront, users get a subdomain
+Similarly to CloudFront, users get automatically generated subdomains
 of \urll{vo.msecnd.net},
-all of which subdomains can front for each other.
+all of which can front for each other.
 There are other fronting domain names, like \urll{ajax.aspnetcdn.com},
-that may offer enough collateral damage.
+that may offer high collateral damage.
 
@@
 the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
+However, if the TLS ClientHello omits SNI, then the Host may be any Fastly domain.
 It is the only service we have found
@@
 One of our goals in developing \meek\ is to force
-the censor to use relatively expensive statistical classifiers
+the censor to use relatively more expensive statistical classifiers
 to effect blocking---generally, to increase the cost of censorship.
-We believe \meek\ as described is resistant to the ``easy''
+We believe \meek\ is resistant to the ``easy''
 forms of blocking, namely IP address and DNS blocking,
@@
 and mostly orthogonal to \meek's main idea, domain fronting.
-It may be that the problem is
+It may be that the problem of traffic analysis is
 best solved by a modular component not
@@
 We did a packet capture
-automatically browsing the home pages
-of the top 500 Alexa web sites using \meek,
-with a firewall in place so that no extraneous traffic was included.
-The used \meek\ in Tor Browser,
+of automatically browsing the home pages
+of the top 500 Alexa web sites using \meek\ in Tor Browser,
 with the browser camouflage described in Section~\ref{sec:browserextension},
@@
 Our representative of ordinary HTTPS traffic
-is a sanitized trace of 10 minutes of HTTPS traffic
-% anon
+is a sanitized 10-minute trace
 from Lawrence Berkeley National Laboratory (LBL),
@@
 % Mention the non-google if it appears in a figure.
-The trace contains packet headers only, not payloads
-were replaced by an incrementing counter.
 The LBL trace consists 313~megabytes of packet headers,
@@
 Figure~\ref{fig:datalen}
-compares the packet length distribution of both sample traffic traces in both directions.
+compares the packet length distributions of both sample traffic traces.
 In both cases, about 38\% of packets have an empty payload, mostly ACKs.
-There is a small peak at the usual TCP Maximum Segment Size
+There is a small peak in both traces at the usual TCP Maximum Segment Size
 of 1460 bytes.
@@
 Figure~\ref{fig:duration} shows the cumulative probability
-of connection duration in our two traces.
+of connection durations in our two traces.
 Considering the LBL trace first,
 we see interesting probability concentrations on
-some round numbers: 10~s, 60~s, 120~s, 180~s, and 240~s.
+round numbers: 10~s, 60~s, 120~s, 180~s, and 240~s.
 We hypothesize that this phenomenon is caused by
@@
 60\% of \meek\ connections lasts five minutes or longer,
-while only 13\% of those of ordinary traffic does.
+while only 13\% of those of ordinary traffic do.
 \meek\ has essentially no connections lasting less than 24 seconds,
@@
 
-The censor may decide to block any long-lived HTTPS connections between
+In light of these findings,
+the censor may decide to block any long-lived HTTPS connections between
 a client and a web service.
@@
 because if the censor terminates connections after, say, 10 minutes,
-that's 10 minutes of circumvention achieved,
+in any case that's 10 minutes of circumvention achieved,
 after which \meek\ can start a new connection
 and allow Tor to rebuild its circuits.
-Future enhancements may even allow reconnecting using the same session ID,
+Future enhancements in meek may even allow reconnecting using the same session ID,
 so there will be no effect on the client other than a brief delay
@@
 with some hosts briefly spiking up above 50 connections,
-but the average case if very heavily skewed to smaller numbers.
+but the average case is very heavily skewed to smaller numbers.
 The average number of connections in the LBL trace is 2.61,
-while that in the meek trace is almost exactly 1, only briefly
+while in the meek trace it is almost exactly 1, only briefly
 deviating when one connection ends and another begins.
-We conclude that a small number of concurrent connections is unremarkable.
+We conclude that having a small number of concurrent connections is unremarkable.
 
@@
 it also depends on the endpoint.
-Google's traffic is likely to be different than Akamai's.
+Google's traffic is different than Akamai's.
 
@@
 only not to deviate from it too much.
-Circumvention traffic must only be difficult enough to distinguish,
+Circumvention traffic must only be difficult enough to distinguish from ordinary traffic,
 that blocking requires a number of false positives unacceptable to the censor.
 Even 1\% of Google traffic accidentally blocked may exceed the collateral damage tolerance of some censors.
-Further, it is hard to characterize what normal use is, of, say, a CDN:
+Further, it is hard to characterize what normal use is of, say, a CDN:
 they provide access to ordinary web sites,
 but also to video streams and software updates,
-and not all clients are browsers.
+and not all clients are web browsers.
 The difficulty we face is symmetric;
@@
 We have seen that censors prefer to use easy classifiers when they exist.
-By removing the easy ways, we increase the cost to the censor.
+By removing the easy ways, we increase the censor's cost.
 
@@
 Development on meek as a Tor pluggable transport~\cite{pt} began in January~2014.
-Most users who use Tor use Tor Browser~\cite{torbrowser},
+Most users who use Tor, use it with Tor Browser~\cite{torbrowser},
 a customized version of Firefox that is
@@
 % like tracking cookies and web browser fingerprinting.
-Tor Browser has an easy interface for selecting a pluggable transport.
+Tor Browser has an easy interface for selecting pluggable transports.
 We made a series experimental releases of Tor Browser featuring meek,
@@
 Our code was merged by the Tor Browser maintainers
-in June and scheduled for an alpha release,
-which is still pending as of this writing.
+in June and is scheduled for an alpha release,
+still pending as of this writing.
 
@@
 The measurements come from the Tor Metrics Portal~\cite{metrics-meek},
-which aggregates statistics self-reported by Tor relays.
+which aggregates statistics reported by Tor relays.
 The number of users is estimated by counting the number
@@
 of unique daily users of meek with Psiphon,
-estimated through clients' self-reporting of most recent connection date.
+estimated through clients' self-reporting of their most recent connection date.
 The Psiphon developers tell us that the drop that occurs
@@
 
-The experimental Tor Browser releases have all used Google with App Engine as the intermediate web service.
+The experimental Tor Browser releases have all been based on Google with App Engine.
 Support for CloudFront was not realized until late July.
-We are running the backends on paid accounts for use by the public.
+We are running the backends on paid accounts of these services for use by the public.
 The cost for bandwidth on App Engine is \$0.12 per gigabyte,
@@
 A longer-term goal is to find a way to fund continued operation
-if the system becomes popular.
+if meek becomes popular.
 Although some of the systems listed in Section~\ref{sec:survey}
@@
 has compelling usability advantages.
-With client software can be configured to use the public backend by default,
+With client software configured to use the public backend by default,
 there is nothing for the user to upload and no out-of-band communication is needed before getting
-started---if everything works it offers no-configure circumvention.
+started---when everything works it offers no-configure circumvention.
 
@@
 Domain fronting derives part of its unblockability from the
-high collateral damage of blocking the domain fronted through.
+high collateral damage of blocking the fronted-through domain.
 Fronting through \urll{www.google.com} to App Engine, for example,
-is betting that censor will lack the temerity to block Google.
+is making a bet that the censor will lack the temerity to block Google.
 The Great Firewall of China called our bluff in June of 2014,
@@
 by the censor and by users of a system.
-To block Google is an extreme measure,
-probably out of reach of most censors.
+To be sure, blocking Google is an extreme measure,
+probably out of the reach of most censors.
 Blocking all of the fronting-capable services listed in
@@
 (i.e., require SNI to be present and SNI and Host header to agree),
-or merely to get rid of their customers who are
-engaged in fronting in the support of circumvention.
+or to get rid of their customers who are
+engaged in enabling circumvention (i.e., us).
 The censor could threaten to block the web service entirely otherwise.
 Whether the attack will succeed depends on the censor's
-and the web service's specific motivations,
+and the web service's specific costs and motivations,
 so we cannot make any general statements.
@@
 whether it hurts the web service or the censor more
-when a web service is blocked.
-Nothing works against a censor with sufficiently high tolerance for
-collateral damage,
-but we also don't have to defeat the world's
-most powerful censor in order to be successful.
-What doesn't work in one place may work in another.
+when the service is blocked.
+% Nothing works against a censor with sufficiently high tolerance for
+% collateral damage,
+% but we also don't have to defeat the world's
+% most powerful censor in order to be successful.
+% What doesn't work in one place may work in another.
 
 Domain fronting shares a potential weakness with decoy routing,
-which is that the overt and covert destinations lie on different
+which is that the overt and covert destinations lie at the ends of different
 network paths.
@@
 distinguish fronted traffic from traffic that is truly destined
-to the front domain.
+to the apparent destination.
 For example, a CDN can be expected to have responses
@@
 
-The intermediate web service enjoys a privileged network position
+The intermediate web service enjoys a privileged network position,
 from which it is able to monitor all circumvention traffic.
@@
 The web service has basically the same network visibility
-as a client's ISP would have if the client were connecting to Tor directly.
+as the client's ISP would have, if the client were not circumventing.
 For this reason, domain fronting should be combined with another
@@
 for example browsing YouTube while fronting through \urll{www.google.com}.
-Even with Tor, in this case the web service gets to see
+Even with Tor, when this happens the web service gets to see
 both entry and exit traffic, and is in a position to
@@
 but popular domains are also the ones people tend to want to go to.
-A possible mitigation is traffic obfuscation that lasts all
-the way to the second hop of a three-hop Tor circuit,
+A possible mitigation is traffic padding that lasts until
+the second hop of a three-hop Tor circuit,
 which would reduce the correlation between entry and exit traffic.
@@
 inside the network controlled by the censor?
-If the edge server forwards the request to the Tor bridge
+If the edge server forwards the request to the bridge
 as an ordinary HTTP request on the public Internet,
@@
 that a censor will at least have to consider seriously
-the costs and benefits before deciding to block SNI outright.
+the costs and benefits before deciding to block SNI-less TLS outright.
 
@@
 its HTTPS requests and responses,
-in order to keep the chunks of the underlying TCP stream
+in order to keep chunks of the underlying TCP stream
 in the proper order.
 The unfortunate side effect of this simple approach
-is delay that gets worse with higher round-trip times.
+is added latency that gets worse with longer round-trip times.
 In future work we plan to add an additional reliability layer,
@@
 and Figure~\ref{fig:wire-parallel} shows the nature of the performance
-improvement that could be gained with a reliability layer.
+improvement that could be gained with a reliability layer
+and parallel requests.
 % Would be useful for Iran-like session cutoff, independent of \meek.
@@
 The browser running the HTTPS camouflage extension (Section~\ref{sec:browserextension})
-has a standard list of trusted certificate authorities.
+has a list of trusted certificate authorities.
 A censor that controls a certificate authority trusted by the browser
@@
 between the client and the intermediate web service,
-and detect fronting by decrypting HTTP requests and checking for specific Host headers.
+and detect fronting by decrypting TLS and checking for specific Host headers.
 Such a censor would be able to detect circumvention,
@@
 (in place of domain fronting on a big CDN).
-The request-reflecting role of a CDN could
+The request-reflecting role of a CDN can
 be played by a PHP script, for example,
@@
 Their URLs unprotected by domain fronting,
-each reflector would be easily blockable,
+each reflector would be easily individually blockable,
 so there would need to be sufficiently many that
@@
 We implemented meek,
-a pluggable transport for Tor,
-show that it resists common methods of blocking,
+a pluggable transport for Tor.
+We show that it resists common methods of blocking,
 and begin an investigation into its
@@
 
+% ANON
 % \section*{Acknowledgments}

### 2014-08-01 docs/meek.tex
Move web services URLs to references

@@
 
-Google App Engine (\url{https://developers.google.com/appengine/})
+Google App Engine~\cite{googleappengine}
 is a web application platform.
@@
 
-Amazon CloudFront (\url{https://aws.amazon.com/cloudfront/}),
+Amazon CloudFront~\cite{cloudfront},
 not to be confused with CloudFlare,
@@
 
-CloudFlare (\url{https://www.cloudflare.com/}),
+CloudFlare~\cite{cloudflare},
 not to be confused with CloudFront,
@@
 
-Akamai (\url{http://www.akamai.com/}) is a large CDN.
+Akamai~\cite{akamai-site} is a large CDN.
 Requests may be fronted through the special HTTPS domain
@@
 
-Microsoft Azure (\url{http://azure.microsoft.com/})
+Microsoft Azure~\cite{azure}
 is a cloud computing platform that features a CDN.
@@
 
-Fastly (\url{http://www.fastly.com/}) is a CDN.
+Fastly~\cite{fastly} is a CDN.
 It is unique among the the services we tested in that

### 2014-08-01 docs/meek.tex
Comment on concurrent connections
Use teletypefont for "meek"
Also, use xspace package for correct spacing after commands.

@@
 \usepackage{textcomp}
+\usepackage{xspace}
 
 % Avoid line breaks in program names.
-\def\meekclient{\mbox{meek-client}}
-\def\meekserver{\mbox{meek-server}}
-\def\meek{meek}
+\newcommand{\meekclient}{\mbox{meek-client}\xspace}
+\newcommand{\meekserver}{\mbox{meek-server}\xspace}
+\newcommand{\meek}{\texttt{meek}\xspace}
 \def\urll#1{\begin{NoHyper}\url{#1}\end{NoHyper}}
@@
 a pluggable transport for Tor.
-\meek\ combines fronting with a proxy server that encodes a TCP stream
+\meek combines fronting with a proxy server that encodes a TCP stream
 as a sequence of HTTP requests and responses.
-The \meek\ server's external interface is that of an ordinary web server.
+The \meek server's external interface is that of an ordinary web server.
 Domain fronting enables a client to reach the server.
@@
 implemented as pluggable transport~\cite{pt} for Tor.
-\meek\ combines fronting with an HTTP-based tunneling proxy:
+\meek combines fronting with an HTTP-based tunneling proxy:
 upstream data are transformed into a sequence of HTTP requests,
@@
 The bridge sends data back to the client in the HTTP response.
-\meekclient\ and \meekserver\ are transport plugins, the interface between Tor and \meek.
+\meekclient and \meekserver are transport plugins, the interface between Tor and \meek.
 The host actually at allowed.example does not participate in the communication.
@@
 
-\meek\ has been built into an alpha version of Tor Browser,
+\meek has been built into an alpha version of Tor Browser,
 and has a small number of users.
@@
 In addition to the Tor pluggable transport,
-systems based on \meek\ are now used by other circumvention systems
+systems based on \meek are now used by other circumvention systems
 including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.
 
-% \meek\ is designed to have features attractive in a circumvention transport.
+% \meek is designed to have features attractive in a circumvention transport.
 % It is easy to use, not requiring the configuration of any bridge addresses.
@@
 where flash proxy uses many cheap, disposable, individually blockable proxies,
-\meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
+\meek uses just a few high-value front domains on hard-to-block network infrastructure.
 A quirk of the browser proxy model is that
@@
 
-GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of
+GoAgent~\cite{goagent} is a direct inspiration for \meek in its use of
 domain fronting with App Engine.
@@
 when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
-\meek\ over App Engine was similarly affected.
+\meek over App Engine was similarly affected.
 % Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.
@@
 with encryption and traffic obfuscation between client and server.
-Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
+Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
 Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
@@
 
-% CORDON? Say how \meek\ would be classified in it?
+% CORDON? Say how \meek would be classified in it?
 
@@
 The components of the system are shown in Figure~\ref{fig:architecture}.
-The parts that are new in meek
-are the programs \meekclient\ and \meekserver,
+The parts that are new in \meek
+are the programs \meekclient and \meekserver,
 which are the pluggable-transports~\cite{pt} interface with Tor.
 
-\meekclient\ is essentially a web client that knows how to front HTTPS requests.
-When \meekclient\ receives outgoing data from a client Tor process, it bundles them up into a POST request
+\meekclient is essentially a web client that knows how to front HTTPS requests.
+When \meekclient receives outgoing data from a client Tor process, it bundles them up into a POST request
 and fronts the request through the web service,
-which in turn forwards the request to \meekserver\ on the bridge.
-If the response contains any HTTP body, \meekclient\ decodes it and returns it back to Tor.
-\meekclient\ takes pains to make its TLS fingerprint
+which in turn forwards the request to \meekserver on the bridge.
+If the response contains any HTTP body, \meekclient decodes it and returns it back to Tor.
+\meekclient takes pains to make its TLS fingerprint
 look like that of a browser; see Section~\ref{sec:browserextension}.
 
-\meekserver\ is a special-purpose web server.
-When \meekserver\ receives a request, it extracts the body and feeds it into
+\meekserver is a special-purpose web server.
+When \meekserver receives a request, it extracts the body and feeds it into
 a local Tor process running as a bridge.
 If there are any data pending to be sent back to the client from Tor,
-\meekserver\ includes it in the body of the HTTP response.
-\meekserver\ also handles session management:
+\meekserver includes it in the body of the HTTP response.
+\meekserver also handles session management:
 because there may be many clients using the service at once,
@@
 
-When \meek\ is used with Google App Engine, one other component is needed:
+When \meek is used with Google App Engine, one other component is needed:
 a small ``reflector'' web app that simply copies any request
@@
 in order and without gaps and duplicates.
-\meek\ takes a naive approach: requests and responses are strictly serialized.
+\meek takes a naive approach: requests and responses are strictly serialized.
 The client doesn't send a second chunk of data
@@
 \caption{
-Requests and responses in the \meek\ HTTP protocol.
+Requests and responses in the \meek HTTP protocol.
 The session ID is randomly generated by the client.
@@
 
-\meekserver\ must handle many clients at once,
+\meekserver must handle many clients at once,
 and therefore maintains many open connections to the local Tor process,
@@
 In order to enable the server to send back data,
-\meek\ uses one of two techniques.
+\meek uses one of two techniques.
 The first is polling:
@@
           &  $+$29 & Tor TLS record \\
-$\approx$ & $+$400 & meek HTTP header \\
-$\approx$ &  $+$50 & meek TLS record \\
+$\approx$ & $+$400 & \meek HTTP header \\
+$\approx$ &  $+$50 & \meek TLS record \\
 \hline
@@
 As is discussed in Section~\ref{sec:trafficanalysis},
-\meekclient\ reuses the same TLS connection for many requests,
+\meekclient reuses the same TLS connection for many requests,
 so the fixed overhead of the initial TLS handshake is amortized.
@@
 implementations may detectably differ.
-\meekclient\ is written in the Go programming language,
+\meekclient is written in the Go programming language,
 which has a custom TLS library~\cite{golang-crypto/tls};
@@
 which are browsers, are different from Go's TLS; the browsers are also unlike each other.
-A censor could block an uncamouflaged \meek\ using Go's fingerprint,
+A censor could block an uncamouflaged \meek using Go's fingerprint,
 if it considered the collateral damage resulting from blocking other Go programs to be slight enough.
@@
 In order to disguise its TLS fingerprint,
-\meekclient\ proxies all its HTTPS requests through an actual web browser.
+\meekclient proxies all its HTTPS requests through an actual web browser.
 We implemented extensions for two web browsers,
@@
 on the client's computer.
-The local Tor process starts a helper process that starts both \meekclient\
+The local Tor process starts a helper process that starts both \meekclient
 and the headless browser,
-then configures \meekclient\ to proxy its requests through the browser extension.
+then configures \meekclient to proxy its requests through the browser extension.
 The user's browser proxies through Tor;
 Tor proxies through \meekclient,
-and \meekclient\ proxies through the headless browser.
+and \meekclient proxies through the headless browser.
 The headless browser is the only part that ever actually touches the network.
@@
 The Firefox extension has special advantages
-when \meek\ is used with Tor Browser
+when \meek is used with Tor Browser
 because Tor Browser
@@
 the headless Firefox is started and stopped transparently
-when \meek\ is activated and deactivated.
+when \meek is activated and deactivated.
 
@@
 On a traditional desktop PC, using a browser is probably the right choice.
-When Psiphon ported \meekclient\ to Android,
+When Psiphon ported \meekclient to Android,
 they didn't use a browser as camouflage,
@@
 % its terms of service~\cite{cloudflare-terms}
-% seem to prohibit the kind of tunneled proxying that \meek\ does:
+% seem to prohibit the kind of tunneled proxying that \meek does:
 % \begin{quote}
@@
 
-One of our goals in developing \meek\ is to force
+One of our goals in developing \meek is to force
 the censor to use relatively more expensive statistical classifiers
 to effect blocking---generally, to increase the cost of censorship.
-We believe \meek\ is resistant to the ``easy''
+We believe \meek is resistant to the ``easy''
 forms of blocking, namely IP address and DNS blocking,
@@
 % Advantage is that we are probably proxying web traffic.
-As \meek\ is based on HTTPS,
-we compare traffic traces of \meek\ against
+As \meek is based on HTTPS,
+we compare traffic traces of \meek against
 traces of ``ordinary'' HTTPS traffic.
@@
 of automatically browsing the home pages
-of the top 500 Alexa web sites using \meek\ in Tor Browser,
+of the top 500 Alexa web sites using \meek in Tor Browser,
 with the browser camouflage described in Section~\ref{sec:browserextension},
 and Google App Engine as the intermediate web service.
-The \meek\ trace is 687~megabytes in all
+The \meek trace is 687~megabytes in all
 and covers about 4.5 hours of network activity.
@@
 \begin{tabular}{r r >{\qquad} r r}
-\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
+\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
 0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
@@
 from the LBL traffic trace,
-and \meek\ running on App Engine, fronted through www.google.com.
+and \meek running on App Engine, fronted through www.google.com.
 % The histogram's bin width is 5~bytes.
@@
 % http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
-Conspicuous in the \meek\ trace are a small number of
+Conspicuous in the \meek trace are a small number of
 frequent packet sizes,
@@
 of Tor's fixed cell size and the nearly fixed-size HTTP headers
-added by \meekclient\ and \meekserver.
+added by \meekclient and \meekserver.
 % In this trace, packets of 1024 bytes are probably single
@@
 %
-% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for \meek\ in order
+% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for \meek in order
 % to hide TLS handshake characteristics.
-% Browsers also apply techniques like HTTP pipelining to improve performance. Since \meek\ is always communicating with
+% Browsers also apply techniques like HTTP pipelining to improve performance. Since \meek is always communicating with
 % the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
@@
 % These browser techniques improve performance, but also pose unexpected consequences. 
-% Although \meek\ alters the packet size distribution of underlying Tor traffic, 
-% the censor may be aware of the distribution of \meek\ itself. 
+% Although \meek alters the packet size distribution of underlying Tor traffic, 
+% the censor may be aware of the distribution of \meek itself. 
 % Additionally, the persistent connection itself can be an issue.
@@
 
-The \meek\ trace shows a propensity for longer connections.
+The \meek trace shows a propensity for longer connections.
 Over 4.5 hours, there were only 10 connections,
@@
 occurred over just a few TCP/TLS connections.
-60\% of \meek\ connections lasts five minutes or longer,
+60\% of \meek connections lasts five minutes or longer,
 while only 13\% of those of ordinary traffic do.
-\meek\ has essentially no connections lasting less than 24 seconds,
+\meek has essentially no connections lasting less than 24 seconds,
 but such short connections account for over 42\% of the LBL HTTPS connections.
@@
 in any case that's 10 minutes of circumvention achieved,
-after which \meek\ can start a new connection
+after which \meek can start a new connection
 and allow Tor to rebuild its circuits.
@@
 
+% TODO: Since the average numbers of connections are quite different, reviewers may think
+% it is remarkable. We should probably show a large percentage of users in the LBL trace only
+% have 1~2 connections throughout. Therefore a meek user is a needle in the haystack.
+
 $$\diamondsuit$$
@@
 \caption{
-Concurrent users of the \meek\ pluggable transport for Tor.
+Concurrent users of the \meek pluggable transport for Tor.
 }
@@
 \caption{
-Daily unique users of \meek\ with Psiphon (note vertical axis).
+Daily unique users of \meek with Psiphon (note vertical axis).
 The decrease at the end of June
@@
 
-Figure~\ref{fig:clients-tor} shows the average number of concurrent users of \meek\ with Tor
+Figure~\ref{fig:clients-tor} shows the average number of concurrent users of \meek with Tor
 since close to the beginning of development.
@@
 
-% We implemented \meek\ as a pluggable transport~\cite{pt} for Tor.
+% We implemented \meek as a pluggable transport~\cite{pt} for Tor.
 % Although it is possible to use the system with proxies other than Tor,
@@
 
-% \meek\ apart from Tor.
+% \meek apart from Tor.
 % more risk for the proxy operator
@@
 
-\meek\ has a home page at
+\meek has a home page at
 \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.

### 2014-08-01 docs/meek.tex
Typos
Change some "meek" into "\meek"

@@
 appears in Section~\ref{sec:trafficanalysis}.
-The analysis is based on comparing traffic traces of meek
+The analysis is based on comparing traffic traces of \meek
 with samples of HTTPS traffic at an Internet router.
@@
 support for fronting that exists.
-Of the services listed, we have so far deployed meek
+Of the services listed, we have so far deployed \meek
 only on Google App Engine and Amazon CloudFront.
@@
 The horizontal axis is logarithmic.
-meek's connections tend to last longer than those of ordinary HTTPS traffic.
+\meek's connections tend to last longer than those of ordinary HTTPS traffic.
 }
@@
 and allow Tor to rebuild its circuits.
-Future enhancements in meek may even allow reconnecting using the same session ID,
+Future enhancements in \meek may even allow reconnecting using the same session ID,
 so there will be no effect on the client other than a brief delay
@@
 of a single client IP address.
-The LBL trace shows 2,745 unique clients and the meek trace only one.
+The LBL trace shows 2,745 unique clients and the \meek trace only one.
 The dark line is a smoothed average number of connections per client.
-The meek count stays close to~1 throughout, only momentarily
+The \meek count stays close to~1 throughout, only momentarily
 jumping to 0 or~2.
 The average number of connections per user in the LBL trace is 2.61,
-and in the meek trace is 1.002.
+and in the \meek trace is 1.002.
 }
@@
 The number of concurrent connections is another potential distinguisher.
-We have seen how meek tends to use one long-lived connection
+We have seen how \meek tends to use one long-lived connection
 through which it tunnels all its requests.
@@
 The average number of connections in the LBL trace is 2.61,
-while in the meek trace it is almost exactly 1, only briefly
+while in the \meek trace it is almost exactly 1, only briefly
 deviating when one connection ends and another begins.
@@
 % it is remarkable. We should probably show a large percentage of users in the LBL trace only
-% have 1~2 connections throughout. Therefore a meek user is a needle in the haystack.
+% have 1~2 connections throughout. Therefore a \meek user is a needle in the haystack.
 
@@
 
-So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish meek
+So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish \meek
 from other HTTPS traffic.
@@
 
-Development on meek as a Tor pluggable transport~\cite{pt} began in January~2014.
+Development on \meek as a Tor pluggable transport~\cite{pt} began in January~2014.
 Most users who use Tor, use it with Tor Browser~\cite{torbrowser},
@@
 Tor Browser has an easy interface for selecting pluggable transports.
-We made a series experimental releases of Tor Browser featuring meek,
+We made a series experimental releases of Tor Browser featuring \meek,
 releasing the first one on February~18.
@@
 The decrease at the end of June
-was caused by an unblocking event that made meek unnecessary for some users.
+was caused by an unblocking event that made \meek unnecessary for some users.
 }
@@
 
-Psiphon began their deployment of meek in June~2014.
+Psiphon began their deployment of \meek in June~2014.
 Figure~\ref{fig:clients-psiphon3} shows the number
-of unique daily users of meek with Psiphon,
+of unique daily users of \meek with Psiphon,
 estimated through clients' self-reporting of their most recent connection date.
@@
 in the middle of June was not caused by a blocking event,
-but rather an unblocking event that made meek unnecessary for some users.
+but rather an unblocking event that made \meek unnecessary for some users.
 Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
@@
 A longer-term goal is to find a way to fund continued operation
-if meek becomes popular.
+if \meek becomes popular.
 Although some of the systems listed in Section~\ref{sec:survey}
@@
 
-The current implementation of meek strictly serializes
+The current implementation of \meek strictly serializes
 its HTTPS requests and responses,
@@
 
-meek's use of HTTPS is subject to the usual public key infrastructure
+\meek's use of HTTPS is subject to the usual public key infrastructure
 and trust model.
@@
 
-The key idea of meek is domain fronting,
+The key idea of \meek is domain fronting,
 but its HTTP tunneling ability is useful on its own.
@@
 order to hide the remote endpoint of a communication.
-We implemented meek,
+We implemented \meek,
 a pluggable transport for Tor.
@@
 resistance against more subtle and expensive means of traffic analysis.
-We discuss the results of an initial deployment of meek
+We discuss the results of an initial deployment of \meek
 in both Tor and Psiphon.

### 2014-08-01 docs/meek.tex
Anonymized LBL

@@
 \newcommand{\meek}{\texttt{meek}\xspace}
+\newcommand{\lbl}{ResearchLab\xspace}
 \def\urll#1{\begin{NoHyper}\url{#1}\end{NoHyper}}
@@
 is a sanitized 10-minute trace
-from Lawrence Berkeley National Laboratory (LBL),
+from 
+%Lawrence Berkeley National Laboratory (\lbl)
+a research lab (anonymized as \lbl for blind submission),
 comprising data to and from TCP port 443 on any Google server.
 % Mention the non-google if it appears in a figure.
-The LBL trace consists 313~megabytes of packet headers,
+The \lbl trace consists 313~megabytes of packet headers,
 not payloads, destined for TCP port 443 on any Google server.
@@
 \begin{tabular}{r r >{\qquad} r r}
-\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
+\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
 0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
@@
 between ordinary HTTPS connections to Google services
-from the LBL traffic trace,
+from the \lbl traffic trace,
 and \meek running on App Engine, fronted through www.google.com.
@@
 of connection durations in our two traces.
-Considering the LBL trace first,
+Considering the \lbl trace first,
 we see interesting probability concentrations on
@@
 \meek has essentially no connections lasting less than 24 seconds,
-but such short connections account for over 42\% of the LBL HTTPS connections.
+but such short connections account for over 42\% of the \lbl HTTPS connections.
 30\% (3 out of 10) of \meek's connections lasted almost exactly one hour,
@@
 of a single client IP address.
-The LBL trace shows 2,745 unique clients and the \meek trace only one.
+The \lbl trace shows 2,745 unique clients and the \meek trace only one.
 The dark line is a smoothed average number of connections per client.
@@
 jumping to 0 or~2.
-The average number of connections per user in the LBL trace is 2.61,
+The average number of connections per user in the \lbl trace is 2.61,
 and in the \meek trace is 1.002.
@@
 Google per client in both traces.
-The number of connections in the LBL trace is variable,
+The number of connections in the \lbl trace is variable,
 with some hosts briefly spiking up above 50 connections,
 but the average case is very heavily skewed to smaller numbers.
-The average number of connections in the LBL trace is 2.61,
+The average number of connections in the \lbl trace is 2.61,
 while in the \meek trace it is almost exactly 1, only briefly
@@
 % TODO: Since the average numbers of connections are quite different, reviewers may think
-% it is remarkable. We should probably show a large percentage of users in the LBL trace only
+% it is remarkable. We should probably show a large percentage of users in the \lbl trace only
 % have 1~2 connections throughout. Therefore a \meek user is a needle in the haystack.

### 2014-08-01 docs/concurrent.R

@@ -56,7 +56,7 @@ numconns <- rbind(numconns, cbind(calc.numconns(x[!x$google & x$source=="lbl", ]
 numconns <- rbind(numconns, cbind(calc.numconns(x[x$google & x$source=="tbb", ]), google=T, source="tbb"))
 
 numconns <- cbind(numconns, alpha=ifelse(numconns$source=="lbl", 0.15, 1.0))
-numconns <- cbind(numconns, label=ifelse(numconns$source=="lbl", "LBL Google HTTPS", "meek on App Engine"))
+numconns <- cbind(numconns, label=ifelse(numconns$source=="lbl", "ResearchLab Google HTTPS", "meek on App Engine"))
 
 calc.breaks <- function(v) {
 	if (v[2] - v[1] < 10) {

### 2014-08-01 docs/datalen.R

@@ -23,7 +23,7 @@ t <- table(x[x$google & x$source=="tbb", ]$datalen)
 
 binwidth = 5
 
-x <- cbind(x, label=ifelse(x$source=="lbl", "LBL Google HTTPS", "meek on App Engine"))
+x <- cbind(x, label=ifelse(x$source=="lbl", "ResearchLab Google HTTPS", "meek on App Engine"))
 
 p <- ggplot(x[x$google, ], aes(datalen))
 p <- p + scale_y_continuous(labels = function(y) binwidth * y)

### 2014-08-01 docs/flowduration.R

@@ -38,7 +38,7 @@ p <- p + xlab("Duration (seconds)") + ylab("Fraction of connections")
 p <- p + theme(axis.text=element_text(size=7), axis.title=element_text(size=8))
 p <- p + theme(panel.grid.minor.x=element_blank())
 p <- p + theme(legend.position="none")
-p <- p + annotate("text", x=220, y=0.82, label="LBL Google HTTPS", hjust=1, size=2.5)
+p <- p + annotate("text", x=220, y=0.82, label="ResearchLab Google HTTPS", hjust=1, size=2.5)
 p <- p + annotate("text", x=800, y=0.44, label="meek on App Engine", hjust=1, size=2.5)
 p <- p + scale_colour_brewer(palette="Set1")
 ggsave("flowduration.pdf", width=4, height=3, units="in")

### 2014-08-01 docs/meek.tex
Escape spaces after "\meek".
Just like 24146bba0601b5e6a7393d22985ea4a50deeb0fa.

@@
 a pluggable transport for Tor.
-\meek combines fronting with a proxy server that encodes a TCP stream
+\meek\ combines fronting with a proxy server that encodes a TCP stream
 as a sequence of HTTP requests and responses.
-The \meek server's external interface is that of an ordinary web server.
+The \meek\ server's external interface is that of an ordinary web server.
 Domain fronting enables a client to reach the server.
@@
 implemented as pluggable transport~\cite{pt} for Tor.
-\meek combines fronting with an HTTP-based tunneling proxy:
+\meek\ combines fronting with an HTTP-based tunneling proxy:
 upstream data are transformed into a sequence of HTTP requests,
@@
 
-\meek has been built into an alpha version of Tor Browser,
+\meek\ has been built into an alpha version of Tor Browser,
 and has a small number of users.
@@
 In addition to the Tor pluggable transport,
-systems based on \meek are now used by other circumvention systems
+systems based on \meek\ are now used by other circumvention systems
 including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.
 
-% \meek is designed to have features attractive in a circumvention transport.
+% \meek\ is designed to have features attractive in a circumvention transport.
 % It is easy to use, not requiring the configuration of any bridge addresses.
@@
 appears in Section~\ref{sec:trafficanalysis}.
-The analysis is based on comparing traffic traces of \meek
+The analysis is based on comparing traffic traces of \meek\
 with samples of HTTPS traffic at an Internet router.
@@
 
-GoAgent~\cite{goagent} is a direct inspiration for \meek in its use of
+GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of
 domain fronting with App Engine.
@@
 The components of the system are shown in Figure~\ref{fig:architecture}.
-The parts that are new in \meek
+The parts that are new in \meek\
 are the programs \meekclient and \meekserver,
@@
 
-When \meek is used with Google App Engine, one other component is needed:
+When \meek\ is used with Google App Engine, one other component is needed:
 a small ``reflector'' web app that simply copies any request
@@
           &  $+$29 & Tor TLS record \\
-$\approx$ & $+$400 & \meek HTTP header \\
-$\approx$ &  $+$50 & \meek TLS record \\
+$\approx$ & $+$400 & \meek\ HTTP header \\
+$\approx$ &  $+$50 & \meek\ TLS record \\
 \hline
@@
 which are browsers, are different from Go's TLS; the browsers are also unlike each other.
-A censor could block an uncamouflaged \meek using Go's fingerprint,
+A censor could block an uncamouflaged \meek\ using Go's fingerprint,
 if it considered the collateral damage resulting from blocking other Go programs to be slight enough.
@@
 support for fronting that exists.
-Of the services listed, we have so far deployed \meek
+Of the services listed, we have so far deployed \meek\
 only on Google App Engine and Amazon CloudFront.
@@
 % its terms of service~\cite{cloudflare-terms}
-% seem to prohibit the kind of tunneled proxying that \meek does:
+% seem to prohibit the kind of tunneled proxying that \meek\ does:
 % \begin{quote}
@@
 
-One of our goals in developing \meek is to force
+One of our goals in developing \meek\ is to force
 the censor to use relatively more expensive statistical classifiers
 to effect blocking---generally, to increase the cost of censorship.
-We believe \meek is resistant to the ``easy''
+We believe \meek\ is resistant to the ``easy''
 forms of blocking, namely IP address and DNS blocking,
@@
 of automatically browsing the home pages
-of the top 500 Alexa web sites using \meek in Tor Browser,
+of the top 500 Alexa web sites using \meek\ in Tor Browser,
 with the browser camouflage described in Section~\ref{sec:browserextension},
 and Google App Engine as the intermediate web service.
-The \meek trace is 687~megabytes in all
+The \meek\ trace is 687~megabytes in all
 and covers about 4.5 hours of network activity.
@@
 \begin{tabular}{r r >{\qquad} r r}
-\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
+\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
 0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
@@
 from the \lbl traffic trace,
-and \meek running on App Engine, fronted through www.google.com.
+and \meek\ running on App Engine, fronted through www.google.com.
 % The histogram's bin width is 5~bytes.
@@
 % http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
-Conspicuous in the \meek trace are a small number of
+Conspicuous in the \meek\ trace are a small number of
 frequent packet sizes,
@@
 occurred over just a few TCP/TLS connections.
-60\% of \meek connections lasts five minutes or longer,
+60\% of \meek\ connections lasts five minutes or longer,
 while only 13\% of those of ordinary traffic do.
-\meek has essentially no connections lasting less than 24 seconds,
+\meek\ has essentially no connections lasting less than 24 seconds,
 but such short connections account for over 42\% of the \lbl HTTPS connections.
@@
 in any case that's 10 minutes of circumvention achieved,
-after which \meek can start a new connection
+after which \meek\ can start a new connection
 and allow Tor to rebuild its circuits.
-Future enhancements in \meek may even allow reconnecting using the same session ID,
+Future enhancements in \meek\ may even allow reconnecting using the same session ID,
 so there will be no effect on the client other than a brief delay
@@
 of a single client IP address.
-The \lbl trace shows 2,745 unique clients and the \meek trace only one.
+The \lbl trace shows 2,745 unique clients and the \meek\ trace only one.
 The dark line is a smoothed average number of connections per client.
-The \meek count stays close to~1 throughout, only momentarily
+The \meek\ count stays close to~1 throughout, only momentarily
 jumping to 0 or~2.
 The average number of connections per user in the \lbl trace is 2.61,
-and in the \meek trace is 1.002.
+and in the \meek\ trace is 1.002.
 }
@@
 The number of concurrent connections is another potential distinguisher.
-We have seen how \meek tends to use one long-lived connection
+We have seen how \meek\ tends to use one long-lived connection
 through which it tunnels all its requests.
@@
 The average number of connections in the \lbl trace is 2.61,
-while in the \meek trace it is almost exactly 1, only briefly
+while in the \meek\ trace it is almost exactly 1, only briefly
 deviating when one connection ends and another begins.
@@
 % it is remarkable. We should probably show a large percentage of users in the \lbl trace only
-% have 1~2 connections throughout. Therefore a \meek user is a needle in the haystack.
+% have 1~2 connections throughout. Therefore a \meek\ user is a needle in the haystack.
 
@@
 
-So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish \meek
+So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish \meek\
 from other HTTPS traffic.
@@
 
-Development on \meek as a Tor pluggable transport~\cite{pt} began in January~2014.
+Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
 Most users who use Tor, use it with Tor Browser~\cite{torbrowser},
@@
 \caption{
-Concurrent users of the \meek pluggable transport for Tor.
+Concurrent users of the \meek\ pluggable transport for Tor.
 }
@@
 \caption{
-Daily unique users of \meek with Psiphon (note vertical axis).
+Daily unique users of \meek\ with Psiphon (note vertical axis).
 The decrease at the end of June
-was caused by an unblocking event that made \meek unnecessary for some users.
+was caused by an unblocking event that made \meek\ unnecessary for some users.
 }
@@
 
-Figure~\ref{fig:clients-tor} shows the average number of concurrent users of \meek with Tor
+Figure~\ref{fig:clients-tor} shows the average number of concurrent users of \meek\ with Tor
 since close to the beginning of development.
@@
 
-Psiphon began their deployment of \meek in June~2014.
+Psiphon began their deployment of \meek\ in June~2014.
 Figure~\ref{fig:clients-psiphon3} shows the number
-of unique daily users of \meek with Psiphon,
+of unique daily users of \meek\ with Psiphon,
 estimated through clients' self-reporting of their most recent connection date.
@@
 in the middle of June was not caused by a blocking event,
-but rather an unblocking event that made \meek unnecessary for some users.
+but rather an unblocking event that made \meek\ unnecessary for some users.
 Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
@@
 A longer-term goal is to find a way to fund continued operation
-if \meek becomes popular.
+if \meek\ becomes popular.
 Although some of the systems listed in Section~\ref{sec:survey}
@@
 
-% We implemented \meek as a pluggable transport~\cite{pt} for Tor.
+% We implemented \meek\ as a pluggable transport~\cite{pt} for Tor.
 % Although it is possible to use the system with proxies other than Tor,
@@
 
-The current implementation of \meek strictly serializes
+The current implementation of \meek\ strictly serializes
 its HTTPS requests and responses,
@@
 
-The key idea of \meek is domain fronting,
+The key idea of \meek\ is domain fronting,
 but its HTTP tunneling ability is useful on its own.
@@
 resistance against more subtle and expensive means of traffic analysis.
-We discuss the results of an initial deployment of \meek
+We discuss the results of an initial deployment of \meek\
 in both Tor and Psiphon.
 
-\meek has a home page at
+\meek\ has a home page at
 \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.

### 2014-08-01 docs/meek.tex
Blank out the home page and source code links.
Blind ICSI.

@@
 According to our communication with
-a representative of the International Computer Science Institute's
-certificate notary~\cite{icsi-notary},
-which observes on the order of 50~million TLS connections daily,
+a representative of
+[a blinded organization observing many TLS connections],
+% ANON
+% the International Computer Science Institute's
+% certificate notary~\cite{icsi-notary},
+% which observes on the order of 50~million TLS connections daily,
 83.5\% of connections used SNI in June~2014.
@@
 
-\meek\ has a home page at
-\url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
-Our source code is in the Git repository at
-\url{https://git.torproject.org/pluggable-transports/meek.git}.
-All our programs are free software.
+% ANON
+% \meek\ has a home page at
+% \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
+% Our source code is in the Git repository at
+% \url{https://git.torproject.org/pluggable-transports/meek.git}.
+% All our programs are free software.
+
 % As of version 0.9 (June~19, 2014), the source code consists of

### 2014-08-01 docs/meek.tex
Blind references to Lantern and Psiphon.

@@
 \meek, or something based on it,
-has been adopted by other circumvention systems including Lantern and Psiphon.
+has been adopted by other circumvention systems including
+[blinded for anonymous submission].
+% ANON
+% Lantern and Psiphon.
 
@@
 In addition to the Tor pluggable transport,
-systems based on \meek\ are now used by other circumvention systems
-including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.
+systems based on \meek\ are now used by other circumvention systems including
+[blinded for anonymous submission].
+% ANON
+% including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.
 
@@
 with encryption and traffic obfuscation between client and server.
-Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
+% ANON
+% Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
 Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
 proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
-Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.
+% ANON
+% Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.
 
@@
 up to a maximum of 5~s.
-The other technique,
-implemented in Psiphon's version of \meek,
+% ANON
+% The other technique,
+% implemented in Psiphon's version of \meek,
+The other technique
 uses long-lived persistent HTTP connections.
@@
 Bulk uploads and downloads tend to have less overhead, bunching many cells at once.
-Persistent HTTP connections as used by Psiphon reduce overhead further,
+Persistent HTTP connections, when they are possible, reduce overhead further,
+% ANON
+% Persistent HTTP connections as used by Psiphon reduce overhead further,
 because only one HTTP header is needed for a large number of transmissions.
@@
 Section~\ref{sec:discussion} describes ways to improve
-performance with high latencies;
-Psiphon's use of persistent connections as described in this section is one of them.
+% ANON
+% performance with high latencies;
+% Psiphon's use of persistent connections as described in this section is one of them.
 
@@
 On a traditional desktop PC, using a browser is probably the right choice.
-When Psiphon ported \meekclient to Android,
+When
+[blinded circumcention tool]
+% ANON
+% Psiphon
+ported \meekclient to Android,
 they didn't use a browser as camouflage,
@@
 releasing the first one on February~18.
-On April~18 we made the first release featuring the browser camouflage
-that is the subject of Section~\ref{sec:browserextension}.
-We announced our releases on Tor development mailing lists,
-whence they were picked up by Tor Weekly News on the Tor blog.
-Our code was merged by the Tor Browser maintainers
-in June and is scheduled for an alpha release,
-still pending as of this writing.
+[Some details of deployment are omitted for anonymous submission.]
+% ANON
+% On April~18 we made the first release featuring the browser camouflage
+% that is the subject of Section~\ref{sec:browserextension}.
+% We announced our releases on Tor development mailing lists,
+% whence they were picked up by Tor Weekly News on the Tor blog.
+% Our code was merged by the Tor Browser maintainers
+% in June and is scheduled for an alpha release,
+% still pending as of this writing.
 
@@
 \caption{
-Daily unique users of \meek\ with Psiphon (note vertical axis).
+Daily unique users of \meek\ with
+[blinded circumvention tool]
+% ANON
+% Psiphon
+(note vertical axis).
 The decrease at the end of June
@@
 
-Psiphon began their deployment of \meek\ in June~2014.
+[Blinded circumvention tool]
+% ANON
+% Psiphon
+began their deployment of \meek\ in June~2014.
 Figure~\ref{fig:clients-psiphon3} shows the number
-of unique daily users of \meek\ with Psiphon,
+of unique daily users of \meek%
+,
+% ANON
+% with Psiphon,
 estimated through clients' self-reporting of their most recent connection date.
-The Psiphon developers tell us that the drop that occurs
+The developers tell us that the drop that occurs
 in the middle of June was not caused by a blocking event,
@@
 are not directly comparable because they count slightly different things,
-it is clear that meek-with-Psiphon, with its thousands of daily users,
+it is clear that meek-with-%
+[blinded circumvention tool],
+% ANON
+% Psiphon,
+with its thousands of daily users,
 is much more widely used than meek-with-Tor, which has not yet seen a formal release,
@@
 resistance against more subtle and expensive means of traffic analysis.
-We discuss the results of an initial deployment of \meek\
-in both Tor and Psiphon.
+We discuss the results of an initial deployment.
+% ANON
+% in both Tor and Psiphon.
 

### 2014-08-01 docs/concurrent.R
Fix alpha in concurrent graph.

@@ -79,7 +79,7 @@ p <- ggplot(data=data)
 p <- p + scale_y_continuous(breaks=calc.breaks)
 p <- p + xlab("Time (seconds)") + ylab("Concurrent HTTPS connections per client")
 p <- p + facet_wrap(~ label, ncol=1, scales="free")
-p <- p + geom_step(aes(ts, numconns, group=orig_h, alpha=data$alpha, colour="coral"))
+p <- p + geom_step(aes(ts, numconns, group=orig_h, alpha=alpha, colour="coral"))
 p <- p + geom_smooth(aes(ts, cumsum(dconns)/scale, weight=weight), size=0.4, colour="black", se=FALSE)
 p <- p + theme(axis.text=element_text(size=7), axis.title=element_text(size=8))
 p <- p + theme(legend.position="none")

### 2014-08-01 docs/concurrent.R
Reorder plot facets.
They got reversed when the labels were anonymized because it put them in
alphabetical order.

@@ -57,6 +57,7 @@ numconns <- rbind(numconns, cbind(calc.numconns(x[x$google & x$source=="tbb", ])
 
 numconns <- cbind(numconns, alpha=ifelse(numconns$source=="lbl", 0.15, 1.0))
 numconns <- cbind(numconns, label=ifelse(numconns$source=="lbl", "ResearchLab Google HTTPS", "meek on App Engine"))
+numconns$label <- factor(numconns$label, levels=c("ResearchLab Google HTTPS", "meek on App Engine"))
 
 calc.breaks <- function(v) {
 	if (v[2] - v[1] < 10) {

### 2014-08-01 docs/datalen.R

@@ -24,6 +24,7 @@ t <- table(x[x$google & x$source=="tbb", ]$datalen)
 binwidth = 5
 
 x <- cbind(x, label=ifelse(x$source=="lbl", "ResearchLab Google HTTPS", "meek on App Engine"))
+x$label <- factor(x$label, levels=c("ResearchLab Google HTTPS", "meek on App Engine"))
 
 p <- ggplot(x[x$google, ], aes(datalen))
 p <- p + scale_y_continuous(labels = function(y) binwidth * y)

### 2014-08-01 docs/concurrent.R
Print out number of clients with few connections in concurrent.R.

@@ -75,6 +75,14 @@ data <- x[x$google & x$source=="tbb", ]
 length(unique(data$id.orig_h))
 sum(data$duration)/(max(data$ts + data$duration) - min(data$ts))/length(unique(data$id.orig_h))
 
+# Number of client IPs.
+numhosts <- length(unique(numconns[numconns$google & numconns$source=="lbl", ]$orig_h))
+# Number of client IPs that never had more than 2 connections.
+numfew <- numhosts - length(unique(numconns[numconns$google & numconns$source=="lbl" & numconns$numconns>2, ]$orig_h))
+numfew
+numhosts
+numfew / numhosts
+
 data <- numconns[numconns$google, ]
 p <- ggplot(data=data)
 p <- p + scale_y_continuous(breaks=calc.breaks)

### 2014-08-01 docs/meek.tex
Missing word.
Put "meek" in normal type.
Say that 28% of clients had 2 concurrent connections or fewer.

@@
 \newcommand{\meekserver}{\mbox{meek-server}\xspace}
-\newcommand{\meek}{\texttt{meek}\xspace}
+\newcommand{\meek}{meek\xspace}
 \newcommand{\lbl}{ResearchLab\xspace}
@@
 % [1] 1.002148
+% [1] 772
+% [1] 2745
+% [1] 0.2812386
 
@@
 The average number of connections in the \lbl trace is 2.61,
-while in the \meek\ trace it is almost exactly 1, only briefly
+with 28\% of clients never having more than 2 concurrent connections.
+In the \meek trace the average is almost exactly 1, only briefly
 deviating when one connection ends and another begins.
 We conclude that having a small number of concurrent connections is unremarkable.
-
-% TODO: Since the average numbers of connections are quite different, reviewers may think
-% it is remarkable. We should probably show a large percentage of users in the \lbl trace only
-% have 1~2 connections throughout. Therefore a \meek\ user is a needle in the haystack.
 
@@
 Tor Browser has an easy interface for selecting pluggable transports.
-We made a series experimental releases of Tor Browser featuring \meek,
+We made a series of experimental releases of Tor Browser featuring \meek,
 releasing the first one on February~18.

### 2014-08-02 docs/meek.tex
Typos

@@
 If the connection is successful, the server may be blacklisted.
-Active probing is a precise means of identifying whether a server as belongs to a circumvention system,
+Active probing is a precise means of identifying whether a server belongs to a circumvention system,
 even when a protocol is hard to classify on the wire.
@@
 with its thousands of daily users,
-is much more widely used than meek-with-Tor, which has not yet seen a formal release,
+is much more widely used than meek-with-Tor, which has not yet seen a formal release.
 

### 2014-08-02 docs/meek.tex
Another top-to-bottom proofreading.

@@
 but actually with a forbidden domain.
-The key idea is the use of different domain names at different communication layers.
+The key idea is the use of different domain names at different layers of communication.
 One domain is used on the ``outside'' of an HTTPS request---in the DNS request and
 TLS Server Name Indication---while another is used
-on the ``inside''---the HTTP Host header, invisible to the
+on the ``inside''---in the HTTP Host header, invisible to the
 censor under HTTPS encryption.
@@
 like content delivery networks and Google,
-that enable fronting by ignoring the outside of an HTTPS request
-and dispatching it internally according to the Host header.
-The effect of fronting is that a user may communicate with one domain,
-even one forbidden by the censor,
-while appearing to communicate with another.
-If a censor is unable otherwise to distinguish fronted and non-fronted traffic,
-then blocking circumvention traffic means blocking the whole web service,
+that support fronting because they ignore the outside of an HTTPS request
+and dispatch it internally according to the Host header.
+If a censor is unable to distinguish fronted circumvention traffic and non-fronted ordinary traffic,
+then blocking fronted traffic means blocking an entire web service,
 with resulting expensive collateral damage.
@@
 a pluggable transport for Tor.
-\meek\ combines fronting with a proxy server that encodes a TCP stream
-as a sequence of HTTP requests and responses.
+\meek\ combines fronting with an HTTP-based tunneling proxy.
 The \meek\ server's external interface is that of an ordinary web server.
-Domain fronting enables a client to reach the server.
-The server receives requests, decodes them, and feeds their payloads into a Tor relay,
-and returns downstream data in the HTTP response.
+Domain fronting enables a client to reach the server, which is presumed blocked by the censor.
+The server receives HTTP requests, decodes them, and feeds their payloads into a Tor relay,
+returning downstream data in the HTTP response.
 A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
@@
 We describe what we have done to disguise other traffic ``tells'' in \meek,
-such as using a real web browser to make HTTPS requests
-for a believable TLS fingerprint.
-We argue that these measures increase the censor's effort
+such as using a real web browser as a tool for making fronted HTTPS requests,
+in order to disguise meek's TLS fingerprint.
+We argue that these measures, combined with domain fronting, increase the censor's effort
 beyond simple one-shot blocking techniques such as IP address blocking, and into
@@
 One way to win against censorship is to entangle circumvention traffic
-with ordinary Internet traffic in a way that either both must be blocked together,
+with ordinary Internet traffic in a way that both must be blocked together,
 or not at all.
-If the ordinary traffic is important enough,
+If the ordinary traffic is valuable enough,
 above the censor's tolerance for overblocking,
@@
 to a general-purpose proxy,
-so that circumvention is not limited to HTTPS, nor to the domains of any specific web service.
+so that circumvention is not limited only to HTTPS, nor to the domains of any specific web service.
 
@@
 in the DNS query,
-the TLS Server Name Indication (SNI) extension~\cite[Section~3]{rfc6066},
-and the HTTP Host header~\cite[Section~14.23]{rfc2616}.
+in the TLS Server Name Indication (SNI) extension~\cite[Section~3]{rfc6066},
+and in the HTTP Host header~\cite[Section~14.23]{rfc2616}.
 Usually, the same domain name appears in all three places.
@@
 while the HTTP Host header,
-which is hidden from censor by HTTPS encryption,
+which is hidden from the censor by HTTPS encryption,
 carries another (the actual destination).
@@
 
-Neither the DNS request nor the SNI can be blocked without
+The censor may block neither the DNS request nor the SNI without
 collaterally blocking the front domain.
@@
 
-A Wget command shows domain fronting in action
+This Wget command shows domain fronting in action
 on Google's infrastructure.
@@
 on receiving a request for a resource not already cached,
-forwards the request to the domain in the Host header
+forwards the request to the domain found in the Host header
 (the ``origin server'').
@@
 can host a simple ``reflector'' application that emulates
-an origin-pull CDN, simply forwarding every request to an origin server.
-In both cases, the intermediate web service does not forward requests just anywhere---it
+an origin-pull CDN, simply forwarding every request to another server.
+In both cases, the intermediate web service does not forward requests to just anywhere---it
 has to be to the domain of a customer.
 In order to run a fronting backend,
-one has to create an account and pay for bandwidth.
+one generally has to create an account with the web service and pay for bandwidth.
 
 A variation on fronting is ``domainless'' fronting,
-in which there is no DNS request and no SNI extension.
+in which there is no DNS request and no SNI.
 It looks to the censor
@@
 or using a web client that doesn't support SNI.
-Domainless fronting can be useful when there is no front domain
-known to have sufficiently high collateral damage.
-The censor is faced with the choice of blocking an entire IP address,
-blocking requests without SNI,
-or finding some other, presumably more expensive, test to try to distinguish
+Domainless fronting can be useful when there is no known front domain
+with sufficiently high collateral damage.
+The censor is faced with the choice of blocking an entire IP address, not only a domain;
+blocking requests without SNI;
+or trying to find some other, presumably more expensive, test to distinguish
 circumvention traffic.
@@
 into the Tor network.
-Downstream data received from Tor
-are returned to the client as HTTP responses.
+Downstream data received by the server from Tor
+are returned to the client within HTTP responses.
 \meek's architecture appears in Figure~\ref{fig:architecture}.
@@
 
-\meek\ has been built into an alpha version of Tor Browser,
+\meek\ has been built into an experimental release of Tor Browser,
 and has a small number of users.
-Our deployment so far uses Google App Engine and Amazon CloudFront.
+Our deployment so far uses Google App Engine and Amazon CloudFront
+as intermediate web service backends.
 % with the hidden actual domain \urll{meek-reflect.appspot.com}
 % hidden by the front \urll{www.google.com}.
-Section~\ref{sec:deployment} discusses other fronting-capable services
-and deployment scenarios.
+Section~\ref{sec:survey} names other fronting-capable services
+and Section~\ref{sec:discussion} describes other possible deployments.
 In addition to the Tor pluggable transport,
@@
 match those of a browser as closely as possible.
-One of our goals is to force the censor
+Our goal is to force the censor
 to employ more sophisticated, expensive, and error-prone statistical tests
 to classify traffic as allowed or prohibited,
-rather than simple domain blacklists or deep packet inspection;
-to force the practice of censorship to exist in a world
+rather than domain blacklists or deep packet inspection---to
+force the practice of censorship to exist in a world
 not of simple packet filters,
 but of probabilities and false positives.
-A preliminary analysis of \meek's resistance to detection
-based on traffic characteristics like packet length distribution
+A preliminary analysis of \meek's resistance to traffic analysis
 appears in Section~\ref{sec:trafficanalysis}.
 The analysis is based on comparing traffic traces of \meek\
-with samples of HTTPS traffic at an Internet router.
+to samples of HTTPS traffic at a network router.
 
@@
 GoAgent and flash proxy are the systems that most directly
-inspire this work.
+inspire ours.
 
@@
 proxy servers to see how they respond.
-If the connection is successful, the server may be blacklisted.
+Then a connection is successful, the server can be blacklisted.
 Active probing is a precise means of identifying whether a server belongs to a circumvention system,
-even when a protocol is hard to classify on the wire.
+even when a protocol is hard to detect on the wire.
 Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
 Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
-by issuing scans that follow up observed client connections, to discover
+by issuing scans that follow up on observed client connections, to discover
 whether a server speaks the Tor protocol.
@@
 Following the first strategy are the so-called ``look-like-nothing'' transports whose
-payloads are indistinguishable from a uniformly random byte stream,
-good examples of which are
+payloads are indistinguishable from a uniformly random byte stream.
+Good examples of look-like-nothing transports are
 obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
@@
 The other strategy against DPI is the steganographic one: look like
-something the censor doesn't block.
+something the censor does not block.
 fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings
 that match a given regular expression,
-for example a regular-expression approximation of HTTP,
-in order to match a firewall's whitelist.
+for example a regular-expression approximation of HTTP.
 StegoTorus~\cite{stegotorus}
@@
 The other grand challenge of proxy-based circumvention is address-based blocking.
-Tor has long faced the problem of the blocking of its entry relays,
+Tor has long faced the problem of the blocking of its relays,
 the addresses of which appear in a public directory.
@@
 always returns the same set of bridges to the same requester,
-preventing enumeration by simple repeated querying.
+preventing enumeration by simple repeated queries.
 BridgeDB is also capable of distributing the addresses
@@
 that must remain unblocked,
-and the client must carry on a believable UDP conversation with the dummy host
-(the authors suggest a VoIP call).
+and the client must carry on a believable UDP conversation with the dummy host---a
+VoIP call, for example.
 
@@
 conscripting web users as temporary proxies.
-Each proxy lasts only as long as a
+Each JavaScript-based proxy lasts only as long as a
 user stays on a web page, so the pool of proxies is constantly changing.
@@
 In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
-is hidden in the path component of the URL.
-For example, in an example S3 URL
+is hidden in the path component of a URL.
+For example, in the S3 URL
 \urll{https://s3.amazonaws.com/bucketname/filename},
-the censor only gets to ``see'' the generic domain part, \urll{s3.amazonaws.com}.
-The path component \urll{/bucketname/filename},
-which would reveal that CloudTransport is being used,
+the censor only gets to ``see'' the generic domain part, ``\urll{s3.amazonaws.com}''.
+The path component ``\urll{/bucketname/filename}'',
+which would reveal the use of CloudTransport,
 cannot be used for blocking because it is encrypted inside HTTPS.
@@
 App Engine kills web requests (and their associated socket connections)
-that take longer than 60~seconds,
+when they take longer than 60~seconds,
 so users must reconnect at least that often.
@@
 
-The censor controls a network and the into and within it.
+The censor controls a network and the links into and within it.
 The censor is able to inspect traffic flowing across all links under its control
@@
 are the programs \meekclient and \meekserver,
-which are the pluggable-transports~\cite{pt} interface with Tor.
+which are \meek's interface with Tor.
 
 \meekclient is essentially a web client that knows how to front HTTPS requests.
-When \meekclient receives outgoing data from a client Tor process, it bundles them up into a POST request
+When \meekclient receives an outgoing chunk of data from a client Tor process, it bundles it up into a POST request
 and fronts the request through the web service,
-which in turn forwards the request to \meekserver on the bridge.
-If the response contains any HTTP body, \meekclient decodes it and returns it back to Tor.
+which in turn forwards it to \meekserver on the bridge.
+If the response returned by \meekserver contains any HTTP body,
+\meekclient decodes the body and sends it back to the Tor client.
 \meekclient takes pains to make its TLS fingerprint
@@
 When \meekserver receives a request, it extracts the body and feeds it into
-a local Tor process running as a bridge.
-If there are any data pending to be sent back to the client from Tor,
+the Tor network.
+If there is anything pending to be sent back to the client from Tor,
 \meekserver includes it in the body of the HTTP response.
 \meekserver also handles session management:
-because there may be many clients using the service at once,
-the server must determine which client session each incoming request belongs to.
-% It does this by means of an X-Session-Id header,
-% described in this section.
+keeping track of which requests correspond to which active Tor connection.
 
@@
 
-The main technical challenge of the protocol is splitting up a TCP stream
+The main technical challenge of the protocol is splitting a TCP stream up
 into a sequence of HTTP requests and responses.
-The underlying TCP stream is broken into chunks so that
-it can be sent over HTTP.
 The body of each HTTP request and HTTP response carries
@@
 are correctly reassembled at the other end,
-in order and without gaps and duplicates.
+in order and without gaps or duplicates.
 \meek\ takes a naive approach: requests and responses are strictly serialized.
@@
 of bodies in the order they arrive.
-Doing it this way is simple and guarantees correctness,
+Handling stream reconstruction this way is simple and guarantees correctness,
 but has performance drawbacks because there is a full round-trip
@@
 \meekserver must handle many clients at once,
-and therefore maintains many open connections to the local Tor process,
+and therefore maintains many open connections to a local Tor process,
 one for each active client.
@@
 the source IP of the requests is that of the intermediate web service,
-not that of the client;
+not of the actual client;
 and a logical stream is chopped into multiple independent HTTP requests,
@@
 Instead, each client generates a random 256-bit session ID for each new Tor stream,
-which it sends with each of its requests in a special
+which it sends with its requests in a special
 X-Session-Id HTTP header.
@@
 if it has nothing else to send,
-simply to give the server an opportunity to reply.
+simply to give the server an opportunity to send something back.
 The polling interval starts short (100~ms) and grows exponentially
@@
 The other technique
-uses long-lived persistent HTTP connections.
+uses streaming HTTP responses over persistent HTTP connections.
 When the server sends a response, it keeps the connection open,
@@
 When the server receives a new request from the same client,
-it closes any response stream it has open to the client and starts a new one.
+it closes any response stream it has open to that client and starts a new one.
 This second technique is especially beneficial for bulk downloads,
@@
 % (in Tor version~0.2.4.22 using a GCM ciphersuite).
-This 543-byte record is what is received by \meekclient,
+This 543-byte record is received by \meekclient,
 which adds an HTTP header whose length is about 400 bytes
 (varying slightly depending on the length of the Host field).
-The HTTP request goes into its own TLS Application Data record,
-which adds about 50~bytes
-(depending on how much padding is used by the ciphersuite selected by the web service).
+The HTTP request goes into its own TLS Application Data record when it becomes HTTPS,
+adding about 50~bytes
+depending on how much padding is used by the ciphersuite in use.
 
@@
 The total overhead varies according to the length
-of the Host field and the specifics of the intermediate web service's TLS,
+of the Host field in the header and the specifics of the intermediate web service's TLS configuration,
 but is somewhere in the neighborhood of $(543+450)/543-1\approx83$\%.
@@
 Bulk uploads and downloads tend to have less overhead, bunching many cells at once.
-Persistent HTTP connections, when they are possible, reduce overhead further,
+Streaming HTTP responses, when they are possible, reduce overhead further,
 % ANON
@@
 Empty polling requests also use bandwidth,
-but they are sent only when the connection is idle
+but they are sent only when the connection is idle,
 so they don't affect upload or download speed.
@@
 Section~\ref{sec:discussion} describes ways to improve
+performance with high latencies.
 % ANON
@@
 that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
-based on the handshake.
+based on their handshake.
 (We are only concerned with fingerprinting the client,
@@
 Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
-which are browsers, are different from Go's TLS; the browsers are also unlike each other.
-A censor could block an uncamouflaged \meek\ using Go's fingerprint,
+shows two browsers which have TLS fingerprints different from Go's
+and different from each other's.
+A censor could block an uncamouflaged \meek\ using Go's TLS fingerprint,
 if it considered the collateral damage resulting from blocking other Go programs to be slight enough.
@@
 on the client's computer.
-The local Tor process starts a helper process that starts both \meekclient
+The local Tor process runs a helper process that starts both \meekclient
 and the headless browser,
@@
 The user's browser proxies through Tor;
-Tor proxies through \meekclient,
+Tor proxies through \meekclient;
 and \meekclient proxies through the headless browser.
@@
 It should be emphasized that the URLs requested by the headless browser extension
-have no relation to the URLs the user actually browses;
+have no relation to the URLs the user browses;
 the extension only ever makes requests to the front domain.
@@
 for instance
-how often it resolves DNS names,
+how often it resolves DNS,
 its connection reuse,
@@
 saving space in distribution packages
-and sparing the user from having to separately configure a browser to run the extension.
+and sparing the user the chore of having to separately configure a browser to run the extension.
 In Tor Browser,
@@
 When
-[blinded circumcention tool]
+[blinded circumvention tool]
 % ANON
@@
 will front only for their own customers,
-so new each deployment typically means becoming a customer and an investment of time and money.
+so new each deployment typically requires an investment of time and money.
 
@@
 however it is not obvious which one is best to use as a front.
-The front domain needs to be popular
+The front domain needs to be a popular one
 (causing high collateral damage if blocked),
-or else the censor may simply block the domain entirely.
-It is doubly bad when a domain is blocked, because not only is circumvention foiled,
+or the censor may simply block it entirely.
+It is doubly bad when a domain is blocked in this way,
+because not only is circumvention foiled,
 but some unsuspecting third party has just had their web site blocked.
@@
 all of which can front for each other.
-There are other fronting domain names, like \urll{ajax.aspnetcdn.com},
+There are other front domain names, like \urll{ajax.aspnetcdn.com},
 that may offer high collateral damage.
@@
 Fastly~\cite{fastly} is a CDN.
-It is unique among the the services we tested in that
-it is the only one that appears to enforce the SNI:
+It is the only one of the services we tested in that
+that appears to enforce SNI:
 if the SNI and Host do not match,
@@
 and active probing.
-We hope that the censor will have to resort to measuring
+We hope to force the censor to resort to measuring
 more subtle features of the communication.
@@
 %Lawrence Berkeley National Laboratory (\lbl)
-a research lab (anonymized as \lbl for blind submission),
+a research lab [blinded as \lbl for anonymous submission],
 comprising data to and from TCP port 443 on any Google server.
@@
 Figure~\ref{fig:datalen}
-compares the packet length distributions of both sample traffic traces.
+compares the packet length distributions of the sample traffic traces.
 In both cases, about 38\% of packets have an empty payload, mostly ACKs.
@@
 Conspicuous in the \meek\ trace are a small number of
-frequent packet sizes,
-and the lack of a cluster of small payload lengths of around 50 bytes.
-Both of these characteristics are probably artifacts
+discrete frequent packet sizes,
+and the lack of a cluster of short payloads of around 50 bytes.
+Both of these characteristics are probably reflections
 of Tor's fixed cell size and the nearly fixed-size HTTP headers
@@
 occurred over just a few TCP/TLS connections.
-60\% of \meek\ connections lasts five minutes or longer,
-while only 13\% of those of ordinary traffic do.
+60\% of \meek\ connections lasted five minutes or longer,
+while only 13\% of those of ordinary traffic did.
 \meek\ has essentially no connections lasting less than 24 seconds,
-but such short connections account for over 42\% of the \lbl HTTPS connections.
+but such short connections account for over 42\% of the \lbl trace.
 30\% (3 out of 10) of \meek's connections lasted almost exactly one hour,
@@
 According to our traffic trace, doing so will not disrupt more than 8\% of ordinary connections;
-whether that is an acceptable cost depends on the censor's
+whether that is an acceptable cost depends on the time threshold and the censor's
 tolerance for collateral damage.
@@
 only not to deviate from it too much.
-Circumvention traffic must only be difficult enough to distinguish from ordinary traffic,
-that blocking requires a number of false positives unacceptable to the censor.
+Circumvention traffic must only be difficult enough to distinguish from ordinary traffic
+that blocking it requires an amount of false positives unacceptable to the censor.
 Even 1\% of Google traffic accidentally blocked may exceed the collateral damage tolerance of some censors.
@@
 Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
-Most users who use Tor, use it with Tor Browser~\cite{torbrowser},
+Most users who use Tor use it with Tor Browser~\cite{torbrowser},
 a customized version of Firefox that is
@@
 since close to the beginning of development.
+A measurement of 5, for example, means that there were on average five
+simultaneous users of the system at any time during the day.
 The measurements come from the Tor Metrics Portal~\cite{metrics-meek},
@@
 
-The experimental Tor Browser releases have all been based on Google with App Engine.
+Our experimental Tor Browser releases have all been based on Google with App Engine.
 Support for CloudFront was not realized until late July.
@@
 there is nothing for the user to upload and no out-of-band communication is needed before getting
-started---when everything works it offers no-configure circumvention.
+started---when everything works it offers circumvention without configuration.
 
@@
 when it blocked access to all Google services~\cite{cn-google-block}.
-In 2012, the government of Pakistan blocked to all of YouTube
+In 2012, the government of Pakistan blocked all of YouTube
 in order to restrict access to one video,
@@
 
-Domain fronting shares a potential weakness with decoy routing,
-which is that the overt and covert destinations lie at the ends of different
+% Discuss TLS throttling as an attack.
+
+Domain fronting shares a potential weakness with decoy routing:
+the overt and covert destinations lie at the ends of different
 network paths.
@@
 There is additional risk when the client is browsing a web site
-controlled by the same service as that they are fronting through,
+controlled by the same service as the one they are fronting through,
 for example browsing YouTube while fronting through \urll{www.google.com}.
@@
 to be popular in order to have high collateral damage,
-but popular domains are also the ones people tend to want to go to.
-A possible mitigation is traffic padding that lasts until
+but popular domains are also the ones that people tend to want to go to.
+A possible mitigation is padding that lasts until
 the second hop of a three-hop Tor circuit,
@@
 A censor that controls a certificate authority trusted by the browser
-would be able to do a man-in-the-middle attack
+is able to perform a man-in-the-middle attack
 between the client and the intermediate web service,
@@
 Their URLs unprotected by domain fronting,
-each reflector would be easily individually blockable,
+each reflector would be easily blockable individually,
 so there would need to be sufficiently many that
@@
 
+[Links to source code omitted for anonymous submission.]
 % ANON

### 2014-08-02 docs/meek.tex
Prevent line breaks in "X-Session-Id".

@@
 so the censor cannot use the
-Host and X-Session-Id headers for classification.
+Host and \mbox{X-Session-Id} headers for classification.
 }
@@
 which it sends with its requests in a special
-X-Session-Id HTTP header.
+\mbox{X-Session-Id} HTTP header.
 \meekserver, when it sees a session ID for the first time,

### 2014-11-23 docs/meek.tex
Make it clear the Psiphon deployment was independent.
Remember to ack Sadia and Michael.
Apply ACM style and make necessary formatting tweaks.
Use the alternate ACM style.
Tighten up.

@@
-\documentclass[conference]{IEEEtran}
+\documentclass{sig-alternate}
+\usepackage{txfonts}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{xspace}
+
+% Turn off ACM copyright block.
+\toappear{}
+
+\urlstyle{same}
 
@@
 \caption{
-Domain fronting uses different domain names at different layers of communication.
+Domain fronting uses different domain names at different layers.
 At the plaintext layers visible to the censor---the DNS request and the
@@
 the front domain \mbox{\textbf{allowed.example}}.
-At the HTTP layer, unreadable to the censor but meaningful to the intermediate web service,
+At the HTTP layer, unreadable to the censor,
 is the actual destination \mbox{\textbf{forbidden.example}}.
@@
 
-\section{Architecture and protocol of \meek}
+\section{Architecture and protocol of meek}
 \label{sec:architecture}
@@
 
-\x16\x03\x01\x02\x00\x01\x00\x01\xfc\x03\x03\x9b\xa9\x9f...
+\x16\x03\x01\x02\x00\x01\x00\x01\xfc\x03\x03\x9b\xa9...
 \end{verbatim}
-\smallskip
 \begin{quote}
@@
 
-\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75\xa2...
+\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75...
 \end{verbatim}
 \end{quote}
-\smallskip
 \begin{verbatim}
@@
 \end{verbatim}
-\smallskip
 \begin{quote}
@@
 
-\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
+\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84...
 \end{verbatim}
@@
 because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
-Figure~\ref{fig:ciphersuites} shows examples of how TLS client
+Figure~\ref{fig:ciphersuites} in Appendix~\ref{sec:ciphersuites} shows examples of how TLS client
 implementations may detectably differ.
@@
 shows how it would appear on the network with no TLS camouflage.
-Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
-shows two browsers which have TLS fingerprints different from Go's
+Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome}
+show two browsers which have TLS fingerprints different from Go's
 and different from each other's.
@@
 if it considered the collateral damage resulting from blocking other Go programs to be slight enough.
+
+In order to disguise its TLS fingerprint,
+\meekclient proxies all its HTTPS requests through an actual web browser.
+We implemented extensions for two web browsers,
+Firefox and Chrome,
+that enable them to make HTTPS requests on behalf of \meekclient.
+The TLS fingerprint looks like that of a browser, because it is that of a browser.
+The browser instance running the extension is completely separate
+from the browser the user interacts with.
+It runs invisibly in the background in a separate process,
+doesn't display a user interface,
+and shares no state with the user's browser.
+
+\begin{figure}
+\centering
+\includegraphics[height=1.5in]{browser-architecture}
+\caption{
+Client architecture including a browser extension for TLS camouflage.
+Dashed lines show the process hierarchy.
+Solid lines show the flow of outgoing communication.
+The headless browser runs in the background and is invisible to the user.
+This figure is a zoomed-in view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
+}
+\label{fig:browser-architecture}
+\end{figure}
+
+Figure~\ref{fig:browser-architecture} shows the interaction of components
+on the client's computer.
+The local Tor process runs a helper process that starts both \meekclient
+and the headless browser,
+then configures \meekclient to proxy its requests through the browser extension.
+The user's browser proxies through Tor;
+Tor proxies through \meekclient;
+and \meekclient proxies through the headless browser.
+The headless browser is the only part that ever actually touches the network.
+It should be emphasized that the URLs requested by the headless browser extension
+have no relation to the URLs the user browses;
+the extension only ever makes requests to the front domain.
+
+The use of a browser extension brings benefits beyond TLS camouflage.
+It means \meek's HTTP tunnel inherits other characteristics of the browser:
+for instance
+how often it resolves DNS,
+its connection reuse,
+and its HTTP keepalive behavior.
+The Firefox extension has special advantages
+when \meek\ is used with Tor Browser
+because Tor Browser
+is a modified version of Firefox:
+we can use the same browser executable for both the browser the user interacts with (Tor Browser)
+and the one providing TLS camouflage (headless Firefox),
+saving space in distribution packages
+and sparing the user the chore of having to separately configure a browser to run the extension.
+In Tor Browser,
+the headless Firefox is started and stopped transparently
+when \meek\ is activated and deactivated.
+
+% The development of the browser extensions posed some unexpected challenges.
+% Tor Browser disables TLS session tickets because they can be used as linking identifiers,
+% but the lack of session tickets shows up as a missing TLS extension,
+% so we had to reenable them in the headless browser.
+% (Doing so doesn't harm Tor Browser's anonymity:
+% if session tickets are used, they are used only on the circumvention layer
+% between the user and the frontend server. Tor Browser's own TLS is tunneled
+% within the circumvention layer, and session tickets are still disabled at that level.)
+% The Chrome extension needed to be split into two pieces, an extension and an app,
+% because an extension cannot open a listening socket and an app cannot make HTTP requests.
+
+No TLS camouflage is needed between the intermediate web service and \meekserver,
+because that portion of the communication flow is not observed by the censor.
+
+Appropriate TLS camouflage may differ depending on circumstances.
+On a traditional desktop PC, using a browser is probably the right choice.
+When
+[blinded circumvention tool]
+% ANON
+% Psiphon
+ported \meekclient to Android,
+they didn't use a browser as camouflage,
+but rather made all HTTPS requests with the standard Android HTTP API.
+This decision makes sense because other Android applications
+also use the standard API and share the same TLS fingerprint.
+
+\section{A survey of fronting-capable\\web services}
+\label{sec:survey}
+
+This section contains a brief survey of fronting-capable
+web services we have found, each with its pros and cons.
+The list is not exhaustive and is meant to illustrate the broad
+support for fronting that exists.
+Of the services listed, we have so far deployed \meek\
+only on Google App Engine and Amazon CloudFront.
+For the others, we have only checked that fronting works.
+Recall that even web services that support fronting
+will front only for their own customers,
+so new each deployment typically requires an investment of time and money.
+
+Google App Engine~\cite{googleappengine}
+is a web application platform.
+Each application gets a user-specified subdomain of \urll{appspot.com},
+which can be fronted through almost any Google domain,
+including google.com, gmail.com, googleapis.com, and many others.
+App Engine can run only web applications,
+not a full Tor bridge;
+for that reason we use a tiny ``reflector'' application
+that merely copies incoming requests to a Tor bridge hosted elsewhere.
+Fronting through App Engine is attractive in the case where
+\urll{appspot.com} is blocked---not unlikely,
+because of the ease of building a proxy there---but
+at least one other Google service is reachable.
+Applications that use less than one gigabyte of bandwidth daily
+are free of charge,
+making possible an upload-your-own-app model
+à la GoAgent.
+
+Amazon CloudFront~\cite{cloudfront},
+not to be confused with CloudFlare,
+is the CDN of Amazon Web Services.
+A CloudFront ``distribution'' associates
+an automatically generated subdomain of \urll{cloudfront.net}
+with an origin server,
+which in our case is an instance of \meekserver.
+The front domain may be any other of CloudFront's automatically generated subdomains, all
+of which support HTTPS through a wildcard certificate.
+CloudFront has a usage tier that is free of charge for a year,
+subject to a bandwidth limit of 50 gigabytes per month.
+
+CloudFlare~\cite{cloudflare},
+not to be confused with CloudFront,
+is a CDN also marketed as protection against
+denial-of-service attacks.
+It appears that any domain name on CloudFlare
+can front for any other, even custom user-selected domains;
+however it is not obvious which one is best to use as a front.
+The front domain needs to be a popular one
+(causing high collateral damage if blocked),
+or the censor may simply block it entirely.
+It is doubly bad when a domain is blocked in this way,
+because not only is circumvention foiled,
+but some unsuspecting third party has just had their web site blocked.
+A solution may be to round-robin through
+a pool of popular domain names;
+or to use ``domainless'' fronting that doesn't send SNI.
+% Though CloudFlare supports domain fronting,
+% its terms of service~\cite{cloudflare-terms}
+% seem to prohibit the kind of tunneled proxying that \meek\ does:
+% \begin{quote}
+% \textsc{Section 10: Limitation on non-HTML caching}\\
+% You acknowledge that CloudFlare's Service is offered as a platform to cache and
+% serve web pages and websites and is not offered for other purposes
+% \ldots\ you understand and agree to use the Service solely
+% for the purpose of hosting and serving web pages\ldots
+% \end{quote}
+
+Akamai~\cite{akamai-site} is a large CDN.
+Requests may be fronted through the special HTTPS domain
+\urll{a248.e.akamai.net},
+which serves a certificate also good for \urll{*.akamaihd.net}.
+The collateral damage of blocking Akamai is enormous:
+in 2010 it carried 15--20\% of all web traffic~\cite{akamai}.
+Akamai costs more than other CDNs;
+it would likely require institutional support
+to keep a circumvention system running on it in the long term.
+
+Microsoft Azure~\cite{azure}
+is a cloud computing platform that features a CDN.
+Similarly to CloudFront, users get automatically generated subdomains
+of \urll{vo.msecnd.net},
+all of which can front for each other.
+There are other front domain names, like \urll{ajax.aspnetcdn.com},
+that may offer high collateral damage.
+
+Fastly~\cite{fastly} is a CDN.
+It is the only one of the services we tested in that
+that appears to enforce SNI:
+if the SNI and Host do not match,
+the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
+However, if the TLS ClientHello omits SNI, then the Host may be any Fastly domain.
+It is the only service we have found
+that requires the ``domainless'' fronting style.
+
+\section{Traffic analysis}
+\label{sec:trafficanalysis}
+
+One of our goals in developing \meek\ is to force
+the censor to use relatively more expensive statistical classifiers
+to effect blocking---generally, to increase the cost of censorship.
+We believe \meek\ is resistant to the ``easy''
+forms of blocking, namely IP address and DNS blocking,
+simple pattern-based DPI,
+and active probing.
+We hope to force the censor to resort to measuring
+more subtle features of the communication.
+In this section we provide a preliminary analysis
+of \meek's resistance to such attacks.
+Specifically, we consider three traffic features:
+packet length distribution,
+number of simultaneous connections,
+and connection lifetime.
+
+The issue of statistical traffic analysis is a general one~\cite{trafficmorphing},
+and mostly orthogonal to \meek's main idea, domain fronting.
+It may be that the problem of traffic analysis is
+best solved by a modular component not
+necessarily specifically designed for \meek.
+
+% Advantage is that we are probably proxying web traffic.
+As \meek\ is based on HTTPS,
+we compare traffic traces of \meek\ against
+traces of ``ordinary'' HTTPS traffic.
+We did a packet capture
+of automatically browsing the home pages
+of the top 500 Alexa web sites using \meek\ in Tor Browser,
+with the browser camouflage described in Section~\ref{sec:browserextension},
+and Google App Engine as the intermediate web service.
+The \meek\ trace is 687~megabytes in all
+and covers about 4.5 hours of network activity.
+Our representative of ordinary HTTPS traffic
+is a sanitized 10-minute trace
+from 
+%Lawrence Berkeley National Laboratory (\lbl)
+a research lab [blinded as \lbl for anonymous submission],
+comprising data to and from TCP port 443 on any Google server.
+% Mention the non-google if it appears in a figure.
+The \lbl trace consists 313~megabytes of packet headers,
+not payloads, destined for TCP port 443 on any Google server.
+The original IP addresses were masked by being
+replaced by a counter before we received the trace.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{datalen.pdf}
+% Output of datalen.R.
+%
+% LBL
+%          0       1430       1418         41       1416       1460       1260
+% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
+%       1400       1359         33
+% 0.01673740 0.01126137 0.01100281
+%
+% meek
+%        1418           0        1460         396         196        1024
+% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
+%         811         783         151        1263
+% 0.012312668 0.007811963 0.007031241 0.006569205
+\begin{tabular}{r r >{\qquad} r r}
+\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
+0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
+1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
+1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
+41 bytes & 6.1\% & 396 bytes & 2.0\% \\
+1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
+1460 bytes & 2.9\% & 1024 bytes & 1.5\%
+\end{tabular}
+\caption{
+Comparison of TCP payload length distributions
+between ordinary HTTPS connections to Google services
+from the \lbl traffic trace,
+and \meek\ running on App Engine, fronted through www.google.com.
+% The histogram's bin width is 5~bytes.
+}
+\label{fig:datalen}
+\end{figure}
+
+\subsection{Packet lengths}
+
+Protocols vary in their packet lengths;
+a censor may block a circumvention protocol if its length distribution
+is distinct enough.
+Figure~\ref{fig:datalen}
+compares the packet length distributions of the sample traffic traces.
+In both cases, about 38\% of packets have an empty payload, mostly ACKs.
+There is a small peak in both traces at the usual TCP Maximum Segment Size
+of 1460 bytes.
+The concentration of values near 1418 bytes
+may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
+% https://github.com/joyent/node/issues/6889
+% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
+Conspicuous in the \meek\ trace are a small number of
+discrete frequent packet sizes,
+and the lack of a cluster of short payloads of around 50 bytes.
+Both of these characteristics are probably reflections
+of Tor's fixed cell size and the nearly fixed-size HTTP headers
+added by \meekclient and \meekserver.
+% In this trace, packets of 1024 bytes are probably single
+% Tor cells and those of 396 are probably empty polling requests.
+
+% David: I don't think the following paragraph is true.
+% Almost all the length>1400 packets are Google→client, not client→Google,
+% as you can see if you split the histogram up by direction.
+%
+% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for \meek\ in order
+% to hide TLS handshake characteristics.
+% Browsers also apply techniques like HTTP pipelining to improve performance. Since \meek\ is always communicating with
+% the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
+% can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
+% records \meek's traffic.
+% In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
+% Google, click a result, and then close the tab that displays search results. The browser may close the 
+% connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
+% opens a new connection. In this case, small requests do not have such opportunity for batching.
+
+% These browser techniques improve performance, but also pose unexpected consequences. 
+% Although \meek\ alters the packet size distribution of underlying Tor traffic, 
+% the censor may be aware of the distribution of \meek\ itself. 
+% Additionally, the persistent connection itself can be an issue.
+% We thus investigated other related characteristics.
+
+\subsection{Connection lifetime}
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{flowduration}
+\caption{
+CDF of connection lifetime.
+The horizontal axis is logarithmic.
+\meek's connections tend to last longer than those of ordinary HTTPS traffic.
+}
+\label{fig:duration}
+\end{figure}
+
+% Output of flowduration.R.
+% LBL
+% [1] "42.6%" "87.0%" "92.2%"
+% meek
+% [1] "10.0%" "30.0%" "40.0%"
+
+We consider the duration of TCP connections as a potential distinguisher.
+Figure~\ref{fig:duration} shows the cumulative probability
+of connection durations in our two traces.
+Considering the \lbl trace first,
+we see interesting probability concentrations on
+round numbers: 10~s, 60~s, 120~s, 180~s, and 240~s.
+We hypothesize that this phenomenon is caused by
+keepalive timeouts in web browsers and servers,
+and polling behavior of web apps.
+The small rise at 600 seconds is an artifact caused
+by the fact that the trace is only 10 minutes long.
+Connections lasting longer than 10 minutes are not accurately reflected,
+however we can say that only about 8\% of connections lasted longer than 10 minutes.
+
+The \meek\ trace shows a propensity for longer connections.
+Over 4.5 hours, there were only 10 connections,
+three of them lasting for an hour.
+The long connections are caused by the client browser extension's
+use of long-lived HTTP keepalive connections,
+combined with \meekclient's polling requests,
+which keep the connection from becoming idle.
+The traffic trace represents the browsing of hundreds of web sites
+and thousands of HTTPS transactions, but they all
+occurred over just a few TCP/TLS connections.
+60\% of \meek\ connections lasted five minutes or longer,
+while only 13\% of those of ordinary traffic did.
+\meek\ has essentially no connections lasting less than 24 seconds,
+but such short connections account for over 42\% of the \lbl trace.
+30\% (3 out of 10) of \meek's connections lasted almost exactly one hour,
+evidently reflecting a built-in time limit in either the client browser extension
+or in App Engine.
+
+In light of these findings,
+the censor may decide to block any long-lived HTTPS connections between
+a client and a web service.
+According to our traffic trace, doing so will not disrupt more than 8\% of ordinary connections;
+whether that is an acceptable cost depends on the time threshold and the censor's
+tolerance for collateral damage.
+The censor can lower the timing threshold, at the cost of more false positives.
+Duration-based blocking is favorable for the circumventor,
+because if the censor terminates connections after, say, 10 minutes,
+in any case that's 10 minutes of circumvention achieved,
+after which \meek\ can start a new connection
+and allow Tor to rebuild its circuits.
+Future enhancements in \meek\ may even allow reconnecting using the same session ID,
+so there will be no effect on the client other than a brief delay
+while a new HTTPS connection is established.
+
+% meek is fairly robust against connection termination.
+% Well, not really for long-lived TCP connections.
+% But it could be.
+% Can reconnect and make a new circuit.
+
+\subsection{Concurrent connections}
+
+% Output of concurrent.R.
+% [1] 2745
+% [1] 2.610621
+% [1] 1
+% [1] 1.002148
+% [1] 772
+% [1] 2745
+% [1] 0.2812386
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{concurrent.pdf}
+\caption{
+Number of simultaneous HTTPS connections to any Google server.
+Each pale line indicates the number of HTTPS connections
+of a single client IP address.
+The \lbl trace shows 2,745 unique clients and the \meek\ trace only one.
+The dark line is a smoothed average number of connections per client.
+The \meek\ count stays close to~1 throughout, only momentarily
+jumping to 0 or~2.
+The average number of connections per user in the \lbl trace is 2.61,
+and in the \meek\ trace is 1.002.
+}
+\label{fig:concurrent}
+\end{figure}
+
+The number of concurrent connections is another potential distinguisher.
+We have seen how \meek\ tends to use one long-lived connection
+through which it tunnels all its requests.
+Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
+Google per client in both traces.
+The number of connections in the \lbl trace is variable,
+with some hosts briefly spiking up above 50 connections,
+but the average case is very heavily skewed to smaller numbers.
+The average number of connections in the \lbl trace is 2.61,
+with 28\% of clients never having more than 2 concurrent connections.
+In the \meek trace the average is almost exactly 1, only briefly
+deviating when one connection ends and another begins.
+We conclude that having a small number of concurrent connections is unremarkable.
+
+% $$\diamondsuit$$
+
+So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish \meek\
+from other HTTPS traffic.
+The long-lived connections and few common packet sizes are
+potential targets for a more concerted attack.
+The fundamental problem we face is essentially that of steganography,
+the need to make our traffic fit some model of ``normal'' traffic.
+The problem is inherently difficult,
+because it is difficult to say just what normal traffic \emph{is}.
+It depends on the network environment;
+it also depends on the endpoint.
+Google's traffic is different than Akamai's.
+
+For the purposes of censorship circumvention,
+one doesn't need to match exactly a ``typical'' traffic profile;
+only not to deviate from it too much.
+Circumvention traffic must only be difficult enough to distinguish from ordinary traffic
+that blocking it requires an amount of false positives unacceptable to the censor.
+Even 1\% of Google traffic accidentally blocked may exceed the collateral damage tolerance of some censors.
+Further, it is hard to characterize what normal use is of, say, a CDN:
+they provide access to ordinary web sites,
+but also to video streams and software updates,
+and not all clients are web browsers.
+The difficulty we face is symmetric;
+if finding the right model is difficult task for us,
+it is also difficult for the censor.
+We have seen that censors prefer to use easy classifiers when they exist.
+By removing the easy ways, we increase the censor's cost.
+
+\section{Deployment}
+\label{sec:deployment}
+
+Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
+Most users who use Tor use it with Tor Browser~\cite{torbrowser},
+a customized version of Firefox that is
+preconfigured to use a built-in Tor client.
+% and patched to defend against application-layer privacy and anonymity threats
+% like tracking cookies and web browser fingerprinting.
+Tor Browser has an easy interface for selecting pluggable transports.
+We made a series of experimental releases of Tor Browser featuring \meek,
+releasing the first one on February~18.
+[Some details of deployment are omitted for anonymous submission.]
+% ANON
+% On April~18 we made the first release featuring the browser camouflage
+% that is the subject of Section~\ref{sec:browserextension}.
+% We announced our releases on Tor development mailing lists,
+% whence they were picked up by Tor Weekly News on the Tor blog.
+% Our code was merged by the Tor Browser maintainers
+% in June and is scheduled for an alpha release,
+% still pending as of this writing.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{clients-meek}
+\caption{
+Concurrent users of the \meek\ pluggable transport for Tor.
+}
+\label{fig:clients-tor}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\linewidth]{clients-psiphon3}
+\caption{
+Daily unique users of \meek\ with
+[blinded circumvention tool]
+% ANON
+% Psiphon
+(note vertical axis).
+The decrease at the end of June
+was caused by an unblocking event that made \meek\ unnecessary for some users.
+}
+\label{fig:clients-psiphon3}
+\end{figure}
+
+Figure~\ref{fig:clients-tor} shows the average number of concurrent users of \meek\ with Tor
+since close to the beginning of development.
+A measurement of 5, for example, means that there were on average five
+simultaneous users of the system at any time during the day.
+The measurements come from the Tor Metrics Portal~\cite{metrics-meek},
+which aggregates statistics reported by Tor relays.
+The number of users is estimated by counting the number
+of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
+% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by \meek.
+
+[Blinded circumvention tool]
+% ANON
+% Psiphon
+began their independent deployment of \meek\ in June~2014.
+Figure~\ref{fig:clients-psiphon3} shows the number
+of unique daily users of \meek%
+,
+% ANON
+% with Psiphon,
+estimated through clients' self-reporting of their most recent connection date.
+The developers tell us that the drop that occurs
+in the middle of June was not caused by a blocking event,
+but rather an unblocking event that made \meek\ unnecessary for some users.
+Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
+are not directly comparable because they count slightly different things,
+it is clear that meek-with-%
+[blinded circumvention tool],
+% ANON
+% Psiphon,
+with its thousands of daily users,
+is much more widely used than meek-with-Tor, which has not yet seen a formal release.
+
+Our experimental Tor Browser releases have all been based on Google with App Engine.
+Support for CloudFront was not realized until late July.
+We are running the backends on paid accounts of these services for use by the public.
+The cost for bandwidth on App Engine is \$0.12 per gigabyte,
+with one gigabyte free each day.
+The total App Engine bill so far has been \$2.07,
+with most days' usage being below the billable threshold.
+There has not yet been enough use of CloudFront to cost anything.
+
+A longer-term goal is to find a way to fund continued operation
+if \meek\ becomes popular.
+Although some of the systems listed in Section~\ref{sec:survey}
+are inexpensive enough that some users could upload their own fronting backend,
+thereby diffusing costs,
+we believe that an organization operating a backend for the use of the public
+has compelling usability advantages.
+With client software configured to use the public backend by default,
+there is nothing for the user to upload and no out-of-band communication is needed before getting
+started---when everything works it offers circumvention without configuration.
+
+% The number of parties able to analyze users' traffic patterns is somewhat increased:
+% the path from user to Tor bridge now includes App Engine and the web app operators,
+% in addition to the ISP and intermediate routers that were there before.
+% On the other hand, the Tor bridge no longer gets to see users' IP addresses:
+% all it sees are many connections from App Engine.
+
+\section{Discussion}
+\label{sec:discussion}
+
+Domain fronting derives part of its unblockability from the
+high collateral damage of blocking the fronted-through domain.
+Fronting through \urll{www.google.com} to App Engine, for example,
+is making a bet that the censor will lack the temerity to block Google.
+The Great Firewall of China called our bluff in June of 2014,
+when it blocked access to all Google services~\cite{cn-google-block}.
+In 2012, the government of Pakistan blocked all of YouTube
+in order to restrict access to one video,
+and in 2011, the government of Egypt briefly ``turned off the net'' completely.
+% http://www.washingtonpost.com/business/economy/youtube-blocked-in-pakistan/2012/09/17/30081fa2-00ea-11e2-b257-e1c2b3548a4a_story.html
+% https://en.wikipedia.org/wiki/Internet_censorship_in_Egypt#2011_Internet_shutdown
+These examples show that blocking resistance is not an absolute,
+black-and-white security property;
+it can only be discussed in an economic context, relative to the costs borne
+by the censor and by users of a system.
+To be sure, blocking Google is an extreme measure,
+probably out of the reach of most censors.
+Blocking all of the fronting-capable services listed in
+Section~\ref{sec:survey} would be even harder.
+
+A censor could attack domain fronting by
+going directly to the operators of the intermediate web service
+and asking them either to break fronting
+(i.e., require SNI to be present and SNI and Host header to agree),
+or to get rid of their customers who are
+engaged in enabling circumvention (i.e., us).
+The censor could threaten to block the web service entirely otherwise.
+Whether the attack will succeed depends on the censor's
+and the web service's specific costs and motivations,
+so we cannot make any general statements.
+It is ultimately a question of who needs whom more:
+whether it hurts the web service or the censor more
+when the service is blocked.
+% Nothing works against a censor with sufficiently high tolerance for
+% collateral damage,
+% but we also don't have to defeat the world's
+% most powerful censor in order to be successful.
+% What doesn't work in one place may work in another.
+
+% Discuss TLS throttling as an attack.
+
+Domain fronting shares a potential weakness with decoy routing:
+the overt and covert destinations lie at the ends of different
+network paths.
+The difference in paths may create side channels---latency measurements for instance---that
+enable the censor to
+distinguish fronted traffic from traffic that is truly destined
+to the apparent destination.
+For example, a CDN can be expected to have responses
+to some fraction of requests already in cache,
+and respond to those requests with low latency.
+Fronted traffic, on the other hand, always continues all the way
+to the origin server after reaching the CDN (as if nothing were ever cached),
+resulting in a higher latency.
+Latency measurement was applied to decoy routing by Schuhard et~al.~\cite[Section~5]{ccs2012-decoys},
+who compared empirical round-trip-time distributions using a
+Kolmogorov--Smirnov test.
+% time between ChangeCipherSpec and ApplicationData
+
+The intermediate web service enjoys a privileged network position,
+from which it is able to monitor all circumvention traffic.
+Even if the censor doesn't know who the users are, the CDN knows.
+The web service has basically the same network visibility
+as the client's ISP would have, if the client were not circumventing.
+For this reason, domain fronting should be combined with another
+layer, for example Tor, that prevents the web service from
+observing the contents and destination of messages.
+There is additional risk when the client is browsing a web site
+controlled by the same service as the one they are fronting through,
+for example browsing YouTube while fronting through \urll{www.google.com}.
+Even with Tor, when this happens the web service gets to see
+both entry and exit traffic, and is in a position to
+perform traffic correlation attacks.
+The problem seems hard to counter, because the front domain needs
+to be popular in order to have high collateral damage,
+but popular domains are also the ones that people tend to want to go to.
+A possible mitigation is padding that lasts until
+the second hop of a three-hop Tor circuit,
+which would reduce the correlation between entry and exit traffic.
+% like what mjuarez is working on, mostly orthogonal to circumvention.
+
+% We implemented \meek\ as a pluggable transport~\cite{pt} for Tor.
+% Although it is possible to use the system with proxies other than Tor,
+% using Tor has some attractive features.
+% The pluggable transports infrastructure makes it relatively easy to prototype
+% a circumvention technique and connect it to a global proxy network.
+% We can treat confidentiality and integrity of tunneled communication
+% as a problem solved by Tor, which we don't need to solve separately.
+% Tor's extra proxy hops mean that the HTTP reflector (App Engine)
+% and the entry bridge do not have to be trusted.
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.40\linewidth}
+\includegraphics[width=\linewidth]{wire-sequential}
+\caption{Sequential}
+\label{fig:wire-sequential}
+\end{subfigure}
+\qquad
+\begin{subfigure}[t]{0.40\linewidth}
+\includegraphics[width=\linewidth]{wire-parallel}
+\caption{Parallel}
+\label{fig:wire-parallel}
+\end{subfigure}
+
+\caption{
+The nature of potential performance gain
+from sending fronted requests in parallel.
+}
+\label{fig:wire}
+\end{figure}
+
+We have assumed that the intermediate web service is
+outside the censor's domain of control,
+so that communication between the web service and Tor bridge
+doesn't have to be protected.
+What happens when the web service---a CDN edge server, for instance---is
+inside the network controlled by the censor?
+If the edge server forwards the request to the bridge
+as an ordinary HTTP request on the public Internet,
+then blocking it is as easy as blocking the IP address of the bridge.
+On the other hand, if the web service encapsulates
+the request and sends it encrypted, or over its own fast private network,
+to another server outside of the censor's control,
+then fronting will still work.
+
+The ``domainless'' fronting style, which omits SNI,
+is useful when there is no good front domain known for a web service.
+At least one CDN, Fastly, requires the domainless style.
+All current web browsers support SNI,
+so it is possible that lack of SNI could be used as a distinguisher.
+According to our communication with
+a representative of
+[a blinded organization observing many TLS connections],
+% ANON
+% the International Computer Science Institute's
+% certificate notary~\cite{icsi-notary},
+% which observes on the order of 50~million TLS connections daily,
+83.5\% of connections used SNI in June~2014.
+There are apparently enough connections without SNI
+that a censor will at least have to consider seriously
+the costs and benefits before deciding to block SNI-less TLS outright.
+
+The current implementation of \meek\ strictly serializes
+its HTTPS requests and responses,
+in order to keep chunks of the underlying TCP stream
+in the proper order.
+The unfortunate side effect of this simple approach
+is added latency that gets worse with longer round-trip times.
+In future work we plan to add an additional reliability layer,
+perhaps like the system of sequence numbers and acknowledgments used in OSS~\cite{oss},
+that would allow requests to be pipelined
+and cope with out-of-order delivery.
+Figure~\ref{fig:wire-sequential} shows how the current implementation works,
+and Figure~\ref{fig:wire-parallel} shows the nature of the performance
+improvement that could be gained with a reliability layer
+and parallel requests.
+% Would be useful for Iran-like session cutoff, independent of \meek.
+
+\meek's use of HTTPS is subject to the usual public key infrastructure
+and trust model.
+The browser running the HTTPS camouflage extension (Section~\ref{sec:browserextension})
+has a list of trusted certificate authorities.
+A censor that controls a certificate authority trusted by the browser
+is able to perform a man-in-the-middle attack
+between the client and the intermediate web service,
+and detect fronting by decrypting TLS and checking for specific Host headers.
+Such a censor would be able to detect circumvention,
+but still not read the client's plaintext because of the
+additional encryption and authentication of the tunneled Tor layer.
+It seems risky for the censor to risk being detected in
+a man-in-the-middle attack merely to confirm that a user is circumventing,
+but it is not impossible for a sufficiently powerful censor.
+The problem doesn't exist when the front domain is one
+that happens have its public key ``pinned'' in the headless browser,
+for instance when using the Chrome extension and fronting through
+\urll{www.google.com}.
+
+% \meek\ apart from Tor.
+% more risk for the proxy operator
+% can require people to run their own proxies à la GoAgent.
+% "Censorship implies surveillance"
+
+The key idea of \meek\ is domain fronting,
+but its HTTP tunneling ability is useful on its own.
+Another idea for deployment is to use
+thousands of simple HTTP reflectors on cheap web hosting
+(in place of domain fronting on a big CDN).
+The request-reflecting role of a CDN can
+be played by a PHP script, for example,
+or a special web server configuration.
+Their URLs unprotected by domain fronting,
+each reflector would be easily blockable individually,
+so there would need to be sufficiently many that
+a censor could not block them all.
+This deployment model is essentially the same as with
+ordinary Tor bridges: have lots of volunteer-operated bridges
+and make it hard to enumerate them all.
+The advantage that an HTTP transport would have
+is that it is easier for a volunteer to upload a PHP file to a web host
+than to set up and maintain a Tor bridge.
+
+\section{Summary}
+\label{sec:summary}
+
+We have presented domain fronting,
+an HTTPS technique that uses different domain names
+at different communication layers in
+order to hide the remote endpoint of a communication.
+We implemented \meek,
+a pluggable transport for Tor.
+We show that it resists common methods of blocking,
+and begin an investigation into its
+resistance against more subtle and expensive means of traffic analysis.
+We discuss the results of an initial deployment.
+% ANON
+% in both Tor and Psiphon.
+
+[Links to source code omitted for anonymous submission.]
+% ANON
+% \meek\ has a home page at
+% \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
+% Our source code is in the Git repository at
+% \url{https://git.torproject.org/pluggable-transports/meek.git}.
+% All our programs are free software.
+
+% As of version 0.9 (June~19, 2014), the source code consists of
+% about 1,100 lines of Go for the client programs,
+% 400 lines for \meekserver, and
+% 100 lines for the reflector application for App Engine.
+% Each of the browser extensions
+% (one for Firefox, one for Chrome)
+% is about 400 lines of JavaScript.
+
+% ANON
+% \section*{Acknowledgments}
+
+% We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
+% Special thanks go to the members of the tor-qa and tor-dev mailing lists
+% who responded to our design ideas, reviewed source code, and tested our prototypes.
+% Thanks to Psiphon~Inc. for help with design and development, and for providing user count estimates.
+% George Kadianakis
+% Georg Koppen
+% Lunar
+% Yawning Angel
+% Ox from Lantern.
+% Johanna Amann for getting the fraction of SNI from ICSI notary:
+%   https://trac.torproject.org/projects/tor/ticket/12208#comment:5
+% Arlo Breault (flashproxy-reg-appspot)
+% Sadia Afroz and Michael Tschantz
+
+%%%%%%%
+
+% HTTPS or not on the App Engine--bridge link.
+% HTTPS obscures session ids, equivalent to obscuring TCP connections in other transports.
+% Increases latency a lot: \approx 100 ms increased to \approx 350 ms when I tried it in March 2014.
+
+\bibliographystyle{abbrv}
+\bibliography{meek}
+
+\appendix
+
+\section{Sample TLS fingerprints}
+\label{sec:ciphersuites}
+
+Figure~\ref{fig:ciphersuites} illustrates the need for camouflage at the TLS layer.
+Even though the TLS application data is effectively hidden by encryption,
+the plaintext parts of TLS reveal information about the implementation.
+The TLS must not be easily identified as belonging to a circumvention tool.
 
@@
 \caption{Firefox 24}
-\begin{minipage}[t][57ex][t]{\textwidth}
+\begin{minipage}[t][65ex][t]{\textwidth}
 \tiny
@@
 
-In order to disguise its TLS fingerprint,
-\meekclient proxies all its HTTPS requests through an actual web browser.
-We implemented extensions for two web browsers,
-Firefox and Chrome,
-that enable them to make HTTPS requests on behalf of \meekclient.
-The TLS fingerprint looks like that of a browser, because it is that of a browser.
-The browser instance running the extension is completely separate
-from the browser the user interacts with.
-It runs invisibly in the background in a separate process,
-doesn't display a user interface,
-and shares no state with the user's browser.
-
-\begin{figure}
-\centering
-\includegraphics[height=1.5in]{browser-architecture}
-\caption{
-Client architecture including a browser extension for TLS camouflage.
-Dashed lines show the process hierarchy.
-Solid lines show the flow of outgoing communication.
-The headless browser runs in the background and is invisible to the user.
-This figure is a zoomed-in view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
-}
-\label{fig:browser-architecture}
-\end{figure}
-
-Figure~\ref{fig:browser-architecture} shows the interaction of components
-on the client's computer.
-The local Tor process runs a helper process that starts both \meekclient
-and the headless browser,
-then configures \meekclient to proxy its requests through the browser extension.
-The user's browser proxies through Tor;
-Tor proxies through \meekclient;
-and \meekclient proxies through the headless browser.
-The headless browser is the only part that ever actually touches the network.
-It should be emphasized that the URLs requested by the headless browser extension
-have no relation to the URLs the user browses;
-the extension only ever makes requests to the front domain.
-
-The use of a browser extension brings benefits beyond TLS camouflage.
-It means \meek's HTTP tunnel inherits other characteristics of the browser:
-for instance
-how often it resolves DNS,
-its connection reuse,
-and its HTTP keepalive behavior.
-The Firefox extension has special advantages
-when \meek\ is used with Tor Browser
-because Tor Browser
-is a modified version of Firefox:
-we can use the same browser executable for both the browser the user interacts with (Tor Browser)
-and the one providing TLS camouflage (headless Firefox),
-saving space in distribution packages
-and sparing the user the chore of having to separately configure a browser to run the extension.
-In Tor Browser,
-the headless Firefox is started and stopped transparently
-when \meek\ is activated and deactivated.
-
-% The development of the browser extensions posed some unexpected challenges.
-% Tor Browser disables TLS session tickets because they can be used as linking identifiers,
-% but the lack of session tickets shows up as a missing TLS extension,
-% so we had to reenable them in the headless browser.
-% (Doing so doesn't harm Tor Browser's anonymity:
-% if session tickets are used, they are used only on the circumvention layer
-% between the user and the frontend server. Tor Browser's own TLS is tunneled
-% within the circumvention layer, and session tickets are still disabled at that level.)
-% The Chrome extension needed to be split into two pieces, an extension and an app,
-% because an extension cannot open a listening socket and an app cannot make HTTP requests.
-
-No TLS camouflage is needed between the intermediate web service and \meekserver,
-because that portion of the communication flow is not observed by the censor.
-
-Appropriate TLS camouflage may differ depending on circumstances.
-On a traditional desktop PC, using a browser is probably the right choice.
-When
-[blinded circumvention tool]
-% ANON
-% Psiphon
-ported \meekclient to Android,
-they didn't use a browser as camouflage,
-but rather made all HTTPS requests with the standard Android HTTP API.
-This decision makes sense because other Android applications
-also use the standard API and share the same TLS fingerprint.
-
-\section{A survey of fronting-capable web services}
-\label{sec:survey}
-
-This section contains a brief survey of fronting-capable
-web services we have found, each with its pros and cons.
-The list is not exhaustive and is meant to illustrate the broad
-support for fronting that exists.
-Of the services listed, we have so far deployed \meek\
-only on Google App Engine and Amazon CloudFront.
-For the others, we have only checked that fronting works.
-Recall that even web services that support fronting
-will front only for their own customers,
-so new each deployment typically requires an investment of time and money.
-
-Google App Engine~\cite{googleappengine}
-is a web application platform.
-Each application gets a user-specified subdomain of \urll{appspot.com},
-which can be fronted through almost any Google domain,
-including google.com, gmail.com, googleapis.com, and many others.
-App Engine can run only web applications,
-not a full Tor bridge;
-for that reason we use a tiny ``reflector'' application
-that merely copies incoming requests to a Tor bridge hosted elsewhere.
-Fronting through App Engine is attractive in the case where
-\urll{appspot.com} is blocked---not unlikely,
-because of the ease of building a proxy there---but
-at least one other Google service is reachable.
-Applications that use less than one gigabyte of bandwidth daily
-are free of charge,
-making possible an upload-your-own-app model
-à la GoAgent.
-
-Amazon CloudFront~\cite{cloudfront},
-not to be confused with CloudFlare,
-is the CDN of Amazon Web Services.
-A CloudFront ``distribution'' associates
-an automatically generated subdomain of \urll{cloudfront.net}
-with an origin server,
-which in our case is an instance of \meekserver.
-The front domain may be any other of CloudFront's automatically generated subdomains, all
-of which support HTTPS through a wildcard certificate.
-CloudFront has a usage tier that is free of charge for a year,
-subject to a bandwidth limit of 50 gigabytes per month.
-
-CloudFlare~\cite{cloudflare},
-not to be confused with CloudFront,
-is a CDN also marketed as protection against
-denial-of-service attacks.
-It appears that any domain name on CloudFlare
-can front for any other, even custom user-selected domains;
-however it is not obvious which one is best to use as a front.
-The front domain needs to be a popular one
-(causing high collateral damage if blocked),
-or the censor may simply block it entirely.
-It is doubly bad when a domain is blocked in this way,
-because not only is circumvention foiled,
-but some unsuspecting third party has just had their web site blocked.
-A solution may be to round-robin through
-a pool of popular domain names;
-or to use ``domainless'' fronting that doesn't send SNI.
-% Though CloudFlare supports domain fronting,
-% its terms of service~\cite{cloudflare-terms}
-% seem to prohibit the kind of tunneled proxying that \meek\ does:
-% \begin{quote}
-% \textsc{Section 10: Limitation on non-HTML caching}\\
-% You acknowledge that CloudFlare's Service is offered as a platform to cache and
-% serve web pages and websites and is not offered for other purposes
-% \ldots\ you understand and agree to use the Service solely
-% for the purpose of hosting and serving web pages\ldots
-% \end{quote}
-
-Akamai~\cite{akamai-site} is a large CDN.
-Requests may be fronted through the special HTTPS domain
-\urll{a248.e.akamai.net},
-which serves a certificate also good for \urll{*.akamaihd.net}.
-The collateral damage of blocking Akamai is enormous:
-in 2010 it carried 15--20\% of all web traffic~\cite{akamai}.
-Akamai costs more than other CDNs;
-it would likely require institutional support
-to keep a circumvention system running on it in the long term.
-
-Microsoft Azure~\cite{azure}
-is a cloud computing platform that features a CDN.
-Similarly to CloudFront, users get automatically generated subdomains
-of \urll{vo.msecnd.net},
-all of which can front for each other.
-There are other front domain names, like \urll{ajax.aspnetcdn.com},
-that may offer high collateral damage.
-
-Fastly~\cite{fastly} is a CDN.
-It is the only one of the services we tested in that
-that appears to enforce SNI:
-if the SNI and Host do not match,
-the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
-However, if the TLS ClientHello omits SNI, then the Host may be any Fastly domain.
-It is the only service we have found
-that requires the ``domainless'' fronting style.
-
-\section{Traffic analysis}
-\label{sec:trafficanalysis}
-
-One of our goals in developing \meek\ is to force
-the censor to use relatively more expensive statistical classifiers
-to effect blocking---generally, to increase the cost of censorship.
-We believe \meek\ is resistant to the ``easy''
-forms of blocking, namely IP address and DNS blocking,
-simple pattern-based DPI,
-and active probing.
-We hope to force the censor to resort to measuring
-more subtle features of the communication.
-In this section we provide a preliminary analysis
-of \meek's resistance to such attacks.
-Specifically, we consider three traffic features:
-packet length distribution,
-number of simultaneous connections,
-and connection lifetime.
-
-The issue of statistical traffic analysis is a general one~\cite{trafficmorphing},
-and mostly orthogonal to \meek's main idea, domain fronting.
-It may be that the problem of traffic analysis is
-best solved by a modular component not
-necessarily specifically designed for \meek.
-
-% Advantage is that we are probably proxying web traffic.
-As \meek\ is based on HTTPS,
-we compare traffic traces of \meek\ against
-traces of ``ordinary'' HTTPS traffic.
-We did a packet capture
-of automatically browsing the home pages
-of the top 500 Alexa web sites using \meek\ in Tor Browser,
-with the browser camouflage described in Section~\ref{sec:browserextension},
-and Google App Engine as the intermediate web service.
-The \meek\ trace is 687~megabytes in all
-and covers about 4.5 hours of network activity.
-Our representative of ordinary HTTPS traffic
-is a sanitized 10-minute trace
-from 
-%Lawrence Berkeley National Laboratory (\lbl)
-a research lab [blinded as \lbl for anonymous submission],
-comprising data to and from TCP port 443 on any Google server.
-% Mention the non-google if it appears in a figure.
-The \lbl trace consists 313~megabytes of packet headers,
-not payloads, destined for TCP port 443 on any Google server.
-The original IP addresses were masked by being
-replaced by a counter before we received the trace.
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{datalen.pdf}
-% Output of datalen.R.
-%
-% LBL
-%          0       1430       1418         41       1416       1460       1260
-% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
-%       1400       1359         33
-% 0.01673740 0.01126137 0.01100281
-%
-% meek
-%        1418           0        1460         396         196        1024
-% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
-%         811         783         151        1263
-% 0.012312668 0.007811963 0.007031241 0.006569205
-\begin{tabular}{r r >{\qquad} r r}
-\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
-0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
-1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
-1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
-41 bytes & 6.1\% & 396 bytes & 2.0\% \\
-1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
-1460 bytes & 2.9\% & 1024 bytes & 1.5\%
-\end{tabular}
-\caption{
-Comparison of TCP payload length distributions
-between ordinary HTTPS connections to Google services
-from the \lbl traffic trace,
-and \meek\ running on App Engine, fronted through www.google.com.
-% The histogram's bin width is 5~bytes.
-}
-\label{fig:datalen}
-\end{figure}
-
-\subsection{Packet lengths}
-
-Protocols vary in their packet lengths;
-a censor may block a circumvention protocol if its length distribution
-is distinct enough.
-Figure~\ref{fig:datalen}
-compares the packet length distributions of the sample traffic traces.
-In both cases, about 38\% of packets have an empty payload, mostly ACKs.
-There is a small peak in both traces at the usual TCP Maximum Segment Size
-of 1460 bytes.
-The concentration of values near 1418 bytes
-may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
-% https://github.com/joyent/node/issues/6889
-% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
-Conspicuous in the \meek\ trace are a small number of
-discrete frequent packet sizes,
-and the lack of a cluster of short payloads of around 50 bytes.
-Both of these characteristics are probably reflections
-of Tor's fixed cell size and the nearly fixed-size HTTP headers
-added by \meekclient and \meekserver.
-% In this trace, packets of 1024 bytes are probably single
-% Tor cells and those of 396 are probably empty polling requests.
-
-% David: I don't think the following paragraph is true.
-% Almost all the length>1400 packets are Google→client, not client→Google,
-% as you can see if you split the histogram up by direction.
-%
-% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for \meek\ in order
-% to hide TLS handshake characteristics.
-% Browsers also apply techniques like HTTP pipelining to improve performance. Since \meek\ is always communicating with
-% the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
-% can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
-% records \meek's traffic.
-% In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
-% Google, click a result, and then close the tab that displays search results. The browser may close the 
-% connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
-% opens a new connection. In this case, small requests do not have such opportunity for batching.
-
-% These browser techniques improve performance, but also pose unexpected consequences. 
-% Although \meek\ alters the packet size distribution of underlying Tor traffic, 
-% the censor may be aware of the distribution of \meek\ itself. 
-% Additionally, the persistent connection itself can be an issue.
-% We thus investigated other related characteristics.
-
-\subsection{Connection lifetime}
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{flowduration}
-\caption{
-CDF of connection lifetime.
-The horizontal axis is logarithmic.
-\meek's connections tend to last longer than those of ordinary HTTPS traffic.
-}
-\label{fig:duration}
-\end{figure}
-
-% Output of flowduration.R.
-% LBL
-% [1] "42.6%" "87.0%" "92.2%"
-% meek
-% [1] "10.0%" "30.0%" "40.0%"
-
-We consider the duration of TCP connections as a potential distinguisher.
-Figure~\ref{fig:duration} shows the cumulative probability
-of connection durations in our two traces.
-Considering the \lbl trace first,
-we see interesting probability concentrations on
-round numbers: 10~s, 60~s, 120~s, 180~s, and 240~s.
-We hypothesize that this phenomenon is caused by
-keepalive timeouts in web browsers and servers,
-and polling behavior of web apps.
-The small rise at 600 seconds is an artifact caused
-by the fact that the trace is only 10 minutes long.
-Connections lasting longer than 10 minutes are not accurately reflected,
-however we can say that only about 8\% of connections lasted longer than 10 minutes.
-
-The \meek\ trace shows a propensity for longer connections.
-Over 4.5 hours, there were only 10 connections,
-three of them lasting for an hour.
-The long connections are caused by the client browser extension's
-use of long-lived HTTP keepalive connections,
-combined with \meekclient's polling requests,
-which keep the connection from becoming idle.
-The traffic trace represents the browsing of hundreds of web sites
-and thousands of HTTPS transactions, but they all
-occurred over just a few TCP/TLS connections.
-60\% of \meek\ connections lasted five minutes or longer,
-while only 13\% of those of ordinary traffic did.
-\meek\ has essentially no connections lasting less than 24 seconds,
-but such short connections account for over 42\% of the \lbl trace.
-30\% (3 out of 10) of \meek's connections lasted almost exactly one hour,
-evidently reflecting a built-in time limit in either the client browser extension
-or in App Engine.
-
-In light of these findings,
-the censor may decide to block any long-lived HTTPS connections between
-a client and a web service.
-According to our traffic trace, doing so will not disrupt more than 8\% of ordinary connections;
-whether that is an acceptable cost depends on the time threshold and the censor's
-tolerance for collateral damage.
-The censor can lower the timing threshold, at the cost of more false positives.
-Duration-based blocking is favorable for the circumventor,
-because if the censor terminates connections after, say, 10 minutes,
-in any case that's 10 minutes of circumvention achieved,
-after which \meek\ can start a new connection
-and allow Tor to rebuild its circuits.
-Future enhancements in \meek\ may even allow reconnecting using the same session ID,
-so there will be no effect on the client other than a brief delay
-while a new HTTPS connection is established.
-
-% meek is fairly robust against connection termination.
-% Well, not really for long-lived TCP connections.
-% But it could be.
-% Can reconnect and make a new circuit.
-
-\subsection{Concurrent connections}
-
-% Output of concurrent.R.
-% [1] 2745
-% [1] 2.610621
-% [1] 1
-% [1] 1.002148
-% [1] 772
-% [1] 2745
-% [1] 0.2812386
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{concurrent.pdf}
-\caption{
-Number of simultaneous HTTPS connections to any Google server.
-Each pale line indicates the number of HTTPS connections
-of a single client IP address.
-The \lbl trace shows 2,745 unique clients and the \meek\ trace only one.
-The dark line is a smoothed average number of connections per client.
-The \meek\ count stays close to~1 throughout, only momentarily
-jumping to 0 or~2.
-The average number of connections per user in the \lbl trace is 2.61,
-and in the \meek\ trace is 1.002.
-}
-\label{fig:concurrent}
-\end{figure}
-
-The number of concurrent connections is another potential distinguisher.
-We have seen how \meek\ tends to use one long-lived connection
-through which it tunnels all its requests.
-Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
-Google per client in both traces.
-The number of connections in the \lbl trace is variable,
-with some hosts briefly spiking up above 50 connections,
-but the average case is very heavily skewed to smaller numbers.
-The average number of connections in the \lbl trace is 2.61,
-with 28\% of clients never having more than 2 concurrent connections.
-In the \meek trace the average is almost exactly 1, only briefly
-deviating when one connection ends and another begins.
-We conclude that having a small number of concurrent connections is unremarkable.
-
-$$\diamondsuit$$
-
-So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish \meek\
-from other HTTPS traffic.
-The long-lived connections and few common packet sizes are
-potential targets for a more concerted attack.
-The fundamental problem we face is essentially that of steganography,
-the need to make our traffic fit some model of ``normal'' traffic.
-The problem is inherently difficult,
-because it is difficult to say just what normal traffic \emph{is}.
-It depends on the network environment;
-it also depends on the endpoint.
-Google's traffic is different than Akamai's.
-
-For the purposes of censorship circumvention,
-one doesn't need to match exactly a ``typical'' traffic profile;
-only not to deviate from it too much.
-Circumvention traffic must only be difficult enough to distinguish from ordinary traffic
-that blocking it requires an amount of false positives unacceptable to the censor.
-Even 1\% of Google traffic accidentally blocked may exceed the collateral damage tolerance of some censors.
-Further, it is hard to characterize what normal use is of, say, a CDN:
-they provide access to ordinary web sites,
-but also to video streams and software updates,
-and not all clients are web browsers.
-The difficulty we face is symmetric;
-if finding the right model is difficult task for us,
-it is also difficult for the censor.
-We have seen that censors prefer to use easy classifiers when they exist.
-By removing the easy ways, we increase the censor's cost.
-
-\section{Deployment}
-\label{sec:deployment}
-
-Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
-Most users who use Tor use it with Tor Browser~\cite{torbrowser},
-a customized version of Firefox that is
-preconfigured to use a built-in Tor client.
-% and patched to defend against application-layer privacy and anonymity threats
-% like tracking cookies and web browser fingerprinting.
-Tor Browser has an easy interface for selecting pluggable transports.
-We made a series of experimental releases of Tor Browser featuring \meek,
-releasing the first one on February~18.
-[Some details of deployment are omitted for anonymous submission.]
-% ANON
-% On April~18 we made the first release featuring the browser camouflage
-% that is the subject of Section~\ref{sec:browserextension}.
-% We announced our releases on Tor development mailing lists,
-% whence they were picked up by Tor Weekly News on the Tor blog.
-% Our code was merged by the Tor Browser maintainers
-% in June and is scheduled for an alpha release,
-% still pending as of this writing.
-
-\begin{figure}
-\includegraphics[width=\linewidth]{clients-meek}
-\caption{
-Concurrent users of the \meek\ pluggable transport for Tor.
-}
-\label{fig:clients-tor}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\linewidth]{clients-psiphon3}
-\caption{
-Daily unique users of \meek\ with
-[blinded circumvention tool]
-% ANON
-% Psiphon
-(note vertical axis).
-The decrease at the end of June
-was caused by an unblocking event that made \meek\ unnecessary for some users.
-}
-\label{fig:clients-psiphon3}
-\end{figure}
-
-Figure~\ref{fig:clients-tor} shows the average number of concurrent users of \meek\ with Tor
-since close to the beginning of development.
-A measurement of 5, for example, means that there were on average five
-simultaneous users of the system at any time during the day.
-The measurements come from the Tor Metrics Portal~\cite{metrics-meek},
-which aggregates statistics reported by Tor relays.
-The number of users is estimated by counting the number
-of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
-% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by \meek.
-
-[Blinded circumvention tool]
-% ANON
-% Psiphon
-began their deployment of \meek\ in June~2014.
-Figure~\ref{fig:clients-psiphon3} shows the number
-of unique daily users of \meek%
-,
-% ANON
-% with Psiphon,
-estimated through clients' self-reporting of their most recent connection date.
-The developers tell us that the drop that occurs
-in the middle of June was not caused by a blocking event,
-but rather an unblocking event that made \meek\ unnecessary for some users.
-Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
-are not directly comparable because they count slightly different things,
-it is clear that meek-with-%
-[blinded circumvention tool],
-% ANON
-% Psiphon,
-with its thousands of daily users,
-is much more widely used than meek-with-Tor, which has not yet seen a formal release.
-
-Our experimental Tor Browser releases have all been based on Google with App Engine.
-Support for CloudFront was not realized until late July.
-We are running the backends on paid accounts of these services for use by the public.
-The cost for bandwidth on App Engine is \$0.12 per gigabyte,
-with one gigabyte free each day.
-The total App Engine bill so far has been \$2.07,
-with most days' usage being below the billable threshold.
-There has not yet been enough use of CloudFront to cost anything.
-
-A longer-term goal is to find a way to fund continued operation
-if \meek\ becomes popular.
-Although some of the systems listed in Section~\ref{sec:survey}
-are inexpensive enough that some users could upload their own fronting backend,
-thereby diffusing costs,
-we believe that an organization operating a backend for the use of the public
-has compelling usability advantages.
-With client software configured to use the public backend by default,
-there is nothing for the user to upload and no out-of-band communication is needed before getting
-started---when everything works it offers circumvention without configuration.
-
-% The number of parties able to analyze users' traffic patterns is somewhat increased:
-% the path from user to Tor bridge now includes App Engine and the web app operators,
-% in addition to the ISP and intermediate routers that were there before.
-% On the other hand, the Tor bridge no longer gets to see users' IP addresses:
-% all it sees are many connections from App Engine.
-
-\section{Discussion}
-\label{sec:discussion}
-
-Domain fronting derives part of its unblockability from the
-high collateral damage of blocking the fronted-through domain.
-Fronting through \urll{www.google.com} to App Engine, for example,
-is making a bet that the censor will lack the temerity to block Google.
-The Great Firewall of China called our bluff in June of 2014,
-when it blocked access to all Google services~\cite{cn-google-block}.
-In 2012, the government of Pakistan blocked all of YouTube
-in order to restrict access to one video,
-and in 2011, the government of Egypt briefly ``turned off the net'' completely.
-% http://www.washingtonpost.com/business/economy/youtube-blocked-in-pakistan/2012/09/17/30081fa2-00ea-11e2-b257-e1c2b3548a4a_story.html
-% https://en.wikipedia.org/wiki/Internet_censorship_in_Egypt#2011_Internet_shutdown
-These examples show that blocking resistance is not an absolute,
-black-and-white security property;
-it can only be discussed in an economic context, relative to the costs borne
-by the censor and by users of a system.
-To be sure, blocking Google is an extreme measure,
-probably out of the reach of most censors.
-Blocking all of the fronting-capable services listed in
-Section~\ref{sec:survey} would be even harder.
-
-A censor could attack domain fronting by
-going directly to the operators of the intermediate web service
-and asking them either to break fronting
-(i.e., require SNI to be present and SNI and Host header to agree),
-or to get rid of their customers who are
-engaged in enabling circumvention (i.e., us).
-The censor could threaten to block the web service entirely otherwise.
-Whether the attack will succeed depends on the censor's
-and the web service's specific costs and motivations,
-so we cannot make any general statements.
-It is ultimately a question of who needs whom more:
-whether it hurts the web service or the censor more
-when the service is blocked.
-% Nothing works against a censor with sufficiently high tolerance for
-% collateral damage,
-% but we also don't have to defeat the world's
-% most powerful censor in order to be successful.
-% What doesn't work in one place may work in another.
-
-% Discuss TLS throttling as an attack.
-
-Domain fronting shares a potential weakness with decoy routing:
-the overt and covert destinations lie at the ends of different
-network paths.
-The difference in paths may create side channels---latency measurements for instance---that
-enable the censor to
-distinguish fronted traffic from traffic that is truly destined
-to the apparent destination.
-For example, a CDN can be expected to have responses
-to some fraction of requests already in cache,
-and respond to those requests with low latency.
-Fronted traffic, on the other hand, always continues all the way
-to the origin server after reaching the CDN (as if nothing were ever cached),
-resulting in a higher latency.
-Latency measurement was applied to decoy routing by Schuhard et~al.~\cite[Section~5]{ccs2012-decoys},
-who compared empirical round-trip-time distributions using a
-Kolmogorov--Smirnov test.
-% time between ChangeCipherSpec and ApplicationData
-
-The intermediate web service enjoys a privileged network position,
-from which it is able to monitor all circumvention traffic.
-Even if the censor doesn't know who the users are, the CDN knows.
-The web service has basically the same network visibility
-as the client's ISP would have, if the client were not circumventing.
-For this reason, domain fronting should be combined with another
-layer, for example Tor, that prevents the web service from
-observing the contents and destination of messages.
-There is additional risk when the client is browsing a web site
-controlled by the same service as the one they are fronting through,
-for example browsing YouTube while fronting through \urll{www.google.com}.
-Even with Tor, when this happens the web service gets to see
-both entry and exit traffic, and is in a position to
-perform traffic correlation attacks.
-The problem seems hard to counter, because the front domain needs
-to be popular in order to have high collateral damage,
-but popular domains are also the ones that people tend to want to go to.
-A possible mitigation is padding that lasts until
-the second hop of a three-hop Tor circuit,
-which would reduce the correlation between entry and exit traffic.
-% like what mjuarez is working on, mostly orthogonal to circumvention.
-
-% We implemented \meek\ as a pluggable transport~\cite{pt} for Tor.
-% Although it is possible to use the system with proxies other than Tor,
-% using Tor has some attractive features.
-% The pluggable transports infrastructure makes it relatively easy to prototype
-% a circumvention technique and connect it to a global proxy network.
-% We can treat confidentiality and integrity of tunneled communication
-% as a problem solved by Tor, which we don't need to solve separately.
-% Tor's extra proxy hops mean that the HTTP reflector (App Engine)
-% and the entry bridge do not have to be trusted.
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.40\linewidth}
-\includegraphics[width=\linewidth]{wire-sequential}
-\caption{Sequential}
-\label{fig:wire-sequential}
-\end{subfigure}
-\qquad
-\begin{subfigure}[t]{0.40\linewidth}
-\includegraphics[width=\linewidth]{wire-parallel}
-\caption{Parallel}
-\label{fig:wire-parallel}
-\end{subfigure}
-
-\caption{
-The nature of potential performance gain
-from sending fronted requests in parallel.
-}
-\label{fig:wire}
-\end{figure}
-
-We have assumed that the intermediate web service is
-outside the censor's domain of control,
-so that communication between the web service and Tor bridge
-doesn't have to be protected.
-What happens when the web service---a CDN edge server, for instance---is
-inside the network controlled by the censor?
-If the edge server forwards the request to the bridge
-as an ordinary HTTP request on the public Internet,
-then blocking it is as easy as blocking the IP address of the bridge.
-On the other hand, if the web service encapsulates
-the request and sends it encrypted, or over its own fast private network,
-to another server outside of the censor's control,
-then fronting will still work.
-
-The ``domainless'' fronting style, which omits SNI,
-is useful when there is no good front domain known for a web service.
-At least one CDN, Fastly, requires the domainless style.
-All current web browsers support SNI,
-so it is possible that lack of SNI could be used as a distinguisher.
-According to our communication with
-a representative of
-[a blinded organization observing many TLS connections],
-% ANON
-% the International Computer Science Institute's
-% certificate notary~\cite{icsi-notary},
-% which observes on the order of 50~million TLS connections daily,
-83.5\% of connections used SNI in June~2014.
-There are apparently enough connections without SNI
-that a censor will at least have to consider seriously
-the costs and benefits before deciding to block SNI-less TLS outright.
-
-The current implementation of \meek\ strictly serializes
-its HTTPS requests and responses,
-in order to keep chunks of the underlying TCP stream
-in the proper order.
-The unfortunate side effect of this simple approach
-is added latency that gets worse with longer round-trip times.
-In future work we plan to add an additional reliability layer,
-perhaps like the system of sequence numbers and acknowledgments used in OSS~\cite{oss},
-that would allow requests to be pipelined
-and cope with out-of-order delivery.
-Figure~\ref{fig:wire-sequential} shows how the current implementation works,
-and Figure~\ref{fig:wire-parallel} shows the nature of the performance
-improvement that could be gained with a reliability layer
-and parallel requests.
-% Would be useful for Iran-like session cutoff, independent of \meek.
-
-\meek's use of HTTPS is subject to the usual public key infrastructure
-and trust model.
-The browser running the HTTPS camouflage extension (Section~\ref{sec:browserextension})
-has a list of trusted certificate authorities.
-A censor that controls a certificate authority trusted by the browser
-is able to perform a man-in-the-middle attack
-between the client and the intermediate web service,
-and detect fronting by decrypting TLS and checking for specific Host headers.
-Such a censor would be able to detect circumvention,
-but still not read the client's plaintext because of the
-additional encryption and authentication of the tunneled Tor layer.
-It seems risky for the censor to risk being detected in
-a man-in-the-middle attack merely to confirm that a user is circumventing,
-but it is not impossible for a sufficiently powerful censor.
-The problem doesn't exist when the front domain is one
-that happens have its public key ``pinned'' in the headless browser,
-for instance when using the Chrome extension and fronting through
-\urll{www.google.com}.
-
-% \meek\ apart from Tor.
-% more risk for the proxy operator
-% can require people to run their own proxies à la GoAgent.
-% "Censorship implies surveillance"
-
-The key idea of \meek\ is domain fronting,
-but its HTTP tunneling ability is useful on its own.
-Another idea for deployment is to use
-thousands of simple HTTP reflectors on cheap web hosting
-(in place of domain fronting on a big CDN).
-The request-reflecting role of a CDN can
-be played by a PHP script, for example,
-or a special web server configuration.
-Their URLs unprotected by domain fronting,
-each reflector would be easily blockable individually,
-so there would need to be sufficiently many that
-a censor could not block them all.
-This deployment model is essentially the same as with
-ordinary Tor bridges: have lots of volunteer-operated bridges
-and make it hard to enumerate them all.
-The advantage that an HTTP transport would have
-is that it is easier for a volunteer to upload a PHP file to a web host
-than to set up and maintain a Tor bridge.
-
-\section{Summary}
-\label{sec:summary}
-
-We have presented domain fronting,
-an HTTPS technique that uses different domain names
-at different communication layers in
-order to hide the remote endpoint of a communication.
-We implemented \meek,
-a pluggable transport for Tor.
-We show that it resists common methods of blocking,
-and begin an investigation into its
-resistance against more subtle and expensive means of traffic analysis.
-We discuss the results of an initial deployment.
-% ANON
-% in both Tor and Psiphon.
-
-[Links to source code omitted for anonymous submission.]
-% ANON
-% \meek\ has a home page at
-% \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
-% Our source code is in the Git repository at
-% \url{https://git.torproject.org/pluggable-transports/meek.git}.
-% All our programs are free software.
-
-% As of version 0.9 (June~19, 2014), the source code consists of
-% about 1,100 lines of Go for the client programs,
-% 400 lines for \meekserver, and
-% 100 lines for the reflector application for App Engine.
-% Each of the browser extensions
-% (one for Firefox, one for Chrome)
-% is about 400 lines of JavaScript.
-
-% ANON
-% \section*{Acknowledgments}
-
-% We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
-% Special thanks go to the members of the tor-qa and tor-dev mailing lists
-% who responded to our design ideas, reviewed source code, and tested our prototypes.
-% Thanks to Psiphon~Inc. for help with design and development, and for providing user count estimates.
-% George Kadianakis
-% Georg Koppen
-% Lunar
-% Yawning Angel
-% Ox from Lantern.
-% Johanna Amann for getting the fraction of SNI from ICSI notary:
-%   https://trac.torproject.org/projects/tor/ticket/12208#comment:5
-% Arlo Breault (flashproxy-reg-appspot)
-
-%%%%%%%
-
-% HTTPS or not on the App Engine--bridge link.
-% HTTPS obscures session ids, equivalent to obscuring TCP connections in other transports.
-% Increases latency a lot: \approx 100 ms increased to \approx 350 ms when I tried it in March 2014.
-
-\bibliographystyle{IEEEtran}
-\bibliography{meek}
-
 \end{document}

### 2014-11-23 docs/meek.tex
Some rewriting.

@@
 a pluggable transport for Tor.
-\meek\ combines fronting with an HTTP-based tunneling proxy.
-The \meek\ server's external interface is that of an ordinary web server.
-Domain fronting enables a client to reach the server, which is presumed blocked by the censor.
-The server receives HTTP requests, decodes them, and feeds their payloads into a Tor relay,
-returning downstream data in the HTTP response.
-A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
-We describe the results of an initial deployment.
-\meek, or something based on it,
-has been adopted by other circumvention systems including
-[blinded for anonymous submission].
+\meek\ combines fronting with an HTTP-based tunneling proxy
+that decodes a sequence of HTTP requests and feeds their contents into Tor.
+A censor sees only a sequence of HTTPS requests to an allowed domain.
+We describe our experience with deploying \meek.
+% \meek, or something based on it,
+% has been adopted by other circumvention systems including
+% [blinded for anonymous submission].
 % ANON
@@
 
-Hiding the endpoint and obscuring byte patterns are important parts of blocking-resistant communication,
+Hiding the endpoint and obscuring byte patterns are important parts of blockinging resistance,
 but there are other, more subtle considerations.
-We describe what we have done to disguise other traffic ``tells'' in \meek,
-such as using a real web browser as a tool for making fronted HTTPS requests,
-in order to disguise meek's TLS fingerprint.
+We describe what we have done to disguise traffic ``tells'' in \meek,
+including using a real web browser to make fronted HTTPS requests
+in order to disguise the TLS fingerprint.
 We argue that these measures, combined with domain fronting, increase the censor's effort
-beyond simple one-shot blocking techniques such as IP address blocking, and into
+beyond simple one-shot blocking techniques such as IP address blacklisting, and into
 the realm of more expensive, less reliable statistical tests.

### 2014-11-23 docs/clients-meek.R
Trim horizontal range of meek-clients graph.

@@ -7,11 +7,12 @@ data <- read.csv("clients-meek.csv", colClasses=colClasses)
 # https://stackoverflow.com/questions/6058677/how-to-create-na-for-missing-data-in-a-time-series/6059113#6059113
 daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
-p <- ggplot(data, aes(x=date, y=clients))
-# p <- p + geom_vline(xintercept=as.numeric(as.Date(c("2014-02-18", "2014-04-11", "2014-04-18", "2014-04-25", "2014-05-07", "2014-05-08"))), color="red")
-p <- p + geom_bar(stat="identity", width=1.1) + xlab(NULL) + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + scale_y_continuous(breaks=0:10, minor_breaks=NULL) + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
+# Exclude today, because it reflects a not-yet-settled value.
+p <- ggplot(data[data$date >= as.Date("2014-08-01") & data$date < Sys.Date(), ], aes(x=date, y=clients))
+p <- p + geom_bar(stat="identity", width=1.1) + xlab(NULL) + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
 ggsave("clients-meek.pdf", width=4, height=1.4, units="in")
 
+# p <- p + geom_vline(xintercept=as.numeric(as.Date(c("2014-02-18", "2014-04-11", "2014-04-18", "2014-04-25", "2014-05-07", "2014-05-08"))), color="red")
 # 2014-02-18 [tor-qa] Please test experimental bundles with meek transport (3.5.2.1-meek-1)
 # https://lists.torproject.org/pipermail/tor-qa/2014-February/000340.html
 # 2014-04-11 [tor-qa] 3.5.4-meek-1 (meek bundles with browser TLS camouflage)

### 2014-11-23 docs/meek.tex
Trimming, revisions.

@@
 
-\begin{figure}
-\includegraphics[width=\linewidth]{clients-psiphon3}
-\caption{
-Daily unique users of \meek\ with
-[blinded circumvention tool]
-% ANON
-% Psiphon
-(note vertical axis).
-The decrease at the end of June
-was caused by an unblocking event that made \meek\ unnecessary for some users.
-}
-\label{fig:clients-psiphon3}
-\end{figure}
+% \begin{figure}
+% \includegraphics[width=\linewidth]{clients-psiphon3}
+% \caption{
+% Daily unique users of \meek\ with
+% [blinded circumvention tool]
+% % ANON
+% % Psiphon
+% (note vertical axis).
+% The decrease at the end of June
+% was caused by an unblocking event that made \meek\ unnecessary for some users.
+% }
+% \label{fig:clients-psiphon3}
+% \end{figure}
 
@@
 since close to the beginning of development.
-A measurement of 5, for example, means that there were on average five
-simultaneous users of the system at any time during the day.
+A measurement of 500, for example, means that there were on average 500
+users of the system at any given time during the day.
 The measurements come from the Tor Metrics Portal~\cite{metrics-meek},
@@
 
-[Blinded circumvention tool]
-% ANON
-% Psiphon
-began their independent deployment of \meek\ in June~2014.
-Figure~\ref{fig:clients-psiphon3} shows the number
-of unique daily users of \meek%
-,
-% ANON
-% with Psiphon,
-estimated through clients' self-reporting of their most recent connection date.
-The developers tell us that the drop that occurs
-in the middle of June was not caused by a blocking event,
-but rather an unblocking event that made \meek\ unnecessary for some users.
-Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
-are not directly comparable because they count slightly different things,
-it is clear that meek-with-%
-[blinded circumvention tool],
-% ANON
-% Psiphon,
-with its thousands of daily users,
-is much more widely used than meek-with-Tor, which has not yet seen a formal release.
+% [Blinded circumvention tool]
+% % ANON
+% % Psiphon
+% began their independent deployment of \meek\ in June~2014.
+% Figure~\ref{fig:clients-psiphon3} shows the number
+% of unique daily users of \meek%
+% ,
+% % ANON
+% % with Psiphon,
+% estimated through clients' self-reporting of their most recent connection date.
+% The developers tell us that the drop that occurs
+% in the middle of June was not caused by a blocking event,
+% but rather an unblocking event that made \meek\ unnecessary for some users.
+% Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
+% are not directly comparable because they count slightly different things,
+% it is clear that meek-with-%
+% [blinded circumvention tool],
+% % ANON
+% % Psiphon,
+% with its thousands of daily users,
+% is much more widely used than meek-with-Tor, which has not yet seen a formal release.
 
@@
 \label{sec:ciphersuites}
-
-Figure~\ref{fig:ciphersuites} illustrates the need for camouflage at the TLS layer.
-Even though the TLS application data is effectively hidden by encryption,
-the plaintext parts of TLS reveal information about the implementation.
-The TLS must not be easily identified as belonging to a circumvention tool.
 
@@
 Selected differences in ClientHello messages in three different TLS implementations.
+This figure illustrates the need for camouflage at the TLS layer.
+Even though the TLS application data is effectively hidden by encryption,
+the plaintext parts of TLS reveal information about the implementation.
+The TLS must not be easily identified as belonging to a circumvention tool.
 }

### 2014-11-23 docs/meek.tex
edits

@@
 subject to a bandwidth limit of 50 gigabytes per month.
+
+Microsoft Azure~\cite{azure}
+is a cloud computing platform that features a CDN.
+Similarly to CloudFront, users get automatically generated subdomains
+of \urll{vo.msecnd.net},
+all of which can front for each other.
+The CDN works only for Azure domains, however,
+so as with App Engine, it is necessary to run a trivial reflector app
+that merely forwards requests out of Azure toward an external proxy.
+There are other front domain names, like \urll{ajax.aspnetcdn.com},
+that may offer high collateral damage.
 
@@
 to keep a circumvention system running on it in the long term.
-
-Microsoft Azure~\cite{azure}
-is a cloud computing platform that features a CDN.
-Similarly to CloudFront, users get automatically generated subdomains
-of \urll{vo.msecnd.net},
-all of which can front for each other.
-There are other front domain names, like \urll{ajax.aspnetcdn.com},
-that may offer high collateral damage.
 
@@
 Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
-Most users who use Tor use it with Tor Browser~\cite{torbrowser},
+Our target for deployment is Tor Browser~\cite{torbrowser},
 a customized version of Firefox that is
@@
 Tor Browser has an easy interface for selecting pluggable transports.
-We made a series of experimental releases of Tor Browser featuring \meek,
-releasing the first one on February~18.
-[Some details of deployment are omitted for anonymous submission.]
 % ANON
+% [Some details of deployment are omitted for anonymous submission.]
+% We made a series of experimental releases of Tor Browser featuring \meek,
+% releasing the first one on February~18.
 % On April~18 we made the first release featuring the browser camouflage
@@
 
+We have so far deployed on three backends:
+Google App Engine,
+Amazon CloudFront,
+and Microsoft Azure.
+Figure~\ref{fig:clients-tor} shows the daily average number of concurrent users of \meek.
+(A measurement of 500, for example, means that there were on average 500
+users of the system at any given time during the day.)
+The App Engine backend was established in February;
+CloudFront in July;
+and Azure in October.
+Also in Figure~\ref{fig:clients-tor} is a table of monthly costs for each web service.
+The pricing for cloud services is complicated,
+depending not only on bandwidth but also on geographical region and other factors.
+For example CloudFront charges per request as well as per gigabyte,
+and about 54\% of the CloudFront bill for October was for requests.
+App Engine charges extra when it has to run multiple instances
+of an app's code to cope with load;
+about 15\% of October's App Engine bill was for such ``instance hours.''
+% These and other cost details are summarized in a mailing list post~\cite{meek-costs-201410}.
+The App Engine and CloudFront backends are running on accounts
+that provide a limited amount of free bandwidth,
+but current use greatly exceeds the free thresholds.
+Azure service is being donated and so has not yet cost anything.
+The total cost so far has been \$187.13,
+but this number is expected to more than double in November and continue to increase.
+
 \begin{figure}
+\centering
 \includegraphics[width=\linewidth]{clients-meek}
+\begin{tabular}{l r r r}
+       &App Engine &CloudFront&  Azure \\
+\hline
+Jan--Jul &  \$2.72 &   \$0.00 & \$0.00 \\
+Aug      &  \$1.56 &   \$3.10 & \$0.00 \\
+Sep      &  \$4.02 &   \$4.59 & \$0.00 \\
+Oct      & \$40.85 & \$130.29 & \$0.00 \\
+\hline
+total    & \$49.15 & \$137.98 & \$0.00 \\
+\end{tabular}
 \caption{
-Concurrent users of the \meek\ pluggable transport for Tor.
+Concurrent users of the \meek\ pluggable transport
+and month-by-month operational costs.
+The total cost to date is \$187.13.
+% ANON
+% The large increase of users on October~15 coincides with
+% the release of Tor Browser~4.0,
+% the first release to make meek easily available.
+Azure CDN service is currently being donated as part of a research grant.
+The user estimates come from the Tor Metrics Portal~\cite{metrics-meek,counting-daily-bridge-users}.
 }
@@
 
-Figure~\ref{fig:clients-tor} shows the average number of concurrent users of \meek\ with Tor
-since close to the beginning of development.
-A measurement of 500, for example, means that there were on average 500
-users of the system at any given time during the day.
-The measurements come from the Tor Metrics Portal~\cite{metrics-meek},
-which aggregates statistics reported by Tor relays.
-The number of users is estimated by counting the number
-of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
-% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by \meek.
+%  &\$49.15 & \$137.98 & \$0.00 & \$187.13 &  \\
+
+% which aggregates statistics reported by Tor relays.
+% The number of users is estimated by counting the number
+% of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
 
@@
 
-Our experimental Tor Browser releases have all been based on Google with App Engine.
-Support for CloudFront was not realized until late July.
-We are running the backends on paid accounts of these services for use by the public.
-The cost for bandwidth on App Engine is \$0.12 per gigabyte,
-with one gigabyte free each day.
-The total App Engine bill so far has been \$2.07,
-with most days' usage being below the billable threshold.
-There has not yet been enough use of CloudFront to cost anything.
-
-A longer-term goal is to find a way to fund continued operation
-if \meek\ becomes popular.
+As users increase, it becomes more pressing
+to find a way to sustain continued operation.
 Although some of the systems listed in Section~\ref{sec:survey}
-are inexpensive enough that some users could upload their own fronting backend,
-thereby diffusing costs,
-we believe that an organization operating a backend for the use of the public
-has compelling usability advantages.
-With client software configured to use the public backend by default,
-there is nothing for the user to upload and no out-of-band communication is needed before getting
-started---when everything works it offers circumvention without configuration.
+are inexpensive enough that some users could upload their own fronting backend
+and bear their own costs,
+we believe that there are compelling usability advantages
+to operating a centralized backends for the use of the public.
+Client software can ship with preconfigured domain names.
+There is nothing for the user to upload and no out-of-band bootstrapping communication is needed.
 

### 2014-11-23 docs/meek.tex
edits

@@
 
-Domain fronting derives part of its unblockability from the
+Domain fronting derives its strength from the
 high collateral damage of blocking the fronted-through domain.
-Fronting through \urll{www.google.com} to App Engine, for example,
-is making a bet that the censor will lack the temerity to block Google.
-The Great Firewall of China called our bluff in June of 2014,
-when it blocked access to all Google services~\cite{cn-google-block}.
+To front through \urll{www.google.com} to App Engine, for example,
+is to make a bet that the censor will lack the temerity to block Google.
+Different censors will differ in their aversion to collateral damage;
+blocking an important service is a costly measure
+that harms users not involved in circumvention and perhaps a society's economic well-being,
+and not all censors can afford to do it.
+The Great Firewall of China took the unprecendented step
+of blocking all Google services in June 2014~\cite{cn-google-block,cn-google-block-greatfire},
+and has since blocked certain CDN domains that were used to host
+mirrors of censored web sites, even at the cost of damaging other unrelated sites~\cite{cn-edgecast-block-greatfire}.
 In 2012, the government of Pakistan blocked all of YouTube
 in order to restrict access to one video,
-and in 2011, the government of Egypt briefly ``turned off the net'' completely.
+and in 2011, the government of Egypt briefly completely ``turned off the net.''
 % http://www.washingtonpost.com/business/economy/youtube-blocked-in-pakistan/2012/09/17/30081fa2-00ea-11e2-b257-e1c2b3548a4a_story.html
@@
 by the censor and by users of a system.
-To be sure, blocking Google is an extreme measure,
-probably out of the reach of most censors.
-Blocking all of the fronting-capable services listed in
-Section~\ref{sec:survey} would be even harder.
+We can at least roughly quantify the cost of blocking a domain-fronting system:
+it is the minimum cost of
+blocking the front domain with resultant collateral damage,
+conducting a traffic-analysis attack to distinguish
+circumvention from ordinary traffic, or
+conducting some other unconsidered attack, for example physical surveillance of Internet users.
+As long as all these costs are high,
+domain fronting is difficult to block.
 

### 2014-11-23 docs/meek.tex
spell check

@@
 
-Hiding the endpoint and obscuring byte patterns are important parts of blockinging resistance,
+Hiding the endpoint and obscuring byte patterns are important parts of blocking resistance,
 but there are other, more subtle considerations.
@@
 and not all censors can afford to do it.
-The Great Firewall of China took the unprecendented step
+The Great Firewall of China took the unprecedented step
 of blocking all Google services in June 2014~\cite{cn-google-block,cn-google-block-greatfire},

### 2014-12-21 docs/meek.tex
switch to non-microscopic IEEEtran class, with placeholder for even-larger 11pt version
Comment about Google pullout of Russia.
light edits/comments up through end of Section 4; more pending

@@
-\documentclass{sig-alternate}
+% \documentclass{sig-alternate}
+\documentclass{IEEEtran}
+% \documentclass[11pt]{IEEEtran}
 \usepackage{txfonts}
@@
 \usepackage{xspace}
+\usepackage{color}
 
 % Turn off ACM copyright block.
-\toappear{}
+% \toappear{}
 
@@
 
+\newcommand{\note}[1]{{\textcolor{red}{[\textit{#1}]}}}
+\newcommand{\vp}[1]{\note{#1 --VP}}
+
 % https://tex.stackexchange.com/questions/113338/use-sans-serif-in-a-verbatim-environment/113339#113339
@@
 \begin{abstract}
+\vp{This abstract is quite long}
 We describe ``domain fronting,'' an application-layer technique
@@
 then blocking fronted traffic means blocking an entire web service,
-with resulting expensive collateral damage.
+resulting in expensive collateral damage.
 
@@
 a pluggable transport for Tor.
-\meek\ combines fronting with an HTTP-based tunneling proxy
+\meek\ combines
+\vp{What is the point of the backslash-space after \meek here?  The
+backslace-xspace already takes care of the trailing whitespace.}
+fronting with an HTTP-based tunneling proxy
 that decodes a sequence of HTTP requests and feeds their contents into Tor.
@@
 to prevent access to information by the network users under their control.
-In response, those users use technical and social means
+In response, those users employ technical and social means
 to gain access to the forbidden information.
-What has emerged is an ongoing conflict between censor and censored,
+We have seen
+an ongoing conflict emerge between censor and censored,
 with advances on both sides, more subtle evasion being countered by more powerful detection.
 
-What we as circumventors have in our favor is the censor's
-distaste for ``collateral damage,''
+We as circumventors have in our favor the censor's
+distaste for ``collateral damage'':
 accidental overblocking committed in the course of trying to censor something else.
 One way to win against censorship is to entangle circumvention traffic
-with ordinary Internet traffic in a way that both must be blocked together,
+with ordinary Internet traffic such that both must be blocked together,
 or not at all.
@@
 behind an HTTPS frontend server.
-These include such high--collateral damage infrastructure as
+These include such high-collateral-damage infrastructure as
 big content delivery networks (CDNs)
 and Google's panoply of services---a nontrivial fraction of the web.
-See Section~\ref{sec:survey} for a list of suitable services.
+(See Section~\ref{sec:survey} for a list of suitable services.)
 Domain fronting can be used to tunnel traffic
@@
 Usually, the same domain name appears in all three places.
-But in a domain-fronted request,
+In a domain-fronted request, however,
 the DNS query and SNI carry one name (the ``front domain''),
@@
 
-The censor may block neither the DNS request nor the SNI without
+The censor can block neither the DNS request nor the SNI without
 collaterally blocking the front domain.
@@
 Here, an HTTPS request for \urll{www.google.com} has a Host header for
-\urll{maps.google.com}. The HTML in the response is that of Google Maps.
+\urll{maps.google.com}, even though the SNI in the TLS handshake specifies
+\texttt{www.google.com}.
+The HTML in the response is that of Google Maps.
 
@@
 like the user is browsing an HTTPS site by its IP address,
-or using a web client that doesn't support SNI.
+or using a web client that does not support SNI.
 Domainless fronting can be useful when there is no known front domain
@@
 We have developed domain fronting into a full-fledged circumvention system called \meek,
-implemented as pluggable transport~\cite{pt} for Tor.
+implemented as a pluggable transport~\cite{pt} for Tor.
 \meek\ combines fronting with an HTTP-based tunneling proxy:
@@
 and Section~\ref{sec:discussion} describes other possible deployments.
+\vp{It's confusing here having out-of-order references to sections.  This
+also occurs below}
 In addition to the Tor pluggable transport,
@@
 
-Domain fronting and HTTPS take care of two big circumvention challenges,
+Domain fronting and HTTPS address two major circumvention challenges,
 those of hiding the destination and of obscuring the contents of a message.
@@
 
+\vp{Seems this should go in the next section instead}
 To our knowledge,
@@
 An address-blocking censor forbids all communication with certain
-addresses, for example IP addresses and domain names, whatever the contents of the communication may be.
+addresses, for example IP addresses and domain names, regardless of
+the contents of the communication.
 A savvy censor will use both means of censorship, and
@@
 Then a connection is successful, the server can be blacklisted.
+\vp{Try not to begin sentences with ``Then'' (or with conjunctions like
+``But'').  Also, the writing has a lot of passive voice here.}
 Active probing is a precise means of identifying whether a server belongs to a circumvention system,
@@
 payloads are indistinguishable from a uniformly random byte stream.
-Good examples of look-like-nothing transports are
+Examples of look-like-nothing transports are
 obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
 Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
-Both obfs2 and obfs3 work by superenciphering an underlying stream,
+Both obfs2 and obfs3 work by superenciphering
+\vp{not clear here what superenciphering means; presumably, it's a reference
+to encrypting a stream that's already encrypted, but the reader has to pause
+and work that out}
+an underlying stream,
 using a key exchange that has no plaintext components.
@@
 until the client proves knowledge of a shared secret.
+\vp{Say, has there been any work on using port-knocking to resist active
+probing?}
 obfs4~\cite{obfs4}
@@
 in order to disrupt a covert channel, without much harming ordinary VoIP calls.
+\vp{The above could be compressed somewhat to save room}
 
@@
 so that anyone can learn a few bridges, but it is hard to learn all of them.
-BridgeDB uses captchas and other rate-limiting measures,
+BridgeDB uses CAPTCHAs and other rate-limiting measures,
 and over short time periods,
@@
 \meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
-A quirk of the browser proxy model is that
+A drawback with flash proxy's use of the browser is that
 the client must be able to receive a TCP connection; in particular it
@@
 rather than in the Host header.
-
+\vp{Sketch the limitations of this approach}
+
+\vp{Lots of passive in this paragraph}
 Decoy routing~\cite{decoyrouting}
@@
 Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
-Decoy routing asks friendly ISPs to deploy special routers that lie
+Decoy routing asks friendly ISPs to deploy special routers that reside
 on network paths between censored users and uncensored ``decoy'' Internet destinations.
@@
 while fronting uses the HTTP Host header, encrypted within HTTPS.
-Fronting has the advantage that it doesn't require knowing cooperation by network intermediaries.
+Fronting has the advantage that it does not require active cooperation by network intermediaries.
 
@@
 \urll{https://s3.amazonaws.com/bucketname/filename},
+\vp{should ``filename'' in the URL be italicized?  It sounds like it's
+a generic placeholder, not a literal}
 the censor only gets to ``see'' the generic domain part, ``\urll{s3.amazonaws.com}''.
@@
 domain fronting with App Engine.
+\vp{Was it literally an inspiration, or was it concurrent development?
+I thought it was more the latter.}
 Traffic is fronted by the Google frontend server,
@@
 and delivered to its destination by a specialized app running on App Engine.
-GoAgent doesn't use an additional general-purpose proxy after fronting;
+GoAgent does not use an additional general-purpose proxy after fronting;
 rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
@@
 and the contents of all communications are revealed to Google.
-Users of GoAgent generally upload their own personal copy of the proxy code to App Engine,
+Users of GoAgent generally upload
+\vp{``generally'' upload---what's their practical alternative?}
+their own personal copy of the proxy code to App Engine,
 which is free of charge to use as long as they do not exceed a bandwidth quota.
@@
 above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
-Use of GoAgent in China was disrupted starting in the beginning of June~2014
+Use of GoAgent in China was disrupted starting in the beginning of June~2014,
 when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
 \meek\ over App Engine was similarly affected.
+\vp{Add mention of what \meek\ platforms still worked.}
 % Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.
@@
 Cloud-Entry~\cite{cloud-entry} is somewhat similar to GoAgent.
-It also uses App Engine, but uses a socket API rather than a URL fetch API,
+It also uses App Engine, but via a socket API rather than a URL fetch API,
 in order to support protocols other than HTTP and HTTPS.
-Cloud-Entry has the same problem with NAT that flash proxy does,
+Cloud-Entry has the same NAT problem as flash proxy,
 because the proxy tries to connect back to the client with a socket.
@@
 % Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.
+\vp{Explain Pisphon's relevance to meek}
 
@@
 
-The model includes four actors:
+Our threat model includes four actors:
 the censor,
@@
 and the destination Tor bridge.
-Circumvention is achieved when the client evades the censor to reach
+\vp{Update this when considering more general services than just
+Tor bridges.}
+We achieve
+circumvention when the client evades the censor to reach
 the bridge,
@@
 The intermediate web service does not need to cooperate with either,
-except to the extent that it doesn't collude with the censor.
+except to the extent that it does not collude with the censor.
 % The censor's goal is to prevent circumvention.
 
-The censor controls a network and the links into and within it.
-The censor is able to inspect traffic flowing across all links under its control
-and may block or allow any packet.
-The censor may inject and replay traffic, and
+The censor controls a (generally national)
+network and the links into and within it.
+The censor can inspect traffic flowing across all links under its control
+and can block or allow any packet.
+The censor can inject and replay traffic, and
 operate its own clients and servers.
@@
 are uncontrolled by the censor.
-The censor does not control a TLS certificate authority;
+The censor does not control a trusted TLS certificate authority;
 specifically it cannot man-in-the-middle an HTTPS session
@@
 
-Section~\ref{sec:discussion} shows what happens when some
+Section~\ref{sec:discussion} analyzes what happens when some
 of the threat model's assumptions are violated;
@@
 when the intermediate web service's frontend server is inside the censor's network
-and when the censor controls a certificate authority.
+and when the censor controls a trusted certificate authority.
 
@@
 
-The components of the system are shown in Figure~\ref{fig:architecture}.
+We show the components of the system in Figure~\ref{fig:architecture}.
 The parts that are new in \meek\
 are the programs \meekclient and \meekserver,
+\vp{It would help to use a different typeface for \meekserver, etc.}
 which are \meek's interface with Tor.
@@
 look like that of a browser; see Section~\ref{sec:browserextension}.
+\vp{This last about TLS fingerprint doesn't need to be introduced here}
 
@@
 it receives and forwards it to a remote instance of \meekserver.
-App Engine cannot directly run a Tor bridge,
+App Engine cannot
+\vp{explain why it can't}
+directly run a Tor bridge,
 so we bounce the requests to somewhere that can.
@@
 into a sequence of HTTP requests and responses.
-The body of each HTTP request and HTTP response carries
+The body of each HTTP request and response carries
 a small chunk of upstream or downstream communication.
@@
 are correctly reassembled at the other end,
-in order and without gaps or duplicates.
+in order, and without gaps or duplicates.
 \meek\ takes a naive approach: requests and responses are strictly serialized.
-The client doesn't send a second chunk of data
-(i.e, make another HTTPS request) until it has
+The client does not send a second chunk of data
+(i.e., make another HTTPS request) until it has
 received the response to its first.
@@
 between every send.
-Section~\ref{sec:discussion} proposes a more efficient encoding
+Section~\ref{sec:discussion} discusses a more efficient encoding
 that would enable multiple requests in parallel.
@@
 (source~IP, source port, dest~IP, dest~port) tuple,
-but that doesn't work for \meek, for two reasons:
+but that does not work for \meek, for two reasons:
 the source IP of the requests is that of the intermediate web service,
@@
 so the source port is always changing.
-Instead, each client generates a random 256-bit session ID for each new Tor stream,
+Instead, each client generates a random 256-bit
+\vp{it seems like overkill to use 256 bits for this $\ldots$}
+session ID for each new Tor stream,
 which it sends with its requests in a special
@@
 The polling interval starts short (100~ms) and grows exponentially
-up to a maximum of 5~s.
+up to a maximum of 5~s.  \vp{Do you jitter the polling?}
 % ANON
@@
 uses streaming HTTP responses over persistent HTTP connections.
+\vp{It would help to have a timing diagram to illustrate this.}
 When the server sends a response, it keeps the connection open,
@@
 This second technique is especially beneficial for bulk downloads,
-but doesn't work on all services:
-notably Google App Engine doesn't support streaming of this kind.
+but does not work on all services:
+notably Google App Engine does not support this kind of streaming.
 
@@
 which adds an HTTP header whose length is about 400 bytes
-(varying slightly depending on the length of the Host field).
+\vp{yikes, that's a lot of overhead $\ldots$}
+(varying slightly depending on the length of the Host
+\vp{It would help to put textual protocol elements in another typeface,
+such as \texttt{Host}; you could define a backslash-header macro for this}
+field).
 The HTTP request goes into its own TLS Application Data record when it becomes HTTPS,
@@
 \end{center}
+\vp{Not clear this table is worth the real estate}
 
@@
 Bulk uploads and downloads tend to have less overhead, bunching many cells at once.
+\vp{It might be helpful to have a table showing upload/download size/efficiency}
 Streaming HTTP responses, when they are possible, reduce overhead further,
@@
 but they are sent only when the connection is idle,
-so they don't affect upload or download speed.
+so they do not affect upload or download speed.
 As is discussed in Section~\ref{sec:trafficanalysis},
@@
 the client first goes to the intermediate web service.
+\vp{Aren't there also additional RTTs?}
 How much latency the extra hop adds depends, of course, on the network location
@@
 It runs invisibly in the background in a separate process,
-doesn't display a user interface,
+does not display a user interface,
 and shares no state with the user's browser.
@@
 % so we had to reenable them in the headless browser.
-% (Doing so doesn't harm Tor Browser's anonymity:
+% (Doing so does not harm Tor Browser's anonymity:
 % if session tickets are used, they are used only on the circumvention layer
@@
 ported \meekclient to Android,
-they didn't use a browser as camouflage,
+they did not use a browser as camouflage,
 but rather made all HTTPS requests with the standard Android HTTP API.
@@
 a pool of popular domain names;
-or to use ``domainless'' fronting that doesn't send SNI.
+or to use ``domainless'' fronting that does not send SNI.
 % Though CloudFlare supports domain fronting,
@@
 For the purposes of censorship circumvention,
-one doesn't need to match exactly a ``typical'' traffic profile;
+one does not need to match exactly a ``typical'' traffic profile;
 only not to deviate from it too much.
@@
 % collateral damage,
-% but we also don't have to defeat the world's
+% but we also do not have to defeat the world's
 % most powerful censor in order to be successful.
-% What doesn't work in one place may work in another.
+% What does not work in one place may work in another.
+
+% Contrary example:
+% "Google slams Russia engineering office doors shut: The tech giant is planning to close its engineering office in Russia following a crackdown on Internet firms in the country."
+% http://www.zdnet.com/article/google-slams-russia-engineering-office-doors-shut/
 
@@
 who compared empirical round-trip-time distributions using a
-Kolmogorov--Smirnov test.
+Kolmogorov-Smirnov test.
 % time between ChangeCipherSpec and ApplicationData
@@
 from which it is able to monitor all circumvention traffic.
-Even if the censor doesn't know who the users are, the CDN knows.
+Even if the censor does not know who the users are, the CDN knows.
 The web service has basically the same network visibility
@@
 % We can treat confidentiality and integrity of tunneled communication
-% as a problem solved by Tor, which we don't need to solve separately.
+% as a problem solved by Tor, which we do not need to solve separately.
 % Tor's extra proxy hops mean that the HTTP reflector (App Engine)
@@
 so that communication between the web service and Tor bridge
-doesn't have to be protected.
+does not have to be protected.
 What happens when the web service---a CDN edge server, for instance---is
@@
 but it is not impossible for a sufficiently powerful censor.
-The problem doesn't exist when the front domain is one
+The problem does not exist when the front domain is one
 that happens have its public key ``pinned'' in the headless browser,

### 2014-12-21 docs/meek.tex
done with edit pass for lower-level tweaks/comments

@@
 in the DNS query,
-in the TLS Server Name Indication (SNI) extension~\cite[Section~3]{rfc6066},
-and in the HTTP Host header~\cite[Section~14.23]{rfc2616}.
+in the TLS Server Name Indication (SNI) extension~\cite[\S 3]{rfc6066},
+and in the HTTP Host header~\cite[\S 14.23]{rfc2616}.
 Usually, the same domain name appears in all three places.
@@
 We estimate the overhead when meek is used to transport Tor.
-Tor uses fixed-size cells of 514 bytes~\cite[Section~0.2]{tor-spec}.
+Tor uses fixed-size cells of 514 bytes~\cite[\S 0.2]{tor-spec}.
 Each cell is wrapped in a TLS Application Data record, which adds 29 bytes
@@
 distinguish fronted from non-fronted traffic.
-This section is about TLS fingerprinting,
-which is the censor's remaining easy distinguisher,
-and how we use a web browser with an unremarkable TLS fingerprint
+In this section we discuss addressing the problem of TLS fingerprinting,
+which is the censor's remaining easy distinguisher.
+We so by using a web browser with an unremarkable TLS fingerprint
 to disguise the HTTPS tunnel.
-Section~\ref{sec:trafficanalysis} is about more subtle and hard-to-apply forms of traffic analysis.
-
-The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}, and leaves
+Section~\ref{sec:trafficanalysis} analyzes
+more subtle and hard-to-apply forms of traffic analysis.
+
+The TLS handshake is largely plaintext~\cite[\S7.4]{rfc5246}, and leaves
 enough room for variation, for example in
@@
 and shares no state with the user's browser.
+\vp{Would be helpful to discuss what sort of overhead this incurs}
 
@@
 [blinded circumvention tool]
+\vp{does this need to be blinded?}
 % ANON
@@
 
-\section{A survey of fronting-capable\\web services}
+\section{A survey of fronting-capable web services}
 \label{sec:survey}
 
+\vp{This whole section should be beefed up with a deeper assessment.  Along
+these lines, it would help to include a summary table.}
 This section contains a brief survey of fronting-capable
@@
 that merely copies incoming requests to a Tor bridge hosted elsewhere.
-Fronting through App Engine is attractive in the case where
-\urll{appspot.com} is blocked---not unlikely,
-because of the ease of building a proxy there---but
-at least one other Google service is reachable.
-Applications that use less than one gigabyte of bandwidth daily
+Fronting through App Engine is attractive in the case where even though
+the censor blocks
+\urll{appspot.com}---which could well occur,
+because of the ease of building a proxy there---at least one
+other Google service remains reachable.
+Applications that use $< 1$~GB of bandwidth daily
 are free of charge,
@@
 
-Amazon CloudFront~\cite{cloudfront},
-not to be confused with CloudFlare,
+Amazon CloudFront~\cite{cloudfront}
+(not to be confused with CloudFlare; see below)
 is the CDN of Amazon Web Services.
@@
 CloudFront has a usage tier that is free of charge for a year,
-subject to a bandwidth limit of 50 gigabytes per month.
+subject to a bandwidth limit of 50~GB/month.
 
@@
 There are other front domain names, like \urll{ajax.aspnetcdn.com},
-that may offer high collateral damage.
-
-CloudFlare~\cite{cloudflare},
-not to be confused with CloudFront,
+that may provide entangling with high collateral damage.
+
+CloudFlare~\cite{cloudflare}
 is a CDN also marketed as protection against
@@
 or to use ``domainless'' fronting that does not send SNI.
+\vp{Would be quite valuable to more broadly assess the viability
+of using domainless fronting}
 % Though CloudFlare supports domain fronting,
@@
 Fastly~\cite{fastly} is a CDN.
-It is the only one of the services we tested in that
-that appears to enforce SNI:
+It is the only one of the services we tested that
+appears to enforce SNI consistency:
 if the SNI and Host do not match,
@@
 and active probing.
+\vp{sketch for the reader why it's resistant to active probing}
 We hope to force the censor to resort to measuring
@@
 and Google App Engine as the intermediate web service.
-The \meek\ trace is 687~megabytes in all
-and covers about 4.5 hours of network activity.
+The \meek\ trace is 687~MB
+and spans 4.5~hours of network activity.
 Our representative of ordinary HTTPS traffic
@@
 %Lawrence Berkeley National Laboratory (\lbl)
-a research lab [blinded as \lbl for anonymous submission],
+a large ($\approx$~4K~users)
+research lab [blinded as \lbl for anonymous submission],
 comprising data to and from TCP port 443 on any Google server.
 % Mention the non-google if it appears in a figure.
-The \lbl trace consists 313~megabytes of packet headers,
+The \lbl trace consists 313~MB of packet headers,
 not payloads, destined for TCP port 443 on any Google server.
 The original IP addresses were masked by being
-replaced by a counter before we received the trace.
+replaced by a counter before we analyzed the trace.
 
@@
 we see interesting probability concentrations on
-round numbers: 10~s, 60~s, 120~s, 180~s, and 240~s.
+round numbers: 10/60/120/180/240~seconds.
 We hypothesize that this phenomenon is caused by
@@
 According to our traffic trace, doing so will not disrupt more than 8\% of ordinary connections;
+\vp{It could though disrupt valuable large transfers, which might be quite
+important}
 whether that is an acceptable cost depends on the time threshold and the censor's
@@
 Duration-based blocking is favorable for the circumventor,
-because if the censor terminates connections after, say, 10 minutes,
-in any case that's 10 minutes of circumvention achieved,
+because if the censor terminates connections after, say, 10~minutes,
+in any case that represents 10~minutes of circumvention achieved,
 after which \meek\ can start a new connection
+\vp{well, it can't start a new connection if the censor's response is to block
+the client}
 and allow Tor to rebuild its circuits.
@@
 so there will be no effect on the client other than a brief delay
+\vp{couldn't you eliminate this by building the new circuit concurrently?
+that won't work if the censor blocks by IP rather than by connection;
+but you have that problem anyway particularly if the censor blocks the
+client rather than, or in addition to, the server}
 while a new HTTPS connection is established.
@@
 of a single client IP address.
+\vp{Not clear what consitutes a ``pale line''.  Try to ensure this
+works when printed in black-and-white.}
 The \lbl trace shows 2,745 unique clients and the \meek\ trace only one.
@@
 with some hosts briefly spiking up above 50 connections,
+\vp{Characterize in terms of distinct clients/IP~addresses, too}
 but the average case is very heavily skewed to smaller numbers.
@@
 We conclude that having a small number of concurrent connections is unremarkable.
+\vp{Could more explicitly frame this in terms of opportunity rather than
+just that it's unremarkable}
 
@@
 one does not need to match exactly a ``typical'' traffic profile;
+\vp{should discuss the theoretical threat of ``constellation'' attacks,
+i.e., where the censor concludes that the overall collective pattern
+of a user smells funny [not a threat that actually matters in practice!]}
 only not to deviate from it too much.
@@
 We have seen that censors prefer to use easy classifiers when they exist.
+\vp{This observation isn't backed up in the paper [or by citation].}
 By removing the easy ways, we increase the censor's cost.
@@
 Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
-Our target for deployment is Tor Browser~\cite{torbrowser},
+For deployment we target
+the Tor Browser~\cite{torbrowser},
 a customized version of Firefox that is
@@
 depending not only on bandwidth but also on geographical region and other factors.
-For example CloudFront charges per request as well as per gigabyte,
+For example CloudFront charges per request as well as per GB,
 and about 54\% of the CloudFront bill for October was for requests.
@@
 Azure CDN service is currently being donated as part of a research grant.
+\vp{It would be valuable to build up some sort of estimate of what it
+would cost if you didn't have the grant.}
 The user estimates come from the Tor Metrics Portal~\cite{metrics-meek,counting-daily-bridge-users}.
@@
 Domain fronting derives its strength from the
-high collateral damage of blocking the fronted-through domain.
+high collateral damage of blocking the domain used for the fronting.
 To front through \urll{www.google.com} to App Engine, for example,
@@
 We can at least roughly quantify the cost of blocking a domain-fronting system:
-it is the minimum cost of
-blocking the front domain with resultant collateral damage,
+it is the minimum cost of:
+blocking the front domain with resultant collateral damage;
 conducting a traffic-analysis attack to distinguish
-circumvention from ordinary traffic, or
+circumvention from ordinary traffic; or
 conducting some other unconsidered attack, for example physical surveillance of Internet users.
@@
 or to get rid of their customers who are
-engaged in enabling circumvention (i.e., us).
+engaged in enabling circumvention (e.g.,~us).
 The censor could threaten to block the web service entirely otherwise.
@@
 to some fraction of requests already in cache,
+\vp{should this discussion move into the previous section?}
 and respond to those requests with low latency.
@@
 resulting in a higher latency.
-Latency measurement was applied to decoy routing by Schuhard et~al.~\cite[Section~5]{ccs2012-decoys},
+Latency measurement was applied to decoy routing by Schuhard et~al.~\cite[\S 5]{ccs2012-decoys},
 who compared empirical round-trip-time distributions using a
@@
 but popular domains are also the ones that people tend to want to go to.
+\vp{Wouldn't one approach be to use multiple fronts, and pick which one
+to go to depending on to what domain the user wants to eventually arrive at?}
 A possible mitigation is padding that lasts until
 the second hop of a three-hop Tor circuit,
+\vp{not clear how this padding would work---needs discussion}
 which would reduce the correlation between entry and exit traffic.
@@
 then fronting will still work.
+\vp{Important to then assess which fronts indeed will do this}
 
@@
 [a blinded organization observing many TLS connections],
+\vp{I don't think this needs to be blinded}
 % ANON
@@
 additional encryption and authentication of the tunneled Tor layer.
-It seems risky for the censor to risk being detected in
+It seems risky for the censor to hazard being detected in
 a man-in-the-middle attack merely to confirm that a user is circumventing,
-but it is not impossible for a sufficiently powerful censor.
+but it is not out of the question for a sufficiently powerful censor.
 The problem does not exist when the front domain is one
@@
 than to set up and maintain a Tor bridge.
+\vp{Should also discuss backends that take users directly to content,
+rather than providing ingress to Tor.}
 

### 2015-01-10 docs/meek.tex
Can observe overhead from CDN invoices.
Need to update overhead estimates for #12778.
Do the xspace thing.

@@
 a pluggable transport for Tor.
-\meek\ combines
-\vp{What is the point of the backslash-space after \meek here?  The
-backslace-xspace already takes care of the trailing whitespace.}
+\meek combines
 fronting with an HTTP-based tunneling proxy
@@
 implemented as a pluggable transport~\cite{pt} for Tor.
-\meek\ combines fronting with an HTTP-based tunneling proxy:
+\meek combines fronting with an HTTP-based tunneling proxy:
 upstream data are transformed into a sequence of HTTP requests,
@@
 
-\meek\ has been built into an experimental release of Tor Browser,
+\meek has been built into an experimental release of Tor Browser,
 and has a small number of users.
@@
 In addition to the Tor pluggable transport,
-systems based on \meek\ are now used by other circumvention systems including
+systems based on \meek are now used by other circumvention systems including
 [blinded for anonymous submission].
@@
 
-% \meek\ is designed to have features attractive in a circumvention transport.
+% \meek is designed to have features attractive in a circumvention transport.
 % It is easy to use, not requiring the configuration of any bridge addresses.
@@
 appears in Section~\ref{sec:trafficanalysis}.
-The analysis is based on comparing traffic traces of \meek\
+The analysis is based on comparing traffic traces of \meek
 to samples of HTTPS traffic at a network router.
@@
 where flash proxy uses many cheap, disposable, individually blockable proxies,
-\meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
+\meek uses just a few high-value front domains on hard-to-block network infrastructure.
 A drawback with flash proxy's use of the browser is that
@@
 when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
-\meek\ over App Engine was similarly affected.
-\vp{Add mention of what \meek\ platforms still worked.}
+\meek over App Engine was similarly affected.
+\vp{Add mention of what \meek platforms still worked.}
 % Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.
@@
 % ANON
-% Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
+% Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
 Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
@@
 We show the components of the system in Figure~\ref{fig:architecture}.
-The parts that are new in \meek\
+The parts that are new in \meek
 are the programs \meekclient and \meekserver,
@@
 in order, and without gaps or duplicates.
-\meek\ takes a naive approach: requests and responses are strictly serialized.
+\meek takes a naive approach: requests and responses are strictly serialized.
 The client does not send a second chunk of data
@@
 
+% These numbers have changed since https://trac.torproject.org/projects/tor/ticket/12778.
 \begin{center}
@@
           &  $+$29 & Tor TLS record \\
-$\approx$ & $+$400 & \meek\ HTTP header \\
-$\approx$ &  $+$50 & \meek\ TLS record \\
+$\approx$ & $+$400 & \meek HTTP header \\
+$\approx$ &  $+$50 & \meek TLS record \\
 \hline
@@
 Bulk uploads and downloads tend to have less overhead, bunching many cells at once.
+% We can tell exactly how much overhead exists in practice by looking at our CDN invoices.
+% According to https://lists.torproject.org/pipermail/tor-dev/2014-December/007916.html,
+% In November 2014 meek-amazon had 167M requests and 1269 GB, or 8153 bytes per request.
+% If each request header is 500 bytes, that's about 6%.
 \vp{It might be helpful to have a table showing upload/download size/efficiency}
@@
 and different from each other's.
-A censor could block an uncamouflaged \meek\ using Go's TLS fingerprint,
+A censor could block an uncamouflaged \meek using Go's TLS fingerprint,
 if it considered the collateral damage resulting from blocking other Go programs to be slight enough.
@@
 support for fronting that exists.
-Of the services listed, we have so far deployed \meek\
+Of the services listed, we have so far deployed \meek
 only on Google App Engine and Amazon CloudFront.
@@
 of automatically browsing the home pages
-of the top 500 Alexa web sites using \meek\ in Tor Browser,
+of the top 500 Alexa web sites using \meek in Tor Browser,
 with the browser camouflage described in Section~\ref{sec:browserextension},
 and Google App Engine as the intermediate web service.
-The \meek\ trace is 687~MB
+The \meek trace is 687~MB
 and spans 4.5~hours of network activity.
@@
 \begin{tabular}{r r >{\qquad} r r}
-\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
+\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
 0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
@@
 from the \lbl traffic trace,
-and \meek\ running on App Engine, fronted through www.google.com.
+and \meek running on App Engine, fronted through www.google.com.
 % The histogram's bin width is 5~bytes.
@@
 % http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
-Conspicuous in the \meek\ trace are a small number of
+Conspicuous in the \meek trace are a small number of
 discrete frequent packet sizes,
@@
 occurred over just a few TCP/TLS connections.
-60\% of \meek\ connections lasted five minutes or longer,
+60\% of \meek connections lasted five minutes or longer,
 while only 13\% of those of ordinary traffic did.
-\meek\ has essentially no connections lasting less than 24 seconds,
+\meek has essentially no connections lasting less than 24 seconds,
 but such short connections account for over 42\% of the \lbl trace.
@@
 in any case that represents 10~minutes of circumvention achieved,
-after which \meek\ can start a new connection
+after which \meek can start a new connection
 \vp{well, it can't start a new connection if the censor's response is to block
@@
 and allow Tor to rebuild its circuits.
-Future enhancements in \meek\ may even allow reconnecting using the same session ID,
+Future enhancements in \meek may even allow reconnecting using the same session ID,
 so there will be no effect on the client other than a brief delay
@@
 works when printed in black-and-white.}
-The \lbl trace shows 2,745 unique clients and the \meek\ trace only one.
+The \lbl trace shows 2,745 unique clients and the \meek trace only one.
 The dark line is a smoothed average number of connections per client.
-The \meek\ count stays close to~1 throughout, only momentarily
+The \meek count stays close to~1 throughout, only momentarily
 jumping to 0 or~2.
 The average number of connections per user in the \lbl trace is 2.61,
-and in the \meek\ trace is 1.002.
+and in the \meek trace is 1.002.
 }
@@
 The number of concurrent connections is another potential distinguisher.
-We have seen how \meek\ tends to use one long-lived connection
+We have seen how \meek tends to use one long-lived connection
 through which it tunnels all its requests.
@@
 
-So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish \meek\
+So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish \meek
 from other HTTPS traffic.
@@
 
-Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
+Development on \meek as a Tor pluggable transport~\cite{pt} began in January~2014.
 For deployment we target
@@
 \caption{
-Concurrent users of the \meek\ pluggable transport
+Concurrent users of the \meek pluggable transport
 and month-by-month operational costs.
@@
 % \caption{
-% Daily unique users of \meek\ with
+% Daily unique users of \meek with
 % [blinded circumvention tool]
@@
 % The decrease at the end of June
-% was caused by an unblocking event that made \meek\ unnecessary for some users.
+% was caused by an unblocking event that made \meek unnecessary for some users.
 % }
@@
 % % Psiphon
-% began their independent deployment of \meek\ in June~2014.
+% began their independent deployment of \meek in June~2014.
 % Figure~\ref{fig:clients-psiphon3} shows the number
@@
 % in the middle of June was not caused by a blocking event,
-% but rather an unblocking event that made \meek\ unnecessary for some users.
+% but rather an unblocking event that made \meek unnecessary for some users.
 % Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
@@
 
-The current implementation of \meek\ strictly serializes
+The current implementation of \meek strictly serializes
 its HTTPS requests and responses,
@@
 
-The key idea of \meek\ is domain fronting,
+The key idea of \meek is domain fronting,
 but its HTTP tunneling ability is useful on its own.
@@
 % ANON
-% \meek\ has a home page at
+% \meek has a home page at
 % \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.

### 2015-01-12 docs/meek.tex
Shorter sessions IDs in diagram.
https://trac.torproject.org/projects/tor/ticket/12778

@@
 Host: forbidden.example
-X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
+X-Session-Id: cbIzfhx1HnR
 Content-Length: 517
@@
 Host: forbidden.example
-X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
+X-Session-Id: cbIzfhx1HnR
 Content-Length: 0

### 2015-02-07 docs/fronting.tex
Rename meek → fronting.
Back to ACM alternate style.
Remove ACM copyright block.
Unblind ICSI notary.

--- 2015-01-12 docs/meek.tex
@@
-% \documentclass{sig-alternate}
-\documentclass{IEEEtran}
-% \documentclass[11pt]{IEEEtran}
+\documentclass{sig-alternate}
 \usepackage{txfonts}
@@
 % Turn off ACM copyright block.
-% \toappear{}
+\toappear{}
 
@@
 \centering
-\includegraphics[width=\linewidth]{fronting}
+\includegraphics[width=\linewidth]{fronting-diagram}
 \caption{
@@
 a representative of
-[a blinded organization observing many TLS connections],
-\vp{I don't think this needs to be blinded}
-% ANON
-% the International Computer Science Institute's
-% certificate notary~\cite{icsi-notary},
-% which observes on the order of 50~million TLS connections daily,
+the International Computer Science Institute's
+certificate notary~\cite{icsi-notary},
+which observes on the order of 50~million TLS connections daily,
 83.5\% of connections used SNI in June~2014.
@@
 \bibliographystyle{abbrv}
-\bibliography{meek}
+\bibliography{fronting}
 

### 2015-02-07 docs/fronting.tex
Remove IEEE author block.
Have to redo it.
Remove grammar notes that are making me crazy.

@@
 \title{Blocking-resistant communication\\through domain fronting}
-
-% ANON
-% \author{David Fifield, Chang Lan}
-% \author{
-% \IEEEauthorblockN{David Fifield and Chang Lan}
-% \IEEEauthorblockA{University of California, Berkeley}
-% }
 
@@
 Then a connection is successful, the server can be blacklisted.
-\vp{Try not to begin sentences with ``Then'' (or with conjunctions like
-``But'').  Also, the writing has a lot of passive voice here.}
 Active probing is a precise means of identifying whether a server belongs to a circumvention system,
@@
 
-\vp{Lots of passive in this paragraph}
 Decoy routing~\cite{decoyrouting}

### 2015-02-07 docs/fronting.tex
Abstract hacking.

@@
 \begin{abstract}
-\vp{This abstract is quite long}
-We describe ``domain fronting,'' an application-layer technique
-for HTTPS
-that hides the remote endpoint of a communication
-for the purpose of censorship circumvention.
-Domain fronting enables communication that is apparently with an allowed domain,
-but actually with a forbidden domain.
+We describe ``domain fronting,'' a versatile censorship circumvention technique
+that hides the remote endpoint of a communication.
+Domain fronting works at the application layer, using HTTPS,
+to communicate with a forbidden host
+while appearing to communicate with some other host,
+permitted by the censor.
 The key idea is the use of different domain names at different layers of communication.
-One domain is used on the ``outside'' of an HTTPS request---in the DNS request and
-TLS Server Name Indication---while another is used
+One domain appears on the ``outside'' of the HTTPS request---in the DNS request and
+TLS Server Name Indication---while another domain appears
 on the ``inside''---in the HTTP Host header, invisible to the
 censor under HTTPS encryption.
+A censor, unable to distinguish fronted and non-fronted traffic to a domain,
+must choose between allowing circumvention traffic
+and blocking the entire domain,
+which results in expensive collateral damage.
+
+Domain fronting is easy to deploy and use and does not require
+special cooperation by network intermediaries.
 We identify a number of hard-to-block web services,
-like content delivery networks and Google,
-that support fronting because they ignore the outside of an HTTPS request
-and dispatch it internally according to the Host header.
-If a censor is unable to distinguish fronted circumvention traffic and non-fronted ordinary traffic,
-then blocking fronted traffic means blocking an entire web service,
-resulting in expensive collateral damage.
-
-We have implemented domain fronting in a system called \meek,
-a pluggable transport for Tor.
-\meek combines
-fronting with an HTTP-based tunneling proxy
-that decodes a sequence of HTTP requests and feeds their contents into Tor.
-A censor sees only a sequence of HTTPS requests to an allowed domain.
-We describe our experience with deploying \meek.
-% \meek, or something based on it,
-% has been adopted by other circumvention systems including
-% [blinded for anonymous submission].
-% ANON
-% Lantern and Psiphon.
-
-Hiding the endpoint and obscuring byte patterns are important parts of blocking resistance,
-but there are other, more subtle considerations.
-We describe what we have done to disguise traffic ``tells'' in \meek,
-including using a real web browser to make fronted HTTPS requests
-in order to disguise the TLS fingerprint.
-We argue that these measures, combined with domain fronting, increase the censor's effort
-beyond simple one-shot blocking techniques such as IP address blacklisting, and into
-the realm of more expensive, less reliable statistical tests.
+such as content delivery networks,
+that support domain-fronted connections
+and are useful for censorship circumvention.
+Domain fronting in various forms is now a circumvention workhorse.
+We describe several months of deployment experience
+in the Tor, Lantern, and Psiphon circumvention systems,
+including user adoption, performance,
+ongoing cost of operation, and lessons learned.
 \end{abstract}
@@
 \section{Introduction}
-
-% VPN arms race We seek to build a system that remains difficult to block even
-% after it has many users.
 

### 2015-02-07 docs/fronting.tex
Intro hacking.

@@
 The key idea is the use of different domain names at different layers of communication.
-One domain appears on the ``outside'' of the HTTPS request---in the DNS request and
+One domain appears on the ``outside'' of an HTTPS request---in the DNS request and
 TLS Server Name Indication---while another domain appears
@@
 
-We as circumventors have in our favor the censor's
-distaste for ``collateral damage'':
-accidental overblocking committed in the course of trying to censor something else.
+Circumventors,
+at a natural disadvantage because the censor controls the network,
+have one point working in their favor:
+the censor's distaste for ``collateral damage,''
+accidental overblocking committed in the course of censorship.
+Collateral damage is harmful to the censor,
+because the overblocked content is economically or socially beneficial,
+so the censor avoids it when possible.
+(Any censor not willing to turn off the Internet completely
+must derive \emph{some} benefit from allowing access,
+which overblocking harms.)
 One way to win against censorship is to entangle circumvention traffic
-with ordinary Internet traffic such that both must be blocked together,
-or not at all.
-If the ordinary traffic is valuable enough,
-above the censor's tolerance for overblocking,
-then the circumvention traffic will get through.
-
-In this paper we describe ``domain fronting,'' a general-purpose technique
+with other traffic, which is valuable enough to
+exceed the censor's tolerance for overblocking.
+
+In this paper we describe ``domain fronting,'' a general-purpose circumvention technique
 based on HTTPS that hides the true destination of a communication
@@
 Fronting works with many web services that host multiple domain names
-behind an HTTPS frontend server.
-These include such high-collateral-damage infrastructure as
-big content delivery networks (CDNs)
+behind a frontend server.
+These include such important infrastructure as
+content delivery networks (CDNs)
 and Google's panoply of services---a nontrivial fraction of the web.
-(See Section~\ref{sec:survey} for a list of suitable services.)
-Domain fronting can be used to tunnel traffic
-to a general-purpose proxy,
-so that circumvention is not limited only to HTTPS, nor to the domains of any specific web service.
+(Section~\ref{sec:survey} is a survey of suitable services.)
+The utility of domain fronting is not limited to HTTPS communication,
+nor to accessing only the domains of a specific web service:
+it works well as a domain-hiding component of a larger circumvention system,
+an HTTPS tunnel leading to a general-purpose proxy.
 
@@
 In an HTTPS request, the destination domain name appears
-in three places relevant to the discussion:
+in three relevant places:
 in the DNS query,
@@
 and in the HTTP Host header~\cite[\S 14.23]{rfc2616}.
-Usually, the same domain name appears in all three places.
+Ordinarily, the same domain name appears in all three places.
 In a domain-fronted request, however,
@@
 while the HTTP Host header,
-which is hidden from the censor by HTTPS encryption,
-carries another (the actual destination).
+hidden from the censor by HTTPS encryption,
+carries another (the covert, forbidden destination).
 
@@
 
-The censor can block neither the DNS request nor the SNI without
+The censor cannot block on the contents of the DNS request nor the SNI without
 collaterally blocking the front domain.
 The Host header is invisible to the censor,
-but visible to the server receiving the HTTPS request,
-which uses the header to internally route the request to its destination.
-No traffic ever reaches the front domain,
-which may be oblivious to the circumvention.
-For those familiar with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance},
-domain fronting can be understood as
+but visible to the frontend server receiving the HTTPS request.
+The frontend server uses the Host header internally to route the request
+to its covert destination; no traffic ever reaches the putative front domain.
+Domain fronting has many similarities with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance};
+it may be understood as
 ``decoy routing at the application layer.''
@@
 
-This Wget command shows domain fronting in action
-on Google's infrastructure.
-Here, an HTTPS request for \urll{www.google.com} has a Host header for
-\urll{maps.google.com}, even though the SNI in the TLS handshake specifies
-\texttt{www.google.com}.
-The HTML in the response is that of Google Maps.
+This Wget command demonstrates domain fronting
+on Google, one of many fronting-capable services.
+Here, the HTTPS request has a Host header for \urll{maps.google.com},
+even though the DNS query and the SNI in the TLS handshake specify \urll{www.google.com}.
+The response comes from \urll{maps.google.com}.
 
@@
 \$ wget -q -O - https://www.google.com/ \char`\\\\
-\strut~~~~--header \textquotesingle{}Host: maps.google.com\textquotesingle{} | \char`\\\\
+\strut~~~~--header \textquotesingle{}Host:~maps.google.com\textquotesingle{} | \char`\\\\
 \strut~~~~grep -o \textquotesingle{}<title>.*</title>\textquotesingle{}\\

### 2015-02-07 docs/fronting.tex
Rewrite look-like-nothing.

@@
 Examples of look-like-nothing transports are
-obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
-Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
-Both obfs2 and obfs3 work by superenciphering
-\vp{not clear here what superenciphering means; presumably, it's a reference
-to encrypting a stream that's already encrypted, but the reader has to pause
-and work that out}
-an underlying stream,
-using a key exchange that has no plaintext components.
-ScrambleSuit~\cite{scramblesuit} is like obfs3 in its
-payload obfuscation, but additionally obscures its traffic signature
-(packet lengths and timing), and is designed to resist active probing.
-A ScrambleSuit server will accept a TCP connection but not send a reply
-until the client proves knowledge of a shared secret.
-\vp{Say, has there been any work on using port-knocking to resist active
-probing?}
-obfs4~\cite{obfs4}
-(which despite the name has more in common with ScrambleSuit than with obfs2 and obfs3)
-builds on ScrambleSuit with more efficient cryptography and an authenticated handshake.
+obfuscated-openssh~\cite{obfuscated-openssh} and its string of successors:
+obfs2~\cite{obfs2}, obfs3~\cite{obfs3}, ScrambleSuit~\cite{scramblesuit}, and obfs4~\cite{obfs4}.
+They all work by re-encrypting
+an underlying stream so that there remains no plaintext components,
+not even in the handshake and key exchange.
+obfs2, introduced in early 2012~\cite{obfsproxy-arms-race},
+used a fairly weak key exchange that can be detected passively;
+it is now deprecated and little used.
+obfs3 is currently Tor's most-used transport~\cite{metrics-obfs3}.
+It improves on obfs2 with a Diffie--Hellman key exchange,
+public keys being encoded so as to be indistinguishable from random binary strings.
+ScrambleSuit and obfs4 add resistance to active probing:
+the server accepts a TCP connection but does not send a reply
+until the client proves knowledge of a secret shared out of band.
+They additionally additionally obscure the traffic signature of the underlying stream
+by modifying packet lengths and timing.
 

### 2015-02-07 docs/fronting.tex
Italics.

@@
 For example, a censored client may ask an HTTPS-based online translation service to
-translate the web page at \urll{http://forbidden.example/}\textsl{data...},
-where ``\textsl{data...}'' is the URL-embedded message the client wants to send.
+translate the web page at \urll{http://forbidden.example/}\textsl{data},
+where ``\textsl{data}'' is the URL-embedded message the client wants to send.
 The translation service requests the URL,
@@
 For example, in the S3 URL
-\urll{https://s3.amazonaws.com/bucketname/filename},
-\vp{should ``filename'' in the URL be italicized?  It sounds like it's
-a generic placeholder, not a literal}
+\urll{https://s3.amazonaws.com/}\textsl{bucketname}/\textsl{filename},
 the censor only gets to ``see'' the generic domain part, ``\urll{s3.amazonaws.com}''.
-The path component ``\urll{/bucketname/filename}'',
+The path component ``/\textsl{bucketname}/\textsl{filename}'',
 which would reveal the use of CloudTransport,

### 2015-02-07 docs/fronting.tex
Prefix figures with "meek-".

@@
 are returned to the client within HTTP responses.
-\meek's architecture appears in Figure~\ref{fig:architecture}.
+\meek's architecture appears in Figure~\ref{fig:meek-architecture}.
 Section~\ref{sec:architecture} describes how it works in detail.
@@
 \centering
-\includegraphics[width=\linewidth]{architecture}
+\includegraphics[width=\linewidth]{meek-architecture}
 \caption{
@@
 }
-\label{fig:architecture}
+\label{fig:meek-architecture}
 \end{figure*}
@@
 
-We show the components of the system in Figure~\ref{fig:architecture}.
+We show the components of the system in Figure~\ref{fig:meek-architecture}.
 The parts that are new in \meek
@@
 \centering
-\includegraphics[height=1.5in]{browser-architecture}
+\includegraphics[height=1.5in]{meek-browser-architecture}
 \caption{
@@
 The headless browser runs in the background and is invisible to the user.
-This figure is a zoomed-in view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
+This figure is a zoomed-in view of the ``Client's PC'' component of Figure~\ref{fig:meek-architecture}.
 }
-\label{fig:browser-architecture}
+\label{fig:meek-browser-architecture}
 \end{figure}
 
-Figure~\ref{fig:browser-architecture} shows the interaction of components
+Figure~\ref{fig:meek-browser-architecture} shows the interaction of components
 on the client's computer.

### 2015-02-07 docs/fronting.tex
Allow breaking URLs at hyphens.
https://tex.stackexchange.com/questions/49788/hyperref-url-long-url-with-dashes-wont-break/49791#49791
\hyphenation{Client-Hello}
It was being broken in one case as
	Clien-
	tHello
Restructure for Lantern and Psiphon.

@@
 \usepackage{graphicx}
-\usepackage{url}
+\usepackage[hyphens]{url}
 \usepackage{caption}
@@
 \usepackage{color}
+
+\hyphenation{Client-Hello}
 
@@
 At the HTTP layer, unreadable to the censor,
-is the actual destination \mbox{\textbf{forbidden.example}}.
+is the actual, covert destination \mbox{\textbf{forbidden.example}}.
 }
@@
 
+A variation is ``domainless'' fronting,
+in which there is no DNS request and no SNI.
+It appears to the censor
+that the user is browsing an HTTPS site by its IP address,
+or using a web client that does not support SNI.
+Domainless fronting can be useful when there is no known front domain
+with sufficiently high collateral damage;
+it leaves the censor the choice of blocking an entire IP address
+(or blocking SNI-less requests entirely),
+rather than blocking only a single domain.
+
 Domain fronting works with CDNs because a CDN's frontend server
@@
 (the ``origin server'').
-(There are other ways for CDNs to work, but this ``origin pull''
+(There are other ways CDNs may work, but this ``origin pull''
 configuration is common.)
-% The certificate you get may be that of the front domain,
-% or may be a generic shared domain.~\cite{httpsincdn}
-Fronting works with Google because Google App Engine, a web application platform,
-can host a simple ``reflector'' application that emulates
-an origin-pull CDN, simply forwarding every request to another server.
-In both cases, the intermediate web service does not forward requests to just anywhere---it
-has to be to the domain of a customer.
-In order to run a fronting backend,
-one generally has to create an account with the web service and pay for bandwidth.
-
-A variation on fronting is ``domainless'' fronting,
-in which there is no DNS request and no SNI.
-It looks to the censor
-like the user is browsing an HTTPS site by its IP address,
-or using a web client that does not support SNI.
-Domainless fronting can be useful when there is no known front domain
-with sufficiently high collateral damage.
-The censor is faced with the choice of blocking an entire IP address, not only a domain;
-blocking requests without SNI;
-or trying to find some other, presumably more expensive, test to distinguish
-circumvention traffic.
-
-We have developed domain fronting into a full-fledged circumvention system called \meek,
-implemented as a pluggable transport~\cite{pt} for Tor.
-\meek combines fronting with an HTTP-based tunneling proxy:
-upstream data are transformed into a sequence of HTTP requests,
-which are fronted in order to reach a proxy server.
-The server decodes the requests and feeds their payloads
-into the Tor network.
-Downstream data received by the server from Tor
-are returned to the client within HTTP responses.
-\meek's architecture appears in Figure~\ref{fig:meek-architecture}.
-Section~\ref{sec:architecture} describes how it works in detail.
-
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{meek-architecture}
-\caption{
-Architecture of \meek.
-The client sends an HTTP request to the Tor bridge by way of an intermediate web service such as a CDN.
-The client protects the bridge's domain name \textbf{forbidden.example} from the censor
-by fronting it with another name, here \textbf{allowed.example}.
-The intermediate web server decrypts the TLS layer and forwards the request to the bridge
-according to the Host header.
-The bridge sends data back to the client in the HTTP response.
-\meekclient and \meekserver are transport plugins, the interface between Tor and \meek.
-The host actually at allowed.example does not participate in the communication.
-}
-\label{fig:meek-architecture}
-\end{figure*}
-
-\meek has been built into an experimental release of Tor Browser,
-and has a small number of users.
-Our deployment so far uses Google App Engine and Amazon CloudFront
-as intermediate web service backends.
-% with the hidden actual domain \urll{meek-reflect.appspot.com}
-% hidden by the front \urll{www.google.com}.
-Section~\ref{sec:survey} names other fronting-capable services
-and Section~\ref{sec:discussion} describes other possible deployments.
-\vp{It's confusing here having out-of-order references to sections.  This
-also occurs below}
-In addition to the Tor pluggable transport,
-systems based on \meek are now used by other circumvention systems including
-[blinded for anonymous submission].
-% ANON
-% including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.
-
-% \meek is designed to have features attractive in a circumvention transport.
-% It is easy to use, not requiring the configuration of any bridge addresses.
-% In Tor Browser, users need only select ``meek''
-% from a pulldown menu in order to use it.
-% It resists blocking by address and by content,
-% Section~\ref{sec:discussion}
-
-Domain fronting and HTTPS address two major circumvention challenges,
-those of hiding the destination and of obscuring the contents of a message.
-There remain other, more subtle, attributes of communication
-that could serve as a basis for blocking.
-For example, the plaintext handshake is a fingerprintable part of TLS.
-Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
-to make \meek's TLS and HTTPS characteristics
-match those of a browser as closely as possible.
-Our goal is to force the censor
-to employ more sophisticated, expensive, and error-prone statistical tests
-to classify traffic as allowed or prohibited,
-rather than domain blacklists or deep packet inspection---to
-force the practice of censorship to exist in a world
-not of simple packet filters,
-but of probabilities and false positives.
-A preliminary analysis of \meek's resistance to traffic analysis
-appears in Section~\ref{sec:trafficanalysis}.
-The analysis is based on comparing traffic traces of \meek
-to samples of HTTPS traffic at a network router.
-
-\vp{Seems this should go in the next section instead}
-To our knowledge,
-the earliest application of domain fronting to circumvention
-was by GoAgent~\cite{goagent},
-a tool based on App Engine and
-once widely used in China.
-Fronting has also been used with success since 2013
-for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
-GoAgent and flash proxy are the systems that most directly
-inspire ours.
-
-% We measure the performance...
+The client issues a request that appears to be destined for
+an unrelated front domain, which may be any of the CDN's domains
+that resolve to an edge server; this fronted request is what the censor sees.
+The edge server decrypts the request,
+reads the Host header and
+forwards the request to the specified origin,
+which in the circumvention scenario is a general-purpose proxy.
+The origin server, being a general-purpose proxy, would be blocked by the censor if accessed directly.
+Fronting hides its address from the censor.
+
+On services that do not automatically forward requests,
+it is usually possible to install a trivial ``reflector'' web application
+that emulates an origin-pull CDN.
+In this case, fronting does not protect the address of the origin per se;
+rather it protects the address of the reflector application,
+which in turn forwards requests to the origin.
+Google App Engine is an example of such a service:
+against a censor that blocks the App Engine domain \urll{appspot.com}
+but allows other Google domains,
+domain fronting provides access to a reflector running on \urll{appspot.com}.
+
+No matter the specifics of particular web services,
+as a general rule they do not forward requests to arbitrary domains---only to domains
+belonging to their customers.
+In order to deploy a domain-fronting proxy,
+one must become a customer of the CDN (or Google, etc.)
+and pay for bandwidth.
+It is the owner of the covert domain who pays the bandwidth bills,
+not the owner of the front domain,
+which need not have any relation to the covert domain beyond
+using the same web service.
+
+The remainder of this paper is devoted to a deep exploration of
+domain fronting as we have deployed it in practice.
+Section~\ref{sec:threatmodel} explains our threat model and assumptions.
+Section~\ref{sec:related-work} gives general background on the circumvention problem
+and outlines its three grand challenges:
+address-based blocking, content-based blocking, and active probing.
+Domain-fronting systems are capable of meeting all three challenges,
+forcing censors to use more expensive, less reliable censorship techniques
+that have heretofore not been seen in practice.
+Section~\ref{sec:survey} is a summary of CDNs and other services
+that are usable for fronting,
+identifying general principles as well as
+individual idiosyncrasies that affect implementation.
+The following sections are case studies of deployment:
+Section~\ref{sec:deploy-tor} for Tor,
+Section~\ref{sec:deploy-lantern} for Lantern, and
+Section~\ref{sec:deploy-psiphon} for Psiphon.
+Section~\ref{sec:trafficanalysis} analyzes domain fronting's resistance
+to statistical traffic analysis attacks.
+Section~\ref{sec:discussion} has general discussion and
+Section~\ref{sec:summary} summarizes.
+
+% Circumvention is often presented as an arms race,
+% evaders racing to set up proxies before the censor finds and blocks them,
+% the censor racing to reverse-engineer the evader's latest technique.
+% We submit that a system that comprehensively addresses
+% address blocking, content blocking, and active probing---one that
+% remains accessible even after the censor knows how it works---occasions
+% a qualitative change in the nature of the arms race.
+% Deprived of easy DPI, cheap address enumeration, and port scanning for proxies,
+% the censor is forced to fall back to more expensive,
+% less reliable statistical analysis on traffic flows.
+% The domain-fronting systems we describe are the result
+% of years of experience with operational
+% censorship circumvention systems.
+% They are complete, start-to-finish systems designed to defeat
+% the capabilities of real-world censors known today.
+
+\section{Threat model}
+\label{sec:threatmodel}
+
+Our threat model includes four actors:
+the censor,
+the censored client,
+the intermediate web service,
+and the covert destination (some kind of proxy).
+We achieve
+circumvention when the client evades the censor to reach
+the bridge,
+because the bridge can then proxy to anywhere.
+The client and bridge cooperate with each other.
+The intermediate web service does not need to cooperate with either,
+except to the extent that it does not collude with the censor.
+% The censor's goal is to prevent circumvention.
+
+The censor controls a (generally national)
+network and the links into and within it.
+The censor can inspect traffic flowing across all links under its control
+and can block or allow any packet.
+The censor can inject and replay traffic, and
+operate its own clients and servers.
+The client lies within the censor's network,
+while the intermediate web service and bridge lie outside.
+The censor blocks direct communication between the client and the bridge,
+but allows HTTPS between the client and at least one front domain or IP address
+on the intermediate web service.
+% In examples, we will use the \textbf{allowed.example} as the front domain
+% and \textbf{forbidden.example} as the domain name of the Tor bridge.
+
+% The censor must operate at line rate; that is,
+% it must not delay traffic unduly while deciding whether to allow it.
+% This consideration is one facet of the censor's sensitivity to
+% collateral damage caused by false positives:
+% mistakenly blocking or degrading non-circumvention traffic causes the censor
+% to incur some penalty, just as mistakenly allowing circumvention traffic does.
+
+The client,
+intermediate web service,
+and destination proxy
+are uncontrolled by the censor.
+The censor does not control a trusted TLS certificate authority;
+specifically it cannot man-in-the-middle an HTTPS session
+without being caught by ordinary certificate verification.
+The client has a way to get a copy of the necessary client programs.
+
+Section~\ref{sec:discussion} analyzes what happens when some
+of the threat model's assumptions are violated;
+specifically what happens
+when the intermediate web service's frontend server is inside the censor's network
+and when the censor controls a trusted certificate authority.
 
@@
 whether a server speaks the Tor protocol.
-The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
-and obfs4~\cite{obfs4},
-described in this section.
 
@@
 If one of them is blocked, there is soon another to replace it.
-Flash proxy's approach to address blocking is in a sense
+Flash proxy's approach to address blocking is
 the opposite of \meek's:
@@
 
-GoAgent~\cite{goagent} is a direct inspiration for \meek in its use of
-domain fronting with App Engine.
-\vp{Was it literally an inspiration, or was it concurrent development?
-I thought it was more the latter.}
+To our knowledge,
+the earliest use of domain fronting for circumvention
+was by GoAgent~\cite{goagent},
+a tool based on App Engine and
+once widely used in China.
 Traffic is fronted by the Google frontend server,
@@
 and the contents of all communications are revealed to Google.
-Users of GoAgent generally upload
-\vp{``generally'' upload---what's their practical alternative?}
+Users of GoAgent upload
 their own personal copy of the proxy code to App Engine,
@@
 Use of GoAgent in China was disrupted starting in the beginning of June~2014,
-when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
+when all Google services were blocked~\cite{cn-google-block}.
 \meek over App Engine was similarly affected.
@@
 
-Psiphon~\cite{psiphon} is a network of many one-hop proxies,
-with encryption and traffic obfuscation between client and server.
-% ANON
-% Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
-Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
-proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
-% ANON
-% Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.
-\vp{Explain Pisphon's relevance to meek}
-
 % Infranet
@@
 
-\section{Threat model}
-
-Our threat model includes four actors:
-the censor,
-the censored client,
-the intermediate web service,
-and the destination Tor bridge.
-\vp{Update this when considering more general services than just
-Tor bridges.}
-We achieve
-circumvention when the client evades the censor to reach
-the bridge,
-because the bridge can then proxy to anywhere.
-The client and bridge cooperate with each other.
-The intermediate web service does not need to cooperate with either,
-except to the extent that it does not collude with the censor.
-% The censor's goal is to prevent circumvention.
-
-The censor controls a (generally national)
-network and the links into and within it.
-The censor can inspect traffic flowing across all links under its control
-and can block or allow any packet.
-The censor can inject and replay traffic, and
-operate its own clients and servers.
-The client lies within the censor's network,
-while the intermediate web service and bridge lie outside.
-The censor blocks direct communication between the client and the bridge,
-but allows HTTPS between the client and at least one front domain or IP address
-on the intermediate web service.
-% In examples, we will use the \textbf{allowed.example} as the front domain
-% and \textbf{forbidden.example} as the domain name of the Tor bridge.
-
-% The censor must operate at line rate; that is,
-% it must not delay traffic unduly while deciding whether to allow it.
-% This consideration is one facet of the censor's sensitivity to
-% collateral damage caused by false positives:
-% mistakenly blocking or degrading non-circumvention traffic causes the censor
-% to incur some penalty, just as mistakenly allowing circumvention traffic does.
-
-The client,
-intermediate web service,
-and destination proxy
-are uncontrolled by the censor.
-The censor does not control a trusted TLS certificate authority;
-specifically it cannot man-in-the-middle an HTTPS session
-without being caught by ordinary certificate verification.
-The client has a way to get a copy of the necessary client programs.
-
-Section~\ref{sec:discussion} analyzes what happens when some
-of the threat model's assumptions are violated;
-specifically what happens
-when the intermediate web service's frontend server is inside the censor's network
-and when the censor controls a trusted certificate authority.
-
-\section{Architecture and protocol of meek}
-\label{sec:architecture}
+\section{Fronting-capable web services}
+\label{sec:survey}
+
+\vp{This whole section should be beefed up with a deeper assessment.  Along
+these lines, it would help to include a summary table.}
+This section contains a brief survey of fronting-capable
+web services we have found, each with its pros and cons.
+The list is not exhaustive and is meant to illustrate the broad
+support for fronting that exists.
+Of the services listed, we have so far deployed \meek
+only on Google App Engine and Amazon CloudFront.
+For the others, we have only checked that fronting works.
+Recall that even web services that support fronting
+will front only for their own customers,
+so new each deployment typically requires an investment of time and money.
+
+Google App Engine~\cite{googleappengine}
+is a web application platform.
+Each application gets a user-specified subdomain of \urll{appspot.com},
+which can be fronted through almost any Google domain,
+including google.com, gmail.com, googleapis.com, and many others.
+App Engine can run only web applications,
+not a full Tor bridge;
+for that reason we use a tiny ``reflector'' application
+that merely copies incoming requests to a Tor bridge hosted elsewhere.
+Fronting through App Engine is attractive in the case where even though
+the censor blocks
+\urll{appspot.com}---which could well occur,
+because of the ease of building a proxy there---at least one
+other Google service remains reachable.
+Applications that use $< 1$~GB of bandwidth daily
+are free of charge,
+making possible an upload-your-own-app model
+à la GoAgent.
+
+Amazon CloudFront~\cite{cloudfront}
+(not to be confused with CloudFlare; see below)
+is the CDN of Amazon Web Services.
+A CloudFront ``distribution'' associates
+an automatically generated subdomain of \urll{cloudfront.net}
+with an origin server,
+which in our case is an instance of \meekserver.
+The front domain may be any other of CloudFront's automatically generated subdomains, all
+of which support HTTPS through a wildcard certificate.
+CloudFront has a usage tier that is free of charge for a year,
+subject to a bandwidth limit of 50~GB/month.
+
+Microsoft Azure~\cite{azure}
+is a cloud computing platform that features a CDN.
+Similarly to CloudFront, users get automatically generated subdomains
+of \urll{vo.msecnd.net},
+all of which can front for each other.
+The CDN works only for Azure domains, however,
+so as with App Engine, it is necessary to run a trivial reflector app
+that merely forwards requests out of Azure toward an external proxy.
+There are other front domain names, like \urll{ajax.aspnetcdn.com},
+that may provide entangling with high collateral damage.
+
+CloudFlare~\cite{cloudflare}
+is a CDN also marketed as protection against
+denial-of-service attacks.
+It appears that any domain name on CloudFlare
+can front for any other, even custom user-selected domains;
+however it is not obvious which one is best to use as a front.
+The front domain needs to be a popular one
+(causing high collateral damage if blocked),
+or the censor may simply block it entirely.
+It is doubly bad when a domain is blocked in this way,
+because not only is circumvention foiled,
+but some unsuspecting third party has just had their web site blocked.
+A solution may be to round-robin through
+a pool of popular domain names;
+or to use ``domainless'' fronting that does not send SNI.
+\vp{Would be quite valuable to more broadly assess the viability
+of using domainless fronting}
+% Though CloudFlare supports domain fronting,
+% its terms of service~\cite{cloudflare-terms}
+% seem to prohibit the kind of tunneled proxying that \meek does:
+% \begin{quote}
+% \textsc{Section 10: Limitation on non-HTML caching}\\
+% You acknowledge that CloudFlare's Service is offered as a platform to cache and
+% serve web pages and websites and is not offered for other purposes
+% \ldots\ you understand and agree to use the Service solely
+% for the purpose of hosting and serving web pages\ldots
+% \end{quote}
+
+Akamai~\cite{akamai-site} is a large CDN.
+Requests may be fronted through the special HTTPS domain
+\urll{a248.e.akamai.net},
+which serves a certificate also good for \urll{*.akamaihd.net}.
+The collateral damage of blocking Akamai is enormous:
+in 2010 it carried 15--20\% of all web traffic~\cite{akamai}.
+Akamai costs more than other CDNs;
+it would likely require institutional support
+to keep a circumvention system running on it in the long term.
+
+Fastly~\cite{fastly} is a CDN.
+It is the only one of the services we tested that
+appears to enforce SNI consistency:
+if the SNI and Host do not match,
+the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
+However, if the TLS ClientHello omits SNI, then the Host may be any Fastly domain.
+It is the only service we have found
+that requires the ``domainless'' fronting style.
+
+\section{Deployment on Tor: meek}
+\label{sec:deploy-tor}
+
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{meek-architecture}
+\caption{
+Architecture of \meek.
+The client sends an HTTP request to the Tor bridge by way of an intermediate web service such as a CDN.
+The client protects the bridge's domain name \textbf{forbidden.example} from the censor
+by fronting it with another name, here \textbf{allowed.example}.
+The intermediate web server decrypts the TLS layer and forwards the request to the bridge
+according to the Host header.
+The bridge sends data back to the client in the HTTP response.
+\meekclient and \meekserver are transport plugins, the interface between Tor and \meek.
+The host actually at allowed.example does not participate in the communication.
+}
+\label{fig:meek-architecture}
+\end{figure*}
 
@@
 Request/response bodies contain successive chunks of a Tor TLS stream
-(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
-is the beginning of a TLS ClientHello message).
+(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01}
+is the beginning of a TLSv1.0 ClientHello message).
 The second POST request is an empty polling request.
@@
 Instead, each client generates a random 256-bit
-\vp{it seems like overkill to use 256 bits for this $\ldots$}
 session ID for each new Tor stream,
@@
 which adds an HTTP header whose length is about 400 bytes
-\vp{yikes, that's a lot of overhead $\ldots$}
 (varying slightly depending on the length of the Host
@@
 
-\section{Camouflage for the TLS layer}
+Development on \meek as a Tor pluggable transport~\cite{pt} began in January~2014.
+For deployment we target
+the Tor Browser~\cite{torbrowser},
+a customized version of Firefox that is
+preconfigured to use a built-in Tor client.
+% and patched to defend against application-layer privacy and anonymity threats
+% like tracking cookies and web browser fingerprinting.
+Tor Browser has an easy interface for selecting pluggable transports.
+% ANON
+% [Some details of deployment are omitted for anonymous submission.]
+% We made a series of experimental releases of Tor Browser featuring \meek,
+% releasing the first one on February~18.
+% On April~18 we made the first release featuring the browser camouflage
+% that is the subject of Section~\ref{sec:browserextension}.
+% We announced our releases on Tor development mailing lists,
+% whence they were picked up by Tor Weekly News on the Tor blog.
+% Our code was merged by the Tor Browser maintainers
+% in June and is scheduled for an alpha release,
+% still pending as of this writing.
+
+We have so far deployed on three backends:
+Google App Engine,
+Amazon CloudFront,
+and Microsoft Azure.
+Figure~\ref{fig:clients-tor} shows the daily average number of concurrent users of \meek.
+(A measurement of 500, for example, means that there were on average 500
+users of the system at any given time during the day.)
+The App Engine backend was established in February;
+CloudFront in July;
+and Azure in October.
+Also in Figure~\ref{fig:clients-tor} is a table of monthly costs for each web service.
+The pricing for cloud services is complicated,
+depending not only on bandwidth but also on geographical region and other factors.
+For example CloudFront charges per request as well as per GB,
+and about 54\% of the CloudFront bill for October was for requests.
+App Engine charges extra when it has to run multiple instances
+of an app's code to cope with load;
+about 15\% of October's App Engine bill was for such ``instance hours.''
+% These and other cost details are summarized in a mailing list post~\cite{meek-costs-201410}.
+The App Engine and CloudFront backends are running on accounts
+that provide a limited amount of free bandwidth,
+but current use greatly exceeds the free thresholds.
+Azure service is being donated and so has not yet cost anything.
+The total cost so far has been \$187.13,
+but this number is expected to more than double in November and continue to increase.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{clients-meek}
+\begin{tabular}{l r r r}
+       &App Engine &CloudFront&  Azure \\
+\hline
+Jan--Jul &  \$2.72 &   \$0.00 & \$0.00 \\
+Aug      &  \$1.56 &   \$3.10 & \$0.00 \\
+Sep      &  \$4.02 &   \$4.59 & \$0.00 \\
+Oct      & \$40.85 & \$130.29 & \$0.00 \\
+\hline
+total    & \$49.15 & \$137.98 & \$0.00 \\
+\end{tabular}
+\caption{
+Concurrent users of the \meek pluggable transport
+and month-by-month operational costs.
+The total cost to date is \$187.13.
+% ANON
+% The large increase of users on October~15 coincides with
+% the release of Tor Browser~4.0,
+% the first release to make meek easily available.
+Azure CDN service is currently being donated as part of a research grant.
+\vp{It would be valuable to build up some sort of estimate of what it
+would cost if you didn't have the grant.}
+The user estimates come from the Tor Metrics Portal~\cite{metrics-meek,counting-daily-bridge-users}.
+}
+\label{fig:clients-tor}
+\end{figure}
+
+\subsection{Camouflage for the TLS layer}
 \label{sec:browserextension}
@@
 
-Appropriate TLS camouflage may differ depending on circumstances.
-On a traditional desktop PC, using a browser is probably the right choice.
-When
-[blinded circumvention tool]
-\vp{does this need to be blinded?}
-% ANON
-% Psiphon
-ported \meekclient to Android,
-they did not use a browser as camouflage,
-but rather made all HTTPS requests with the standard Android HTTP API.
-This decision makes sense because other Android applications
-also use the standard API and share the same TLS fingerprint.
-
-\section{A survey of fronting-capable web services}
-\label{sec:survey}
-
-\vp{This whole section should be beefed up with a deeper assessment.  Along
-these lines, it would help to include a summary table.}
-This section contains a brief survey of fronting-capable
-web services we have found, each with its pros and cons.
-The list is not exhaustive and is meant to illustrate the broad
-support for fronting that exists.
-Of the services listed, we have so far deployed \meek
-only on Google App Engine and Amazon CloudFront.
-For the others, we have only checked that fronting works.
-Recall that even web services that support fronting
-will front only for their own customers,
-so new each deployment typically requires an investment of time and money.
-
-Google App Engine~\cite{googleappengine}
-is a web application platform.
-Each application gets a user-specified subdomain of \urll{appspot.com},
-which can be fronted through almost any Google domain,
-including google.com, gmail.com, googleapis.com, and many others.
-App Engine can run only web applications,
-not a full Tor bridge;
-for that reason we use a tiny ``reflector'' application
-that merely copies incoming requests to a Tor bridge hosted elsewhere.
-Fronting through App Engine is attractive in the case where even though
-the censor blocks
-\urll{appspot.com}---which could well occur,
-because of the ease of building a proxy there---at least one
-other Google service remains reachable.
-Applications that use $< 1$~GB of bandwidth daily
-are free of charge,
-making possible an upload-your-own-app model
-à la GoAgent.
-
-Amazon CloudFront~\cite{cloudfront}
-(not to be confused with CloudFlare; see below)
-is the CDN of Amazon Web Services.
-A CloudFront ``distribution'' associates
-an automatically generated subdomain of \urll{cloudfront.net}
-with an origin server,
-which in our case is an instance of \meekserver.
-The front domain may be any other of CloudFront's automatically generated subdomains, all
-of which support HTTPS through a wildcard certificate.
-CloudFront has a usage tier that is free of charge for a year,
-subject to a bandwidth limit of 50~GB/month.
-
-Microsoft Azure~\cite{azure}
-is a cloud computing platform that features a CDN.
-Similarly to CloudFront, users get automatically generated subdomains
-of \urll{vo.msecnd.net},
-all of which can front for each other.
-The CDN works only for Azure domains, however,
-so as with App Engine, it is necessary to run a trivial reflector app
-that merely forwards requests out of Azure toward an external proxy.
-There are other front domain names, like \urll{ajax.aspnetcdn.com},
-that may provide entangling with high collateral damage.
-
-CloudFlare~\cite{cloudflare}
-is a CDN also marketed as protection against
-denial-of-service attacks.
-It appears that any domain name on CloudFlare
-can front for any other, even custom user-selected domains;
-however it is not obvious which one is best to use as a front.
-The front domain needs to be a popular one
-(causing high collateral damage if blocked),
-or the censor may simply block it entirely.
-It is doubly bad when a domain is blocked in this way,
-because not only is circumvention foiled,
-but some unsuspecting third party has just had their web site blocked.
-A solution may be to round-robin through
-a pool of popular domain names;
-or to use ``domainless'' fronting that does not send SNI.
-\vp{Would be quite valuable to more broadly assess the viability
-of using domainless fronting}
-% Though CloudFlare supports domain fronting,
-% its terms of service~\cite{cloudflare-terms}
-% seem to prohibit the kind of tunneled proxying that \meek does:
-% \begin{quote}
-% \textsc{Section 10: Limitation on non-HTML caching}\\
-% You acknowledge that CloudFlare's Service is offered as a platform to cache and
-% serve web pages and websites and is not offered for other purposes
-% \ldots\ you understand and agree to use the Service solely
-% for the purpose of hosting and serving web pages\ldots
-% \end{quote}
-
-Akamai~\cite{akamai-site} is a large CDN.
-Requests may be fronted through the special HTTPS domain
-\urll{a248.e.akamai.net},
-which serves a certificate also good for \urll{*.akamaihd.net}.
-The collateral damage of blocking Akamai is enormous:
-in 2010 it carried 15--20\% of all web traffic~\cite{akamai}.
-Akamai costs more than other CDNs;
-it would likely require institutional support
-to keep a circumvention system running on it in the long term.
-
-Fastly~\cite{fastly} is a CDN.
-It is the only one of the services we tested that
-appears to enforce SNI consistency:
-if the SNI and Host do not match,
-the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
-However, if the TLS ClientHello omits SNI, then the Host may be any Fastly domain.
-It is the only service we have found
-that requires the ``domainless'' fronting style.
+\section{Deployment on Lantern}
+\label{sec:deploy-lantern}
+
+Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
+proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
+
+Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.
+
+enproxy
+
+automated scanner
+
+\section{Deployment on Psiphon}
+\label{sec:deploy-psiphon}
+
+Psiphon~\cite{psiphon} is a network of many one-hop proxies,
+with encryption and traffic obfuscation between client and server.
+
+Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{clients-psiphon3}
+\caption{
+Daily unique users of \meek with
+Psiphon
+The decrease at the end of June
+was caused by an unblocking event that made \meek unnecessary for some users.
+}
+\label{fig:clients-psiphon3}
+\end{figure}
+
+how clients choose a technique
+
+unfronted mode
+
+users: Figure~\ref{fig:clients-psiphon3}
+
+% Appropriate TLS camouflage may differ depending on circumstances.
+% On a traditional desktop PC, using a browser is probably the right choice.
+% When Psiphon
+% ported \meekclient to Android,
+% they did not use a browser as camouflage,
+% but rather made all HTTPS requests with the standard Android HTTP API.
+% This decision makes sense because other Android applications
+% also use the standard API and share the same TLS fingerprint.
 
@@
 By removing the easy ways, we increase the censor's cost.
-
-\section{Deployment}
-\label{sec:deployment}
-
-Development on \meek as a Tor pluggable transport~\cite{pt} began in January~2014.
-For deployment we target
-the Tor Browser~\cite{torbrowser},
-a customized version of Firefox that is
-preconfigured to use a built-in Tor client.
-% and patched to defend against application-layer privacy and anonymity threats
-% like tracking cookies and web browser fingerprinting.
-Tor Browser has an easy interface for selecting pluggable transports.
-% ANON
-% [Some details of deployment are omitted for anonymous submission.]
-% We made a series of experimental releases of Tor Browser featuring \meek,
-% releasing the first one on February~18.
-% On April~18 we made the first release featuring the browser camouflage
-% that is the subject of Section~\ref{sec:browserextension}.
-% We announced our releases on Tor development mailing lists,
-% whence they were picked up by Tor Weekly News on the Tor blog.
-% Our code was merged by the Tor Browser maintainers
-% in June and is scheduled for an alpha release,
-% still pending as of this writing.
-
-We have so far deployed on three backends:
-Google App Engine,
-Amazon CloudFront,
-and Microsoft Azure.
-Figure~\ref{fig:clients-tor} shows the daily average number of concurrent users of \meek.
-(A measurement of 500, for example, means that there were on average 500
-users of the system at any given time during the day.)
-The App Engine backend was established in February;
-CloudFront in July;
-and Azure in October.
-Also in Figure~\ref{fig:clients-tor} is a table of monthly costs for each web service.
-The pricing for cloud services is complicated,
-depending not only on bandwidth but also on geographical region and other factors.
-For example CloudFront charges per request as well as per GB,
-and about 54\% of the CloudFront bill for October was for requests.
-App Engine charges extra when it has to run multiple instances
-of an app's code to cope with load;
-about 15\% of October's App Engine bill was for such ``instance hours.''
-% These and other cost details are summarized in a mailing list post~\cite{meek-costs-201410}.
-The App Engine and CloudFront backends are running on accounts
-that provide a limited amount of free bandwidth,
-but current use greatly exceeds the free thresholds.
-Azure service is being donated and so has not yet cost anything.
-The total cost so far has been \$187.13,
-but this number is expected to more than double in November and continue to increase.
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{clients-meek}
-\begin{tabular}{l r r r}
-       &App Engine &CloudFront&  Azure \\
-\hline
-Jan--Jul &  \$2.72 &   \$0.00 & \$0.00 \\
-Aug      &  \$1.56 &   \$3.10 & \$0.00 \\
-Sep      &  \$4.02 &   \$4.59 & \$0.00 \\
-Oct      & \$40.85 & \$130.29 & \$0.00 \\
-\hline
-total    & \$49.15 & \$137.98 & \$0.00 \\
-\end{tabular}
-\caption{
-Concurrent users of the \meek pluggable transport
-and month-by-month operational costs.
-The total cost to date is \$187.13.
-% ANON
-% The large increase of users on October~15 coincides with
-% the release of Tor Browser~4.0,
-% the first release to make meek easily available.
-Azure CDN service is currently being donated as part of a research grant.
-\vp{It would be valuable to build up some sort of estimate of what it
-would cost if you didn't have the grant.}
-The user estimates come from the Tor Metrics Portal~\cite{metrics-meek,counting-daily-bridge-users}.
-}
-\label{fig:clients-tor}
-\end{figure}
-
-% \begin{figure}
-% \includegraphics[width=\linewidth]{clients-psiphon3}
-% \caption{
-% Daily unique users of \meek with
-% [blinded circumvention tool]
-% % ANON
-% % Psiphon
-% (note vertical axis).
-% The decrease at the end of June
-% was caused by an unblocking event that made \meek unnecessary for some users.
-% }
-% \label{fig:clients-psiphon3}
-% \end{figure}
-
-%  &\$49.15 & \$137.98 & \$0.00 & \$187.13 &  \\
-
-% which aggregates statistics reported by Tor relays.
-% The number of users is estimated by counting the number
-% of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
 

### 2015-02-07 docs/fronting.tex
Speculatively remove Cloud-Entry.
I think we'll need the space and I don't think development of that tool
got very far.

@@
 
-Cloud-Entry~\cite{cloud-entry} is somewhat similar to GoAgent.
-It also uses App Engine, but via a socket API rather than a URL fetch API,
-in order to support protocols other than HTTP and HTTPS.
-Cloud-Entry has the same NAT problem as flash proxy,
-because the proxy tries to connect back to the client with a socket.
-App Engine kills web requests (and their associated socket connections)
-when they take longer than 60~seconds,
-so users must reconnect at least that often.
+% Cloud-Entry~\cite{cloud-entry} is somewhat similar to GoAgent.
+% It also uses App Engine, but via a socket API rather than a URL fetch API,
+% in order to support protocols other than HTTP and HTTPS.
+% Cloud-Entry has the same NAT problem as flash proxy,
+% because the proxy tries to connect back to the client with a socket.
+% App Engine kills web requests (and their associated socket connections)
+% when they take longer than 60~seconds,
+% so users must reconnect at least that often.
 

### 2015-02-07 docs/fronting.tex
Move commented JumpBox ref to the TLS camouflage section.
This is where it belongs if I decide to put it in.
Hack related work.
Make active probing a peer of address blocking and content blocking.

@@
 
-Broadly speaking, there are two main challenges in circumvention:
-blocking by content and blocking by address.
+Broadly speaking, there are three main challenges in proxy-based circumvention:
+blocking by content, blocking by address, and active probing.
 Blocking by content is based on \emph{what you say},
-and blocking by address is based on \emph{whom you talk to}.
+blocking by address is based on \emph{whom you talk to},
+and active probing means \emph{the censor acts as a client}.
+A savvy censor will employ all these techniques, and
+effective circumvention requires countering them all.
+
 A content-blocking censor inspects packets and payloads,
@@
 the contents of the communication.
-A savvy censor will use both means of censorship, and
-effective circumvention requires countering both.
-
-To the above challenges we add a related one, active probing.
-An active-probing censor does not merely passively observe traffic:
-it injects its own traffic,
-acting as if it were an ordinary client and connecting to suspected
-proxy servers to see how they respond.
-Then a connection is successful, the server can be blacklisted.
+An active-probing censor does not limit itself to observation and manipulation
+only of user-induced traffic.
+It sends its own proxy requests (active probes),
+either proactively or on demand in response to observed traffic,
+and blacklists any proxies it finds thereby.
 Active probing is a precise means of identifying whether a server belongs to a circumvention system,
-even when a protocol is hard to detect on the wire.
+even when a protocol is hard to detect on the wire---in this way it can
+regarded as a way of reducing accidental overblocking.
 Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
-Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
-by issuing scans that follow up on observed client connections, to discover
-whether a server speaks the Tor protocol.
+Wilde~\cite{wilde} that China's Great Firewall discovers secret Tor bridges
+by issuing its own followup scans after observing a suspected Tor connection.
 
 There are two general strategies for countering content-based blocking.
-The first is to make traffic look unlike
-anything forbidden by the censor; that is, fail to match a blacklist. The second is
-to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
+The first is to look unlike anything the censor blocks;
+the second is to look like something the censor allows.
 Following the first strategy are the so-called ``look-like-nothing'' transports whose
@@
 The other strategy against DPI is the steganographic one: look like
-something the censor does not block.
+something allowed by the censor.
 fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings
@@
 in order to disrupt a covert channel, without much harming ordinary VoIP calls.
-\vp{The above could be compressed somewhat to save room}
-
-The other grand challenge of proxy-based circumvention is address-based blocking.
+
+The challenge of address-based blocking is a difficult one
+that has inspired various creative circumvention ideas.
 Tor has long faced the problem of the blocking of its relays,
@@
 In response, Tor began to reserve a portion of its
-new relays as secret ``bridges''~\cite{tor-blocking}
+relays as secret ``bridges''~\cite{tor-blocking}
 whose addresses are not publicly known.
 BridgeDB, the database of secret bridges,
-carefully distributes bridge addresses
-so that anyone can learn a few bridges, but it is hard to learn all of them.
+carefully distributes addresses
+so that anyone may learn a few bridges, but it is hard to enumerate all of them.
 BridgeDB uses CAPTCHAs and other rate-limiting measures,
 and over short time periods,
-always returns the same set of bridges to the same requester,
+always returns the same bridges to the same requester,
 preventing enumeration by simple repeated queries.
 BridgeDB is also capable of distributing the addresses
-of obfuscated bridges (obfs3 or ScrambleSuit);
-the combination
-of careful bridge address distribution and obfuscated protocols
-gives Tor's system a realistic claim to addressing both main challenges of circumvention.
-Address distribution appears to be the weaker side of the defense,
-as evidenced by real-world censors' apparent preference for
-blocking bridge addresses over real-time DPI-based blocking~\cite{foci12-winter}.
+of obfuscated bridges (currently obfs3, obfs4, ScrambleSuit, and fteproxy),
+granting some address-blocking resistance to those systems that otherwise lack it.
+% Address distribution appears to be the weaker side of the defense,
+% as evidenced by real-world censors' apparent preference for
+% blocking bridge addresses over real-time DPI-based blocking~\cite{foci12-winter}.
 
@@
 Flash proxy's approach to address blocking is
-the opposite of \meek's:
+the opposite of domain fronting's:
 where flash proxy uses many cheap, disposable, individually blockable proxies,
-\meek uses just a few high-value front domains on hard-to-block network infrastructure.
+domain fronting uses just a few high-value front domains on hard-to-block network infrastructure.
 A drawback with flash proxy's use of the browser is that
@@
 a small amount of unblockable data in a process called rendezvous.
-The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
+The default rendezvous mechanism has been domain fronting through Google App Engine since 2013~\cite{flashproxy-reg-appspot}.
 Flash proxy itself does nothing to defend against DPI.
@@
 WebSocket, a meta-protocol running on HTTP,
-but inside the WebSocket framing is the ordinary Tor protocol.
+but inside the WebSocket framing is the ordinary TLS-based Tor protocol.
 % There exists a prototype transport that attempts to get both
@@
 OSS shares certain similarities with domain fronting:
-an unblockable web service takes the place of the front domain,
-and the destination of the communication is embedded somewhere in an HTTPS query
+a hard-to-block web service takes the place of the front domain,
+and the destination is embedded somewhere in an HTTPS query
 rather than in the Host header.
-\vp{Sketch the limitations of this approach}
+OSS has high overhead and low capacity,
+and suffers the same limitations with NAT on the client that flash proxy has.
 
@@
 while fronting uses the HTTP Host header, encrypted within HTTPS.
-Fronting has the advantage that it does not require active cooperation by network intermediaries.
+Fronting has the advantage that it does not require cooperation by network intermediaries.
 
@@
 was by GoAgent~\cite{goagent},
-a tool based on App Engine and
+a tool based on Google App Engine and
 once widely used in China.
-Traffic is fronted by the Google frontend server,
-using the ``domainless'' fronting model without SNI,
-and delivered to its destination by a specialized app running on App Engine.
+Users of GoAgent upload
+a personal copy of the proxy code to App Engine,
+where it runs on a subdomain of \urll{appspot.com}.
+In order to reach \urll{appspot.com},
+GoAgent fronts through a Google IP address,
+using the ``domainless'' model without SNI.
 GoAgent does not use an additional general-purpose proxy after fronting;
-rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
-Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
-and the contents of all communications are revealed to Google.
-Users of GoAgent upload
-their own personal copy of the proxy code to App Engine,
-which is free of charge to use as long as they do not exceed a bandwidth quota.
+rather, it fetches URLs directly from the App Engine servers.
+Because of that, GoAgent does not support protocols other than HTTP and HTTPS,
+and the end-to-end security of HTTPS is lost,
+as web pages exist in plaintext on the App Engine servers before being re-encrypted back to the client.
+App Engine is free to use under a daily bandwidth quota of 1~GB.
 According to a May 2013 survey~\cite{collateral-freedom},
-GoAgent was the circumvention tool most used in
+GoAgent was the most-used circumvention tool in
 China, with 35\% of survey respondents having used it in the previous month.
-This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
-above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
+It ranked higher than paid~(29\%) and free VPNs~(18\%), and far
+above special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
 Use of GoAgent in China was disrupted starting in the beginning of June~2014,
 when all Google services were blocked~\cite{cn-google-block}.
-\meek over App Engine was similarly affected.
-\vp{Add mention of what \meek platforms still worked.}
-% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.
+The block also affected meek, the subject of Section~\ref{sec:deploy-tor},
+when used with App Engine, though it continued to work in China over the alternate backends
+Amazon CloudFront and Microsoft Azure.
 
@@
 % CORDON? Say how \meek would be classified in it?
-
-% Section~\ref{sec:browserextension}, JumpBox
-% http://securecomm.org/2014/show/tutorials
 
@@
 because that portion of the communication flow is not observed by the censor.
+
+% Section~\ref{sec:browserextension}, JumpBox
+% http://securecomm.org/2014/show/tutorials
 

### 2015-02-09 docs/clients-meek.R
Refactor client graphs, use thousands separators.

@@ -9,8 +9,12 @@ daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
 # Exclude today, because it reflects a not-yet-settled value.
 p <- ggplot(data[data$date >= as.Date("2014-08-01") & data$date < Sys.Date(), ], aes(x=date, y=clients))
-p <- p + geom_bar(stat="identity", width=1.1) + xlab(NULL) + ylab("Mean concurrent users") + scale_x_date(labels=date_format("%b %Y")) + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
-ggsave("clients-meek.pdf", width=4, height=1.4, units="in")
+p <- p + geom_bar(stat="identity", width=1.1)
+p <- p + xlab(NULL) + ylab("Mean concurrent users")
+p <- p + scale_x_date(labels=date_format("%b %Y"))
+p <- p + scale_y_continuous(labels=comma)
+p <- p + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
+ggsave("clients-meek.pdf", p, width=4, height=1.4, units="in")
 
 # p <- p + geom_vline(xintercept=as.numeric(as.Date(c("2014-02-18", "2014-04-11", "2014-04-18", "2014-04-25", "2014-05-07", "2014-05-08"))), color="red")
 # 2014-02-18 [tor-qa] Please test experimental bundles with meek transport (3.5.2.1-meek-1)

### 2015-02-09 docs/clients-psiphon3.R

@@ -6,5 +6,9 @@ data$date <- as.Date(data$date, format="%b %d, %Y")
 daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
 p <- ggplot(data, aes(x=date, y=clients))
-p <- p + geom_bar(stat="identity", width=1.1) + xlab(NULL) + ylab("Daily unique users") + scale_x_date(labels=date_format("%b %Y")) + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
-ggsave("clients-psiphon3.pdf", width=4, height=1.4, units="in")
+p <- p + geom_bar(stat="identity", width=1.1)
+p <- p + xlab(NULL) + ylab("Daily unique users")
+p <- p + scale_x_date(labels=date_format("%b %Y"))
+p <- p + scale_y_continuous(labels=comma)
+p <- p + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
+ggsave("clients-psiphon3.pdf", p, width=4, height=1.4, units="in")

### 2015-02-09 docs/fronting.tex
\hyphenation{Go-Agent}
It was being broken as
	GoA-
	gent
CDN survey table.

@@
 \usepackage{color}
-
-\hyphenation{Client-Hello}
+\usepackage{threeparttable}
+
+\hyphenation{Client-Hello Go-Agent}
 
@@
 \newcommand{\vp}[1]{\note{#1 --VP}}
+
+\newcommand{\yes}\checkmark
 
@@
 
-\vp{This whole section should be beefed up with a deeper assessment.  Along
-these lines, it would help to include a summary table.}
+\begin{table*}[ht]
+\centering
+\begin{threeparttable}
+
+\caption{
+Summary of fronting-capable services.
+}
+\label{tab:survey}
+
+\begin{tabular}{l r r r r c}
+service                    &        \$/GB & \$/10K requests & \$/hour & \$/month & allows SNI$\ne$Host\tnote{1} \\
+\hline
+Google App Engine\tnote{2} &        0.120 &              -- &    0.05 &       -- & \yes \\
+Amazon CloudFront          & 0.085--0.250 &    0.010--0.022 &      -- &       -- & \yes \\
+Microsoft Azure            & 0.087--0.138 &              -- &      -- &       -- & \yes \\
+CloudFlare                 &           -- &              -- &      -- &      200 & \yes \\
+Akamai\tnote{3}            &           -- &              -- &      -- &      400 & \yes \\
+Fastly\tnote{4}            & 0.120--0.190 &    0.010--0.012 &      -- &       -- &      \\
+Level~3\tnote{5}           & 0.035--0.200 &              -- &      -- &       -- & \\
+% EdgeCast
+\noalign{\smallskip}
+\end{tabular}
+
+\begin{tablenotes}
+\item[1] A missing checkmark in the ``allows SNI$\ne$Host'' column means the service requires the ``domainless'' fronting style.
+\item[2] App Engine dynamically scales the number of ``instances'' of the application code in order to handle changing load. Roughly, every instance after the first costs \$0.05/hour.
+\item[3] Akamai does not publish pricing information; the prices here are from a reseller called Cache Simple, which quotes \$400/month for 1000~GB transfer, and \$0.50/GB beyond that.
+\item[4] Fastly has a minimum montly charge of \$50.
+\item[5] Level~3 does support domain fronting per se, but paths under the \urll{secure.footprint.net} domain can likely serve the same purpose.
+Level~3 does not publish pricing information; the prices here are from a reseller called VPS.NET, which quotes \$34.95 for the first 1000~GB and \$200 thereafter.
+\end{tablenotes}
+
+\end{threeparttable}
+\end{table*}
+
+In this section we survey a variety of web services and evaluate
+their suitability for domain fronting.
+Most of the services we evaluated support fronting in one form or another,
+but they each have their own quirks and performance characteristics.
+Table~\ref{tab:survey} summarizes the services.
+
 This section contains a brief survey of fronting-capable

### 2015-02-11 docs/fronting.tex
Expansion of survey.

@@
 as web pages exist in plaintext on the App Engine servers before being re-encrypted back to the client.
-App Engine is free to use under a daily bandwidth quota of 1~GB.
 According to a May 2013 survey~\cite{collateral-freedom},
@@
 The block also affected meek, the subject of Section~\ref{sec:deploy-tor},
-when used with App Engine, though it continued to work in China over the alternate backends
+when used with App Engine, though it continued to work in China over alternate backends,
 Amazon CloudFront and Microsoft Azure.
@@
 Summary of fronting-capable services.
+Does not include some general classes of services (such as shared web hosting)
+that may work for domain fronting.
+Pricing is accurate as of February~2015.
+A ``no'' in the ``allows SNI$\ne$Host'' means that the service requires the ``domainless'' fronting style.
 }
@@
 \begin{tabular}{l r r r r c}
-service                    &        \$/GB & \$/10K requests & \$/hour & \$/month & allows SNI$\ne$Host\tnote{1} \\
+service                    &        \$/GB & \$/10K requests & \$/hour & \$/month & allows SNI$\ne$Host \\
 \hline
-Google App Engine\tnote{2} &        0.120 &              -- &    0.05 &       -- & \yes \\
-Amazon CloudFront          & 0.085--0.250 &    0.010--0.022 &      -- &       -- & \yes \\
-Microsoft Azure            & 0.087--0.138 &              -- &      -- &       -- & \yes \\
-CloudFlare                 &           -- &              -- &      -- &      200 & \yes \\
-Akamai\tnote{3}            &           -- &              -- &      -- &      400 & \yes \\
-Fastly\tnote{4}            & 0.120--0.190 &    0.010--0.012 &      -- &       -- &      \\
-Level~3\tnote{5}           & 0.035--0.200 &              -- &      -- &       -- & \\
+Google App Engine\tnote{1} &        0.120 &              -- &    0.05 &       -- & yes \\
+Amazon CloudFront          & 0.085--0.250 &    0.010--0.022 &      -- &       -- & yes \\
+Microsoft Azure            & 0.087--0.138 &              -- &      -- &       -- & yes \\
+CloudFlare                 &           -- &              -- &      -- &      200 & yes \\
+Fastly\tnote{2}            & 0.120--0.190 &    0.010--0.012 &      -- &       -- & no  \\
+Akamai\tnote{3}            &           -- &              -- &      -- &      400 & yes \\
+Level~3\tnote{4}           & 0.035--0.200 &              -- &      -- &       -- & no  \\
 % EdgeCast
@@
 \begin{tablenotes}
-\item[1] A missing checkmark in the ``allows SNI$\ne$Host'' column means the service requires the ``domainless'' fronting style.
-\item[2] App Engine dynamically scales the number of ``instances'' of the application code in order to handle changing load. Roughly, every instance after the first costs \$0.05/hour.
+\item[1] App Engine dynamically scales the number of ``instances'' of the application code in order to handle changing load. Roughly, every instance after the first costs \$0.05/hour.
+\item[2] Fastly has a minimum monthly charge of \$50.
 \item[3] Akamai does not publish pricing information; the prices here are from a reseller called Cache Simple, which quotes \$400/month for 1000~GB transfer, and \$0.50/GB beyond that.
-\item[4] Fastly has a minimum montly charge of \$50.
-\item[5] Level~3 does support domain fronting per se, but paths under the \urll{secure.footprint.net} domain can likely serve the same purpose.
+\item[4] Level~3 does support domain fronting per se, but paths under the \urll{secure.footprint.net} domain can likely serve the same purpose.
 Level~3 does not publish pricing information; the prices here are from a reseller called VPS.NET, which quotes \$34.95 for the first 1000~GB and \$200 thereafter.
@@
 but they each have their own quirks and performance characteristics.
-Table~\ref{tab:survey} summarizes the services.
-
-This section contains a brief survey of fronting-capable
-web services we have found, each with its pros and cons.
-The list is not exhaustive and is meant to illustrate the broad
-support for fronting that exists.
-Of the services listed, we have so far deployed \meek
-only on Google App Engine and Amazon CloudFront.
-For the others, we have only checked that fronting works.
-Recall that even web services that support fronting
-will front only for their own customers,
-so new each deployment typically requires an investment of time and money.
-
-Google App Engine~\cite{googleappengine}
+The survey is not exhaustive but it includes many of the most prominent
+content delivery networks.
+Table~\ref{tab:survey} is a summary.
+
+Pricing across services varies widely,
+and depends on complicated factors such as geographical region,
+bandwidth tiers, and free thresholds.
+Some services charge for bandwidth,
+some for time, and some for other resources.
+Most services charge between \$0.10 and \$0.20 per GB;
+usually bandwidth is cheaper in North America and Europe
+than in the rest of the world.
+
+Recall that even services that support domain fronting
+will front only for the domains of their own customers.
+Deployment on a new service typically requires becoming a customer,
+and an outlay of time and money.
+Of the services surveyed, we have deployed domain fronting in some form
+on Google App Engine, Amazon CloudFront, Microsoft Azure, CloudFlare, and Fastly.
+For the others, we have only checked that domain fronting
+(or some similar technique)
+is likely to work.
+
+\smallskip
+
+% https://cloud.google.com/appengine/pricing
+\textbf{Google App Engine}~\cite{googleappengine}
 is a web application platform.
+Users can upload a web app needing nothing more than a Google account.
 Each application gets a user-specified subdomain of \urll{appspot.com},
-which can be fronted through almost any Google domain,
+for which almost any Google domain can serve as a front,
 including google.com, gmail.com, googleapis.com, and many others.
-App Engine can run only web applications,
-not a full Tor bridge;
-for that reason we use a tiny ``reflector'' application
-that merely copies incoming requests to a Tor bridge hosted elsewhere.
-Fronting through App Engine is attractive in the case where even though
-the censor blocks
-\urll{appspot.com}---which could well occur,
-because of the ease of building a proxy there---at least one
-other Google service remains reachable.
-Applications that use $< 1$~GB of bandwidth daily
-are free of charge,
-making possible an upload-your-own-app model
-à la GoAgent.
-
-Amazon CloudFront~\cite{cloudfront}
-(not to be confused with CloudFlare; see below)
+App Engine can run only web applications serving short-lived requests,
+not a general-purpose proxy such as a Tor bridge.
+For that reason we use a tiny ``reflector'' application
+that merely forwards incoming requests to a long-lived proxy running elsewhere.
+Fronting through App Engine is attractive in the case where the censor blocks
+\urll{appspot.com} but at least one
+other Google domain is reachable.
+App Engine costs \$0.12/GB and \$0.05 for each ``instance hour''
+(the number of running instances of the app is adjusted dynamically
+to meet load, and you pay for each instance after the first).
+Applications are free of charge if they stay below certain
+usage thresholds, for example 1~GB of bandwidth daily,
+making possible a distributed, upload-your-own-app model
+in the style of GoAgent.
+
+% https://aws.amazon.com/cloudfront/pricing/
+\textbf{Amazon CloudFront}~\cite{cloudfront}
 is the CDN of Amazon Web Services.
-A CloudFront ``distribution'' associates
+A CloudFront ``distribution,'' as a CDN configuration is called, associates
 an automatically generated subdomain of \urll{cloudfront.net}
-with an origin server,
-which in our case is an instance of \meekserver.
-The front domain may be any other of CloudFront's automatically generated subdomains, all
-of which support HTTPS through a wildcard certificate.
+with an origin server.
+The front domain may be any other \urll{cloudfront.net} subdomain
+(all of which support HTTPS through a wildcard certificate),
+or any other DNS alias for them.
+CloudFront is easy to set up:
+one must only set the origin domain and no reflector app is needed.
+Pricing per GB ranges from \$0.085 for the United States and Europe,
+up to \$0.25 for South America,
+with price breaks starting at 10~TB/month.
+There is an additional charge per 10,000 HTTPS requests,
+ranging from \$0.0075 in the United States
+to \$0.0160 in South America.
 CloudFront has a usage tier that is free of charge for a year,
@@
 
-Microsoft Azure~\cite{azure}
+% https://azure.microsoft.com/en-us/pricing/details/cdn/
+\textbf{Microsoft Azure}~\cite{azure}
 is a cloud computing platform that features a CDN.
-Similarly to CloudFront, users get automatically generated subdomains
-of \urll{vo.msecnd.net},
-all of which can front for each other.
-The CDN works only for Azure domains, however,
-so as with App Engine, it is necessary to run a trivial reflector app
-that merely forwards requests out of Azure toward an external proxy.
-There are other front domain names, like \urll{ajax.aspnetcdn.com},
-that may provide entangling with high collateral damage.
-
-CloudFlare~\cite{cloudflare}
+Like CloudFront, Azure assigns automatically generated subdomains
+of \urll{vo.msecnd.net}.
+any of which can front for any other.
+There are other possible front domain names, like \urll{ajax.aspnetcdn.com},
+that are used as infrastructure by many web sites,
+lending them high collateral damage.
+Unlike CloudFront's, Azure's CDN works only for Azure-affiliated domains,
+so as with App Engine, it is necessary to run a reflector app on Azure
+that forwards requests to some other proxy proxy.
+
+% https://www.cloudflare.com/plans
+\textbf{CloudFlare}~\cite{cloudflare}
 is a CDN also marketed as protection against
 denial-of-service attacks.
-It appears that any domain name on CloudFlare
-can front for any other, even custom user-selected domains;
-however it is not obvious which one is best to use as a front.
-The front domain needs to be a popular one
-(causing high collateral damage if blocked),
-or the censor may simply block it entirely.
-It is doubly bad when a domain is blocked in this way,
-because not only is circumvention foiled,
-but some unsuspecting third party has just had their web site blocked.
-A solution may be to round-robin through
-a pool of popular domain names;
-or to use ``domainless'' fronting that does not send SNI.
-\vp{Would be quite valuable to more broadly assess the viability
-of using domainless fronting}
-% Though CloudFlare supports domain fronting,
-% its terms of service~\cite{cloudflare-terms}
-% seem to prohibit the kind of tunneled proxying that \meek does:
-% \begin{quote}
-% \textsc{Section 10: Limitation on non-HTML caching}\\
-% You acknowledge that CloudFlare's Service is offered as a platform to cache and
-% serve web pages and websites and is not offered for other purposes
-% \ldots\ you understand and agree to use the Service solely
-% for the purpose of hosting and serving web pages\ldots
-% \end{quote}
-
-Akamai~\cite{akamai-site} is a large CDN.
+Almost any domain name on CloudFlare
+can front for any other, even custom user-controlled domains.
+(We have found some domains, like \urll{imgur.com},
+that do not work as fronts, though they can be fronted to.)
+CloudFlare charges per month and does not separately charge for bandwidth.
+There is a free tier intended for small web sites,
+which would be adequate for a personal domain-fronting installation.
+The ``business'' plan is \$200/month.
+
+% https://www.fastly.com/pricing/
+\textbf{Fastly}~\cite{fastly} is a CDN.
+It is unusual in that it validates the SNI:
+if the SNI and Host do not match,
+the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
+However, if the TLS ClientHello simply omits SNI, then the Host may be any Fastly domain.
+Fastly therefore requires the ``domainless'' fronting style.
+Fastly's pricing model is similar to CloudFront's.
+They charge between \$0.12 and \$0.19 per GB
+and \$0.0075 and \$0.009 per 10,000 requests, depending on region.
+
+% http://cachesimple.com/get.php?p=plans
+\textbf{Akamai}~\cite{akamai-site} is a large CDN.
 Requests may be fronted through the special HTTPS domain
 \urll{a248.e.akamai.net},
-which serves a certificate also good for \urll{*.akamaihd.net}.
-The collateral damage of blocking Akamai is enormous:
+or other customer-configured DNS aliases,
+though as with CloudFlare it appears that certain domains
+get special treatment and do not work as fronts.
+Akamai has to potential to provide a lot of cover:
 in 2010 it carried 15--20\% of all web traffic~\cite{akamai}.
-Akamai costs more than other CDNs;
-it would likely require institutional support
-to keep a circumvention system running on it in the long term.
-
-Fastly~\cite{fastly} is a CDN.
-It is the only one of the services we tested that
-appears to enforce SNI consistency:
-if the SNI and Host do not match,
-the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
-However, if the TLS ClientHello omits SNI, then the Host may be any Fastly domain.
-It is the only service we have found
-that requires the ``domainless'' fronting style.
+Akamai does not publish pricing details,
+but it is reputed to be among the pricier CDNs.
+We found a reseller, Cache Simple,
+that charges \$400 for 1000~GB/month, and \$0.50/GB after that.
+The special domain
+\urll{a248.e.akamai.net}
+began to be DNS-poisoned in China in late September~2014~\cite{akamai-greatfire}
+(possibly because it had been used to mirror blocked web sites),
+necessitating an alternative front domain in that country.
+
+\textbf{Level~3}~\cite{level3}
+is a tier-1 network operator that has a CDN.
+Unlike other services in this section,
+Level~3 does not appear to support domain fronting.
+However, we mention it because it may be possible to build similar functionality
+using distinct URL paths under the domain \urll{secure.footprint.net}
+(essentially using the path, rather than the Host header, as a hidden tag).
+Level~3 does not publish pricing data.
+We found a reseller, VPS.NET, that quotes
+\$34.95 for the first 1000~GB and \$200 thereafter.
+As with \urll{a248.e.akamai.net},
+the domain \urll{secure.footprint.net} is
+currently DNS-poisoned in China.
+
+% \textbf{EdgeCast}~\cite{edgecast}
+% GFW blocking of edgecast.net.
+
+\smallskip
+
+There are other potential domain-fronting deployments apart from CDNs.
+For example, there are cheap web hosts that support both PHP and
+HTTPS (with a shared certificate).
+These features are enough to support a reflector written in PHP,
+which users can upload under their own initiative.
+In this do-it-yourself model, blocking resistance comes not from a strong front domain,
+but from the diffuseness of many proxies, each carrying only a small amount of traffic.
+
+% https://lists.torproject.org/pipermail/tor-dev/2015-February/008239.html
+Another alternative is deployment with the cooperation of an existing important web site,
+the blocking of which would result in high collateral damage.
+It is a nice feature of domain fronting that it does not require cooperating
+by the intermediate web service,
+but if you have cooperation, you can achieve greater efficiency.
+The important web site could, for example, reserve a
+magic URL path or domain name, and forward matching requests
+to a proxy running locally.
+The web site does two jobs:
+its ordinary high-value operations that make it expensive to block,
+and a side job of handling circumvention traffic.
+The censor cannot tell which is which
+because the difference is confused by HTTPS.
 
@@
 rather than providing ingress to Tor.}
+
+% Moved from CloudFlare section:
+% The front domain needs to be a popular one
+% (causing high collateral damage if blocked),
+% or the censor may simply block it entirely.
+% It is doubly bad when a domain is blocked in this way,
+% because not only is circumvention foiled,
+% but some unsuspecting third party has just had their web site blocked.
+% A solution may be to round-robin through
+% a pool of popular domain names;
+% or to use ``domainless'' fronting that does not send SNI.
 

### 2015-02-11 docs/fronting.tex
Coax the survey table into \linewidth.

@@
 
-\begin{table*}[ht]
+\begin{table}
 \centering
@@
 that may work for domain fronting.
-Pricing is accurate as of February~2015.
-A ``no'' in the ``allows SNI$\ne$Host'' means that the service requires the ``domainless'' fronting style.
+Prices are current as of February~2015 and are
+rounded to the nearest cent.
 }
@@
 
-\begin{tabular}{l r r r r c}
-service                    &        \$/GB & \$/10K requests & \$/hour & \$/month & allows SNI$\ne$Host \\
+\begin{tabular*}{\linewidth}{l r r r r}
+service             &        \$/GB & \$/10K reqs. & \$/hour & \$/month \\
 \hline
-Google App Engine\tnote{1} &        0.120 &              -- &    0.05 &       -- & yes \\
-Amazon CloudFront          & 0.085--0.250 &    0.010--0.022 &      -- &       -- & yes \\
-Microsoft Azure            & 0.087--0.138 &              -- &      -- &       -- & yes \\
-CloudFlare                 &           -- &              -- &      -- &      200 & yes \\
-Fastly\tnote{2}            & 0.120--0.190 &    0.010--0.012 &      -- &       -- & no  \\
-Akamai\tnote{3}            &           -- &              -- &      -- &      400 & yes \\
-Level~3\tnote{4}           & 0.035--0.200 &              -- &      -- &       -- & no  \\
+App Engine\tnote{1} &       0.12 &              -- &    0.05 &       -- \\
+CloudFront          & 0.09--0.25 &      0.01--0.02 &      -- &       -- \\
+Azure               & 0.09--0.14 &              -- &      -- &       -- \\
+CloudFlare          &         -- &              -- &      -- &      200 \\
+Fastly\tnote{2}     & 0.12--0.19 &            0.01 &      -- &       -- \\
+Akamai\tnote{3}     &         -- &              -- &      -- &      400 \\
+Level~3\tnote{4}    & 0.03--0.20 &              -- &      -- &       -- \\
 % EdgeCast
 \noalign{\smallskip}
-\end{tabular}
+\end{tabular*}
 
@@
 \item[1] App Engine dynamically scales the number of ``instances'' of the application code in order to handle changing load. Roughly, every instance after the first costs \$0.05/hour.
-\item[2] Fastly has a minimum monthly charge of \$50.
-\item[3] Akamai does not publish pricing information; the prices here are from a reseller called Cache Simple, which quotes \$400/month for 1000~GB transfer, and \$0.50/GB beyond that.
+\item[2] Fastly edge servers require that the SNI match the Host header, therefore it is necessary to use ``domainless'' fronting and omit SNI. There is a minimum monthly charge of \$50.
+\item[3] Akamai does not publish pricing information; the prices here are from a reseller called Cache Simple, which quotes \$400/month for 1000~GB transfer, and \$0.50/GB for overages.
 \item[4] Level~3 does support domain fronting per se, but paths under the \urll{secure.footprint.net} domain can likely serve the same purpose.
@@
 \end{threeparttable}
-\end{table*}
+\end{table}
 

### 2015-02-11 docs/fronting.tex
Add Azure pricing to text.
Add in Lantern text.
Mostly unedited except for BibTeX cites.

@@
 that forwards requests to some other proxy proxy.
+Bandwidth is \$0.087--0.138/GB, with price breaks starting at 10~TB/month.
 
@@
 
-Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
-proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
-
-Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.
-
-enproxy
-
-automated scanner
+Lantern~\cite{lantern} is a free circumvention tool targeting casual web browsing.
+Lantern does not employ onion routing and in general does not provide the
+same level of anonymity guarantees as Tor.  Lantern primarily focuses on
+performance and availability.
+
+At its core, Lantern is a network of shared HTTPS proxy servers combined
+with a client application that allows censored users to find and use those
+proxy servers to proxy traffic from their existing web browsers.  This same
+client application also allows uncensored users to host such proxy servers
+on their own networks for use by other Lantern users. Lantern ultimately
+aims to provide a secure mechanism for distributing knowledge about both
+Lantern-hosted and peer-hosted proxy servers using a trust-network based
+distribution mechanism such as kaleidoscope~\cite{kaleidoscope}.  In the meantime, Lantern
+also randomly assigns users to Lantern-hosted proxy servers.
+
+Lantern uses a centralized infrastructure for authenticating users and
+assigning proxies to them.  Lantern's threat model assumes that this
+centralized infrastructure is or can be blocked by the censors.
+Consequently, users must have a priori access to a functioning proxy which
+they can use to bootstrap onto the Lantern network and learn about more
+proxies. Prior to Lantern adopting domain-fronting, we gave users access to
+such proxies (which we call fallbacks) by embedding their information in
+customized software installers that we distributed directly to users.  This
+prevented users from downloading Lantern directly and required them to
+request an email invitation from us with a link to their custom installer.
+Furthermore, since anyone could request an installer, the censors could
+theoretically learn about all of our proxies simply by continually
+requesting installers.
+
+\subsection{Timeline for Deploying Domain-Fronting}
+
+\begin{figure}
+\centering
+\includegraphics[height=1.5in]{lantern}
+\caption{
+Megabytes per second served by domain-fronted Lantern proxies
+(Lantern-hosted and peers).
+}
+\label{fig:lantern-bandwidth}
+\end{figure}
+
+Lantern rolled out domain-fronting via CloudFlare in July 2014 in order to
+allow users to direct-download Lantern without an email invitation.  In
+this initial implementation, direct-downloaded Lantern clients proxied all
+their traffic using domain-fronting.  It worked, and we experienced steady
+growth in direct downloads and traffic from direct-downloaded clients.
+
+At the beginning of October 2014, we started randomly assigning direct
+HTTPS proxies to users who had direct-downloaded Lantern.  This diverted
+traffic from domain-fronted servers to more efficient direct servers.
+
+In December 2014 and January 2015, Lantern experienced a dramatic surge in
+domain-fronted traffic, jumping from 1 MB/s to 100 MB/s within those two
+months. At first we assumed that direct proxies had been blocked, but it
+turns out that the majority of this new traffic originated in the
+Philippines, which is not a heavily censored country. From what we're
+hearing, it looks like Philippine users are using Lantern to get around
+their ISPs bandwidth caps~\cite{needed}.
+
+\subsection{General Deployment Considerations}
+
+Unlike with meek, Lantern's equivalent of reflectors (which we call
+proxies) are also exit nodes.  So in our infrastructure, we have:
+
+user agent → Lantern client → CDN → Lantern proxy → destination.
+
+Lantern hosts dozens of such proxies on commodity VPS providers like
+Digital Ocean. In addition, uncensored users who run the Lantern client can
+register themselves as domain-fronted proxies as well, so overall there are
+theoretically a very large number of proxies in rotation at any one time.
+
+\subsection{Choice of CDN}
+In our initial implementation, we used Fastly as our CDN.  Fastly ended up
+being unsuitable because their infrastructure isn't meant to support a
+large number of backends, so we transitioned to CloudFlare.  CloudFlare has
+worked well so far because it supports a large number of backends, it has
+an API that we can use to manage those backends and it has cheap flat-rate
+pricing that doesn't charge based on bandwidth consumption. It also has
+a sufficient number of relatively high-profile domains through which we can
+front.
+
+\subsection{Implementation Components}
+Lantern's domain fronting is implemented in Go and made available through
+the flashlight~\cite{flashlight} application.
+The core of flashlight's domain fronting is encapsulated in two libraries,
+enproxy~\cite{enproxy} and fronted~\cite{fronted}.
+
+enproxy provides an implementation of Go's standard net.Conn interface that
+encapsulates reads and writes as a series of HTTP requests via a stateful
+enproxy proxy.  This allows flashlight to proxy any streaming-oriented
+traffic (e.g. TCP).  Unlike meek, enproxy supports full-duplex~\cite{beating-gfw-with-go} operation
+so that reads don't wait on writes, which can be handy for bidirectional
+protocols like XMPP.  Lantern actually uses XMPP as a signaling channel for
+peer-to-peer traffic, and tunnels XMPP via domain-fronted proxies.
+
+fronted uses domain-fronting to transmit enproxy's HTTP requests in a
+blocking-resistant manner. It provides a facility for configuring a number
+of different front domains (masquerade hosts) and includes the ability to
+connect to them directly by IP address rather than DNS. In practice,
+flashlight uses several hundred masquerade hosts when communicating via
+CloudFlare.
+
+\subsection{Sticky Routing}
+Domain-fronted Lantern requests go to one of two host names,
+fallbacks.getiantem.org and peers.getiantem.org.  Fallbacks is a pool of
+servers hosted by Lantern, and peers is the pool of servers constituted by
+online Lantern peers.  When using CloudFlare, a server is selected based by
+round robin.  Just like with meek, Lantern's domain-fronting protocol is
+stateful, so subsequent HTTP requests for the same connection need to find
+their way back to the same proxy that handled the original request.  We
+accomplish this by having the responding proxy return its specific hostname
+in a header which the client then users on subsequent requests, thereby
+bypassing the round robin.
+
+\subsection{Added Latency in Domain-fronted Encapsulated HTTP Transports and
+Mitigations for the Same}
+Encapsulating a streaming network connection in a series of HTTP requests
+introduces additional latency beyond TCP. In the case of flashlight and
+CloudFlare, there are several causes of this latency:
+
+Firstly, domain-fronting requires the establishment of additional TCP
+connections. In a best case scenario, the user agent can open a single TCP
+connection directly to the destination server.  With Lantern, the inclusion
+of the client, CloudFlare and the proxy introduce three additional TCP
+connections between the user agent and the destination.  This is mitigated
+somewhat by the fact that CloudFlare pools and reuses connections to the
+Lantern proxy.  Unfortunately, the Lantern client cannot do the same for
+connections to CloudFlare as CloudFlare seems to time out idle connections
+fairly aggressively.  We mitigate this somewhat by aggressively
+pre-connecting to CloudFlare when we detect activity~\cite{connpool}.
+
+Secondly, even though enproxy operates mostly in full-duplex, reads cannot
+begin until the first request and the response containing the
+sticky-routing header have been processed. There is no mitigation for this.
+
+Thirdly, enproxy does not pipeline http requests.  This means that even
+though reads and writes are full duplex, the flush of one set of writes
+cannot proceed until the previous flush of the previous set of writes has
+been acknowledged with an http response, meaning that a full round-trip is
+necessary between each flush. Implementing HTTP 2.0 would provide request
+pipelining and potentially improve on latency substantially.
+
+Fourthly, enproxy has no way of knowing when the user agent is done
+writing.  If the data were streaming directly from user agent through to
+the proxy, this wouldn't be a problem, but CDNs like CloudFlare buffer
+uploads fairly aggressively, so small uploads aren't actually forwarded to
+the proxy until the HTTP request is finished.  enproxy assumes that a
+writer is finished if it detects inactivity for more than 35 milliseconds,
+at which point it flushes the write by finishing the HTTP request.  This
+introduces at least 35 milliseconds of additional latency, and potentially
+more if we guessed wrong and the write wasn't actually finished, since we
+now have to wait for a full round trip before the next write can proceed.
+This latency is particularly noticeable when proxying TLS traffic, as the
+TLS handshake consists of several small messages sent back and forth
+between user agent and server.
+
+This fourth source of latency can be eliminated if enproxy can know for
+sure when a writer is finished. This could be achieved by changing the
+interface so that rather than implementing net.Conn and proxying generic
+streams of traffic, enproxy could actually proxy HTTP requests directly. It
+would be able to tell when the user agent is finished sending an HTTP
+request and when the destination is finished responding.  However, doing
+the same for HTTPS would require man-in-the-middling the TLS connection in
+order to expose the flow of requests.  Furthermore, this approach only
+works for HTTP clients.  Supporting other sorts of traffic like XMPP would
+require implementing support for those protocols as well.
+
+\subsection{Buffering versus Streaming Requests and Responses}
+HTTP supports both buffered requests/responses (fixed content-length) and
+streaming (chunked encoding). For large downloads and uploads in
+particular, streaming is attractive because it allows writes to stream
+through the proxy and CDN without blocking and as part of a single HTTP
+request/response.  Some CDNs support streaming requests and responses, some
+support only streaming responses, and some support neither streaming
+requests nor responses.  CloudFlare supports streaming in both directions.
+
+enproxy provides pluggable strategies to use either streaming or
+buffering.
+
+\subsection{Managing Proxy Rotations}
+Lantern hosted proxies are fairly stable, but peer proxies tend to come
+online and offline fairly frequently. The CDN (CloudFlare) configuration
+needs to be kept up-to-date based on which proxies are available at any
+given time. We achieve this using the peerscanner~\cite{peerscanner} application, which
+provides a REST API for proxies to register and unregister themselves.
+peerscanner does continual connectivity checking of registered proxies and
+maintains the CloudFlare configuration accordingly. This process is
+unfortunately not foolproof, because there is some latency in the
+connectivity checking and some further latency in the updating of
+CloudFlare's configuration and the propagation of those updates through
+CloudFlare's infrastructure (haven't measured this).  This means that there
+will be periods of time during which an offline proxy is still in rotation,
+which causes an error for any user that's unlucky enough to get routed to
+it.
+
+\subsection{Direct Domain Fronting}
+One of our services is a geolocation server. Rather than proxying traffic to it
+via our enproxy proxies, we actually have it registered on CloudFlare and
+domain-front to it directly.  This reduces latency and saves resources on our
+end.  We've talked about doing direct domain-fronting for popular sites by just
+registering their IPs in CloudFlare under special domains, for example
+\urll{facebook.direct.getiantem.org}.  To do this for anything that's HTTPS would
+require us to man-in-the-middle connections from the user agent.  The biggest
+problem with man-in-the-middling isn't that our client-side Lantern software
+sees the traffic in the clear, it's that the CDN also sees it in the clear.
 

### 2015-02-11 docs/fronting.tex
Fix clients-lantern graphic.
Add Psiphon text.
Unedited except for cites and typographic conventions.

@@
 \centering
-\includegraphics[height=1.5in]{lantern}
+\includegraphics[height=1.5in]{clients-lantern}
 \caption{
@@
 
-Psiphon~\cite{psiphon} is a network of many one-hop proxies,
-with encryption and traffic obfuscation between client and server.
-
-Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
-
 \begin{figure}
@@
 Daily unique users of \meek with
-Psiphon
-The decrease at the end of June
-was caused by an unblocking event that made \meek unnecessary for some users.
+Psiphon.
+We don't have user accounts or track users by e.g., IP address. We do
+count connection events. The unique user number is derived from a
+coarse-grained ``last connected'' timestamp sent by clients: if the last day
+connected is before day being counted, then that connected event is a
+unique user for that day.
 }
@@
 
-how clients choose a technique
-
-unfronted mode
-
-users: Figure~\ref{fig:clients-psiphon3}
+The Psiphon circumvention system~\cite{psiphon} is a centrally managed, geographically
+diverse network of thousands of proxy servers. Psiphon is a
+performance-oriented, ``one hop'' proxy architecture. Much of our server
+infrastructure is hosted with cloud providers. As of January 2015, Psiphon
+has over 2 million daily unique users.
+
+Psiphon deploys clients for popular platforms, including Windows and
+Android. Our clients are designed to tunnel a broad range of host traffic:
+web browsing, video streaming, and mobile app data transfer. Psiphon
+clients are designed for ease of use, and users are not asked to perform
+any manual configuration.
+
+As a circumvention system, Psiphon has faced threats including blocking by
+DPI---both blacklisting and whitelisting---and blocking by network
+end-points. For example, in 2013, Psiphon circumvented DPI which
+whitelisted HTTP by sending a ``HTTP prefix''---the first few bytes of an
+HTTP request---before the start of its regular upstream flow~\cite{information-controls}.
+
+Psiphon takes measures to distribute its server addresses in such a way
+that most clients discover enough servers to have several options in the
+case of a server being blocked, while making it difficult to enumerate all
+servers. In February 2014, Psiphon was specifically targeted for blocking
+by network end-point, and this blocking was sufficiently aggressive to have
+major impact on our user base, though not all users were blocked. As part
+of our response we integrated and deployed fronting with meek. We fully
+deployed this in June 2014. Our implementation is largely based on Tor's
+meek-client and meek-server, with some modifications.
+
+Psiphon employs meek as two distinct protocols: fronted meek, and what we
+call ``unfronted meek''. Fronted meek uses the domain fronting technique.
+
+In unfronted meek, we omit the TLS layer and the protocol on the wire is
+HTTP. As fully compliant HTTP, unfronted meek supersedes our HTTP prefix
+defense against HTTP whitelisting. Unfronted meek is not routed through
+CDNs, and as such is only a DPI whitelist defense and not a defense against
+enumeration of our network end-points. We envision a potential fronted HTTP
+protocol with both properties, which requires cooperating with CDNs to
+route our HTTP requests based on, for example, some obfuscated HTTP header
+element.
+
+\subsection{Implementation}
+
+Psiphon's core protocol is SSH. SSH provides an encryption layer for
+communication between Psiphon clients and servers; the primary purpose of
+this encryption is to frustrate DPI. On top of SSH, we add an obfuscation
+layer~\cite{obfuscated-openssh} that transforms the SSH handshake into a random stream; and
+random padding of packets in the SSH handshake sequence. Psiphon clients
+authenticate servers using SSH public keys obtained through out-of-band
+channels, a process that is bootstrapped with server keys embedded in the
+client binaries.
+
+Our obfuscated SSH is the payload for the meek transport. As such, the meek
+payload appears to be random data and lacks a trivial packet size signature
+in its initial requests and responses.
+
+In Psiphon's modified meek protocol, the session ID cookie contains
+additional payload: a protocol version number, and the destination Psiphon
+server address. As this cookie will be plaintext in unfronted meek, the
+payload is encrypted---with NaCl crypto\_box---using a public key
+associated with the destination meek-server; then obfuscated; then
+formatted as an innocuous-appearing cookie with a randomly selected key
+value. The protocol version number is used by meek-server to determine if
+the meek-client supports several enhancements we have added. The server
+address is the destination SSH server that meek-server forwards traffic to.
+
+We further modified the meek protocol so that the meek-clients only
+transmits its chosen session ID on the first meek HTTP request, after which
+the meek-server assigns a distinct ID to be used on subsequent requests.
+This allows meek-server to distinguish between new and existing sessions
+when a meek-client sends a request after a long delay, such as after an
+Android device awakes from sleeping, where the meek-server may have already
+expired and discarded its session.
+
+Psiphon ported meek-client to Java for our Android client. For Android, we
+make HTTP and HTTPS requests using the Apache HttpClient component, with
+the expectation that this will have characteristics similar to TLS sessions
+for other Android apps making web service requests.
+
+The Psiphon meek-server inspects CDN injected headers to determine user
+client IP address. The address is mapped to a region and the region is used
+to record usage statistics.
+
+\subsection{Server Selection}
+
+When a user starts a Psiphon client, the client initiates connections to up
+to 10 different servers simultaneously, keeping the first fully established
+connection. Candidate servers are chosen at random from cached lists of
+known servers and a mix of different protocols are used. The purpose of the
+simultaneous connections are to minimize user wait time in case certain
+protocols are blocked, certain servers are blocked by address, or certain
+servers are at capacity and rejecting new connections. This process also
+helps us with automatically using the lowest latency server for the user as
+it tends to pick the closest data center, and lowest cost as it tends to
+pick direct connections over fronted due to lower latency.
+
+We made two modifications to server selection to accommodate fronting.
+First, we changed the notion of an established connection from TCP
+connection completion to full SSH handshake completion. This ensures the
+full two hops are measured in the fronted case. Second, we adjusted our
+protocol selection schedule to ensure that, while we generally favor the
+fastest connection, we do not expose our system to an attack that forces us
+to always use a degraded protocol. For example, the adversary could
+implement a DPI attack that allows all connections to establish but then
+terminate or severely throttle non-whitelisted protocols after some short
+time period. If we detect such degraded conditions, we shift protocol
+selection in favor of unfronted and fronted protocols over the faster
+obfuscated SSH direct connections.
+
+\subsection{Performance}
+
+For clients, we identified a need to improve video streaming and download
+performance for traffic tunneled through meek. In addressing this, our
+considerations included a cost-per-HTTP-request for some candidate CDNs,
+lack of support for HTTP pipelining in our components, and a concern about
+the DPI signature of upstream-only or downstream-only HTTP connections. So,
+as a compromise, we made a tweak to the meek protocol: instead of sending
+at most 64K of payload in each HTTP response, response data will be
+streamed back, using chunked encoding, as long as there is data to send and
+for no longer than 200 milliseconds.
+
+This tweak yielded a significant performance improvement, with download
+speeds increasing by 4--5×, and 1080p video playback becoming smooth. Under
+heavy downstream conditions, we observe peak payloads of 1MB, with 300k on
+average, although the exact traffic signature is highly dependent on the
+tunneled application. We tuned the timeout parameter through subjective
+usability testing focusing on latency while web browsing and simultaneously
+downloading large files.
 

### 2015-02-11 docs/clients-psiphon.R
New Psiphon clients data.

@@ -1,14 +1,14 @@
 library(ggplot2)
 library(scales)
-data <- read.csv("psiphon3-fronted-meek-unique-users-all-regions.csv", skip=2, col.names=c("date", "clients"))
+data <- read.csv("clients-psiphon.csv", col.names=c("proto", "date", "clients"))
 data$date <- as.Date(data$date, format="%b %d, %Y")
 
 daterange <- seq(min(data$date), max(data$date), "1 day")
 data <- data.frame(date=daterange, clients=data$clients[match(daterange, data$date)])
-p <- ggplot(data, aes(x=date, y=clients))
+p <- ggplot(data[data$date>=as.Date("2014-12-07"), ], aes(x=date, y=clients))
 p <- p + geom_bar(stat="identity", width=1.1)
 p <- p + xlab(NULL) + ylab("Daily unique users")
 p <- p + scale_x_date(labels=date_format("%b %Y"))
 p <- p + scale_y_continuous(labels=comma)
 p <- p + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
-ggsave("clients-psiphon3.pdf", p, width=4, height=1.4, units="in")
+ggsave("clients-psiphon.pdf", p, width=4, height=1.4, units="in")

### 2015-02-11 docs/bandwidth-lantern.R
Generate bandwidth-lantern graph.

@@ -1,0 +1,14 @@
+library(ggplot2)
+library(scales)
+data <- read.csv("bandwidth-lantern.csv", col.names=c("date", "KBps", "MBps"))
+data$date <- as.Date(data$date, format="%m/%d/%Y")
+
+daterange <- seq(min(data$date), max(data$date), "1 week")
+data <- data.frame(date=daterange, MBps=data$MBps[match(daterange, data$date)])
+p <- ggplot(data, aes(x=date, y=MBps))
+p <- p + geom_bar(stat="identity", width=7.1)
+p <- p + xlab(NULL) + ylab("MB/s")
+p <- p + scale_x_date(labels=date_format("%b %Y"))
+p <- p + scale_y_continuous(labels=comma)
+p <- p + theme(axis.text=element_text(size=7), axis.title=element_text(size=8), axis.title.x=element_blank())
+ggsave("bandwidth-lantern.pdf", p, width=4, height=1.4, units="in")

### 2015-02-13 docs/fronting.tex
New Psiphon clients data.
Generate bandwidth-lantern graph.
Trimming Lantern content

@@
 
-Lantern~\cite{lantern} is a free circumvention tool targeting casual web browsing.
-Lantern does not employ onion routing and in general does not provide the
-same level of anonymity guarantees as Tor.  Lantern primarily focuses on
-performance and availability.
-
-At its core, Lantern is a network of shared HTTPS proxy servers combined
-with a client application that allows censored users to find and use those
-proxy servers to proxy traffic from their existing web browsers.  This same
-client application also allows uncensored users to host such proxy servers
-on their own networks for use by other Lantern users. Lantern ultimately
+Lantern~\cite{lantern} is a free circumvention tool for casual web browsing.
+Lantern does not employ onion routing and focuses more on performance and
+availability rather than anonymity.
+
+Lantern encompases a network of shared HTTPS proxy servers along with a client
+application that allows censored users to find and use those proxy servers to
+proxy traffic for their existing web browsers. The Lantern client also allows
+uncensored users to host proxy servers for use by other Lantern users. Lantern 
 aims to provide a secure mechanism for distributing knowledge about both
 Lantern-hosted and peer-hosted proxy servers using a trust-network based
-distribution mechanism such as kaleidoscope~\cite{kaleidoscope}.  In the meantime, Lantern
-also randomly assigns users to Lantern-hosted proxy servers.
+distribution mechanism such as kaleidoscope~\cite{kaleidoscope}. In the
+meantime, Lantern also randomly assigns users to Lantern-hosted proxy servers.
 
@@
 assigning proxies to them. Lantern's threat model assumes that this
-centralized infrastructure is or can be blocked by the censors.
-Consequently, users must have a priori access to a functioning proxy which
-they can use to bootstrap onto the Lantern network and learn about more
-proxies. Prior to Lantern adopting domain-fronting, we gave users access to
-such proxies (which we call fallbacks) by embedding their information in
-customized software installers that we distributed directly to users.  This
-prevented users from downloading Lantern directly and required them to
-request an email invitation from us with a link to their custom installer.
-Furthermore, since anyone could request an installer, the censors could
-theoretically learn about all of our proxies simply by continually
-requesting installers.
-
-\subsection{Timeline for Deploying Domain-Fronting}
+centralized infrastructure can be blocked by censors. So, users must have a
+priori access to an unblocked proxy which they can use to bootstrap onto the
+Lantern network. We call these "fallbacks".
+
+Lantern originally distributed the IP addresses of fallbacks by embedding them
+in customized software installers that we sent to users via email in response to
+a request from the user. This prevented users from directly downloading Lantern
+from our website and made it easy for censors to discover proxies simply by
+signing up for Lantern (though in practice we never saw this happen).
+
+\subsection{Timeline for Deploying Domain Fronting}
 
@@
 \centering
-\includegraphics[height=1.5in]{clients-lantern}
+\includegraphics[width=\linewidth]{bandwidth-lantern}
 \caption{
-Megabytes per second served by domain-fronted Lantern proxies
+Megabytes per second served by domain fronted Lantern proxies
 (Lantern-hosted and peers).
@@
 
-Lantern rolled out domain-fronting via CloudFlare in July 2014 in order to
-allow users to direct-download Lantern without an email invitation.  In
-this initial implementation, direct-downloaded Lantern clients proxied all
-their traffic using domain-fronting.  It worked, and we experienced steady
-growth in direct downloads and traffic from direct-downloaded clients.
-
-At the beginning of October 2014, we started randomly assigning direct
-HTTPS proxies to users who had direct-downloaded Lantern.  This diverted
-traffic from domain-fronted servers to more efficient direct servers.
+After initially testing with Fastly, Lantern rolled out domain fronting on
+CloudFlare in July 2014, allowing users to direct-download Lantern for the first
+time. These direct-downloaded Lantern clients proxied all their traffic via
+domain fronting. CloudFlare has proven attractive because 1) it has a sufficient
+number of unblocked front domains available in China, 2) it doesn't charge for
+bandwidth and 3) it provides an API for registering and unregistering our
+proxies.
+
+After experiencing steady growth, in October 2014 we started randomly assigning
+direct HTTPS proxies to users who had direct-downloaded Lantern. This diverted
+traffic from domain fronted servers to more efficient direct servers.
 
 In December 2014 and January 2015, Lantern experienced a dramatic surge in
-domain-fronted traffic, jumping from 1 MB/s to 100 MB/s within those two
-months. At first we assumed that direct proxies had been blocked, but it
-turns out that the majority of this new traffic originated in the
-Philippines, which is not a heavily censored country. From what we're
-hearing, it looks like Philippine users are using Lantern to get around
-their ISPs bandwidth caps~\cite{needed}.
-
-\subsection{General Deployment Considerations}
-
-Unlike with meek, Lantern's equivalent of reflectors (which we call
-proxies) are also exit nodes.  So in our infrastructure, we have:
-
-user agent → Lantern client → CDN → Lantern proxy → destination.
-
-Lantern hosts dozens of such proxies on commodity VPS providers like
-Digital Ocean. In addition, uncensored users who run the Lantern client can
-register themselves as domain-fronted proxies as well, so overall there are
-theoretically a very large number of proxies in rotation at any one time.
-
-\subsection{Choice of CDN}
-In our initial implementation, we used Fastly as our CDN.  Fastly ended up
-being unsuitable because their infrastructure isn't meant to support a
-large number of backends, so we transitioned to CloudFlare.  CloudFlare has
-worked well so far because it supports a large number of backends, it has
-an API that we can use to manage those backends and it has cheap flat-rate
-pricing that doesn't charge based on bandwidth consumption. It also has
-a sufficient number of relatively high-profile domains through which we can
-front.
+domain fronted traffic, jumping from 1 MB/s to 100 MB/s within those two
+months, and activity has remained at around the 100 MB/s level since then.
 
 \subsection{Implementation Components}
-Lantern's domain fronting is implemented in Go and made available through
-the flashlight~\cite{flashlight} application.
-The core of flashlight's domain fronting is encapsulated in two libraries,
-enproxy~\cite{enproxy} and fronted~\cite{fronted}.
+Lantern's domain fronting is available via the flashlight~\cite{flashlight}
+application, which uses the enproxy~\cite{enproxy} and fronted~\cite{fronted}
+libraries to implement domain fronting
 
@@
 enproxy proxy. This allows flashlight to proxy any streaming-oriented
-traffic (e.g. TCP).  Unlike meek, enproxy supports full-duplex~\cite{beating-gfw-with-go} operation
-so that reads don't wait on writes, which can be handy for bidirectional
-protocols like XMPP.  Lantern actually uses XMPP as a signaling channel for
-peer-to-peer traffic, and tunnels XMPP via domain-fronted proxies.
-
-fronted uses domain-fronting to transmit enproxy's HTTP requests in a
-blocking-resistant manner. It provides a facility for configuring a number
-of different front domains (masquerade hosts) and includes the ability to
-connect to them directly by IP address rather than DNS. In practice,
-flashlight uses several hundred masquerade hosts when communicating via
-CloudFlare.
+traffic (e.g. TCP). Unlike meek, enproxy supports
+full-duplex~\cite{beating-gfw-with-go} operation, which can be handy for
+bidirectional protocols like XMPP, which Lantern uses for P2P signaling.
+
+fronted uses domain fronting to transmit enproxy's HTTP requests in a
+blocking-resistant manner. In practice, we configure fronted with several
+hundred host domains dialed via IP (no DNS lookup).
 
 \subsection{Sticky Routing}
-Domain-fronted Lantern requests go to one of two host names,
-fallbacks.getiantem.org and peers.getiantem.org.  Fallbacks is a pool of
-servers hosted by Lantern, and peers is the pool of servers constituted by
-online Lantern peers.  When using CloudFlare, a server is selected based by
-round robin.  Just like with meek, Lantern's domain-fronting protocol is
-stateful, so subsequent HTTP requests for the same connection need to find
-their way back to the same proxy that handled the original request.  We
-accomplish this by having the responding proxy return its specific hostname
-in a header which the client then users on subsequent requests, thereby
-bypassing the round robin.
+Domain fronted Lantern requests go to host names that represent pools of servers
+such as fallbacks.getiantem.org. CloudFlare distributes requests to the servers
+in round robin. Just like with meek, Lantern's domain-fronting protocol is
+stateful, so subsequent HTTP requests for the same connection are routed back to
+the original responding proxy using the proxy's specific hostname, which the
+client obtains from a custom HTTP header.
 
@@
 
-Firstly, domain-fronting requires the establishment of additional TCP
-connections. In a best case scenario, the user agent can open a single TCP
-connection directly to the destination server.  With Lantern, the inclusion
-of the client, CloudFlare and the proxy introduce three additional TCP
-connections between the user agent and the destination.  This is mitigated
-somewhat by the fact that CloudFlare pools and reuses connections to the
-Lantern proxy.  Unfortunately, the Lantern client cannot do the same for
-connections to CloudFlare as CloudFlare seems to time out idle connections
-fairly aggressively.  We mitigate this somewhat by aggressively
+Firstly, domain fronting requires the establishment of additional TCP
+connections. At best, the user agent can open a single TCP
+connection directly to the destination server. With Lantern, the client,
+CloudFlare and the proxy introduce three additional TCP connections between the
+user agent and the destination. To reduce latency, CloudFlare pools and reuses
+connections to the Lantern proxy. Unfortunately, the Lantern client cannot do
+the same for connections to CloudFlare because CloudFlare seems to time out
+idle connections fairly aggressively. We mitigate this by aggressively
 pre-connecting to CloudFlare when we detect activity~\cite{connpool}.
@@
 
-Thirdly, enproxy does not pipeline http requests.  This means that even
-though reads and writes are full duplex, the flush of one set of writes
-cannot proceed until the previous flush of the previous set of writes has
-been acknowledged with an http response, meaning that a full round-trip is
-necessary between each flush. Implementing HTTP 2.0 would provide request
-pipelining and potentially improve on latency substantially.
+Thirdly, enproxy does not pipeline http requests. So even though reads and
+writes are full duplex, the flush of one set of writes cannot proceed until the
+flush of the previous set of writes has been acknowledged with an http response,
+meaning that a full round-trip is necessary between each flush. Implementing
+HTTP 2.0 would provide request pipelining and potentially improve on latency
+substantially.
 
@@
 the proxy, this wouldn't be a problem, but CDNs like CloudFlare buffer
-uploads fairly aggressively, so small uploads aren't actually forwarded to
+uploads fairly aggressively and small uploads aren't actually forwarded to
 the proxy until the HTTP request is finished. enproxy assumes that a
@@
 This latency is particularly noticeable when proxying TLS traffic, as the
-TLS handshake consists of several small messages sent back and forth
-between user agent and server.
+TLS handshake consists of several small messages between user agent and server.
 
 This fourth source of latency can be eliminated if enproxy can know for
-sure when a writer is finished. This could be achieved by changing the
-interface so that rather than implementing net.Conn and proxying generic
-streams of traffic, enproxy could actually proxy HTTP requests directly. It
-would be able to tell when the user agent is finished sending an HTTP
-request and when the destination is finished responding.  However, doing
-the same for HTTPS would require man-in-the-middling the TLS connection in
-order to expose the flow of requests.  Furthermore, this approach only
-works for HTTP clients.  Supporting other sorts of traffic like XMPP would
-require implementing support for those protocols as well.
-
-\subsection{Buffering versus Streaming Requests and Responses}
-HTTP supports both buffered requests/responses (fixed content-length) and
-streaming (chunked encoding). For large downloads and uploads in
-particular, streaming is attractive because it allows writes to stream
-through the proxy and CDN without blocking and as part of a single HTTP
-request/response.  Some CDNs support streaming requests and responses, some
-support only streaming responses, and some support neither streaming
-requests nor responses.  CloudFlare supports streaming in both directions.
-
-enproxy provides pluggable strategies to use either streaming or
-buffering.
-
-\subsection{Managing Proxy Rotations}
-Lantern hosted proxies are fairly stable, but peer proxies tend to come
-online and offline fairly frequently. The CDN (CloudFlare) configuration
-needs to be kept up-to-date based on which proxies are available at any
-given time. We achieve this using the peerscanner~\cite{peerscanner} application, which
-provides a REST API for proxies to register and unregister themselves.
-peerscanner does continual connectivity checking of registered proxies and
-maintains the CloudFlare configuration accordingly. This process is
-unfortunately not foolproof, because there is some latency in the
-connectivity checking and some further latency in the updating of
-CloudFlare's configuration and the propagation of those updates through
-CloudFlare's infrastructure (haven't measured this).  This means that there
-will be periods of time during which an offline proxy is still in rotation,
-which causes an error for any user that's unlucky enough to get routed to
-it.
+sure when a writer is finished. This can be achieved by enproxy handle the HTTP
+protocol specifically. This would allow enproxy to know when the user agent is
+finished sending an HTTP request and when the destination is finished
+responding. However, doing the same for HTTPS would require man-in-the-middling
+the TLS connection in order to expose the flow of requests. Furthermore, this
+approach only works for HTTP clients. Supporting other sorts of traffic like
+XMPP would require additional support for those protocols.
 
 \subsection{Direct Domain Fronting}
-One of our services is a geolocation server. Rather than proxying traffic to it
-via our enproxy proxies, we actually have it registered on CloudFlare and
-domain-front to it directly.  This reduces latency and saves resources on our
-end.  We've talked about doing direct domain-fronting for popular sites by just
-registering their IPs in CloudFlare under special domains, for example
-\urll{facebook.direct.getiantem.org}.  To do this for anything that's HTTPS would
-require us to man-in-the-middle connections from the user agent.  The biggest
-problem with man-in-the-middling isn't that our client-side Lantern software
-sees the traffic in the clear, it's that the CDN also sees it in the clear.
+The Lantern network includes a geolocation server. This server is directly
+registered on CloudFlare and the Lantern client domain-fronts directly to the
+geolocation server without using any proxies. This reduces latency and saves
+proxy resources. This sort of direct domain fronting technique can in theory be
+implemented for any HTTP site simply be registering it under a custom domain
+such as \urll{facebook.direct.getiantem.org}. This can even be accomplished for
+HTTPS but requires the Lantern client to man-in-the-middle connections from the
+user agent, exposing the plaintext not only to the Lantern client but also to
+CloudFlare. In practice, any sights that use CloudFlare themselves already
+expose their plaintext to CloudFlare, so this may be an acceptable solution.
 
@@
 \begin{figure}
-\includegraphics[width=\linewidth]{clients-psiphon3}
+\includegraphics[width=\linewidth]{clients-psiphon}
 \caption{
@@
 }
-\label{fig:clients-psiphon3}
+\label{fig:clients-psiphon}
 \end{figure}
@@
 % began their independent deployment of \meek in June~2014.
-% Figure~\ref{fig:clients-psiphon3} shows the number
+% Figure~\ref{fig:clients-psiphon} shows the number
 % of unique daily users of \meek%
@@
 % but rather an unblocking event that made \meek unnecessary for some users.
-% Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
+% Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon}
 % are not directly comparable because they count slightly different things,
